### 2024-08-29 paper/main.tex
feat: Add bachelor thesis proposal and experiment setup

\documentclass{article}

\usepackage{blindtext}
\usepackage[square,numbers]{natbib}
\usepackage[nottoc]{tocbibind}

\title{\textbf{Proposal for bachelor thesis}\\
Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}

\author{Author: Wensheng Zhang}

\date{\today}

\begin{document}

\maketitle

\tableofcontents

\begin{abstract}
The goal of the bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs. 
\end{abstract}

\section{Setup}

In following, I will descripe datasets, models and training framework for the setup of the experiment.

\subsection{Datasets}
The dataset used in the experiment is TUDataset~\cite{morris_tudataset_2020}. Since the size of some datasets are quiet small (under 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data. One of the folds is treated as test dataset and another fold is treated as validation dataset. The rest of the folds are used for training.

\subsection{Models}
I have used GCN layer and GAT layer in the experiment. In the futher experiment, I will consider to use other GNN layers.

\section{Experiment}
The experiment consists in three steps: 1. Train the models from datasets adn valuate the models to calculate the generalization error. 2. calculate the parameters of the graphs from the dataset. 3. Analyze the influence of the graph parameters on the generalization error of the GNNs.

\section{Introduction}
\blindtext

\section{Theoretical Framework}

\blindtext

\section{Objective}

\blindtext

\section{Justification}

\blindtext

\section{Development}

\blindtext

\section{Solution}

\blindtext

\section{Conclusion}

\blindtext

\bibliographystyle{abbrvnat} % or another style like unsrt, alpha, etc.
\bibliography{bibliography}

% All reduce Graphs
\newpage 
    \section{Appendix}

\blindtext

\end{document}

### 2024-08-29 paper/main.tex
feat: Add GAT layers and update experiment results

@@
 \documentclass{article}
+\usepackage[margin=1.5in]{geometry}
 
 \usepackage{blindtext}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+% \usepackage{figure}
+
+\graphicspath{ {./media/} }
 \usepackage[square,numbers]{natbib}
 \usepackage[nottoc]{tocbibind}
+\usepackage{booktabs}
+\usepackage{multirow}
+
+\usepackage{tikz}
+\usepackage{listings}
+\usepackage{setspace}
+\definecolor{Code}{rgb}{0,0,0}
+\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
+\definecolor{Numbers}{rgb}{0.5,0,0}
+\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
+\definecolor{Keywords}{rgb}{0,0,1}
+\definecolor{self}{rgb}{0,0,0}
+\definecolor{Strings}{rgb}{0,0.63,0}
+\definecolor{Comments}{rgb}{0,0.63,1}
+\definecolor{Backquotes}{rgb}{0,0,0}
+\definecolor{Classname}{rgb}{0,0,0}
+\definecolor{FunctionName}{rgb}{0,0,0}
+\definecolor{Operators}{rgb}{0,0,0}
+\definecolor{Background}{rgb}{0.98,0.98,0.98}
+\lstdefinelanguage{Python}{
+	numbers=left,
+	numberstyle=\footnotesize,
+	numbersep=1em,
+	xleftmargin=1em,
+	framextopmargin=2em,
+	framexbottommargin=2em,
+	showspaces=false,
+	showtabs=false,
+	showstringspaces=false,
+	frame=l,
+	tabsize=4,
+	% Basic
+	basicstyle=\ttfamily\small\setstretch{1},
+	backgroundcolor=\color{Background},
+	% Comments
+	commentstyle=\color{Comments}\slshape,
+	% Strings
+	stringstyle=\color{Strings},
+	morecomment=[s][\color{Strings}]{"""}{"""},
+	morecomment=[s][\color{Strings}]{'''}{'''},
+	% keywords
+	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
+	keywordstyle={\color{Keywords}\bfseries},
+	% additional keywords
+	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
+	keywordstyle={[2]\color{Decorators}\slshape},
+	emph={self},
+	emphstyle={\color{self}\slshape},
+	%
+}
 
@@
 \begin{abstract}
-The goal of the bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs. 
+The goal of the bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
 \end{abstract}
@@
 \section{Setup}
+In following, I will descripe training framework, datasets and models for the setup of the experiment.
 
-In following, I will descripe datasets, models and training framework for the setup of the experiment.
+\subsection{Training Framework}
+The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
+PyTorch Geometric is a library for deep learning on graphs and other irregular structures.
+It consists of various methods and utilities to ease the implementation of GNNs.
 
 \subsection{Datasets}
-The dataset used in the experiment is TUDataset~\cite{morris_tudataset_2020}.
+The dataset in the experiment is TUDataset~\cite{morris_tudataset_2020}.
+TUDataset is often used for the GNN evaluation.
+It consists data across different domains, including small molecules, bioinformatics, social networks and synthetic.
 Since the size of some datasets are quiet small (under 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-One of the folds is treated as test dataset and another fold is treated as validation dataset.
+A dataset is splited into 1:1:8, inwhich one of the folds is treated as test dataset and another is treated as validation dataset.
 The rest of the folds are used for training.
@@
 \subsection{Models}
-I have used GCN layer and GAT layer in the experiment. In the futher experiment, I will consider to use other GNN layers.
+I have used GCN layer~\cite{kipf2017semisupervised} and GAT layer~\cite{velickovic2020pointer} in the experiment.
+In the futher experiment, I will consider to use other GNN layers.
+In the Appendix, I will provide the code of the example models.
 
 \section{Experiment}
-The experiment consists in three steps: 1.
-Train the models from datasets adn valuate the models to calculate the generalization error.
+% \includegraphics{experiment_procedure.pdf}
+
+\begin{figure}[h]
+    \includegraphics[width=0.5\textwidth]{experiment_procedure.pdf}
+    \caption{A illutration of experiment Procedure}
+    \label{fig:experiment}
+\end{figure}
+
+The experiment consists in three parts: 1.
+Train the models from datasets and evaluate the models to calculate the generalization error.
 2.
@@
 Analyze the influence of the graph parameters on the generalization error of the GNNs.
+(See Figure~\ref{fig:experiment})
 
-\section{Introduction}
-\blindtext
+Here I take seven datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
 
-\section{Theoretical Framework}
+\begin{table}[]
+    \centering
+    \begin{tabular}{@{}lll@{}}
+    \toprule
+    \multicolumn{1}{c}{\multirow{2}{*}{Dataset}} & \multicolumn{2}{c}{Parameter}                                            \\ \cmidrule(l){2-3} 
+    \multicolumn{1}{c}{}                         & \multicolumn{1}{c}{Ave. degree} & \multicolumn{1}{c}{Ave. shortest path} \\ \midrule
+    FRANKENSTEIN                                 & 2.0627         & 3.6521                     \\
+    NCI1                                         & 2.1550         & 5.4697                     \\
+    COIL-RAG                                     & 1.8277         & 1.0606                     \\
+    Letter-high                                  & 1.8896         & 1.5173                     \\
+    DD                                           & 4.9790         & 7.9700                     \\
+    PTOTEIN\_full                                & 3.7346         & 4.7123                     \\
+    COLORS-3                                     & 2.9288         & 2.0945                     \\ \bottomrule
+    \end{tabular}
+    \caption{The calculated parameters from a set of datasets}
+    \label{tab:parameter}
+\end{table}
 
-\blindtext
-
-\section{Objective}
-
-\blindtext
-
-\section{Justification}
-
-\blindtext
-
-\section{Development}
-
-\blindtext
-
-\section{Solution}
-
-\blindtext
-
-\section{Conclusion}
-
-\blindtext
+\newpage
 
 \bibliographystyle{abbrvnat} % or another style like unsrt, alpha, etc.
-\bibliography{bibliography}
+\bibliography{bibliography} % refers to example.bib
 
@@
 \newpage
+
 \section{Appendix}
 
-\blindtext
+\subsection*{Example of GCN model}
+
+\begin{lstlisting}[language=Python]
+import torch
+from torch import nn
+import torch.nn.functional as F
+from torch_geometric.nn import GCNConv
+from torch_geometric.nn import global_mean_pool
+
+class GCN(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels):
+        super().__init__()
+        self.conv1 = GCNConv(in_channels, hidden_channels)
+        self.conv2 = GCNConv(hidden_channels, hidden_channels)
+        self.conv3 = GCNConv(hidden_channels, hidden_channels)
+        self.conv4 = GCNConv(hidden_channels, hidden_channels)
+        self.conv5 = GCNConv(hidden_channels, hidden_channels)
+        self.fc1 = nn.Linear(hidden_channels, hidden_channels)
+        self.fc2 = nn.Linear(hidden_channels, out_channels)
+
+    def forward(self, x, edge_index, batch, edge_weight=None):
+        x = self.conv1(x, edge_index, edge_weight).relu()
+        x = self.conv2(x, edge_index, edge_weight).relu()
+        x = self.conv3(x, edge_index, edge_weight).relu()
+        x = self.conv4(x, edge_index, edge_weight).relu()
+        x = self.conv5(x, edge_index, edge_weight).relu()
+        x = global_mean_pool(x, batch)
+        x = self.fc1(x).relu()
+        x = F.dropout(x, p=0.5, training=self.training)
+        x = self.fc2(x)
+        return x
+
+    def reset_parameters(self):
+        for (_, module) in self._modules.items():
+            module.reset_parameters()
+
+\end{lstlisting}
 

### 2024-09-02 main.py
update main py

@@ -1,34 +1,87 @@
+from train_procedure import get_generalization_error_from_a_dataset
 import pandas as pd
+import logging
+from tabulate import tabulate
+from utils import get_average_degree, get_average_shortest_path, read_file_to_list
+from tqdm import tqdm
+import logging
 import matplotlib.pyplot as plt
 
-df1 = pd.DataFrame({
-    'Name': ['FRANKENSTEIN', 'NCI1', 'COIL-RAG', 'Letter-high', 'DD', 'PROTEINS_full', 'COLORS-3'],
-    'Ave. generalization error': [-0.0015, 0.0479, -0.0043, 0.0513, 0.1483, -0.0213, 0.0090]
-})
 
-df2 = pd.DataFrame({
-    'Name': ['FRANKENSTEIN', 'NCI1', 'COIL-RAG', 'Letter-high', 'DD', 'PROTEINS_full', 'COLORS-3'],
-    'Ave. degree': [2.0627741588132293, 2.1550138021472596, 1.8277218368573067, 1.8896836075252956, 4.979061666490266, 3.7346421664401634, 2.928853359699249],
-    'Ave. shortest path': [3.6521139346083733, 5.469777618361717, 1.0606131260794474, 1.5173343777117363, 7.970076470113258, 4.712380854361992, 2.0945741756348464]
-})
+def calculate_generalation_error():
+    logger = logging.getLogger(__name__)
+    logging.basicConfig(filename='./results/parameters.log', encoding='utf-8', level=logging.INFO, format='%(message)s', filemode='a')
+    datasets = read_file_to_list('datasets.txt')
+    
+    df = pd.DataFrame({
+        'Name': [],
+        'Ave. generalization error': [],
+        'std': []
+    })
+    
+    for dataset in datasets:
+        generalization_error, std = get_generalization_error_from_a_dataset(dataset)
+        df.loc[len(df)] = [dataset, generalization_error, std]
+    
+    logger.info(tabulate(df, headers='keys', tablefmt='psql'))
+    df.to_csv('generalization_error.csv')
 
-df_combined = pd.merge(df1, df2, on='Name')
+def calcualte_parameters():
+    logger = logging.getLogger(__name__)
+    logging.basicConfig(filename='./results/parameters.log', encoding='utf-8', level=logging.INFO, format='%(message)s', filemode='a')
+    datasets = read_file_to_list('datasets.txt')
 
[…]

### 2024-09-02 net.py
use less layer

@@ -43,7 +43,6 @@ class GAT(torch.nn.Module):
         self.conv2 = GATConv(hidden_channels, hidden_channels)
         self.conv3 = GATConv(hidden_channels, hidden_channels)
         self.conv4 = GATConv(hidden_channels, hidden_channels)
-        self.conv5 = GATConv(hidden_channels, hidden_channels)
         
         self.fc1 = nn.Linear(hidden_channels, hidden_channels)
         self.fc2 = nn.Linear(hidden_channels, out_channels)
@@ -55,7 +54,6 @@ class GAT(torch.nn.Module):
         x = self.conv2(x, edge_index, edge_weight).relu()
         x = self.conv3(x, edge_index, edge_weight).relu()
         x = self.conv4(x, edge_index, edge_weight).relu()
-        x = self.conv5(x, edge_index, edge_weight).relu()
         x = global_mean_pool(x, batch)  # [batch_size, hidden_channels]
         x = self.fc1(x).relu()
         x = F.dropout(x, p=0.5, training=self.training)

### 2024-09-02 train_procedure.py
rename file

@@ -56,7 +56,7 @@ def get_training_result(dataset_name, hidden_channels=64, num_epochs=200, batch_
 
     criterion = torch.nn.CrossEntropyLoss()
     optimizer = torch.optim.Adam(model.parameters(), lr=0.01)
-
+    
     def train(loader):
         model.train()
         loss_all = 0
@@ -127,7 +127,7 @@ def get_training_result(dataset_name, hidden_channels=64, num_epochs=200, batch_
     plot_training_results(dataset_name, netParams, train_accs, val_accs, train_losses, val_losses)
 
 
-def get_generalization_error(dataset_name, hidden_channels=64, num_epochs=200, batch_size=64, split=False):
+def get_generalization_error_from_a_dataset(dataset_name, hidden_channels=64, num_epochs=200, batch_size=64, split=False):
     # Load dataset
     dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
     dataset = dataset.shuffle()
@@ -187,8 +187,9 @@ def get_generalization_error(dataset_name, hidden_channels=64, num_epochs=200, b
     best_train_accuracy_list = []
     for i in range(10):
         model.reset_parameters()
-        print(f'Run {i+1}')
         optimizer = torch.optim.Adam(model.parameters(), lr=0.01)
+        scheduler = torch.optim.lr_scheduler.ReduceLROnPlateau(optimizer, mode='min', factor=0.7, patience=5, min_lr=0.0001)
+        print(f'Run {i+1}')
 
         test_mask = torch.zeros(len(dataset), dtype=torch.bool)
 
@@ -223,17 +224,24 @@ def get_generalization_error(dataset_name, hidden_channels=64, num_epochs=200, b
         best_val_loss, best_test_acc, best_train_acc = float('inf'), 0, 0
 
         start = time.time()
+        patience = 20
         for epoch in range(num_epochs+1):
             train_loss = train(train_loader)
             val_loss = val(val_loader)
             train_acc = test(train_loader)
             val_acc = test(val_loader)
+            scheduler.step(val_loss)
 
             if val_loss < best_val_loss:
                 test_acc = test(test_loader)
                 best_val_loss = val_loss
                 best_test_acc = test_acc
                 best_train_acc = train_acc
+                patience = 20
+            else:
+                patience -= 1
+                if patience == 0:
[…]

### 2024-09-02 utils.py
add read_file_to_list function

@@ -91,3 +91,22 @@ def get_average_shortest_path(dataset_name, show_errors=False):
             
     return sum(avg_shortest_paths) / len(avg_shortest_paths)
 
+def read_file_to_list(file_path):
+    """
+    Reads the content from a text file and converts it to a list.
+
+    Args:
+        file_path (str): Path to the text file.
+
+    Returns:
+        list: List of strings, where each string is a line from the file.
+    """
+    try:
+        with open(file_path, 'r') as file:
+            content = file.readlines()
+            # Remove newline characters from each line
+            content = [line.strip() for line in content]
+            return content
+    except FileNotFoundError:
+        print(f"File not found: {file_path}")
+        return []

### 2024-09-02 paper/main.tex
final proposal version v1

@@
 \documentclass{article}
-\usepackage[margin=1.5in]{geometry}
+\usepackage{geometry}
+\geometry{
+    a4paper,
+    left=30mm,
+    right=30mm,
+    top=20mm,
+    bottom=20mm
+}
 
@@
 \begin{abstract}
-The goal of the bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
+The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
 \end{abstract}
 
-\section{Setup}
+\section{Introduction}
+
+What is graph parameters?
+Graph parameters are the properties of the graph, which can be calculated from the graph.
+For example, the average degree of the graph, the average shortest path of the graph, the average number of coloring in the 1-WL algorithm, etc.
+In the early experiment, the graph parameters are calculated as the average degree and the average shortest path of the graphs.
+\\
+In the another hand, the generalization error is a measure of how well the model generalizes to unseen data.
+In the experiment, the generalization error is calculated as the difference between the training accuracy and the test accuracy.
+\\
+Why is it important to understand the influence of graph parameters on the generalization error of GNNs?
+The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs.
+For example, if we know that the average degree of the graph has a significant influence on the generalization error of GNNs, we can design GNNs that are more robust to the average degree of the graph.
+
+\section{Setup in the early experiment}
 In following, I will descripe training framework, datasets and models for the setup of the experiment.
@@
 \subsection{Models}
-I have used GCN layer~\cite{kipf2017semisupervised} and GAT layer~\cite{velickovic2020pointer} in the experiment.
-In the futher experiment, I will consider to use other GNN layers.
-In the Appendix, I will provide the code of the example models.
+In the early experiment, I have used GCN layer~\cite{kipf2017semisupervised} and GAT layer~\cite{velickovic2020pointer}.
+To prevent overfitting, dropout is used in the model.
+Relu is used as activation function.
+In the Appendix, I have provided the code of example models.
 
@@
 \begin{figure}[h]
+    \centering
     \includegraphics[width=0.5\textwidth]{experiment_procedure.pdf}
@@
 
+\subsection{Experimental details in the early stage}
+I use Adam optimizer with learning rate 0.01.
+The batch size is set to 64.
+The hidden dimension of the GNN layer is set to 64.
+The number of epochs is set to 200.
+To prevent overfitting and to save time, the early stopping is used with patience 20.
+The loss function is set to CrossEntropyLoss.
+
+\section{Results}
+
 Here I take seven datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
 
-\begin{table}[]
+\begin{table}[h!]
     \centering
@@
     \multicolumn{1}{c}{}                         & \multicolumn{1}{c}{Ave. degree} & \multicolumn{1}{c}{Ave. shortest path} \\ \midrule
-    FRANKENSTEIN                                 & 2.0627         & 3.6521                     \\
+    Mutagenicity                                 & 2.0379         & 4.4825                     \\
     NCI1                                         & 2.1550         & 5.4697                     \\
@@
 \end{table}
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{@{}lll@{}}
+    \toprule
+    Dataset        & Ave. generalization error & Standard Deviation   \\ \midrule
+    Mutagenicity   & 0.0268      & 0.02335 \\
+    NCI1           & 0.0138      & 0.02649 \\
+    COIL-RAG       & 0.0450      & 0.01378 \\
+    Letter-high    & 0.0403      & 0.04342 \\
+    DD             & 0.0524      & 0.05849 \\
+    PROTEINS\_full & 0.0189      & 0.05032 \\
+    COLORS-3       & 0.0076      & 0.01428 \\ \bottomrule
+    \end{tabular}
+    \caption{The calculated generalization error from a set of datasets}
+    \label{tab:error}
+\end{table}
+
+Then I plot the generalization error against the graph parameters. The result is shown in Figure~\ref{fig:scatter}.
+
+\begin{figure}[h!]
+    \includegraphics[width=\textwidth]{final_results.png}
+    \caption{The generalization error against the graph parameters}
+    \label{fig:scatter}
+\end{figure}
+
+\section{In the further work}
+In the future, I plan to explore different GNN layers and datasets to evaluate the consistency of the results.
+Additionally, I will consider experimenting with various graph parameters.
+In \cite{gera2018annotated}, the authors have proposed a set of graph parameters that can be used to characterize the graph.
+I will use these parameters in the future work.
 
@@
         self.conv4 = GCNConv(hidden_channels, hidden_channels)
-        self.conv5 = GCNConv(hidden_channels, hidden_channels)
         self.fc1 = nn.Linear(hidden_channels, hidden_channels)
@@
         x = self.conv4(x, edge_index, edge_weight).relu()
-        x = self.conv5(x, edge_index, edge_weight).relu()
         x = global_mean_pool(x, batch)

### 2024-09-02 get_generalization_error.py
tmp

@@ -1,25 +1,0 @@
-from my_gnn import get_generalization_error
-import pandas as pd
-from tqdm import tqdm
-import logging
-from tabulate import tabulate
-
-
-logger = logging.getLogger(__name__)
-logging.basicConfig(filename='./results/parameters.log', encoding='utf-8', level=logging.INFO, format='%(message)s', filemode='a')
-datasets = ["FRANKENSTEIN", "NCI1", "COIL-RAG", "Letter-high", "DD", "PROTEINS_full", "COLORS-3"]
-
-df = pd.DataFrame({
-    'Name': [],
-    'Ave. generalization  error': []
-})
-
-
-for dataset in tqdm(datasets):
-    df.loc[len(df)] = [dataset, get_generalization_error(dataset)]
-
-
-logger.info(tabulate(df, headers='keys', tablefmt='psql'))
-df.to_csv('generalization_error.csv')
-
-    

### 2024-09-09 paper/main.tex
Update main.tex with additional information about graph parameters and generalization error

@@
 \usepackage{multirow}
+
+\usepackage{amssymb}
 
@@
 
-What is graph parameters?
-Graph parameters are the properties of the graph, which can be calculated from the graph.
+Graph learning became a hot topic in the field of machine learning in recent years.
+Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
+GNNs have been shown to be effective in a wide range of tasks, such as node classification, link prediction, and graph classification.
+However, the behavior of GNNs is not well understood.
+In particular, it is not clear how the graph parameters/characteristics influence the generalization error of GNNs.
+The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs.
+\\
+
+What is a graph parameter?
+A Graph parameter is a function $f: \mathbb{G} \Rightarrow \mathbb{R}$, which maps a graph to a real number.
 For example, the average degree of the graph, the average shortest path of the graph, the average number of coloring in the 1-WL algorithm, etc.
 In the early experiment, the graph parameters are calculated as the average degree and the average shortest path of the graphs.
+\\
+
 \\

### 2024-09-11 paper/main.tex
Update main.tex with additional information about graph parameters and generalization error

@@
     right=30mm,
-    top=20mm,
-    bottom=20mm
+    top=30mm,
+    bottom=30mm
 }
 
-\usepackage{blindtext}
+\usepackage{annotate-equations}
 \usepackage{graphicx}
@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 
@@
 
-\tableofcontents
-
 \begin{abstract}
@@
 However, the behavior of GNNs is not well understood.
-In particular, it is not clear how the graph parameters/characteristics influence the generalization error of GNNs.
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs.
+In particular, it is not clear about the relationshit between the graph parameters/characteristics and the generalization error of GNNs.
+The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
+
+Before we untangle this problem, we need to define some terms.
+
+In graph theory, we assume $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}|v,w \in V , v \neq w\}$ is the set of edges.
+$N(v)$ is the neighborhood of a node $v$, defined as $N(v) = \{w | \{v,w\} \in E\}$.
+$d(v)$ is the degree of a node $v$ which refers to the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
+
+What is a graph parameter?  A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}$, which maps a graph to a real number. It characterizes a graph in a certain perspective.
+For example, the average degree of the graph, the average shortest path of the graph, the centrality meature of the graph, the average number of coloring in the 1-WL algorithm, etc.
+I will define concrete definitions in the section \ref{sec:graph_parameters}.
+In my early experiment, the average degree and the average shortest path of the graph were used as graph parameters.
+
+On the another hand, the graph classification task is a task where the goal is to classify a graph into one of several classes.
+In this thesis, the thesis will focus on the graph classification task.
+The generalization error $E_{gen}$ is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
+
+Here, the accuracy $Acc$ is defined as the proportion of correctly classified graphs, that is, 
+$$Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$$
+
+The generalization error is defined as
 \\
 
-What is a graph parameter?
-A Graph parameter is a function $f: \mathbb{G} \Rightarrow \mathbb{R}$, which maps a graph to a real number.
-For example, the average degree of the graph, the average shortest path of the graph, the average number of coloring in the 1-WL algorithm, etc.
-In the early experiment, the graph parameters are calculated as the average degree and the average shortest path of the graphs.
-\\
+\begin{equation*}
+    E_{gen} = \eqnmarkbox[blue]{node1}{Acc_{train}} - \eqnmarkbox[blue]{node2}{Acc_{test}}
+\end{equation*}
+\annotate[yshift=0.5em]{left}{node1}{over train dataset}
+\annotate[yshift=0.5em]{right}{node2}{over test dataset}
 
-\\
-In the another hand, the generalization error is a measure of how well the model generalizes to unseen data.
-In the experiment, the generalization error is calculated as the difference between the training accuracy and the test accuracy.
-\\
 Why is it important to understand the influence of graph parameters on the generalization error of GNNs?
-The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs.
-For example, if we know that the average degree of the graph has a significant influence on the generalization error of GNNs, we can design GNNs that are more robust to the average degree of the graph.
-
+The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs so that researchers can can tune GNNs to improve their predictive performance on new graphs.
 \section{Setup in the early experiment}
-In following, I will descripe training framework, datasets and models for the setup of the experiment.
+In following, I will descripe training framework, datasets, models and concrete graph parameters for the setup of the experiment.
 
@@
 \subsection{Datasets}
-The dataset in the experiment is TUDataset~\cite{morris_tudataset_2020}.
+The dataset used for the classification is TUDataset~\cite{morris_tudataset_2020}.
 TUDataset is often used for the GNN evaluation.
-It consists data across different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets are quiet small (under 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-A dataset is splited into 1:1:8, inwhich one of the folds is treated as test dataset and another is treated as validation dataset.
-The rest of the folds are used for training.
+It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
+Since the size of some datasets is quiet small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
+A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
+The remaining folds are used for training.
+
+In the early experiment, I took 10 datasets from different domains as examples.
+The datasets are Mutagenicity, NCI1, COIL-RAG, Letter-high, DD, PROTEIN\_full, COLORS-3, AIDS, ENZYMES, Cuneiform.
+In the future, I will explore more datasets in the experiment.
 
 \subsection{Models}
-In the early experiment, I have used GCN layer~\cite{kipf2017semisupervised} and GAT layer~\cite{velickovic2020pointer}.
-To prevent overfitting, dropout is used in the model.
-Relu is used as activation function.
+In the early experiment, I have used Graph Convolutional Networks(GCN) layer~\cite{kipf2017semisupervised} and Graph Attention Networks(GAT) layer~\cite{velickovic2020pointer} to construct models.
+In order to overfitting, dropout is used in the model and Relu function is used as activation function.
 In the Appendix, I have provided the code of example models.
+In the future, I will explore more GNN layers in the experiment, including Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, GATv2~\cite{brody2021attentive} and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural} etc.
+
+\subsection{Graph Parameters Unter Investigation} \label{sec:graph_parameters}
+As graph parameters defined abstractly above, I give here the concrete definition of the graph parameters in the experiment.\\
+\begin{description}
+    \item [Average degree] The average degree of the graph $d_{avg}$ is defined as the average of the degrees of all nodes in the graph, that is
+    $$ d_{avg} = \frac{1}{|V|} \sum_{v \in V} d(v)$$
+    \item [Average shortest path length] The average shortest path length of the graph $a$ is defined as the average of the shortest paths between all pairs of nodes in the graph.
+The shortest path $d(s, t)$ between two nodes $v$ and $w$ is the minimum number of edges that need to be traversed to go from $v$ to $w$.
+The formal definition is
+    $$
+a = \frac{1}{|V|(|V|-1)} \sum_{v \in V} \sum_{w \in V, w \neq v} d(v, w)
+    $$
+    \item [Centrality measure of graphs] At first we have the definition of centrality measure in the \textbf{node level}.
+The centrality measure of a node is a measure of the importance of the node in the graph.
+There are many centrality measures, such as degree centrality, closeness centrality, betweenness centrality, and eigenvector centrality.
+
+    \textit{Degree centrality} is identical to the average degree of the graph defined above.
+
+    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of shortest paths from the node $v$ to all other nodes in the graph, that is 
+    $$C_C(v) = \frac{1}{\sum_{w\in V}{d(v ,w)}}$$
+    where $d(v, w)$ is the shortest path between node $v$ and node $w$.
+
+    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of all-pairs shortest paths that pass through $v$. The definition can be given by the expression:
+    $$
+        C_B(v) = \sum_{s,t \in V} \frac{\sigma_{st}(v)}{\sigma_{st}}
+    $$
+    where $\sigma_{st}$ is the number of shortest paths between nodes $s$ and $t$, and $\sigma_{st}(v)$ is the number of shortest paths between nodes $s$ and $t$ that pass through node $v$.
+
+    \textit{Eigenvector centrality} Eigenvector centrality is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
+Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$ -th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
+Mathematically, it can be expressed as:
+
+    \[ C_E(v) = \frac{1}{\lambda} \sum_{u \in N(v)} a_{vu} C_E(u) \]
+
+    where $ \lambda$ is the largest eigenvalue of the adjacency matrix $A$.
+$a_{vu}$ is the element of the adjacency matrix $A$ corresponding to the edge between nodes $v$  and $u$.
+$ C_E(u)$  is the eigenvector centrality of node $u$.
+
+    Finally in the \textbf{graph level}, the centrality measure of the graph is defined as the average of the centrality measures over all nodes in the graph.
+    \item [Average number of coloring in the 1-WL algorithm] The 1-dimensional Weisfeiler-Leman algorithm (1-WL) is a algorithm that assigns a unique label(color) to each node in the graph.
+The average number of coloring in the 1-WL algorithm is defined as the average number of colors used to color the nodes in the graph.
+The 1-WL algorithm is a powerful graph isomorphism algorithm that can be used to determine if two graphs are isomorphic.
+I give the procedure of the 1-WL algorithm here:
+    \begin{enumerate}
+        \item Assign the same color to all nodes in the graph.
+        \item Two nodes $v$, $u$ are assigned a different color if there is a color c such that the number of c-colored neighbors of $u$ is not equal to the number of c-colored neighbors of $v$.
+        \item Repeat step 2 until the colors of all nodes do not change.
+    \end{enumerate}
+
+\end{description}
+
+Besides the graph parameters defined above, I will explore more graph parameters in the experiment if possible.
 
@@
 \subsection{Experimental details in the early stage}
-I use Adam optimizer with learning rate 0.01.
+Initially, I use Adam optimizer with learning rate 0.01.
 The batch size is set to 64.
@@
 
-\section{Results}
+In the future, I will explore different hyperparameters, such as learning rate, batch size, size of hidden dimension, and patience in the early stopping.
 
-Here I take seven datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
+% \clearpage
+
+\section{Results of early experiment} \label{sec:results}
+
+Here I take ten datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
 
@@
     PTOTEIN\_full                                & 3.7346         & 4.7123                     \\
-    COLORS-3                                     & 2.9288         & 2.0945                     \\ \bottomrule
+    COLORS-3                                     & 2.9288         & 2.0945                     \\
+
+    AIDS  &  2.01286  & 3.2864 \\
+    ENZYMES  &  3.8626  & 4.4461 \\
+    Cuneiform  &  4.0795  & 2.24442 \\ \bottomrule
+
     \end{tabular}
-    \caption{The calculated parameters from a set of datasets}
+    \caption{The calculated parameters from a set of datasets, here used two parameters, the average degree of the graph and the average shortest path of the graph which defined in the section \ref{sec:graph_parameters}.}
     \label{tab:parameter}
@@
     PROTEINS\_full & 0.0189      & 0.05032 \\
-    COLORS-3       & 0.0076      & 0.01428 \\ \bottomrule
+    COLORS-3       & 0.0076      & 0.01428 \\
+    AIDS           &  0.00931    & 0.008642 \\
+    ENZYMES           &  0.0345    & 0.052339 \\
+    Cuneiform           &  0.2392    & 0.09868 \\ \bottomrule
     \end{tabular}
-    \caption{The calculated generalization error from a set of datasets}
+    \caption{The table shows the calculated generalization error from a set of datasets, where the generalization error is calculated as the difference between the training accuracy and the test accuracy.}
     \label{tab:error}
@@
 
-Then I plot the generalization error against the graph parameters. The result is shown in Figure~\ref{fig:scatter}.
+I then used a scatter plot to visualize the generalization error against the two graph parameters.
+The result is shown in Figure~\ref{fig:scatter}.
+Also I calculated the correlation between the generalization error and the graph parameters.
+The result is shown in Table~\ref{tab:correlation}.
 
@@
     \includegraphics[width=\textwidth]{final_results.png}
-    \caption{The generalization error against the graph parameters}
+    \caption{The generalization error against the graph parameters, the x-axis is the average degree of the graph, the y-axis is the generalization error of the model.
+The each point in the plot is the calculated result from different datasets.
+It is obvious that more datasets are needed to get more reliable results.}
     \label{fig:scatter}
@@
 
-\section{In the further work}
-In the future, I plan to explore different GNN layers and datasets to evaluate the consistency of the results.
-Additionally, I will consider experimenting with various graph parameters.
-In \cite{gera2018annotated}, the authors have proposed a set of graph parameters that can be used to characterize the graph.
-I will use these parameters in the future work.
+\begin{table}[h]
+    \centering
+    \begin{tabular}{@{}ll@{}}
+    \toprule
+                       & Ave. Generalization Error \\ \midrule
+    Ave degree            & 0.4068                    \\
+    Ave. shortest path & -0.2074                   \\ \bottomrule
+    \end{tabular}
+    \caption{The correlation between the generalization error and the graph parameters. The correlation is calculated by the Pearson correlation coefficient.}
+    \label{tab:correlation}
+    \end{table}
 
@@
 
-\bibliographystyle{abbrvnat} % or another style like unsrt, alpha, etc.
-\bibliography{bibliography} % refers to example.bib
+\section{Objective of the thesis}
+
+The Objective of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs.
+Beside the content of early experiment, I will explore more GNN layers in the experiment, such as Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, GATv2~\cite{brody2021attentive} and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural} etc.
+I will explore all the graph parameter I mensioned in \ref{sec:graph_parameters} and more if possibly.
+
+I will also explore different hyperparameters, such as learning rate, batch size, hidden dimension, number of epochs, and patience in the early stopping to find the best setting for the models/datasets.
+
+In the section~\ref{sec:results}, I have made the experiment on 10 datasets. In the future, I will make the experiment on more datasets to get more reliable results.
+
+\clearpage
+
+\tableofcontents
+
+\newpage
+
+\bibliographystyle{abbrvnat}
+\bibliography{main} % refers to example.bib
 

### 2024-09-11 imdb-binary.py
Add script for training GCN on IMDB-BINARY dataset

@@ -1,0 +1,126 @@
+import torch.nn.functional as F
+from torch_geometric.datasets import TUDataset
+from torch_geometric.utils import degree
+import torch_geometric.transforms as T
+
+import torch
+from torch_geometric.datasets import TUDataset
+from torch_geometric.loader import DataLoader
+from utils import timeSince, plot_training_results, NetParams
+from net import GCN
+import time
+
+
+dataset_name = 'IMDB-BINARY'
+num_epochs = 200
+hidden_channels = 64
+batch_size = 64
+
+class PreTransform(object):
+    def __call__(self, data):
+        data.x = degree(data.edge_index[0], data.num_nodes, dtype=torch.long)
+        data.x = F.one_hot(data.x, num_classes=136).to(torch.float) # 136 is the maximum number in the dataset
+        return data
+
+dataset = TUDataset(
+    root='data/TUDataset', 
+    name=dataset_name, 
+    pre_transform=PreTransform(),
+    force_reload = True
+)
+
+dataset = dataset.shuffle()
+centered_line = f'Dataset: {dataset}'.center(93)
+print('=' * 93 + f'\n{centered_line}\n' + '=' * 93 + '\n')
+
+train_dataset_size = int(len(dataset) * 0.8)
+train_dataset = dataset[:train_dataset_size]
+val_dataset = dataset[train_dataset_size:]
+
+dataset_num_features = dataset.num_features
+dataset_num_classes = dataset.num_classes
+
+
+train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
+val_loader = DataLoader(val_dataset, batch_size=batch_size, shuffle=False)
+
+# Define model
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+print(f'Device: {device}')
+model = GCN(
+    in_channels=dataset.num_features,
+    hidden_channels=hidden_channels,
+    out_channels=dataset.num_classes,
+).to(device)
+
+criterion = torch.nn.CrossEntropyLoss()
+optimizer = torch.optim.Adam(model.parameters(), lr=0.01)
+
+def train(loader):
+    model.train()
+    loss_all = 0
+    for data in loader:
+        data = data.to(device)
+        optimizer.zero_grad()
+        out = model(data.x, data.edge_index, data.batch)
+        loss = criterion(out, data.y.long())
+        loss.backward()
+        loss_all += loss.item() * data.num_graphs
[…]

### 2024-09-11 main.py
Refactor file paths and add correlation calculation

@@ -7,11 +7,12 @@ from tqdm import tqdm
 import logging
 import matplotlib.pyplot as plt
 
+DATAPATH = 'datasets2.txt'
 
 def calculate_generalation_error():
     logger = logging.getLogger(__name__)
     logging.basicConfig(filename='./results/parameters.log', encoding='utf-8', level=logging.INFO, format='%(message)s', filemode='a')
-    datasets = read_file_to_list('datasets.txt')
+    datasets = read_file_to_list(DATAPATH)
     
     df = pd.DataFrame({
         'Name': [],
@@ -24,12 +25,12 @@ def calculate_generalation_error():
         df.loc[len(df)] = [dataset, generalization_error, std]
     
     logger.info(tabulate(df, headers='keys', tablefmt='psql'))
-    df.to_csv('generalization_error.csv')
+    df.to_csv(f'generalization_error_{DATAPATH}.csv')
 
 def calcualte_parameters():
     logger = logging.getLogger(__name__)
     logging.basicConfig(filename='./results/parameters.log', encoding='utf-8', level=logging.INFO, format='%(message)s', filemode='a')
-    datasets = read_file_to_list('datasets.txt')
+    datasets = read_file_to_list(DATAPATH)
 
     df = pd.DataFrame({
         'Name': [],
@@ -41,7 +42,7 @@ def calcualte_parameters():
         df.loc[len(df)] = [dataset, get_average_degree(dataset), get_average_shortest_path(dataset)]
 
     logger.info(tabulate(df, headers='keys', tablefmt='psql'))
-    df.to_csv('parameters.csv')
+    df.to_csv(f'parameters_{DATAPATH}.csv')
 
 
 def compare_generalization_error_and_parameters():
@@ -55,14 +56,14 @@ def compare_generalization_error_and_parameters():
     plt.figure(figsize=(10, 5))
 
     plt.subplot(1, 2, 1)
-    plt.plot(df_sorted_by_degree['Ave. degree'], df_sorted_by_degree['Ave. generalization error'], marker='o', color='b')
+    plt.scatter(df_sorted_by_degree['Ave. degree'], df_sorted_by_degree['Ave. generalization error'], marker='o', color='b')
     plt.title('Ave. Degree vs. Ave. Generalization Error')
     plt.xlabel('Ave. Degree')
     plt.ylabel('Ave. Generalization Error')
 
     df_sorted_by_shortest_path = df_combined.sort_values('Ave. shortest path')
     plt.subplot(1, 2, 2)
[…]

### 2024-09-11 train_procedure.py
Refactor file paths and add correlation calculation

@@ -126,7 +126,6 @@ def get_training_result(dataset_name, hidden_channels=64, num_epochs=200, batch_
     netParams = NetParams(hidden_channels, num_epochs, batch_size)
     plot_training_results(dataset_name, netParams, train_accs, val_accs, train_losses, val_losses)
 
-
 def get_generalization_error_from_a_dataset(dataset_name, hidden_channels=64, num_epochs=200, batch_size=64, split=False):
     # Load dataset
     dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
@@ -137,13 +136,11 @@ def get_generalization_error_from_a_dataset(dataset_name, hidden_channels=64, nu
 
     # Define model
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-    # print(device)
     model = GCN(
         in_channels=dataset.num_features,
         hidden_channels=hidden_channels,
         out_channels=dataset.num_classes,
     ).to(device)
-    # print(f'Model structure: {model}\n\n')
 
     criterion = torch.nn.CrossEntropyLoss()
 
@@ -270,11 +267,13 @@ def get_generalization_error_from_a_dataset(dataset_name, hidden_channels=64, nu
 
 if __name__ == '__main__':
 
-    HIDDEN_CHANNELS = 64
-    MAX_NUM_EPOCHS = 200
-    BATCH_SIZE = 64
-    # DATASET_NAME = 'DD'
-    DATASET_NAME = 'Mutagenicity'
+    # HIDDEN_CHANNELS = 64
+    # MAX_NUM_EPOCHS = 200
+    # BATCH_SIZE = 64
+    # # DATASET_NAME = 'DD'
+    # DATASET_NAME = 'Mutagenicity'
     
-    print(DATASET_NAME)
-    print(get_generalization_error_from_a_dataset(DATASET_NAME))
+    # print(DATASET_NAME)
+    # print(get_generalization_error_from_a_dataset(DATASET_NAME))
+
+    get_training_result('IMDB-BINARY')

### 2024-09-27 paper/main.tex
edit tex file and update bibliography

@@
 Graph learning became a hot topic in the field of machine learning in recent years.
-Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
+Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
 GNNs have been shown to be effective in a wide range of tasks, such as node classification, link prediction, and graph classification.
 However, the behavior of GNNs is not well understood.
-In particular, it is not clear about the relationshit between the graph parameters/characteristics and the generalization error of GNNs.
+In particular, it is not clear about the relationship between the graph parameters/characteristics and the generalization error of GNNs.
 The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
 
-Before we untangle this problem, we need to define some terms.
+Before we untangle this problem, we need to define some terms with regard to the graph.
+In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
+The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$.
+The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
 
-In graph theory, we assume $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}|v,w \in V , v \neq w\}$ is the set of edges.
-$N(v)$ is the neighborhood of a node $v$, defined as $N(v) = \{w | \{v,w\} \in E\}$.
-$d(v)$ is the degree of a node $v$ which refers to the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
-
-What is a graph parameter?  A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}$, which maps a graph to a real number. It characterizes a graph in a certain perspective.
-For example, the average degree of the graph, the average shortest path of the graph, the centrality meature of the graph, the average number of coloring in the 1-WL algorithm, etc.
+With these foundational terms in place, we can now introduce the concept of a graph parameter, which allows us to quantify certain properties of a graph.
+A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a set of real numbers.
+It characterizes a graph in a certain perspective.
+Examples of such parameters include the average degree of the graph, the average shortest path of the graph, the centrality measure of the graph, the average number of colourings in the 1-WL algorithm, and so forth.
 I will define concrete definitions in the section \ref{sec:graph_parameters}.
@@
 On the another hand, the graph classification task is a task where the goal is to classify a graph into one of several classes.
-In this thesis, the thesis will focus on the graph classification task.
-The generalization error $E_{gen}$ is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
+The present thesis will focus on the graph classification task.
+The empirical generalization error $E_{gen}$ is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
 
@@
 
-The generalization error is defined as
+The empirical generalization error is defined as
 \\
@@
 \subsection{Datasets}
-The dataset used for the classification is TUDataset~\cite{morris_tudataset_2020}.
+The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
 TUDataset is often used for the GNN evaluation.
@@
 \subsection{Models}
-In the early experiment, I have used Graph Convolutional Networks(GCN) layer~\cite{kipf2017semisupervised} and Graph Attention Networks(GAT) layer~\cite{velickovic2020pointer} to construct models.
+In the early experiment, I have used Graph Convolutional Networks(GCN) layer~\cite{kipf2016semi} and Graph Attention Networks(GAT) layer~\cite{velickovic2020pointer} to construct models.
 In order to overfitting, dropout is used in the model and Relu function is used as activation function.
@@
 
-\subsection{Graph Parameters Unter Investigation} \label{sec:graph_parameters}
+\subsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
 As graph parameters defined abstractly above, I give here the concrete definition of the graph parameters in the experiment.\\

### 2024-09-27 utils.py
Add IMDB dataset transformation

@@ -110,3 +110,43 @@ def read_file_to_list(file_path):
     except FileNotFoundError:
         print(f"File not found: {file_path}")
         return []
+
+class IMDBPreTransform(object):
+    def __call__(self, data):
+        data.x = degree(data.edge_index[0], data.num_nodes, dtype=torch.long)
+        data.x = F.one_hot(data.x, num_classes=136).to(torch.float)
+        return data
+
+def load_dataset(dataset_name: str):
+    if dataset_name is 'IMDB-BINARY':
+        return TUDataset('data/TUDataset', name='IMDB-BINARY', pre_transform=IMDBPreTransform(), forch_reload=True)
+    else:
+        return TUDataset('data/TUDataset', name=dataset_name, use_node_attr=True)
+
+def get_dataloader(dataset, fold: int, batch_size=64, is_10_fold_validation_enabled=True):
+    """
+    split the dataset into 10 fold, take one into dataloader and return that dataloader. If 10 fold validation is not enabled, return put all data into dataloader
+    """
+    
+    if is_10_fold_validation_enabled is False:
+        return DataLoader(dataset, batch_size=batch_size, shuffle=True)
+
+
+    n = len(dataset) // 10
+    test_mask[fold*n:(fold+1)*n] = 1
+    val_mask = torch.zeros(len(dataset), dtype=torch.bool)
+
+    if fold == 9:
+        val_mask[0:n] = 1
+    else:
+        val_mask[(fold+1)*n:(fold+2)*n] = 1
+
+    train_dataset = dataset[~test_mask & ~val_mask]
+    val_dataset = dataset[val_mask]
+    test_dataset = dataset[test_mask]
+
+    train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
+    val_loader = DataLoader(val_dataset, batch_size=batch_size, shuffle=False)
+    test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=False)
+
+    return train_loader, val_loader, test_loader

### 2024-09-29 paper/main.tex
Refactor bibliography and update dataset references

@@
 \usepackage{multirow}
+\usepackage{enumitem}
+\usepackage{float}
 
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 
@@
 Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
-GNNs have been shown to be effective in a wide range of tasks, such as node classification, link prediction, and graph classification.
+GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
+The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
+This information is then used to make predictions.
+GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}.
+Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.
+
 However, the behavior of GNNs is not well understood.
-In particular, it is not clear about the relationship between the graph parameters/characteristics and the generalization error of GNNs.
+In particular, it is not clear about the relationship between the graph parameters/characteristics and the empirical generalization error of GNNs.
 The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
@@
 The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
+In addition to the nodes and edges that comprise the graph, we attach a more complex set of data to each node.
+A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included.
+These vectors can be used to characterize graphs or nodes in graphs.
+The adjacency matrix $A \in \mathbb{R}^{n \times n}$ is a matrix that represents the connections between nodes in the graph.
+The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.
 
-With these foundational terms in place, we can now introduce the concept of a graph parameter, which allows us to quantify certain properties of a graph.
+With these foundational terms in place, we can now introduce the concept of a graph parameter.
 A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a set of real numbers.
-It characterizes a graph in a certain perspective.
-Examples of such parameters include the average degree of the graph, the average shortest path of the graph, the centrality measure of the graph, the average number of colourings in the 1-WL algorithm, and so forth.
+Furthermore, such functions need to be permutation invariant, i.e.
+$f(G) = f(G')$ if $G$ and $G'$ are isomorphic graphs.
+A graph parameter characterizes a graph from a certain perspective and allows us to quantify certain properties of a graph.
+Examples of such parameters include the average degree of the graph, the average shortest path of the graph, the centrality measure of the graph, the average number of coloring in the 1-WL algorithm, and so forth.
 I will define concrete definitions in the section \ref{sec:graph_parameters}.
-In my early experiment, the average degree and the average shortest path of the graph were used as graph parameters.
 
-On the another hand, the graph classification task is a task where the goal is to classify a graph into one of several classes.
-The present thesis will focus on the graph classification task.
-The empirical generalization error $E_{gen}$ is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
+On the another hand, the graph classification task aims to classify a graph into one of several classes.
+This thesis will specifically focus on addressing this task.
+A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
+This is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
+It is defined as
 
-Here, the accuracy $Acc$ is defined as the proportion of correctly classified graphs, that is, 
-$$Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$$
+$$
+    E_{gen} = {Acc_{train}} - {Acc_{test}}
+$$
+where $Acc_{train}$ is the accuracy of the model on the training dataset, and $Acc_{test}$ is the accuracy of the model on the test dataset.
+The accuracy $Acc$ on a dataset is defined as the proportion of correctly classified graphs, that is, $Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$.
 
-The empirical generalization error is defined as
-\\
+The empirical generalization error is also known as the generalization gap~\cite{goodfellow2016deep}.
+Typically, the learning on the training dataset and test dataset behaves differently.
+The model may perform well on the training dataset but poorly on the test dataset.
+By observing the generalization error, we can decide on a stopping criterion for the training process.
+And the generalization error can be used to determine whether the model is overfitting or underfitting.
+Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the dataset.
+In this thesis, I will investigate how the graph parameters influence the generalization error of GNNs.
+The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs so that researchers can tune GNNs to improve their predictive performance on new graphs.
 
-\begin{equation*}
-    E_{gen} = \eqnmarkbox[blue]{node1}{Acc_{train}} - \eqnmarkbox[blue]{node2}{Acc_{test}}
-\end{equation*}
-\annotate[yshift=0.5em]{left}{node1}{over train dataset}
-\annotate[yshift=0.5em]{right}{node2}{over test dataset}
-
-Why is it important to understand the influence of graph parameters on the generalization error of GNNs?
-The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs so that researchers can can tune GNNs to improve their predictive performance on new graphs.
-\section{Setup in the early experiment}
-In following, I will descripe training framework, datasets, models and concrete graph parameters for the setup of the experiment.
+\section{Experimental Setup}
+The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.
 
@@
 It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quiet small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
+Since the size of some datasets is quite small (less than 500 data points/graphs), I will use 10-fold cross validation in the training process, in order to fully utilize the data.
 A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
 The remaining folds are used for training.
-
-In the early experiment, I took 10 datasets from different domains as examples.
-The datasets are Mutagenicity, NCI1, COIL-RAG, Letter-high, DD, PROTEIN\_full, COLORS-3, AIDS, ENZYMES, Cuneiform.
-In the future, I will explore more datasets in the experiment.
+The training is repeated 10 times, each time with a different test fold.
+The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
 
 \subsection{Models}
-In the early experiment, I have used Graph Convolutional Networks(GCN) layer~\cite{kipf2016semi} and Graph Attention Networks(GAT) layer~\cite{velickovic2020pointer} to construct models.
-In order to overfitting, dropout is used in the model and Relu function is used as activation function.
-In the Appendix, I have provided the code of example models.
-In the future, I will explore more GNN layers in the experiment, including Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, GATv2~\cite{brody2021attentive} and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural} etc.
+In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
+The GCN model is shown in the appendix.
+The GCN model consists of four GCN layers, each followed by a ReLU activation function.
+The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.
+
+\subsection{Experimental details}
+The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
+To prevent overfitting and to optimize the use of time, the early stopping is employed.
+The loss function is defined as the cross-entropy loss function.
+The hyperparameters of the model are considered to be tuned.
+The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping.
+The generalization error is calculated as the difference between the training accuracy and the test accuracy.
 
 \subsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
-As graph parameters defined abstractly above, I give here the concrete definition of the graph parameters in the experiment.\\
+As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.
+
 \begin{description}
@@
     $$
+
+    \item [Graph diameter] The graph diameter $d$ is the maximum of the shortest paths between all pairs of nodes in the graph, that is,
+    $$
+d = \max_{v \in V} \max_{w \in V, w \neq v} d(v, w)
+    $$
+
+    \item [Graph density] The graph density $p$ is the ratio of the number of edges in the graph to the number of the maximum possible edges in the graph, that is,
+    $$
+p = \frac{2|E|}{|V|(|V|-1)}
+    $$
+
+    \item [Graph clustering coefficient] The graph clustering coefficient $C$ is a measure of the degree to which nodes in a graph tend to cluster together.
+The clustering coefficient of a node $v$ (as known as the local clustering coefficient) is defined as the fraction of the number of triangles that include node $v$ to the maximum possible number of triples centered on node $v$.
+The clustering coefficient of the graph (as known as the global clustering coefficient) is defined as the average of the clustering coefficients of all nodes in the graph.
+The formal definition is
+    $$
+C = \frac{1}{|V|} \sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}
+    $$
+    where the term $|\{(i,j)\in E \mid i, j \in N(v)\}|$ is the number of edges between the neighbors of node $v$, i.e.
+the number of triangles containing node $v$.
+Furthermore, the term $\sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}$ is the sum of the local clustering coefficients of all nodes in the graph, in which the degree of node $v$ is denoted as $d(v)$.
+
     \item [Centrality measure of graphs] At first we have the definition of centrality measure in the \textbf{node level}.
@@
 
-    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of shortest paths from the node $v$ to all other nodes in the graph, that is 
+    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of the shortest paths from the node $v$ to all other nodes in the graph, that is 
     $$C_C(v) = \frac{1}{\sum_{w\in V}{d(v ,w)}}$$
@@
 
-    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of all-pairs shortest paths that pass through $v$. The definition can be given by the expression:
+    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of the shortest paths between all pairs of nodes that pass through node $v$, that is
+
     $$
@@
     $$
-    where $\sigma_{st}$ is the number of shortest paths between nodes $s$ and $t$, and $\sigma_{st}(v)$ is the number of shortest paths between nodes $s$ and $t$ that pass through node $v$.
+    where $\sigma_{st}$ is the number of the shortest paths between nodes $s$ and $t$, and $\sigma_{st}(v)$ is the number of the shortest paths between nodes $s$ and $t$ that pass through node $v$.
 
-    \textit{Eigenvector centrality} Eigenvector centrality is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
-Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$ -th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
+    \textit{Eigenvector centrality} is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
+Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$-th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
 Mathematically, it can be expressed as:
@@
 
-    Finally in the \textbf{graph level}, the centrality measure of the graph is defined as the average of the centrality measures over all nodes in the graph.
-    \item [Average number of coloring in the 1-WL algorithm] The 1-dimensional Weisfeiler-Leman algorithm (1-WL) is a algorithm that assigns a unique label(color) to each node in the graph.
+    Finally, in the \textbf{graph level}, the centrality measure of the graph is defined as the average of the centrality measures over all nodes in the graph.
+
+    \item [Average number of coloring in the 1-WL algorithm] 
+    \sloppy
+    The 1-dimensional Weisfeiler-Leman algorithm (1-WL)~\cite{weisfeiler1968reduction} is an algorithm that assigns a unique label(color) to each node in the graph, also known as color refinement.
 The average number of coloring in the 1-WL algorithm is defined as the average number of colors used to color the nodes in the graph.
@@
 
-Besides the graph parameters defined above, I will explore more graph parameters in the experiment if possible.
-
-\section{Experiment}
-% \includegraphics{experiment_procedure.pdf}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{experiment_procedure.pdf}
-    \caption{A illutration of experiment Procedure}
-    \label{fig:experiment}
-\end{figure}
-
-The experiment consists in three parts: 1.
-Train the models from datasets and evaluate the models to calculate the generalization error.
-2.
-calculate the parameters of the graphs from the dataset.
-3.
-Analyze the influence of the graph parameters on the generalization error of the GNNs.
-(See Figure~\ref{fig:experiment})
-
-\subsection{Experimental details in the early stage}
-Initially, I use Adam optimizer with learning rate 0.01.
-The batch size is set to 64.
-The hidden dimension of the GNN layer is set to 64.
-The number of epochs is set to 200.
-To prevent overfitting and to save time, the early stopping is used with patience 20.
-The loss function is set to CrossEntropyLoss.
-
-In the future, I will explore different hyperparameters, such as learning rate, batch size, size of hidden dimension, and patience in the early stopping.
-
-% \clearpage
-
 \section{Results of early experiment} \label{sec:results}
 
-Here I take ten datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
+Here I took ten datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
 
@@
     DD                                           & 4.9790         & 7.9700                     \\
-    PTOTEIN\_full                                & 3.7346         & 4.7123                     \\
+    PROTEIN\_full                                & 3.7346         & 4.7123                     \\
     COLORS-3                                     & 2.9288         & 2.0945                     \\
@@
 
-I then used a scatter plot to visualize the generalization error against the two graph parameters.
+Also, I used a scatter plot to visualize the generalization error against the two graph parameters.
 The result is shown in Figure~\ref{fig:scatter}.
-Also I calculated the correlation between the generalization error and the graph parameters.
+Also, I calculated the correlation between the generalization error and the graph parameters.
 The result is shown in Table~\ref{tab:correlation}.
@@
     \caption{The generalization error against the graph parameters, the x-axis is the average degree of the graph, the y-axis is the generalization error of the model.
-The each point in the plot is the calculated result from different datasets.
+Each point in the plot is the calculated result from different datasets (see the table~\ref{tab:parameter}).
 It is obvious that more datasets are needed to get more reliable results.}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
     \centering
@@
 
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{experiment_procedure.pdf}
+    \caption{An illustration of experiment Procedure}
+    \label{fig:experiment}
+\end{figure}
+
 The Objective of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs.
-Beside the content of early experiment, I will explore more GNN layers in the experiment, such as Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, GATv2~\cite{brody2021attentive} and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural} etc.
-I will explore all the graph parameter I mensioned in \ref{sec:graph_parameters} and more if possibly.
 
-I will also explore different hyperparameters, such as learning rate, batch size, hidden dimension, number of epochs, and patience in the early stopping to find the best setting for the models/datasets.
+In the section~\ref{sec:schedule}, I give the preliminary schedule of the thesis.
+The thesis will be divided into seven parts: Introduction, Experimental setup, Result, Discussion, Conclusion, References, and Appendix.
 
-In the section~\ref{sec:results}, I have made the experiment on 10 datasets. In the future, I will make the experiment on more datasets to get more reliable results.
+The methodologies of the experiment is described in the figure~\ref{fig:experiment}.
+The experiment consists of three parts: 1.
+Train the models from datasets and evaluate the models to calculate the generalization error.
+2.
+Calculate the parameters of the graphs from the dataset.
+3.
+Analyze the influence of the graph parameters on the generalization error of the GNNs.
+
+The following questions will be addressed in the thesis:
+\begin{itemize}[noitemsep]
+    \item How do different GNN layers perform on different graph parameters? (the methodologies)
+    \item How do graph parameters influence the generalization error of GNNs? (the results)
+\end{itemize}
+
+The following GNN layers will be explored in the experiment:
+\begin{itemize}[noitemsep]
+    \item Graph Convolutional Networks(GCN)~\cite{kipf2016semi}
+    \item Graph Attention Networks(GAT)~\cite{velickovic2020pointer}
+    \item GATv2~\cite{brody2021attentive}
+    \item Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}
+    \item Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}
+\end{itemize}
+
+The following graph parameters will be explored in the experiment:
+\begin{itemize}[noitemsep]
+    \item Average degree
+    \item Average shortest path length
+    \item Graph diameter
+    \item Graph density
+    \item Graph clustering coefficient
+    \item Centrality measure of graphs
+    \item Average number of coloring in the 1-WL algorithm
+\end{itemize}
+
+Furthermore, it is necessary to adjust the hyperparameters, including the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping for the models and datasets under consideration.
+
+In the section~\ref{sec:results}, I ran the experiment on 10 datasets. In the future, the experiment will be repeated on a larger number of datasets to enhance the reliability of the results.
+
+\newpage
+
+\section{Preliminary Schedule} \label{sec:schedule}
+
+\begin{enumerate}
+% \def\labelenumi{\arabic{enumi}.}
+% \tightlist
+\item
+  Introduction
+\item
+  Experimental setup
+\item
+  Result
+\item
+  Discussion
+\item
+  Conclusion
+\item
+  References
+\item
+  Appendix
+\end{enumerate}
 
 \clearpage
-
-\tableofcontents
-
-\newpage
 
@@
 
-% All reduce Graphs
-\newpage
+\clearpage
 

### 2024-10-06 paper/main.tex
Finish the proposal

@@
 However, the behavior of GNNs is not well understood.
-In particular, it is not clear about the relationship between the graph parameters/characteristics and the empirical generalization error of GNNs.
+Particularly, the relationship between graph parameters/characteristics and the empirical generalization error of GNNs is not clear.
 The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
@@
 In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
+We use $\mathbb{G}$ to represent the set of all possible graphs.
 The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$.
 The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
-In addition to the nodes and edges that comprise the graph, we attach a more complex set of data to each node.
+In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.
 A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included.
 These vectors can be used to characterize graphs or nodes in graphs.
-The adjacency matrix $A \in \mathbb{R}^{n \times n}$ is a matrix that represents the connections between nodes in the graph.
+The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph.
 The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.
@@
 With these foundational terms in place, we can now introduce the concept of a graph parameter.
-A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a set of real numbers.
-Furthermore, such functions need to be permutation invariant, i.e.
-$f(G) = f(G')$ if $G$ and $G'$ are isomorphic graphs.
-A graph parameter characterizes a graph from a certain perspective and allows us to quantify certain properties of a graph.
-Examples of such parameters include the average degree of the graph, the average shortest path of the graph, the centrality measure of the graph, the average number of coloring in the 1-WL algorithm, and so forth.
-I will define concrete definitions in the section \ref{sec:graph_parameters}.
+A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
+Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
+A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
+This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
 
-On the another hand, the graph classification task aims to classify a graph into one of several classes.
+Additionally, the graph classification task aims to classify a graph into one of several classes.
 This thesis will specifically focus on addressing this task.
@@
 
-\begin{enumerate}
-% \def\labelenumi{\arabic{enumi}.}
-% \tightlist
+\begin{itemize}
+
 \item
-  Introduction
+  1. Introduction
 \item
-  Experimental setup
+  2. Background on learning on graphs
 \item
-  Result
+  2.1 Notation
 \item
-  Discussion
+  2.2 Machine learning
 \item
-  Conclusion
+  2.3 Graph neural networks
 \item
-  References
+  2.4 Graph parameters
 \item
-  Appendix
-\end{enumerate}
+  3. Experimental study
+\item
+  3.1 Experimental setup
+\item
+  3.2. Results
+\item
+  3.3. Discussion
+\item
+  6. Conclusion
+\item
+  7. References
+\item
+  9. Appendix
+
+\end{itemize}
 

### 2024-10-08 main.py
Refactor main.py to include new graph analysis functions and add a new option for foo()

@@ -2,7 +2,7 @@ from train_procedure import get_generalization_error_from_a_dataset
 import pandas as pd
 import logging
 from tabulate import tabulate
-from utils import get_average_degree, get_average_shortest_path, read_file_to_list
+from utils import get_average_degree, get_average_shortest_path, get_graph_diameter, get_graph_density, get_graph_clustering_coefficient, get_average_closeness_centrality, get_average_betweenness_centrality, get_average_eigenvector_centrality, wl_1d_color_count, read_file_to_list
 from tqdm import tqdm
 import logging
 import matplotlib.pyplot as plt
@@ -83,6 +83,21 @@ def get_correlation():
     correlation2 = df1['Ave. generalization error'].corr(df2['Ave. shortest path'])
     print(f'Correlation of ave. shortest path and ave. generalization error: {correlation2}')
 
+
+def foo():
+    datasets = read_file_to_list(DATAPATH)
+
+    df = pd.DataFrame({
+        'Name': [],
+        'get_average_number_of_coloring_1WL': []
+    })
+
+    for dataset in tqdm(datasets):
+        df.loc[len(df)] = [dataset, wl_1d_color_count(dataset)]
+
+    print(df)
+
+
 if __name__ == '__main__':
     # get input from user
     print('Please choose from the following options:')
@@ -90,7 +105,8 @@ if __name__ == '__main__':
     print('2. Get Parameters')
     print('3. Compare generalization error and parameters')
     print('4. Get correlation')
-    print('5. Exit')
+    print('5. foo')
+    print('6. Exit')
     option = input('Enter your choice: ')
 
     if option == '1':
@@ -101,3 +117,7 @@ if __name__ == '__main__':
         compare_generalization_error_and_parameters()
     elif option == '4':
         get_correlation()
+    elif option == '5':
+        foo()
+    else:
+        pass

### 2024-10-08 utils.py
Add graph analysis functions to calculate various graph metrics

@@ -7,6 +7,7 @@ import math
 from dataclasses import dataclass
 from torch_geometric.datasets import TUDataset
 from tqdm import tqdm
+import torch
 
 
 
@@ -90,6 +91,156 @@ def get_average_shortest_path(dataset_name, show_errors=False):
         print(f'Error rate: {num_errors / len(dataset)}')
             
     return sum(avg_shortest_paths) / len(avg_shortest_paths)
+
+def get_graph_diameter(dataset_name, show_errors=False):
+    '''
+    Calculate the diameter of the graph
+    '''
+    dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
+    diameters = []
+    num_errors = 0
+
+    for data in dataset:
+        G = to_networkx(data)
+        try:
+            diameters.append(nx.diameter(G))
+        except:
+            num_errors += 1
+            continue
+    if show_errors:
+        print(f'Number of errors: {num_errors}')
+        print(f'Error rate: {num_errors / len(dataset)}')
+
+    return sum(diameters) / len(diameters)
+
+def get_graph_density(dataset_name):
+    '''
+    Calculate the density of the graph
+    '''
+    dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
+    densities = []
+
+    for data in dataset:
+        G = to_networkx(data)
+        densities.append(nx.density(G))
+
+    return sum(densities) / len(densities)
+
+def get_graph_clustering_coefficient(dataset_name):
+    '''
+    Calculate the clustering coefficient of the graph
+    '''
+    dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
+    clustering_coefficients = []
+
+    for data in dataset:
+        G = to_networkx(data)
+        clustering_coefficients.append(nx.average_clustering(G))
+
+    return sum(clustering_coefficients) / len(clustering_coefficients)
+
+def get_graph_transitivity(dataset_name):
+    '''
+    Calculate the transitivity of the graph
+    '''
+    dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
+    transitivity = []
+
+    for data in dataset:
+        G = to_networkx(data)
+        transitivity.append(nx.transitivity(G))
+
+    return sum(transitivity) / len(transitivity)
+
+def get_graph_assortativity(dataset_name):
+    '''
+    Calculate the assortativity of the graph
+    '''
[…]

### 2024-11-10 src/run.py
Implement dataset sweep creation and execution in run.py; add run_test.py for extended sweep testing

@@ -1,6 +1,33 @@
-from train import hyperparameter_tuning
 import wandb
+from utils import read_file_to_list, setup_wandb_sweep
+from train import hyperparameter_tuning
+import os.path as osp
+import pandas as pd
 
 
-sweep_id = 's4v4a4ij'
-wandb.agent(sweep_id, hyperparameter_tuning, count=1, project='bt')
+project_name = 'bt'
+path = osp.join(osp.dirname(__file__), '..', 'data', 'test_dataset.txt')
+dataset_list = read_file_to_list(path)
+
+for dataset_name in dataset_list:
+	print(f'Dataset name: {dataset_name}')
+	path = osp.join(osp.dirname(__file__), '..', 'data', 'dataset.csv')
+	df = pd.read_csv(path)
+
+	# check if the df contains a row with the name of the dataset
+	print('Checking if the sweep exists')
+	if df[df['name'] == dataset_name].empty:
+		print('Creating sweep')
+		sweep_id = setup_wandb_sweep(project_name, dataset_name)
+		print(f'Sweep id: {sweep_id}')
+		# save the dataset name, sweep_id and project name to the csv
+		df = pd.concat([df, pd.DataFrame([{'name': dataset_name, 'project': project_name, 'sweep_id': sweep_id}])], ignore_index=True)
+		df.to_csv(path, index=False)
+	else:
+		print('Dataset found')
+		sweep_id = df[df['name'] == dataset_name]['sweep_id'].values[0]
+		print(f'Sweep id: {sweep_id}')
+
+	# run the sweep
+	print('Running sweep')
+	wandb.agent(sweep_id, hyperparameter_tuning, count=1, project=project_name)

### 2024-11-10 src/run_test.py

@@ -1,0 +1,6 @@
+from train import hyperparameter_tuning
+import wandb
+
+
+sweep_id = 's4v4a4ij'
+wandb.agent(sweep_id, hyperparameter_tuning, count=1000, project='bt')

### 2024-11-10 src/main.py
Remove unused dataset statistics function and related code from main.py

@@ -11,7 +11,6 @@ from utils import (
     get_average_closeness_centrality,
     get_average_betweenness_centrality,
     get_average_eigenvector_centrality,
-    get_dataset_statistics,
     wl_1d_color_count,
     read_file_to_list
 )
@@ -174,15 +173,6 @@ def get_correlation():
         df2['Ave. shortest path'])
     print(f'Correlation of ave. shortest path and ave. generalization error: {
           correlation2}')
-
-
-def foo():
-    DATAPATH = 'data/test_dataset.txt'
-
-    datasets = read_file_to_list(DATAPATH)
-
-    for dataset in datasets:
-        get_dataset_statistics(dataset)
 
 
 def interactive_mode():

### 2024-11-10 src/train.py
Refactor train procedure in train.py: remove unused dataset splitting and logging code; update function documentation and return best test accuracy

@@ -1,6 +1,6 @@
 import torch
 from torch_geometric.loader import DataLoader
-from utils import timeSince, plot_training_results, NetParams, TrainParams, load_dataset, setup_wandb
+from utils import timeSince, plot_training_results, NetParams, TrainParams, load_dataset, setup_wandb_sweep
 from net import get_model
 import time
 import wandb
@@ -8,34 +8,15 @@ import wandb
 
 def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParams, is_wandb=False, num_folds: int = 5):
     """
-    This function die the following:
-    - Load the dataset, using 80:20 train-val split, without the cross-validation.
-    - Train the model
-    - Get the training result of the dataset, including the training loss, validation loss, training accuracy, and
-    - Plot the results.
+    Train a model on a dataset with the given hyperparameters
+    :param dataset_name: Name of the dataset
+    :param model_name: Name of the model
+    :param trainParams: Hyperparameters for training
+    :param is_wandb: Whether to use wandb or not, default is False
+    :param num_folds: Number of folds for cross-validation
     """
 
-    # Define dataset and dataloader
     dataset = load_dataset(dataset_name)
-
-    # n = len(dataset) // 10
-
-    # test_mask = torch.zeros(len(dataset), dtype=torch.bool)
-    # test_mask[0:n] = 1
-    # val_mask = torch.zeros(len(dataset), dtype=torch.bool)
-    # val_mask[n:2*n] = 1
-
-    # train_dataset = dataset[~test_mask & ~val_mask]
-    # val_dataset = dataset[val_mask]
-    # test_dataset = dataset[test_mask]
-
-    # train_loader = DataLoader(
-    #     train_dataset, batch_size=trainParams.batch_size, shuffle=True)
-    # val_loader = DataLoader(
-    #     val_dataset, batch_size=trainParams.batch_size, shuffle=False)
-    # test_loader = DataLoader(
-    #     test_dataset, batch_size=trainParams.batch_size, shuffle=False)
-
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     print(f'Device: {device}')
@@ -138,15 +119,6 @@ def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParam
             val_accs.append(val_acc)
             train_accs.append(train_acc)
 
-            # if is_wandb:
-            #     wandb.log({
[…]

### 2024-11-10 src/utils.py
Refactor setup_wandb function in utils.py: update sweep configuration to use Bayesian method, add early termination parameters, and improve error handling in file reading

@@ -371,16 +371,17 @@ def wl_1d_color_count(dataset_name, verbose=False):
     return sum(color_count_sum) / len(color_count_sum)
 
 
-def setup_wandb():
+def setup_wandb_sweep(project_name: str = 'bt', dataset_name: str = 'DD'):
     sweep_config = {
-        'method': 'random',
+        'method': 'bayes',
+        'name': dataset_name,
         'metric': {
-            'name': 'best_test_acc',
-            'goal': 'minimize'
+            'goal': 'minimize',
+            'name': 'best_test_acc'
         },
         'parameters': {
             'dataset_name': {
-                'values': ['ENZYMES', 'PROTEINS', 'DD', 'COIL-RAG', 'BZR_MD', 'Letter-high']
+                'value': dataset_name
             },
             'hidden_size': {
                 'values': [32, 64, 128, 256]
@@ -400,18 +401,17 @@ def setup_wandb():
             'normlization': {
                 'values': ['batch', 'graph']
             }
+        },
+        'early_terminate': {
+            'type': 'hyperband',
+            'min_iter': 10,
+            's': 0,
+            'eta': 3,
+            'max_iter': 81
         }
-        # normal:
-        # graph normal
-        # batch normal https://pytorch-geometric.readthedocs.io/en/latest/generated/torch_geometric.nn.norm.GraphNorm.html?highlight=graphnorm#torch_geometric.nn.norm.GraphNorm
-        
-        # lr 默认的
-        # patience for early stopping 100-200
-        # num_epochs 1000
-        # patience for plateau 10, 20, 30
     }
 
-    sweep_id = wandb.sweep(sweep_config, project='bt')
+    sweep_id = wandb.sweep(sweep_config, project=project_name)
     return sweep_id
 
 def draw_graph(dataset_name):
@@ -446,6 +446,9 @@ def read_file_to_list(file_path):
     except FileNotFoundError:
         print(f"File not found: {file_path}")
         return []
+    except Exception as e:
+        print(f"An error occurred: {e}")
+        return []
 
 
 def get_dataset_statistics(dataset_name):
@@ -476,7 +479,7 @@ def load_dataset(dataset_name: str):
     path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'data', 'TUDataset')
     if dataset_name == 'IMDB-BINARY':
[…]

### 2024-11-10 src/run.py
Update sweep execution count in run.py to 432 for extended hyperparameter tuning

@@ -30,4 +30,4 @@ for dataset_name in dataset_list:
 
 	# run the sweep
 	print('Running sweep')
-	wandb.agent(sweep_id, hyperparameter_tuning, count=1, project=project_name)
+	wandb.agent(sweep_id, hyperparameter_tuning, count=432, project=project_name)

### 2024-11-10 src/utils.py
Fix formatting in description string for average shortest path calculation

@@ -115,8 +115,7 @@ def get_average_shortest_path(dataset_name, verbose=False):
 
     for data in track(
         dataset,
-        description=f'Calculating average shortest path length for {
-            dataset_name}',
+        description=f'Calculating average shortest path length for {dataset_name}',
         disable=not verbose
     ):
         G = to_networkx(data)

### 2024-11-10 src/utils.py
Fix formatting in description strings for graph analysis functions in utils.py

@@ -137,11 +137,9 @@ def get_average_shortest_path(dataset_name, verbose=False):
         #     print(f'Error: {e}')
         #     break
     if num_errors > 0:
-        print(f'Number and Rate of not strongly connected graph: {
-              num_errors} out of {len(dataset)} | {num_errors / len(dataset)}')
+        print(f'Number and Rate of not strongly connected graph: {num_errors} out of {len(dataset)} | {num_errors / len(dataset)}')
     if num_null_graphs > 0:
-        print(f'Number and Rate of null graph: {
-            num_null_graphs} out of {len(dataset)} | {num_null_graphs / len(dataset)}')
+        print(f'Number and Rate of null graph: {num_null_graphs} out of {len(dataset)} | {num_null_graphs / len(dataset)}')
 
     return sum(avg_shortest_paths) / len(avg_shortest_paths)
 
@@ -181,8 +179,7 @@ def get_graph_diameter(dataset_name, verbose=False):
             raise
 
     if num_errors > 0:
-        print(f'Number and Rate of not strongly connected graph: {
-              num_errors} out of {len(dataset)} | {num_errors / len(dataset)}')
+        print(f'Number and Rate of not strongly connected graph: {num_errors} out of {len(dataset)} | {num_errors / len(dataset)}')
     return sum(diameters) / len(diameters)
 
 
@@ -214,8 +211,7 @@ def get_graph_clustering_coefficient(dataset_name, verbose=False):
 
     for data in track(
         dataset,
-        description=f'Calculating graph clustering coefficient for {
-            dataset_name}',
+        description=f'Calculating graph clustering coefficient for {dataset_name}',
         disable=not verbose
     ):
         G = to_networkx(data)
@@ -275,8 +271,7 @@ def get_average_closeness_centrality(dataset_name, verbose=False):
 
     for data in track(
             dataset,
-            description=f'Calculating average closeness centrality for {
-                dataset_name}',
+            description=f'Calculating average closeness centrality for {dataset_name}',
             disable=not verbose):
         G = to_networkx(data)
         closeness_centralities.append(sum(nx.closeness_centrality(G).values())
@@ -295,8 +290,7 @@ def get_average_betweenness_centrality(dataset_name, verbose=False):
 
     for data in track(
             dataset,
-            description=f'Calculating average betweenness centrality for {
-                dataset_name}',
+            description=f'Calculating average betweenness centrality for {dataset_name}',
             disable=not verbose):
         G = to_networkx(data)
[…]

### 2024-11-12 src/utils.py
Add learning rate parameter and run cap to W&B sweep configuration in utils.py

@@ -391,6 +391,11 @@ def setup_wandb_sweep(project_name: str = 'bt', dataset_name: str = 'DD'):
             },
             'normlization': {
                 'values': ['batch', 'graph']
+            },
+            'learning_rate': {
+                'distribution': 'log_uniform',
+                'min': 1e-5,
+                'max': 1e-2
             }
         },
         'early_terminate': {
@@ -399,7 +404,8 @@ def setup_wandb_sweep(project_name: str = 'bt', dataset_name: str = 'DD'):
             's': 0,
             'eta': 3,
             'max_iter': 81
-        }
+        },
+        'run_cap': 300
     }
 
     sweep_id = wandb.sweep(sweep_config, project=project_name)

### 2024-11-12 proposal/main.tex
Remove dropout layer from GCN forward method in main.tex

--- 2024-10-06 paper/main.tex
@@
         x = self.fc1(x).relu()
-        x = F.dropout(x, p=0.5, training=self.training)
         x = self.fc2(x)

### 2024-11-12 src/parameter.py
Add GraphParameters class with methods for various graph metrics calculations

@@ -6,6 +6,222 @@ import networkx as nx
 import networkx.exception as nx_exception
 
 
+class GraphParameters:
+    def __init__(self, dataset_name, verbose=False):
+        self.dataset = TUDataset(root='data/TUDataset',
+                                 name=dataset_name)
+        self.verbose = verbose
+    
+    def get_average_degree(self):
+        '''
+        Calculate the average degree of the graph
+        '''
+        degs = []
+
+        for data in track(self.dataset, description=f'Calculating average degree for {self.dataset.name}', disable=not self.verbose):
+            deg = degree(data.edge_index[0], data.num_nodes)
+            degs.append(deg.mean().item())
+
+        return sum(degs) / len(degs)
+    
+    def get_average_shortest_path(self):
+        '''
+        Calculate the average shortest path of the graph
+        '''
+        avg_shortest_paths = []
+
+        for data in track(
+            self.dataset,
+            description=f'Calculating average shortest path for {self.dataset.name}',
+            disable=not self.verbose
+        ):
+            G = to_networkx(data)
+            if G.is_directed():
+                G = G.to_undirected()
+            for C in (G.subgraph(c).copy() for c in nx.connected_components(G)):
+                if len(C) <= 1:
+                    continue
+                avg_shortest_paths.append(nx.average_shortest_path_length(C))
+
+        return sum(avg_shortest_paths) / len(avg_shortest_paths)
+    
+    def get_graph_diameter(self):
+        '''
+        Calculate the diameter of the graph
+        '''
+        diameters = []
+
+        for data in track(
+                self.dataset,
+                description=f'Calculating graph diameter for {self.dataset.name}',
+                disable=not self.verbose):
+            G = to_networkx(data)
+
+            if G.is_directed():
+                G = G.to_undirected()
+            for C in (G.subgraph(c).copy() for c in nx.connected_components(G)):
+                if len(C) <= 1:
+                    continue
+                try:
+                    diameters.append(nx.diameter(C))
+                except nx_exception.NetworkXError:
+                    pass
+
+        return sum(diameters) / len(diameters)
+
+    def get_graph_density(self):
+        '''
+        Calculate the density of the graph
+        '''
+        densities = []
+
+        for data in track(
+                self.dataset,
+                description=f'Calculating graph density for {self.dataset.name}',
+                disable=not self.verbose):
+            G = to_networkx(data)
+            densities.append(nx.density(G))
+
+        return sum(densities) / len(densities)
+    
+    def get_graph_clustering_coefficient(self):
+        '''
[…]

### 2024-11-12 src/train.py
Add learning rate parameter to TrainParams and update optimizer in train procedure

@@ -77,7 +77,7 @@ def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParam
 
     for i in range(num_folds):
         model.reset_parameters()
-        optimizer = torch.optim.Adam(model.parameters(), weight_decay=1e-4)
+        optimizer = torch.optim.Adam(model.parameters(), lr=trainParams.learning_rate, weight_decay=1e-4)
         scheduler = torch.optim.lr_scheduler.ReduceLROnPlateau(optimizer, mode='min', patience=trainParams.patience_plateau)
         print(f'On Fold {i+1}')
 
@@ -176,7 +176,7 @@ def hyperparameter_tuning(config=None):
     with wandb.init(config=config):
         config = wandb.config
         trainParams = TrainParams(
-            config.hidden_size, config.num_hidden_layers, config.batch_size, config.default_patience, config.patience_plateau, config.normlization
+            config.hidden_size, config.num_hidden_layers, config.batch_size, config.default_patience, config.patience_plateau, config.normlization, config.learning_rate
         )
         train_procedure(config.dataset_name, 'GCN', trainParams, is_wandb=True)
 

### 2024-11-12 src/utils.py

@@ -55,6 +55,7 @@ class TrainParams:
     patience_earlystopping: int
     patience_plateau: int
     normlization: str
+    learning_rate: float
 
 
 def plot_training_results(dataset_name: str, train_accs, val_accs, train_losses, 

### 2024-11-12 src/utils.py
Update learning rate distribution in wandb sweep setup to uniform with adjusted min and max values

@@ -394,9 +394,9 @@ def setup_wandb_sweep(project_name: str = 'bt', dataset_name: str = 'DD'):
                 'values': ['batch', 'graph']
             },
             'learning_rate': {
-                'distribution': 'log_uniform',
-                'min': 1e-5,
-                'max': 1e-2
+                'distribution': 'uniform',
+                'min': 0.0001,
+                'max': 0.01
             }
         },
         'early_terminate': {

### 2025-01-04 src/net.py
Refactor GATv2 model initialization and training procedure to include additional parameters for heads, dropout, and residual connections

@@ -74,11 +74,11 @@ class GAT(nn.Module):
 
 
 class GATv2(nn.Module):
-    def __init__(self, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int, norm: str = 'batch', heads: int = 1, concat: bool = True, dropout: float = 0, residual: bool = False):
+    def __init__(self, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int, norm: str = 'batch', heads: int = 1, dropout: float = 0, residual: bool = False):
         super().__init__()
-        self.conv1 = GATv2Conv(in_channels, hidden_channels, heads, concat, dropout, residual)
+        self.conv1 = GATv2Conv(in_channels, hidden_channels, heads=heads, concat=False, dropout=dropout, residual=residual)
         self.convs = nn.ModuleList(
-            [GATv2Conv(hidden_channels, hidden_channels, heads, concat, dropout, residual) for _ in range(num_hidden_layers)])
+            [GATv2Conv(hidden_channels, hidden_channels, heads=heads, concat=False, dropout=dropout, residual=residual) for _ in range(num_hidden_layers)])
         self.norms = nn.ModuleList(
             [normalization_resolver(norm, hidden_channels) for _ in range(num_hidden_layers + 1)])
         self.fc1 = nn.Linear(hidden_channels, hidden_channels)
@@ -189,7 +189,7 @@ class MPNN(nn.Module):
         self.fc2.reset_parameters()
 
 
-def get_model(model_name: str, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int = 4, norm: str = 'batch'):
+def get_model(model_name: str, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int = 4, norm: str = 'batch', heads: int = 1, concat: bool = True, dropout: float = 0, residual: bool = False):
     if model_name == 'MPNN':
         return MPNN(in_channels, hidden_channels, out_channels, num_hidden_layers, norm)
     elif model_name == 'GCN':
@@ -197,7 +197,7 @@ def get_model(model_name: str, in_channels: int, hidden_channels: int, out_chann
     elif model_name == 'GAT':
         return GAT(in_channels, hidden_channels, out_channels, num_hidden_layers, norm)
     elif model_name == 'GATv2':
-        return GATv2(in_channels, hidden_channels, out_channels, num_hidden_layers, norm)
[…]

### 2025-01-04 src/train.py

@@ -6,7 +6,7 @@ import time
 import wandb
 
 
-def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParams, is_wandb=False, num_folds: int = 5):
+def train_procedure(dataset_name: str,  model_name: str, trainParams, is_wandb=False, num_folds: int = 5):
     """
     Train a model on a dataset with the given hyperparameters
     :param dataset_name: Name of the dataset
@@ -22,14 +22,27 @@ def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParam
     print(f'Device: {device}')
 
     # Define model
-    model = get_model(
-        model_name=model_name,      
-        in_channels=dataset.num_features,
-        hidden_channels=trainParams.hidden_size,
-        out_channels=dataset.num_classes,
-        num_hidden_layers=trainParams.num_hidden_layers,
-        norm=trainParams.normlization
-    ).to(device)
+    if model_name == 'GATv2':
+        model = get_model(
+            model_name=model_name,
+            in_channels=dataset.num_features,
+            hidden_channels=trainParams.hidden_size,
+            out_channels=dataset.num_classes,
+            num_hidden_layers=trainParams.num_hidden_layers,
+            norm=trainParams.normlization,
+            heads=trainParams.heads,
+            dropout=trainParams.dropout,
+            residual=trainParams.residual
+        ).to(device)
+    else:
+        model = get_model(
+            model_name=model_name,      
+            in_channels=dataset.num_features,
+            hidden_channels=trainParams.hidden_size,
+            out_channels=dataset.num_classes,
+            num_hidden_layers=trainParams.num_hidden_layers,
+            norm=trainParams.normlization
+        ).to(device)
 
     criterion = torch.nn.CrossEntropyLoss()
 
@@ -136,7 +149,7 @@ def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParam
                 patience -= 1
                 if patience == 0:
                     break
-            if epoch % 20 == 0:
+            if epoch % 50 == 0:
                 train_losses.append(train_loss)
                 val_losses.append(val_loss)
                 val_accs.append(val_acc)
@@ -183,17 +196,19 @@ def train_procedure(dataset_name: str,  model_name: str, trainParams: TrainParam
 
     return best_test_acc
 
-def train_test(dataset_name: str, model_name: str = 'GCN'):
-    hidden_size = 128
[…]

### 2025-01-04 src/run.py
Update project name to 'bt_GATv2' and enhance sweep configuration with additional parameters for heads, dropout, and residual options

@@ -7,7 +7,7 @@ import argparse
 
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-p", "--project_name", help="project name", default='bt_GCN')
+parser.add_argument("-p", "--project_name", help="project name", default='bt_GATv2')
 parser.add_argument("-i", "--sweep_id", help="sweep id")
 args = parser.parse_args()
 

### 2025-01-04 src/setup_sweep.py

@@ -9,7 +9,9 @@ parser.add_argument("-t", "--temporory", help="set a temporary flag",
                     action="store_true")
 args = parser.parse_args()
 
-project_name = 'bt_GCN'
+print(f'Temporary flag: {args.temporory}')
+
+project_name = 'bt_GATv2'
 path = osp.join(osp.dirname(__file__), '..', 'data', 'test_dataset.txt')
 dataset_list = read_file_to_list(path)
 
@@ -28,7 +30,7 @@ for dataset_name in dataset_list:
 			sweep_id = setup_wandb_sweep(project_name, dataset_name)
 		print(f'Sweep id: {sweep_id}')
 		# save the dataset name, sweep_id and project name to the csv
-		df = pd.concat([df, pd.DataFrame([{'name': f'{dataset_name}_temp', 'project': project_name, 'sweep_id': sweep_id}])], ignore_index=True)
+		df = pd.concat([df, pd.DataFrame([{'name': f'{dataset_name}', 'project': project_name, 'sweep_id': sweep_id}])], ignore_index=True)
 		df.to_csv(path, index=False)
 	else:
 		print('Dataset found')

### 2025-01-04 src/utils.py

@@ -12,6 +12,7 @@ from rich.progress import track
 import wandb
 import os.path as osp
 import pandas as pd
+from typing import Optional
 
 
 class MyFilter(object):
@@ -57,6 +58,9 @@ class TrainParams:
     patience_plateau: int
     normlization: str
     learning_rate: float
+    heads: Optional[int] = None
+    dropout: Optional[float] = None
+    residual: Optional[bool] = None
 
 
 def plot_training_results(dataset_name: str, train_accs, val_accs, train_losses, 
@@ -413,12 +417,17 @@ def setup_wandb_sweep(project_name: str = 'bt', dataset_name: str = 'DD', temp=F
     if temp is True:
         sweep_config['name'] = dataset_name + '_temp'
 
+    if project_name == 'bt_SGC':
+        sweep_config['parameters']['model_name'] = { 'value': 'SGC' }
+
     if project_name == 'bt_GATv2':
-        sweep_config['heads'] = { 'values': [1, 2, 4] }
-        sweep_config['concat'] = { 'values': [True, False] }
-        sweep_config['dropout'] = { 'values': [0, 0.1, 0.2] }
-        sweep_config['residual'] = { 'values': [True, False] }
-        sweep_config['run_cap'] = 100
+        sweep_config['parameters']['model_name'] = { 'value': 'GATv2' }
+        sweep_config['parameters']['heads'] = { 'values': [1, 2, 4] }
+        sweep_config['parameters']['dropout'] = { 'values': [0, 0.1, 0.2] }
+        sweep_config['parameters']['residual'] = { 'values': [True, False] }
+    
+    if project_name == 'bt_MPNN':
+        sweep_config['parameters']['model_name'] = { 'value': 'MPNN' }
 
     sweep_id = wandb.sweep(sweep_config, project=project_name)
     return sweep_id

### 2025-01-14 thesis/main.tex
Add thesis tex files
Update the thesis

--- 2024-11-12 proposal/main.tex
@@
 
-\title{\textbf{Proposal for bachelor thesis}\\
+\title{\textbf{Bachelor thesis}\\
 Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}
@@
 \section{Introduction}\label{sec:intro}
-
 Graph learning became a hot topic in the field of machine learning in recent years.
@@
 
-Before we untangle this problem, we need to define some terms with regard to the graph.
+Speaking more specifically.
+First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree.
+In graph theory, \textit{graph parameter} is used to quantify them.
+And a dataset consists of multiple graphs, each with its graph parameter.
+In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset.
+In this thesis, 57 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
+Second, I train different GNN models on each dataset and find that their generalization abilities varied.
+I show that there is a certain relationship between generalization ability and different graph parameters.
+
+\subsection{Related work}
+The following section provides an overview of the related work.
+
+\subsubsection{Graph parameters}
+
+\subsubsection{Generalization error}
+
+\section{Background on learning on graphs}
+The following sections provide an overview of the concepts and methods related to graph learning, machine learning, and graph neural networks.
+
+\subsection{Notion}
+At first, we need to define some terms with regard to the graph.
 In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
@@
 
-With these foundational terms in place, we can now introduce the concept of a graph parameter.
-A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
-Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
-A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
-This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
+\subsection{Machine learning}
+Machine learning is a subfield of artificial intelligence that focuses on the development of algorithms that can learn from and make predictions or decisions based on data.
+The goal of machine learning is to develop models that can generalize well to unseen data.
+The model is trained on a training dataset, which consists of input-output pairs.
+The model is then evaluated on a test dataset, which is separate from the training dataset.
 
-Additionally, the graph classification task aims to classify a graph into one of several classes.
-This thesis will specifically focus on addressing this task.
+\subsubsection{Generalization}
 A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
@@
 And the generalization error can be used to determine whether the model is overfitting or underfitting.
-Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the dataset.
-In this thesis, I will investigate how the graph parameters influence the generalization error of GNNs.
-The understanding of the influence of graph parameters on the generalization error of GNNs can help us to understand the behavior of GNNs so that researchers can tune GNNs to improve their predictive performance on new graphs.
+Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g.
+Graph parameter).
 
-\section{Experimental Setup}
+\subsection{Graph Neural Networks}
+Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
+GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
+The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
+This information is then used to make predictions.
+GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification, edge prediction, and graph classification.
+Popular GNNs in recent years include Graph Convolutional Networks (GCN), Graph Attention Networks (GAT), and Message Passing Neural Networks (MPNN).
+
+\subsection{Graph parameters}
+Now we can introduce the concept of a graph parameter.
+A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
+Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
+A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
+This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
+
+\section{Experimental study}
+
+\subsection{Experimental setup}
 The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.
 
-\subsection{Training Framework}
+\subsubsection{Training Framework}
 The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
@@
 
-\subsection{Datasets}
+\subsubsection{Hyperparameters tuning}
+Before training the models, for each pair of dataset and model, the hyperparameters of the model are tuned.
+In the experiment, 5-fold cross-validation is used to tune the hyperparameters instead of 10-fold cross validation in the final experiment.
+The reason is that the 10-fold cross-validation is computationally expensive and time-consuming.
+
+The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler.
+Additionally, for the GATv2 model, the number of heads, the dropout rate, and residual are also tuned.
+
+The hyperparameters are tuned using the Bayesian optimization method\cite{frazier2018tutorial}.
+The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
+
+There are five models and 57 datasets, resulting in 285 pairs of dataset and model.
+For each pair, the hyperparameters are tuned using the Bayesian optimization method.
+The hyperparameters are tuned using the validation dataset.
+The validation dataset is a subset of the training dataset that is used to tune the hyperparameters of the model.
+The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
+
+\subsubsection{Datasets}
 The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
@@
 It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quite small (less than 500 data points/graphs), I will use 10-fold cross validation in the training process, in order to fully utilize the data.
+Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
 A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
@@
 
-\subsection{Models}
+I list information about the 57 datasets used in the experiment in the appendix~\ref{sec:datasets}.
+
+\subsubsection{Models}
 In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
@@
 
-\subsection{Experimental details}
+\subsubsection{Experimental details}
 The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
@@
 
-\subsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
+\subsubsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
 As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.
@@
 
-\section{Results of early experiment} \label{sec:results}
+\subsection{Results}
 
-Here I took ten datasets from TUDataset as examples. The calculated parameters are shown in Table~\ref{tab:parameter}. The generalization error of the models are shown in Table~\ref{tab:error}.
+\subsubsection{Graph parameters of the datasets}
 
-\begin{table}[h!]
+\begin{table}[!ht]
+    \footnotesize
     \centering
-    \begin{tabular}{@{}lll@{}}
-    \toprule
-    \multicolumn{1}{c}{\multirow{2}{*}{Dataset}} & \multicolumn{2}{c}{Parameter}                                            \\ \cmidrule(l){2-3} 
-    \multicolumn{1}{c}{}                         & \multicolumn{1}{c}{Ave. degree} & \multicolumn{1}{c}{Ave. shortest path} \\ \midrule
-    Mutagenicity                                 & 2.0379         & 4.4825                     \\
-    NCI1                                         & 2.1550         & 5.4697                     \\
-    COIL-RAG                                     & 1.8277         & 1.0606                     \\
-    Letter-high                                  & 1.8896         & 1.5173                     \\
-    DD                                           & 4.9790         & 7.9700                     \\
-    PROTEIN\_full                                & 3.7346         & 4.7123                     \\
-    COLORS-3                                     & 2.9288         & 2.0945                     \\
-
-    AIDS  &  2.01286  & 3.2864 \\
-    ENZYMES  &  3.8626  & 4.4461 \\
-    Cuneiform  &  4.0795  & 2.24442 \\ \bottomrule
-
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+    \hline
+        \textbf{Name} & \textbf{Ave.
+degree} & \textbf{Ave.
+shortest path} & \textbf{Graph diameter} & \textbf{Graph density} & \textbf{Graph clustering coefficient} & \textbf{Ave.
+closeness centrality} & \textbf{Ave.
+betweenness centrality} & \textbf{Ave.
+eigenvector centrality} & \textbf{1-WL color count} \\ \hline
+        COIL-DEL & 4.673071633424515 & 2.128750184714701 & 4.06974358974359 & 0.3275202823564923 & 0.546258039207784 & 0.5122126871677409 & 0.0647750716657882 & 0.2431245565997526 & 21.102564102564106 \\ \hline
+        COIL-RAG & 1.8277218368573067 & 1.0604823111763986 & 1.242159383033419 & 0.924030303030303 & 0.5903545713545713 & 0.94372526076617 & 0.0462785547785547 & 0.5905014648511226 & 1.3115384615384615 \\ \hline
+        Cuneiform & 4.079588014981273 & 2.244427103288844 & 3.0 & 0.2222330604444725 & 0.8634154547075895 & 0.4613474974345972 & 0.0722909733763576 & 0.1963017855703223 & 2.0 \\ \hline
+        Fingerprint & 1.4868577990824814 & 2.115136284036567 & 4.344413012729844 & 0.4391785351497472 & 0.0017307791737759 & 0.5069423734352098 & 0.1840341453794884 & 0.4207756269406634 & 3.656584457887389 \\ \hline
+        FIRSTMM\_DB & 4.50236815941043 & 12.309044701937715 & 30.676056338028168 & 0.0074027477877271 & 0.2631922211539924 & 0.0551742654129266 & 0.0188189276256195 & 0.0092704028700914 & 1357.8292682926829 \\ \hline
+        Letter-high & 1.889683607525296 & 1.4794456563750826 & 2.444490301279405 & 0.5791851851851852 & 0.2976163139329805 & 0.6794971082752952 & 0.1657867724867724 & 0.4611670600331147 & 2.994222222222222 \\ \hline
+        Letter-low & 1.3213534599145254 & 1.33364428641149 & 1.955783308931186 & 0.4165470899470899 & 0.0 & 0.4955472438922087 & 0.1618904761904762 & 0.4407481624189365 & 2.471111111111111 \\ \hline
+        Letter-med & 1.352705840084288 & 1.3502031822344325 & 2.006610576923077 & 0.4245777777777778 & 0.0139393298059964 & 0.5071406868429822 & 0.1683222222222222 & 0.4416562761104123 & 2.517333333333333 \\ \hline
+        MSRC\_9 & 4.81534002269555 & 3.113629895894764 & 7.004524886877828 & 0.1235873024311543 & 0.5412981657910688 & 0.33102605797573 & 0.055215313789426 & 0.1368862401087341 & 40.36199095022624 \\ \hline
+        MSRC\_21 & 5.102391318360188 & 4.094474312024695 & 9.621669626998225 & 0.0680571076593652 & 0.5146660459581984 & 0.251511488615992 & 0.041532868642658 & 0.0936632954729105 & 77.22735346358792 \\ \hline
+        MSRC\_21C & 4.782574662751558 & 3.113761314016 & 6.971291866028708 & 0.1240107738760322 & 0.5427170070575877 & 0.3315153420789583 & 0.0557392711060186 & 0.1371850938080253 & 40.05263157894737 \\ \hline
+        DD & 4.979061666490266 & 7.919898418826995 & 19.70016611295681 & 0.0278322962071925 & 0.4793770769559906 & 0.1402074694227141 & 0.0324963430907113 & 0.0342447661028087 & 278.28013582342953 \\ \hline
+        ENZYMES & 3.862625308732192 & 4.2810541955964485 & 10.4265625 & 0.1598878125179543 & 0.4533912862690096 & 0.263573448964092 & 0.1158938852730127 & 0.1471447702872793 & 28.575 \\ \hline
+        KKI & 3.1856769969664422 & 3.500870554422239 & 8.144578313253012 & 0.1792960793494088 & 0.3526436673677589 & 0.3358793648012939 & 0.1297799757896069 & 0.1757034314039908 & 24.81927710843373 \\ \hline
+        OHSU & 4.327667933476122 & 4.921680537597515 & 12.69620253164557 & 0.0822944467200859 & 0.3808295357080805 & 0.2407028072344937 & 0.0655860979728088 & 0.0823969445758651 & 77.51898734177215 \\ \hline
+        Peking\_1 & 3.5514470044304343 & 3.968106920104182 & 9.623529411764704 & 0.1276151076564966 & 0.3673053988324483 & 0.2889094228756093 & 0.0998385744518594 & 0.1284748145692827 & 36.72941176470588 \\ \hline
+        PROTEINS & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
+        PROTEINS\_full & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
+        COLORS-3 & 2.928853359699249 & 2.5810313856214724 & 5.275766205587198 & 0.1695881211511339 & 0.1450387037596311 & 0.3502761440955542 & 0.0639043708084029 & 0.1737080119571242 & 56.95904761904762 \\ \hline
+        SYNTHETIC & 3.920000076293945 & 3.5064646464646465 & 7.0 & 0.0395959595959595 & 0.0203095238095238 & 0.2893391429701345 & 0.0255761698618841 & 0.0831547830080052 & 100.0 \\ \hline
+        SYNTHETICnew & 3.9250000715255737 & 3.4872567329242026 & 7.274834437086093 & 0.0396464646464646 & 0.0229497089947089 & 0.289441726009901 & 0.0255427746856318 & 0.0836273264155355 & 99.96333333333334 \\ \hline
+        Synthie & 3.6210444450378416 & 2.6348743925562266 & 5.494845360824742 & 0.038420429009193 & 0.0937036201778145 & 0.2766177855177352 & 0.0231922369186012 & 0.0786632559723412 & 90.6125 \\ \hline
+        TRIANGLES & 3.1404920884927114 & 2.263375484124684 & 4.557498816896771 & 0.2416135135324899 & 0.2286352011335792 & 0.4374025890339534 & 0.0821216496736849 & 0.226180376713217 & 19.88371111111111 \\ \hline
+        AIDS & 2.0128653862178325 & 3.490507728804514 & 7.762604013705335 & 0.1935408261794486 & 0.0071746166779525 & 0.3500774185559109 & 0.1911961844012523 & 0.262770387548969 & 11.8145 \\ \hline
+        BZR & 2.1466610419897387 & 5.154837461860052 & 11.65679012345679 & 0.0648920405178712 & 8.903397114779228e-05 & 0.2054846442932875 & 0.1245291263310628 & 0.1416530437212679 & 29.607407407407408 \\ \hline
+        BZR\_MD & 20.30392156862745 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2203726689661978 & 1.0 \\ \hline
+        COX2 & 2.107735009469108 & 5.936420803578038 & 13.790149892933618 & 0.0529052472359257 & 0.0007216110850642 & 0.1757209022905502 & 0.1262987138392391 & 0.1288265342157682 & 28.09421841541756 \\ \hline
+        COX2\_MD & 25.27722772277228 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.1957034193657646 & 1.0 \\ \hline
+        DHFR & 2.102359890622437 & 6.144674814243727 & 14.603174603174605 & 0.0536754666970741 & 0.0 & 0.1734264353163348 & 0.1288500765571343 & 0.1271607693927877 & 32.21560846560847 \\ \hline
+        DHFR\_MD & 22.8676844783715 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2076620678810238 & 1.0 \\ \hline
+        ER\_MD & 20.327354260089685 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2244695039966339 & 1.0 \\ \hline
+        FRANKENSTEIN & 2.0627741588132293 & 3.6742676066855062 & 8.423452029938762 & 0.1705038719060743 & 0.0106826329262756 & 0.3148146889108825 & 0.1923606317376928 & 0.2432099454364741 & 13.42448697256168 \\ \hline
+        MCF-7 & 2.1516180606917765 & 5.050070569624072 & 12.141178938535766 & 0.0980572307942984 & 0.0020345164969653 & 0.2175444791564102 & 0.1724077067751488 & 0.1725022149133201 & 21.418113071660063 \\ \hline
+        MCF-7H & 2.0888838372172147 & 5.858613378052236 & 13.306228605946709 & 0.0537227676449342 & 0.0005825022974507 & 0.1778419519669024 & 0.1198217621207925 & 0.1223362659022958 & 32.9756211739287 \\ \hline
+        MOLT-4 & 2.146077948348501 & 4.951738679286625 & 11.874633536790505 & 0.0987082247303717 & 0.0019246147011501 & 0.2183304220273518 & 0.1714407445609207 & 0.1734293274657891 & 21.028995347667543 \\ \hline
+        MOLT-4H & 2.0858484049375803 & 5.738056140581633 & 12.992424764134702 & 0.0539489355320176 & 0.0005343843281943 & 0.17815930623996 & 0.1192636780853368 & 0.1228930198480923 & 32.272249465610464 \\ \hline
+        Mutagenicity & 2.0379886209469995 & 4.418912992995495 & 9.63701923076923 & 0.0912875415379717 & 0.0031125822886973 & 0.2466634939984061 & 0.1371754284356414 & 0.1710356482094367 & 20.874567673507038 \\ \hline
+        MUTAG & 2.18877208359698 & 3.626150957182829 & 8.21808510638298 & 0.1384540671648269 & 0.0 & 0.293764054092514 & 0.1694459751944365 & 0.2197353385133972 & 14.8031914893617 \\ \hline
+        NCI1 & 2.15501380214726 & 5.234873158476093 & 12.659402381487306 & 0.088944910671084 & 0.0030999008340164 & 0.2026186665583615 & 0.1631676786426253 & 0.1607325923179734 & 24.721411192214116 \\ \hline
+        NCI109 & 2.156446177386937 & 5.183950502801717 & 12.49528936742934 & 0.0894286690245151 & 0.0030732389355228 & 0.20411132911515 & 0.1624231134845694 & 0.1617585552708976 & 24.52410952265568 \\ \hline
+        NCI-H23 & 2.1451602406810686 & 4.950946501654924 & 11.869525050337558 & 0.0987776628128759 & 0.0018996992922189 & 0.2183535143438838 & 0.1715792456717554 & 0.1735208031755432 & 20.99303645329963 \\ \hline
+        NCI-H23H & 2.085327596320919 & 5.734343001278942 & 12.983736711151325 & 0.0539842770435475 & 0.0005268942359655 & 0.1782099752168056 & 0.1192891041739607 & 0.1229635264798962 & 32.22578246970485 \\ \hline
+        OVCAR-8 & 2.145637268375766 & 4.945169149304127 & 11.85222800857742 & 0.0987730040211328 & 0.0018986224960467 & 0.2183941696064956 & 0.171403631603811 & 0.1735393405097124 & 20.98556125974924 \\ \hline
+        OVCAR-8H & 2.0856259705836995 & 5.728655397369023 & 12.966769410758882 & 0.0539777071171825 & 0.0005298176630677 & 0.1782129665549435 & 0.1192148511162624 & 0.1229665170804826 & 32.22561457202093 \\ \hline
+        P388 & 2.109217112454913 & 4.355752638151867 & 10.21824835544779 & 0.1190787859581164 & 0.0037544697177687 & 0.2459957278657192 & 0.1789538865626834 & 0.1958220277248745 & 17.133174189814813 \\ \hline
+        P388H & 2.0638945394922854 & 5.289795718220624 & 11.765664188214403 & 0.0639638393366292 & 0.0009642194122106 & 0.1971310478874152 & 0.1240122910178544 & 0.1373237905541068 & 26.71100983796296 \\ \hline
+        PC-3 & 2.1520653447146643 & 5.05018085139685 & 12.140862989009436 & 0.098055200309084 & 0.0019733135754618 & 0.2175815805232795 & 0.1725492873407526 & 0.172560720893664 & 21.37340506743248 \\ \hline
+        PC-3H & 2.08922384690422 & 5.857822430952191 & 13.30650249313117 & 0.0537656750613318 & 0.0005561305149752 & 0.1779189564869681 & 0.1200247359820712 & 0.1224665687629844 & 32.881929550328984 \\ \hline
+        PTC\_FM & 1.9758043374578045 & 3.311647990381311 & 7.36676217765043 & 0.2154944740700171 & 0.0091220986824968 & 0.3693003427913903 & 0.2055882581121011 & 0.2786143302706905 & 9.91404011461318 \\ \hline
+        PTC\_FR & 1.9863111707899304 & 3.387662268892836 & 7.589743589743589 & 0.2085568638656639 & 0.0088214579442649 & 0.3612672957602951 & 0.2045358868174996 & 0.2734008790739162 & 10.22222222222222 \\ \hline
+        PTC\_MM & 1.9701179610121815 & 3.301432053360394 & 7.339285714285714 & 0.2223452925857377 & 0.0130582137161084 & 0.374488207420213 & 0.2059637189235834 & 0.2823441282735879 & 9.803571428571429 \\ \hline
+        PTC\_MR & 1.9805375618297 & 3.3577641223936463 & 7.523255813953488 & 0.2137888896192228 & 0.009509685286154 & 0.3666473296924281 & 0.2062170509277356 & 0.2777684525909222 & 10.040697674418604 \\ \hline
+        SF-295 & 2.145489384462884 & 4.9445677038396125 & 11.852116182572614 & 0.09881526807439 & 0.0019131887956769 & 0.2184346701016761 & 0.1714761059761314 & 0.1735919743359789 & 20.97159246107621 \\ \hline
+        SF-295H & 2.0855234748235936 & 5.727434951743517 & 12.9664274556856 & 0.0539895579758234 & 0.0005299113307649 & 0.1782697110808576 & 0.1192036786794211 & 0.1229816733300816 & 32.196146110104046 \\ \hline
+        SN12C & 2.145026913904858 & 4.94825141099449 & 11.86401279205747 & 0.0987936439503507 & 0.001927945706436 & 0.2183468315283276 & 0.1714975830848956 & 0.1735570013676089 & 20.99167583241676 \\ \hline
+        SN12CH & 2.0853053252079072 & 5.730086714838555 & 12.973598487437071 & 0.0540104189866913 & 0.0005390487212868 & 0.1781938757210136 & 0.1192686561921279 & 0.1230077396296653 & 32.236301369863014 \\ \hline
+        SW-620 & 2.1452310279340394 & 4.94393636762053 & 11.851577038136291 & 0.0988746005232462 & 0.0018522578567537 & 0.2185003794708548 & 0.1714920826604129 & 0.1736489333480562 & 20.97197276226192 \\ \hline
+        SW-620H & 2.0854275176564645 & 5.725806234940699 & 12.962851360467733 & 0.054054544610838 & 0.0005110193017508 & 0.1783225632271403 & 0.1192839052512742 & 0.1230820111720522 & 32.19651139840126 \\ \hline
+        UACC257 & 2.145698715720169 & 4.955834964420495 & 11.885704040162564 & 0.0987250195703296 & 0.0018738116805416 & 0.218300263582104 & 0.1716221375949755 & 0.1734631006815176 & 20.994198259477844 \\ \hline
+        UACC257H & 2.0856917230912635 & 5.740515645090362 & 13.003174313183676 & 0.0539749990285044 & 0.0005209407683445 & 0.1781806662974605 & 0.1193640515072574 & 0.122956068725157 & 32.22436731019306 \\ \hline
+        Yeast & 2.099442849357738 & 4.364322361013096 & 10.26343257027636 & 0.1210553127513687 & 0.0022671334945899 & 0.2476806589296417 & 0.183060827627568 & 0.1985665767951158 & 16.67475282973832 \\ \hline
+        YeastH & 2.0589509621359707 & 5.245391698622407 & 11.6875493153864 & 0.0642704732457107 & 0.0005773570062507 & 0.1983872537891083 & 0.1254655281986756 & 0.1384817929367545 & 26.05320284921044 \\ \hline
+        Sum & 242.8347529362711 & 258.6723790469145 & 587.9183294923151 & 12.731666924394474 & 11.845921907393928 & 20.687237238791475 & 7.3848149134808 & 11.636469235194477 & 3245.599253687252 \\ \hline
     \end{tabular}
-    \caption{The calculated parameters from a set of datasets, here used two parameters, the average degree of the graph and the average shortest path of the graph which defined in the section \ref{sec:graph_parameters}.}
-    \label{tab:parameter}
-\end{table}
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{@{}lll@{}}
-    \toprule
-    Dataset        & Ave. generalization error & Standard Deviation   \\ \midrule
-    Mutagenicity   & 0.0268      & 0.02335 \\
-    NCI1           & 0.0138      & 0.02649 \\
-    COIL-RAG       & 0.0450      & 0.01378 \\
-    Letter-high    & 0.0403      & 0.04342 \\
-    DD             & 0.0524      & 0.05849 \\
-    PROTEINS\_full & 0.0189      & 0.05032 \\
-    COLORS-3       & 0.0076      & 0.01428 \\
-    AIDS           &  0.00931    & 0.008642 \\
-    ENZYMES           &  0.0345    & 0.052339 \\
-    Cuneiform           &  0.2392    & 0.09868 \\ \bottomrule
-    \end{tabular}
-    \caption{The table shows the calculated generalization error from a set of datasets, where the generalization error is calculated as the difference between the training accuracy and the test accuracy.}
-    \label{tab:error}
-\end{table}
-
-Also, I used a scatter plot to visualize the generalization error against the two graph parameters.
-The result is shown in Figure~\ref{fig:scatter}.
-Also, I calculated the correlation between the generalization error and the graph parameters.
-The result is shown in Table~\ref{tab:correlation}.
-
-\begin{figure}[h!]
-    \includegraphics[width=\textwidth]{final_results.png}
-    \caption{The generalization error against the graph parameters, the x-axis is the average degree of the graph, the y-axis is the generalization error of the model.
-Each point in the plot is the calculated result from different datasets (see the table~\ref{tab:parameter}).
-It is obvious that more datasets are needed to get more reliable results.}
-    \label{fig:scatter}
-\end{figure}
-
-\begin{table}[ht]
-    \centering
-    \begin{tabular}{@{}ll@{}}
-    \toprule
-                       & Ave. Generalization Error \\ \midrule
-    Ave degree            & 0.4068                    \\
-    Ave. shortest path & -0.2074                   \\ \bottomrule
-    \end{tabular}
-    \caption{The correlation between the generalization error and the graph parameters. The correlation is calculated by the Pearson correlation coefficient.}
-    \label{tab:correlation}
+    \caption{Graph parameters of the datasets}
 \end{table}
@@
 
-\section{Objective of the thesis}
+\subsubsection{Generalization error of GCN model}
 
-\begin{figure}[h!]
+\begin{table}[!ht]
     \centering
-    \includegraphics[width=0.5\textwidth]{experiment_procedure.pdf}
-    \caption{An illustration of experiment Procedure}
-    \label{fig:experiment}
-\end{figure}
-
-The Objective of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of GNNs.
-
-In the section~\ref{sec:schedule}, I give the preliminary schedule of the thesis.
-The thesis will be divided into seven parts: Introduction, Experimental setup, Result, Discussion, Conclusion, References, and Appendix.
-
-The methodologies of the experiment is described in the figure~\ref{fig:experiment}.
-The experiment consists of three parts: 1.
-Train the models from datasets and evaluate the models to calculate the generalization error.
-2.
-Calculate the parameters of the graphs from the dataset.
-3.
-Analyze the influence of the graph parameters on the generalization error of the GNNs.
-
-The following questions will be addressed in the thesis:
-\begin{itemize}[noitemsep]
-    \item How do different GNN layers perform on different graph parameters? (the methodologies)
-    \item How do graph parameters influence the generalization error of GNNs? (the results)
-\end{itemize}
-
-The following GNN layers will be explored in the experiment:
-\begin{itemize}[noitemsep]
-    \item Graph Convolutional Networks(GCN)~\cite{kipf2016semi}
-    \item Graph Attention Networks(GAT)~\cite{velickovic2020pointer}
-    \item GATv2~\cite{brody2021attentive}
-    \item Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}
-    \item Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}
-\end{itemize}
-
-The following graph parameters will be explored in the experiment:
-\begin{itemize}[noitemsep]
-    \item Average degree
-    \item Average shortest path length
-    \item Graph diameter
-    \item Graph density
-    \item Graph clustering coefficient
-    \item Centrality measure of graphs
-    \item Average number of coloring in the 1-WL algorithm
-\end{itemize}
-
-Furthermore, it is necessary to adjust the hyperparameters, including the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping for the models and datasets under consideration.
-
-In the section~\ref{sec:results}, I ran the experiment on 10 datasets. In the future, the experiment will be repeated on a larger number of datasets to enhance the reliability of the results.
+    \begin{tabular}{|l|l|l|}
+    \hline
+        Name & Ave. generalization error & Standard deviation \\ \hline
+        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\ \hline
+        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\ \hline
+        MOLT-4 & 0.0 & 0.014102176763117313 \\ \hline
+        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\ \hline
+        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\ \hline
+        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\ \hline
+        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\ \hline
+        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\ \hline
+        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\ \hline
+        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\ \hline
+        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\ \hline
+        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\ \hline
+        P388 & 0.008062511682510376 & 0.01043933816254139 \\ \hline
+        P388H & 0.006343752145767212 & 0.007148966193199158 \\ \hline
+        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\ \hline
+        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\ \hline
+        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\ \hline
+        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\ \hline
+        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\ \hline
+        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\ \hline
+        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\ \hline
+        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\ \hline
+        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\ \hline
+        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\ \hline
+        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\ \hline
+        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\ \hline
+        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\ \hline
+        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\ \hline
+        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\ \hline
+        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\ \hline
+        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\ \hline
+        DD & -0.1750326007604599 & 0.3490835428237915 \\ \hline
+        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\ \hline
+        KKI & 0.04776120185852051 & 0.2546080946922302 \\ \hline
+        OHSU & 0.39824172854423523 & 0.138640895485878 \\ \hline
+        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\ \hline
+        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\ \hline
+        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\ \hline
+        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\ \hline
+        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ \hline
+    \end{tabular}
+    \caption{Generalization error of the GCN model on 57 datasets}
+    \label{tab:ge_gcn} % ge -> generalization error
+\end{table}
 
@@
 
-\section{Preliminary Schedule} \label{sec:schedule}
+\subsubsection{Generalization error of SGC model}
 
-\begin{itemize}
+\subsubsection{Generalization error of GATv2 model}
 
-\item
-  1. Introduction
-\item
-  2. Background on learning on graphs
-\item
-  2.1 Notation
-\item
-  2.2 Machine learning
-\item
-  2.3 Graph neural networks
-\item
-  2.4 Graph parameters
-\item
-  3. Experimental study
-\item
-  3.1 Experimental setup
-\item
-  3.2. Results
-\item
-  3.3. Discussion
-\item
-  6. Conclusion
-\item
-  7. References
-\item
-  9. Appendix
+\subsubsection{Generalization error of MPNN model}
 
-\end{itemize}
+\subsubsection{Corrolation analysis between generalization error and graph parameters}
+
+\subsection{Discussion}
+
+\section{Conclusion}
 
@@
 
-\subsection*{Example of GCN model}
+\subsection{Basic information about TUDataset}\label{sec:datasets}
+This table~\ref{tab:datasets} shows the information about a list of datasets used in this thesis.
+
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|}
+    \hline
+        name & Graphs & Classes & Avg. Nodes & Avg. Edges & catagory \\ \hline
+        AIDS & 2000 & 2 & 15.69 & 16.20 & Small molecules \\ \hline
+        BZR & 405 & 2 & 35.75 & 38.36 & Small molecules \\ \hline
+        BZR\_MD & 306 & 2 & 21.30 & 225.06 & Small molecules \\ \hline
+        COX2 & 467 & 2 & 41.22 & 43.45 & Small molecules \\ \hline
+        COX2\_MD & 303 & 2 & 26.28 & 335.12 & Small molecules \\ \hline
+        DHFR & 756 & 2 & 42.43 & 44.54 & Small molecules \\ \hline
+        DHFR\_MD & 393 & 2 & 23.87 & 283.02 & Small molecules \\ \hline
+        ER\_MD & 446 & 2 & 21.33 & 234.85 & Small molecules \\ \hline
+        FRANKENSTEIN & 4337 & 2 & 16.90 & 17.88 & Small molecules \\ \hline
+        MCF-7 & 27770 & 2 & 26.40 & 28.53 & Small molecules \\ \hline
+        MCF-7H & 27770 & 2 & 47.31 & 49.44 & Small molecules \\ \hline
+        MOLT-4 & 39765 & 2 & 26.10 & 28.14 & Small molecules \\ \hline
+        MOLT-4H & 39765 & 2 & 46.70 & 48.74 & Small molecules \\ \hline
+        Mutagenicity & 4337 & 2 & 30.32 & 30.77 & Small molecules \\ \hline
+        MUTAG & 188 & 2 & 17.93 & 19.79 & Small molecules \\ \hline
+        NCI1 & 4110 & 2 & 29.87 & 32.30 & Small molecules \\ \hline
+        NCI109 & 4127 & 2 & 29.68 & 32.13 & Small molecules \\ \hline
+        NCI-H23 & 40353 & 2 & 26.07 & 28.10 & Small molecules \\ \hline
+        NCI-H23H & 40353 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
+        OVCAR-8 & 40516 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
+        OVCAR-8H & 40516 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
+        P388 & 41472 & 2 & 22.11 & 23.56 & Small molecules \\ \hline
+        P388H & 41472 & 2 & 40.45 & 41.89 & Small molecules \\ \hline
+        PC-3 & 27509 & 2 & 26.36 & 28.49 & Small molecules \\ \hline
+        PC-3H & 27509 & 2 & 47.20 & 49.33 & Small molecules \\ \hline
+        PTC\_FM & 349 & 2 & 14.11 & 14.48 & Small molecules \\ \hline
+        PTC\_FR & 351 & 2 & 14.56 & 15.00 & Small molecules \\ \hline
+        PTC\_MM & 336 & 2 & 13.97 & 14.32 & Small molecules \\ \hline
+        PTC\_MR & 344 & 2 & 14.29 & 14.69 & Small molecules \\ \hline
+        SF-295 & 40271 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
+        SF-295H & 40271 & 2 & 46.65 & 48.68 & Small molecules \\ \hline
+        SN12C & 40004 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
+        SN12CH & 40004 & 2 & 46.69 & 48.72 & Small molecules \\ \hline
+        SW-620 & 40532 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
+        SW-620H & 40532 & 2 & 46.63 & 48.66 & Small molecules \\ \hline
+        UACC257 & 39988 & 2 & 26.09 & 28.13 & Small molecules \\ \hline
+        UACC257H & 39988 & 2 & 46.68 & 48.71 & Small molecules \\ \hline
+        Yeast & 79601 & 2 & 21.54 & 22.84 & Small molecules \\ \hline
+        YeastH & 79601 & 2 & 39.45 & 40.75 & Small molecules \\ \hline
+        DD & 1178 & 2 & 284.32 & 715.66 & Bioinformatics \\ \hline
+        ENZYMES & 600 & 6 & 32.63 & 62.14 & Bioinformatics \\ \hline
+        KKI & 83 & 2 & 26.96 & 48.42 & Bioinformatics \\ \hline
+        OHSU & 79 & 2 & 82.01 & 199.66 & Bioinformatics \\ \hline
+        Peking\_1 & 85 & 2 & 39.31 & 77.35 & Bioinformatics \\ \hline
+        PROTEINS\_full & 1113 & 2 & 39.06 & 72.82 & Bioinformatics \\ \hline
+        COIL-DEL & 3900 & 100 & 21.54 & 54.24 & Computer vision \\ \hline
+        COIL-RAG & 3900 & 100 & 3.01 & 3.02 & Computer vision \\ \hline
+        Cuneiform & 267 & 30 & 21.27 & 44.80 & Computer vision \\ \hline
+        Fingerprint & 2149 & 15 & 7.06 & 5.76 & Computer vision \\ \hline
+        FIRSTMM\_DB & 41 & 11 & 1377.27 & 3074.10 & Computer vision \\ \hline
+        Letter-high & 2250 & 15 & 4.67 & 4.50 & Computer vision \\ \hline
+        Letter-low & 2250 & 15 & 4.68 & 3.13 & Computer vision \\ \hline
+        Letter-med & 2250 & 15 & 4.67 & 3.21 & Computer vision \\ \hline
+        MSRC\_9 & 221 & 8 & 40.58 & 97.94 & Computer vision \\ \hline
+        MSRC\_21 & 563 & 20 & 77.52 & 198.32 & Computer vision \\ \hline
+        MSRC\_21C & 209 & 20 & 40.28 & 96.60 & Computer vision \\ \hline
+        COLORS-3 & 10500 & 11 & 61.31 & 91.03 & Synthetic \\ \hline
+        SYNTHETIC & 300 & 2 & 100.00 & 196.00 & Synthetic \\ \hline
+        SYNTHETICnew & 300 & 2 & 100.00 & 196.25 & Synthetic \\ \hline
+        Synthie & 400 & 4 & 95.00 & 172.93 & Synthetic \\ \hline
+    \end{tabular}
+    \caption{Basic information about the datasets used in the experiment}
+    \label{tab:datasets}
+\end{table}
+
+\subsection{Example of GCN model}
 
@@
 import torch
-from torch import nn
-import torch.nn.functional as F
-from torch_geometric.nn import GCNConv
-from torch_geometric.nn import global_mean_pool
-
-class GCN(torch.nn.Module):
-    def __init__(self, in_channels, hidden_channels, out_channels):
-        super().__init__()
-        self.conv1 = GCNConv(in_channels, hidden_channels)
-        self.conv2 = GCNConv(hidden_channels, hidden_channels)
-        self.conv3 = GCNConv(hidden_channels, hidden_channels)
-        self.conv4 = GCNConv(hidden_channels, hidden_channels)
-        self.fc1 = nn.Linear(hidden_channels, hidden_channels)
-        self.fc2 = nn.Linear(hidden_channels, out_channels)
-
-    def forward(self, x, edge_index, batch, edge_weight=None):
-        x = self.conv1(x, edge_index, edge_weight).relu()
-        x = self.conv2(x, edge_index, edge_weight).relu()
-        x = self.conv3(x, edge_index, edge_weight).relu()
-        x = self.conv4(x, edge_index, edge_weight).relu()
-        x = global_mean_pool(x, batch)
-        x = self.fc1(x).relu()
-        x = self.fc2(x)
-        return x
-
-    def reset_parameters(self):
-        for (_, module) in self._modules.items():
-            module.reset_parameters()
 

### 2025-01-14 src/main.py
Refactor hyperparameter file handling to support dynamic project names and update generalization error logging

@@ -39,7 +39,8 @@ else:
 
 
 def calculate_generalation_error():
-    path = osp.join(osp.dirname(__file__), 'results', 'best_hyperparameters.csv')
+    project_name = 'bt_SGC'
+    path = osp.join(osp.dirname(__file__), 'results', 'best_hyperparameters_{project_name}.csv')
     best_hyperparameters = pd.read_csv(path)
     
     for i in range(len(best_hyperparameters)):
@@ -60,6 +61,8 @@ def calculate_generalation_error():
 
         if model_name == 'bt_GCN':
             model_name = 'GCN'
+        if model_name == 'bt_SGC':
+            model_name = 'GCN'
 
         trainParams = TrainParams(hidden_size=hidden_size, num_hidden_layers=num_hidden_layers, batch_size=batch_size,
                                     learning_rate=learning_rate, patience_earlystopping=default_patience, patience_plateau=patience_plateau, normlization=normlization)
@@ -73,7 +76,7 @@ def calculate_generalation_error():
             'Ave. generalization error': [generalization_error],
             'Standard deviation': [standard_deviation]
         })
-        df.to_csv('results/generalization_error.csv', mode='a')
+        df.to_csv(f'results/generalization_error_{project_name}.csv', mode='a')
 
 
 def calcualte_parameters():
@@ -286,7 +289,7 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
         ]
 
     # save the best hyperparameters to csv, and print the table, do not replace the existing file
-    df_hyperparameters.to_csv('results/best_hyperparameters.csv', mode='a')
+    df_hyperparameters.to_csv(f'results/best_hyperparameters_{project_name}.csv', mode='a')
     print(tabulate(df_hyperparameters, headers='keys', tablefmt='psql'))
 
 
@@ -355,7 +358,8 @@ def handle_option(option):
     elif option == '4' or option == 'get_correlation':
         get_correlation()
     elif option == '5' or option == 'get_hyperparameters':
-        get_best_hyperparameters()
+        project_name = input('Enter the project name: ')
+        get_best_hyperparameters(project_name)
     elif option == '6' or option == 'sum_the_parameters':
         sum_the_parameters()
     else:

### 2025-01-14 src/main.py
Fix string formatting in file path for best hyperparameters in calculate_generalation_error function

@@ -40,7 +40,7 @@ else:
 
 def calculate_generalation_error():
     project_name = 'bt_SGC'
-    path = osp.join(osp.dirname(__file__), 'results', 'best_hyperparameters_{project_name}.csv')
+    path = osp.join(osp.dirname(__file__), 'results', f'best_hyperparameters_{project_name}.csv')
     best_hyperparameters = pd.read_csv(path)
     
     for i in range(len(best_hyperparameters)):

### 2025-01-17 thesis/main.tex
udpate thesis

@@
 The model is then evaluated on a test dataset, which is separate from the training dataset.
+
+\subsubsection{Gradient Descent}
+Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
+The algorithm works by computing the gradient of the function at a given point and then updating the point in the direction of the negative gradient.
+The update rule is given by
+
+$$
+    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t)
+$$
+where $\theta_t$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(\theta_t)$ is the gradient of the function $f$ at $\theta_t$.
+The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
+
+\subsubsection{Stochastic Gradient Descent}
+Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
+The algorithm works by randomly selecting a mini-batch of data points from the training dataset, computing the gradient of the loss function with respect to the mini-batch, and then updating the parameters based on the gradient.
+The update rule is given by
+
+$$
+    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t; x_{i:t}, y_{i:t})
+$$
+where $x_{i:t}$ and $y_{i:t}$ are the mini-batch of data points and labels, respectively. The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
+
+\subsubsection{Backpropagation}
+Backpropagation is an algorithm used to compute the gradients of the loss function with respect to the parameters of a neural network.
+The algorithm works by computing the gradient of the loss function with respect to the output of the network and then propagating the gradient backward through the network to compute the gradients of the loss function with respect to the parameters.
+The gradients are then used to update the parameters of the network using an optimization algorithm such as gradient descent.
+
+\subsubsection{Regularization}
+Regularization is a technique used to prevent overfitting in machine learning models.
+Overfitting occurs when a model learns the noise in the training data rather than the underlying pattern.
+Regularization works by adding a penalty term to the loss function that discourages the model from learning complex patterns that are specific to the training data.
+There are two common types of regularization: $L1$ regularization and $L2$ regularization.
+$L1$ regularization adds a penalty term that is proportional to the $L1$ norm of the parameters, while $L2$ regularization adds a penalty term that is proportional to the $L2$ norm of the parameters.
+The regularization parameter $\lambda$ controls the strength of the regularization.
+
+\subsubsection{Early Stopping}
+Early stopping is a technique used to prevent overfitting in machine learning models.
+The idea is to monitor the performance of the model on a validation dataset during training and stop training when the performance starts to degrade.
+This is done by saving the model parameters at each iteration and selecting the model with the best performance on the validation dataset.
+Early stopping is a form of regularization that prevents the model from learning the noise in the training data.
+
+\subsubsection{Cross-validation}
+Cross-validation is a technique used to evaluate the performance of a machine learning model.
+The idea is to split the dataset into multiple subsets, or folds, and train the model on one subset while evaluating it on the remaining subsets.
+This process is repeated multiple times, with each subset used as the test set once.
+The performance of the model is then averaged over all the folds to obtain an estimate of the model's generalization performance.
+Cross-validation is used to prevent overfitting and to obtain a more accurate estimate of the model's performance.
+
+\subsubsection{Hyperparameter tuning}
+Hyperparameter tuning is the process of selecting the optimal hyperparameters for a machine learning model.
+Hyperparameters are parameters that are set before the training process begins and control the behavior of the model.
+Examples of hyperparameters include the learning rate, batch size, number of hidden layers, and number of epochs.
+Hyperparameter tuning is typically done using a grid search or random search over a predefined set of hyperparameters.
+The goal is to find the set of hyperparameters that results in the best performance on a validation dataset.
+
+\subsubsection{Loss function}
+The loss function is a function that measures the difference between the predicted output of a model and the true output.
+The goal of training a machine learning model is to minimize the loss function, which is done by adjusting the parameters of the model using an optimization algorithm such as gradient descent.
+The choice of loss function depends on the task at hand.
+For classification tasks, the cross-entropy loss function is commonly used, while for regression tasks, the mean squared error loss function is often used.
+
+\subsubsection{Optimization algorithm}
+An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
+The goal is to find the set of parameters that minimizes the loss function.
+Gradient descent is a common optimization algorithm used in machine learning, but there are many variants of gradient descent that are designed to improve convergence speed and stability.
+Some popular optimization algorithms include Adam~\cite{kingma2014adam}, RMSprop~\cite{graves2013generating}, and Adagrad~\cite{duchi2011adaptive}.
+These algorithms use different strategies to update the parameters of the model and can be more effective than standard gradient descent in certain situations.
 
@@
 \subsubsection{Generalization error of SGC model}
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{|l|l|l|}
+    \hline
+        Name & Ave. generalization error & Standard deviation \\ \hline
+        PROTEINS\_full & 0.04741409420967102 & 0.5624663829803467 \\ \hline
+        DD & -0.21720178425312042 & 0.40132829546928406 \\ \hline
+        ENZYMES & 0.3279166519641876 & 0.060605552047491074 \\ \hline
+        KKI & 0.10951493680477142 & 0.24877962470054626 \\ \hline
+        OHSU & 0.07604396343231201 & 0.1943538784980774 \\ \hline
+        Peking\_1 & 0.1769927442073822 & 0.22724425792694092 \\ \hline
+        COLORS-3 & 0.11781251430511475 & 0.04669201001524925 \\ \hline
+        SYNTHETIC & -0.37541666626930237 & 0.4494529068470001 \\ \hline
+        SYNTHETICnew & -0.36666664481163025 & 0.46157106757164 \\ \hline
+        Synthie & 0.13749998807907104 & 0.042466290295124054 \\ \hline
+        AIDS & 0.006437480449676514 & 0.011520843021571636 \\ \hline
+        BZR & 0.10815385729074478 & 0.21917256712913513 \\ \hline
+        BZR\_MD & 0.1678861677646637 & 0.09830881655216217 \\ \hline
+        COX2 & 0.07495072484016418 & 0.13212721049785614 \\ \hline
+        COX2\_MD & 0.14868313074111938 & 0.16540752351284027 \\ \hline
+        DHFR & 0.1332409381866455 & 0.1551705300807953 \\ \hline
+        DHFR\_MD & 0.0777045264840126 & 0.2503173351287842 \\ \hline
+        ER\_MD & -0.008367183618247509 & 0.15631815791130066 \\ \hline
+        FRANKENSTEIN & 0.10787498950958252 & 0.05383045971393585 \\ \hline
+        MCF-7 & 0.35490626096725464 & 0.17573890089988708 \\ \hline
+        MCF-7H & 0.3593124747276306 & 0.1884346306324005 \\ \hline
+        MOLT-4 & 0.18021871149539948 & 0.39803561568260193 \\ \hline
+        MOLT-4H & 0.18649999797344208 & 0.3838197886943817 \\ \hline
+        Mutagenicity & 0.04325000196695328 & 0.028246337547898293 \\ \hline
+        MUTAG & 0.07375730574131012 & 0.13988283276557922 \\ \hline
+        NCI1 & 0.09100000560283661 & 0.16161812841892242 \\ \hline
+        NCI109 & -0.06128125637769699 & 0.2943810522556305 \\ \hline
+        NCI-H23 & 0.31696873903274536 & 0.07884199917316437 \\ \hline
+        NCI-H23H & 0.3696562349796295 & 0.06490368396043777 \\ \hline
+        OVCAR-8 & 0.3291874825954437 & 0.0815950483083725 \\ \hline
+        OVCAR-8H & 0.2902187705039978 & 0.0771569237112999 \\ \hline
+        P388 & 0.3618437647819519 & 0.13428252935409546 \\ \hline
+        P388H & -0.052218757569789886 & 0.3646376132965088 \\ \hline
+        PC-3 & -0.08028124272823334 & 0.29225972294807434 \\ \hline
+        PC-3H & 0.2593437135219574 & 0.22314861416816711 \\ \hline
+        PTC\_FM & 0.10863511264324188 & 0.14730817079544067 \\ \hline
+        PTC\_FR & 0.08632432669401169 & 0.09645862877368927 \\ \hline
+        PTC\_MM & 0.09649830311536789 & 0.0817335695028305 \\ \hline
+        PTC\_MR & 0.060720354318618774 & 0.18291200697422028 \\ \hline
+        SF-295 & 0.3124375343322754 & 0.11770480871200562 \\ \hline
+        SF-295H & 0.28881245851516724 & 0.12331245839595795 \\ \hline
+        SN12C & 0.2917812764644623 & 0.05537300556898117 \\ \hline
+        SN12CH & 0.3397812247276306 & 0.09572991728782654 \\ \hline
+        SW-620 & 0.3427812457084656 & 0.2430398166179657 \\ \hline
+        SW-620H & 0.39274999499320984 & 0.1998475342988968 \\ \hline
+        UACC257 & -0.10218751430511475 & 0.2883416414260864 \\ \hline
+        UACC257H & 0.3322499692440033 & 0.22775331139564514 \\ \hline
+        Yeast & 0.0 & 0.0 \\ \hline
+        YeastH & 0.0 & 0.0 \\ \hline
+    \end{tabular}
+\end{table}
 

### 2025-01-17 src/net.py
Enhance MPNN model initialization to support customizable MLP hidden dimension

@@ -142,20 +142,20 @@ class SGC(nn.Module):
 
 
 class MPNN(nn.Module):
-    def __init__(self, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int, norm: str = 'batch'):
+    def __init__(self, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int, norm: str = 'batch', mlp_hidden_dim: int = 32):
         super().__init__()
         self.nn1 = nn.Sequential(
-            nn.Linear(1, 32),
+            nn.Linear(1, mlp_hidden_dim),
             nn.ReLU(),
-            nn.Linear(32, in_channels * hidden_channels)
+            nn.Linear(mlp_hidden_dim, in_channels * hidden_channels)
         )
         self.conv1 = NNConv(in_channels, hidden_channels, self.nn1)
         self.convs = nn.ModuleList([
             NNConv(hidden_channels, hidden_channels,
                 nn.Sequential(
-                    nn.Linear(1, 32),
+                    nn.Linear(1, mlp_hidden_dim),
                     nn.ReLU(),
-                    nn.Linear(32, hidden_channels * hidden_channels)
+                    nn.Linear(mlp_hidden_dim, hidden_channels * hidden_channels)
                 ))
             for _ in range(num_hidden_layers)
         ])
@@ -189,9 +189,9 @@ class MPNN(nn.Module):
         self.fc2.reset_parameters()
 
 
-def get_model(model_name: str, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int = 4, norm: str = 'batch', heads: int = 1, concat: bool = True, dropout: float = 0, residual: bool = False):
+def get_model(model_name: str, in_channels: int, hidden_channels: int, out_channels: int, num_hidden_layers: int = 4, norm: str = 'batch', heads: int = 1, concat: bool = True, dropout: float = 0, residual: bool = False, mlp_hidden_dim = 32):
     if model_name == 'MPNN':
-        return MPNN(in_channels, hidden_channels, out_channels, num_hidden_layers, norm)
+        return MPNN(in_channels, hidden_channels, out_channels, num_hidden_layers, norm, mlp_hidden_dim)
     elif model_name == 'GCN':
         return GCN(in_channels, hidden_channels, out_channels, num_hidden_layers, norm)
     elif model_name == 'GAT':

### 2025-01-17 src/run.py
Update default project name in argument parser to 'bt_MPNN'

@@ -7,7 +7,7 @@ import argparse
 
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-p", "--project_name", help="project name", default='bt_GATv2')
+parser.add_argument("-p", "--project_name", help="project name", default='bt_MPNN')
 parser.add_argument("-i", "--sweep_id", help="sweep id")
 args = parser.parse_args()
 

### 2025-01-17 src/utils.py
Add mlp_hidden_dim parameter for MPNN and update sweep configuration

@@ -58,9 +58,10 @@ class TrainParams:
     patience_plateau: int
     normlization: str
     learning_rate: float
-    heads: Optional[int] = None
-    dropout: Optional[float] = None
-    residual: Optional[bool] = None
+    heads: Optional[int] = None # for GATv2
+    dropout: Optional[float] = None # for GATv2
+    residual: Optional[bool] = None # for GATv2
+    mlp_hidden_dim: Optional[int] = None # for MPNN
 
 
 def plot_training_results(dataset_name: str, train_accs, val_accs, train_losses, 
@@ -428,6 +429,7 @@ def setup_wandb_sweep(project_name: str = 'bt', dataset_name: str = 'DD', temp=F
     
     if project_name == 'bt_MPNN':
         sweep_config['parameters']['model_name'] = { 'value': 'MPNN' }
+        sweep_config['parameters']['mlp_hidden_dim'] = { 'values': [16, 32, 64] }
 
     sweep_id = wandb.sweep(sweep_config, project=project_name)
     return sweep_id

### 2025-01-17 src/train.py
Add support for customizable MLP hidden dimension in MPNN training procedure

@@ -34,6 +34,16 @@ def train_procedure(dataset_name: str,  model_name: str, trainParams, is_wandb=F
             dropout=trainParams.dropout,
             residual=trainParams.residual
         ).to(device)
+    elif model_name == 'MPNN':
+        model = get_model(
+            model_name=model_name,
+            in_channels=dataset.num_features,
+            hidden_channels=trainParams.hidden_size,
+            out_channels=dataset.num_classes,
+            num_hidden_layers=trainParams.num_hidden_layers,
+            norm=trainParams.normlization,
+            mlp_hidden_dim=trainParams.mlp_hidden_dim
+        ).to(device)
     else:
         model = get_model(
             model_name=model_name,      
@@ -221,6 +231,8 @@ def hyperparameter_tuning(config=None):
             trainParams.heads = config.heads
             trainParams.dropout = config.dropout
             trainParams.residual = config.residual
+        if config.model_name == 'MPNN':
+            trainParams.mlp_hidden_dim = config.mlp_hidden_dim
 
         # trainParams = {
         #     'hidden_size': config.hidden_size,

### 2025-01-17 src/setup_sweep.py
Update project name in setup_sweep.py to 'bt_MPNN'

@@ -11,7 +11,7 @@ args = parser.parse_args()
 
 print(f'Temporary flag: {args.temporory}')
 
-project_name = 'bt_GATv2'
+project_name = 'bt_MPNN'
 path = osp.join(osp.dirname(__file__), '..', 'data', 'test_dataset.txt')
 dataset_list = read_file_to_list(path)
 

### 2025-01-20 thesis/main.tex
Add new references to main.bib for pattern recognition and graph neural networks

@@
 \section{Background on learning on graphs}
-The following sections provide an overview of the concepts and methods related to graph learning, machine learning, and graph neural networks.
+The following sections provide an overview of the concepts and methods related to graph theory, machine learning, and graph neural networks.
 
@@
 \subsection{Machine learning}
-Machine learning is a subfield of artificial intelligence that focuses on the development of algorithms that can learn from and make predictions or decisions based on data.
-The goal of machine learning is to develop models that can generalize well to unseen data.
-The model is trained on a training dataset, which consists of input-output pairs.
-The model is then evaluated on a test dataset, which is separate from the training dataset.
+In the following section, we provide an overview of the concepts and methods related to machine learning.
+
+\subsubsection{Supervised learning}
+Machine learning can be roughly divided into three categories: supervised learning, unsupervised learning, and reinforcement learning~\cite{bishop2006pattern}.
+
+Supervised learning is a type of machine learning that involves training a model on a labeled dataset.
+The model is trained to learn the relationship between the input features and the output labels.
+The goal is to learn a mapping from the input features to the output labels so that the model can make predictions on new, unseen data.
+One common task in supervised learning is classification, where the goal is to assign each input vector to one of a finite number of classes (categories).
+In the graph learning context, the predicted output can be a label for each node in the graph, a label for the entire graph, or a label for each edge in the graph, e.g.
+node classification, graph classification, and link prediction~\cite{velivckovic2023everything}.
+
+\subsubsection{Feed-forward neural networks}
+
+Feed-forward neural networks, also known as multilayer perceptrons (MLPs), are a type of neural network that consists of multiple layers of neurons.
+The neurons in each layer are connected to the neurons in the next layer, and the output of each neuron is computed as a weighted sum of the inputs followed by a non-linear activation function.
+The output of the network is computed by passing the input through the network and computing the output of the final layer.
+The weights of the network are learned using an optimization algorithm such as gradient descent.
+Feed-forward neural networks are a powerful tool for learning complex patterns in data and have been successfully applied to a wide range of tasks, such as image recognition, speech recognition, and natural language processing.
+
+The function of a feed-forward neural network can be written as
+
+$$ 
+    y = f(W^{(L)} \cdot f(W^{(L-1)} \cdot \ldots \cdot f(W^{(1)} \cdot x + b^{(1)}) + b^{(2)}) + \ldots + b^{(L)})
+$$
+
+where $x$ is the input vector, $W^{(i)}$ and $b^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function. The output $y$ is the predicted output of the network.
+
+\subsubsection{Loss function}
+The loss function is a function that measures the difference between the predicted output of a model and the true output.
+The goal of training a machine learning model is to minimize the loss function, which is done by adjusting the parameters of the model using an optimization algorithm such as gradient descent.
+The choice of loss function depends on the task at hand.
+For classification tasks, the cross-entropy loss function is commonly used, while for regression tasks, the mean squared error loss function is often used.
+
+The cross-entropy loss function is defined as
+
+$$
+    L(y, \hat{y}) = -\sum_{i} y_i \log(\hat{y}_i)
+$$
+
+where $y$ is the true output, $\hat{y}$ is the predicted output, and $i$ is the index of the classes.
+The cross-entropy loss function is used to measure the difference between the true output and the predicted output of a classification model.
+
+\subsubsection{Activation function}
+An activation function is a non-linear function that is applied to the output of a neuron in a neural network.
+The activation function introduces non-linearity into the network, allowing it to learn complex patterns in the data.
+There are many activation functions that can be used in neural networks, such as the sigmoid function, the tanh function, and the ReLU function.
+The ReLU function is one of the most commonly used activation functions in deep learning because it is simple and computationally efficient.
+The ReLU function is defined as
+
+$$
+    \text{ReLU}(\cdot)=\max(0,\cdot)
+$$
+
+The ReLU function is used to introduce non-linearity into the network and has been shown to be effective in training deep neural networks.
 
@@
 $$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t)
+    W^{(t+1)} = W^{(t)} - \alpha \nabla f(W^{(t)})
 $$
-where $\theta_t$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(\theta_t)$ is the gradient of the function $f$ at $\theta_t$.
+where $W^{(t)}$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(W^{(t)})$ is the gradient of the function $f$ with respect to the parameters $W^{(t)}$.
 The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
+Gradient descent is a popular optimization algorithm used in machine learning to train neural networks and other models.
 
@@
 $$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t; x_{i:t}, y_{i:t})
+    W^{(t+1)} = W^{(t)} - \alpha \nabla f(W^{(t)}, x^{(t)})
 $$
-where $x_{i:t}$ and $y_{i:t}$ are the mini-batch of data points and labels, respectively. The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Backpropagation}
-Backpropagation is an algorithm used to compute the gradients of the loss function with respect to the parameters of a neural network.
-The algorithm works by computing the gradient of the loss function with respect to the output of the network and then propagating the gradient backward through the network to compute the gradients of the loss function with respect to the parameters.
-The gradients are then used to update the parameters of the network using an optimization algorithm such as gradient descent.
-
-\subsubsection{Regularization}
-Regularization is a technique used to prevent overfitting in machine learning models.
-Overfitting occurs when a model learns the noise in the training data rather than the underlying pattern.
-Regularization works by adding a penalty term to the loss function that discourages the model from learning complex patterns that are specific to the training data.
-There are two common types of regularization: $L1$ regularization and $L2$ regularization.
-$L1$ regularization adds a penalty term that is proportional to the $L1$ norm of the parameters, while $L2$ regularization adds a penalty term that is proportional to the $L2$ norm of the parameters.
-The regularization parameter $\lambda$ controls the strength of the regularization.
+where $x^{(t)}$ is a mini-batch of data points from the training dataset.
+Stochastic gradient descent is more computationally efficient than standard gradient descent and can be used to train large-scale machine learning models.
 
@@
 The idea is to monitor the performance of the model on a validation dataset during training and stop training when the performance starts to degrade.
-This is done by saving the model parameters at each iteration and selecting the model with the best performance on the validation dataset.
-Early stopping is a form of regularization that prevents the model from learning the noise in the training data.
+This is done by keeping track of the validation loss and stopping training when the validation loss stops decreasing or starts to increase.
+Early stopping is used to prevent the model from memorizing the training data and to obtain a more generalizable model.
 
@@
 Examples of hyperparameters include the learning rate, batch size, number of hidden layers, and number of epochs.
-Hyperparameter tuning is typically done using a grid search or random search over a predefined set of hyperparameters.
-The goal is to find the set of hyperparameters that results in the best performance on a validation dataset.
+Hyperparameter tuning is an important step in the machine learning pipeline and can have a significant impact on the performance of the model.
+There are many techniques for hyperparameter tuning, such as grid search, random search, and Bayesian optimization.
+In this thesis, Bayesian optimization is used to tune the hyperparameters of the models.
 
-\subsubsection{Loss function}
-The loss function is a function that measures the difference between the predicted output of a model and the true output.
-The goal of training a machine learning model is to minimize the loss function, which is done by adjusting the parameters of the model using an optimization algorithm such as gradient descent.
-The choice of loss function depends on the task at hand.
-For classification tasks, the cross-entropy loss function is commonly used, while for regression tasks, the mean squared error loss function is often used.
+Bayesian optimization is more efficient than grid search and random search because it uses a probabilistic model to guide the search for the optimal hyperparameters.
+The idea is to model the objective function (e.g.
+the validation accuracy of the model) as a Gaussian process and use the model to select the next set of hyperparameters to evaluate.
+This process is repeated until the optimal hyperparameters are found.
 
@@
 
-\subsection{Graph parameters}
+In the following sections, we provide an overview of the methods related to this thesis.
+
+\subsubsection{Graph Convolutional Networks (GCN)}
+
+Graph Convolutional Networks (GCNs) are a class of neural networks that can operate on graph-structured data.
+The GCN model $f(X, A)$, as proposed by Kipf and Welling~\cite{kipf2016semi}, is defined as
+
+$$ 
+ H^{(l+1)} = \sigma(\tilde{D}^{-\frac{1}{2}}\tilde{A}\tilde{D}^{-\frac{1}{2}}H^{(l)}W^{(l)})
+$$
+
+where $H^{(l)}\in \mathbb{R}^{N\times D}$ is the node feature matrix at layer $l$; $H^{(0)} = X$.
+$\tilde{A} = A + I$ is the adjacency matrix of the graph with self-connections added, $\tilde{D}$ is the degree matrix of $\tilde{A}$, $W^{(l)}$ is the weight matrix of the layer, and $\sigma$ is the activation function, such as the $\text{ReLU}(\cdot)=\max(0,\cdot)$.
+The GCN layer aggregates information from neighboring nodes and updates the node features by applying a linear transformation followed by a non-linear activation function.
+The output of the GCN layer is the node feature matrix at the next layer.
+The GCN layer can be stacked to create deep GCN models, which have been shown to be effective in a wide range of tasks, such as node classification, edge prediction, and graph classification.
+
+\subsubsection{Simplified Graph Convolution (SGC)}
+
+Simplified Graph Convolution (SGC)~\cite{wu2019simplifying} is a simplified version of the GCN model that removes the non-linear activation function and the normalization of the adjacency matrix.
+The SGC model is defined as
+
+$$
+ X' = (\tilde{D}^{-\frac{1}{2}}\tilde{A}\tilde{D}^{-\frac{1}{2}})^K XW
+$$
+
+where $X$ is the node feature matrix, $W$ is the weight matrix, $\tilde{A}$ is the adjacency matrix with self-connections added, $\tilde{D}$ is the degree matrix of $\tilde{A}$, and $K$ is the number of layers.
+
+\subsubsection{Graph Attention Networks (GAT)}
+
+Graph Attention Networks (GAT)~\cite{velickovic2020pointer} are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes. The GAT model is defined as
+
+$$
+    h_i^{(l+1)} = \sigma(\sum_{j\in N(i)}\alpha_{ij}^{(l)}W^{(l)}h_j^{(l)})
+$$
+
+where $h_i^{(l)}$ is the node feature vector of node $i$ at layer $l$, $W^{(l)}$ is the weight matrix of the layer, $\sigma$ is the activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between node $i$ and node $j$ at layer $l$.
+The attention coefficient is computed as
+
+\subsubsection{Message Passing Neural Networks (MPNN)}
+Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} has been the leading model for graph learning. The MPNN model is defined as
+
+$$
+    m_i^{(t+1)} = \sum_{j\in N(i)}M^{(t)}(h_i^{(t)}, h_j^{(t)}, e_{ij})
+$$
+
+where $m_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is the message function, $h_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
+The message function $M^{(t)}$ is a neural network that takes as input the node feature vectors of node $i$ and node $j$, and the edge feature vector between them, and outputs the message vector $m_i^{(t)}$.
+
+\subsection{Graph parameters} \label{sec:graph_parameters}
 Now we can introduce the concept of a graph parameter.
@@
 
-\subsubsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
-As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.
+\subsubsection{Graph Parameters Under Investigation}
+As graph parameters defined abstractly in the section~\ref{sec:graph_parameters}, I give here the concrete definition of the graph parameters that are used in the experiment.
+The graph parameters are calculated for each dataset and used as input features for the model.
+The graph parameters are calculated using the NetworkX library~\cite{hagberg2008exploring}.
 

### 2025-01-20 src/main.py
Refactor calculate_generalation_error function to accept a file path parameter and update CSV writing logic

@@ -38,13 +38,13 @@ else:
     DATAPATH = 'data/test_dataset.txt'
 
 
-def calculate_generalation_error():
-    project_name = 'bt_SGC'
-    path = osp.join(osp.dirname(__file__), 'results', f'best_hyperparameters_{project_name}.csv')
-    best_hyperparameters = pd.read_csv(path)
+def calculate_generalation_error(file_path: str):
+    if file_path is None:
+        project_name = 'bt_SGC'
+        file_path = osp.join(osp.dirname(__file__), 'results', f'best_hyperparameters_{project_name}.csv')
+    best_hyperparameters = pd.read_csv(file_path)
     
     for i in range(len(best_hyperparameters)):
-        
         dataset_name = best_hyperparameters.loc[i, 'dataset_name']
         model_name = best_hyperparameters.loc[i, 'model_name']
         batch_size = best_hyperparameters.loc[i, 'batch_size'].item()
@@ -76,7 +76,7 @@ def calculate_generalation_error():
             'Ave. generalization error': [generalization_error],
             'Standard deviation': [standard_deviation]
         })
-        df.to_csv(f'results/generalization_error_{project_name}.csv', mode='a')
+        df.to_csv(f'results/generalization_error_{project_name}.csv', mode='a', header=not os.path.exists(f'results/generalization_error_{project_name}.csv'))
 
 
 def calcualte_parameters():
@@ -371,9 +371,10 @@ def handle_option(option):
 
 
 if __name__ == '__main__':
-    # Set default as interactive mode, user can choose the option
-    # Otherwise, use args to run the specific function
-    if args.function:
-        handle_option(args.function)
-    else:
-        interactive_mode()
+    # # Set default as interactive mode, user can choose the option
+    # # Otherwise, use args to run the specific function
+    # if args.function:
+    #     handle_option(args.function)
+    # else:
+    #     interactive_mode()
+    get_best_hyperparameters()

### 2025-01-25 thesis/main.tex
Add new references to main.bib for generalization in neural networks

@@
 Graph learning became a hot topic in the field of machine learning in recent years.
-Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
+Graph Neural Networks (GNNs)~\cite{gori2005new}, also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
 GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
@@
 \subsection{Related work}
-The following section provides an overview of the related work.
+In the following section, I provide an overview of the related work on the generalization of neural networks, including feed-forward neural networks, recurrent neural networks, and graph neural networks.
 
-\subsubsection{Graph parameters}
+\subsubsection{Graph Neural Networks}
+Graph neural networks were initially proposed by Gori et al.~\cite{gori2005new} and Scarselli et al.~\cite{scarselli2008graph} as a variant of recurrent neural networks and demonstrated its generalization capabilities.
+The work of Kipf and Welling~\cite{kipf2016semi} introduced the Graph Convolutional Networks (GCN) model, which received widespread attention from the research community.
+Velickovic et al.~\cite{velickovic2020pointer} proposed the Graph Attention Networks (GAT) model, which uses attention mechanisms to aggregate information from neighboring nodes.
+Brody et al.~\cite{brody2021attentive} proposed the GATv2 model, which improves the performance of the GAT model by introducing residual connections and multi-head attention.
+Gilmer et al.~\cite{gilmer2017neural} introduced the Message Passing Neural Networks (MPNN) model, which demonstrated the significant results on the molecular property prediction benchmark;
 
-\subsubsection{Generalization error}
+\subsubsection{Generalization}
+While significant progress has been made in understanding the generalization properties of feed-forward neural networks (FNNs) and recurrent neural networks (RNNs), the generalization abilities of graph neural networks (GNNs) remain less explored due to their of irregular graph structures.
+
+Golowich et al.~\cite{golowich2018size} showed the generalization abilities of Feed-forward neural networks (FNNs) with Rademacher complexity.
+The work of Zhang et al.~\cite{zhang2018stabilizing} used SVD-based parameterization to improve the generalization by effectively addressing gradient issues.
+
+In terms of Recurrent neural networks(RNNs), Chen et al.~\cite{chen2019generalization} studied the generalization properties of vanilla RNNs as well as their variants.
+Z.
+Allen-Zhu et al.~\cite{allen2019can} demonstrates that vanilla SGD enables RNNs to efficiently learn concept classes and overcomes prior exponential generalization bounds.
+
+But unlike the FNNs and RNNs, GNNs deal with irregular data structures.
+The related work on the generalization of GNNs is limited.
+Scarselli et al.~\cite{scarselli2018vapnik} explored the generalization ability of GNNs by using the Vapnik-Chervonenkis (VC) dimension and further indicated that the generalization ability of such models improve as the number of connected nodes.
+After that, Garg et al.~\cite{garg2020generalization} studied the generalization ability of GNNs via Rademacher bounds.
+In comparison to the work of Scarselli et al., Garg et al.
+provided a tighter bound on the generalization error of GNNs.
+
+Nevertheless, Morris et al.~\cite{morris2024futuredirectionstheorygraph} pointed out that the generalization ability of GNNs is still not well understood.
+The bounds established in these studies typically rely solely on general graph parameters, such as the maximum degree or total number of nodes, often overlooking more expressive graph parameters.
 
@@
 The output of the network is computed by passing the input through the network and computing the output of the final layer.
-The weights of the network are learned using an optimization algorithm such as gradient descent.
+The weights of the network are learned by using an optimization algorithm such as gradient descent.
 Feed-forward neural networks are a powerful tool for learning complex patterns in data and have been successfully applied to a wide range of tasks, such as image recognition, speech recognition, and natural language processing.
@@
 
-where $x$ is the input vector, $W^{(i)}$ and $b^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function. The output $y$ is the predicted output of the network.
+where $x$ is the input vector, $W^{(i)}$ and $b^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function.
+The output $y$ is the predicted output of the network.
+$L$ is denoted as the depth of the network.
 
@@
 \subsubsection{Graph Attention Networks (GAT)}
-
-Graph Attention Networks (GAT)~\cite{velickovic2020pointer} are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes. The GAT model is defined as
+Graph Attention Networks (GAT) are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes.
+The GAT model updates the feature representation of a node by assigning different importance scores, known as attention coefficients, to its neighbors.
+The updated node feature $\mathbf{h}_i^{(l+1)}$ at layer $l+1$ is given by:
 
 $$
-    h_i^{(l+1)} = \sigma(\sum_{j\in N(i)}\alpha_{ij}^{(l)}W^{(l)}h_j^{(l)})
+\mathbf{h}_i^{(l+1)} = \sigma \left( \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l)} \mathbf{W}^{(l)} \mathbf{h}_j^{(l)} \right)
 $$
 
-where $h_i^{(l)}$ is the node feature vector of node $i$ at layer $l$, $W^{(l)}$ is the weight matrix of the layer, $\sigma$ is the activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between node $i$ and node $j$ at layer $l$.
-The attention coefficient is computed as
+where $\mathbf{h}_i^{(l)}$ is the feature vector of node $i$ at layer $l$, $\mathbf{W}^{(l)}$ is a learnable weight matrix, $\sigma$ is an activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between nodes $i$ and $j$.
+These coefficients are computed as:
+
+$$
+\alpha_{ij}^{(l)} = \frac{\exp \left( \text{LeakyReLU} \left( \mathbf{a}^{(l)^\top} [\mathbf{W}^{(l)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l)} \mathbf{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \text{LeakyReLU} \left( \mathbf{a}^{(l)^\top} [\mathbf{W}^{(l)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l)} \mathbf{h}_k^{(l)}] \right) \right)}
+$$
+
+where $\|$ denotes the concatenation of node features, and $\mathbf{a}^{(l)}$ is a shared attention vector. The softmax function ensures the attention coefficients sum to one for a node's neighbors.
+
+GAT is particularly effective for tasks where different neighbors contribute unequally to a node's representation.
+By using attention mechanisms, GAT dynamically weighs neighbor contributions, enabling more expressive feature aggregation compared to earlier methods like GCNs.
+
+\subsubsection{Graph Attention Networks v2 (GATv2)}
+Graph Attention Networks v2 (GATv2)~\cite{brody2021attentive} is an improved version of the GAT model that introduces residual connections and multi-head attention. The GATv2 model is defined as
+
+$$
+    \mathbf{h}_i^{(l+1)} = \sigma \left( \sum_{h=1}^{H} \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l,h)} \mathbf{W}^{(l,h)} \mathbf{h}_j^{(l)} \right) + \mathbf{h}_i^{(l)}
+$$
+
+where $H$ is the number of attention heads, $\alpha_{ij}^{(l,h)}$ is the attention coefficient between nodes $i$ and $j$ for head $h$, and $\mathbf{W}^{(l,h)}$ is the weight matrix for head $h$.
+The attention coefficients are computed as
+
+$$
+    \alpha_{ij}^{(l,h)} = \frac{\exp \left( \text{LeakyReLU} \left( \mathbf{a}^{(l,h)^\top} [\mathbf{W}^{(l,h)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l,h)} \mathbf{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \text{LeakyReLU} \left( \mathbf{a}^{(l,h)^\top} [\mathbf{W}^{(l,h)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l,h)} \mathbf{h}_k^{(l)}] \right) \right)}
+$$
+
+The GATv2 model uses multi-head attention to allow the model to attend to different parts of the input space.
+The model also introduces residual connections to improve the flow of information through the network.
+The GATv2 model has been shown to outperform the original GAT model on a wide range of tasks.
 
 \subsubsection{Message Passing Neural Networks (MPNN)}
-Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} has been the leading model for graph learning. The MPNN model is defined as
+Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} have been the leading model for graph learning.
+The MPNN model operates by iteratively passing messages between nodes and updating their representations.
+At each iteration $t$, the message vector $m_i^{(t+1)}$ for node $i$ is computed as:
 
@@
 
-where $m_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is the message function, $h_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
+where $m_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is a learnable message function (typically implemented as a neural network, such as an MLP), $h_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $h_j^{(t)}$ is the node feature vector of node $j$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
 The message function $M^{(t)}$ is a neural network that takes as input the node feature vectors of node $i$ and node $j$, and the edge feature vector between them, and outputs the message vector $m_i^{(t)}$.

### 2025-01-29 src/main.py
Update get_correlation function to accept model parameter and adjust file paths for results

@@ -1,8 +1,8 @@
 import os
-from train import get_generalization_error_from_a_dataset
+# from train import get_generalization_error_from_a_dataset
 import pandas as pd
 import logging
-from tabulate import tabulate
+# from tabulate import tabulate
 from utils import (
     get_average_degree,
     get_average_shortest_path,
@@ -151,7 +151,7 @@ def compare_generalization_error_and_parameters():
     plt.show()
 
 
-def get_correlation():
+def get_correlation(model: str = 'GCN'):
     '''
     Get the correlation between the generalization error and the parameters
     1. Ave. degree
@@ -169,7 +169,9 @@ def get_correlation():
     Use scatter plot to show the correlation between the generalization error and the parameters
     '''
 
-    df1 = pd.read_csv('results/generalization_error.csv')
+
+
+    df1 = pd.read_csv(f'results/generalization_error_bt_{model}.csv')
     df2 = pd.read_csv('results/parameters.csv')
 
     df_combined = pd.merge(df1, df2, on='Name').drop(columns=['Unnamed: 0'])
@@ -202,7 +204,7 @@ def get_correlation():
     plt.show()
     
     # save the scatter plot to a file
-    plt.savefig('results/correlation.png')
+    plt.savefig(f'results/correlation_{model}.png')
 
     # ignore the dataset with less than 1000 graphs
     # Use the function number_of_graphs to get the number of graphs
@@ -224,7 +226,7 @@ def get_correlation():
     plt.tight_layout()
 
     # save the scatter plot to a file
-    plt.savefig('results/correlation_ignore_less_than_1000.png')
+    plt.savefig(f'results/correlation_ignore_less_than_1000_{model}.png')
 
 
 def interactive_mode():
@@ -377,4 +379,5 @@ if __name__ == '__main__':
     #     handle_option(args.function)
     # else:
     #     interactive_mode()
-    get_best_hyperparameters()
+    model = 'GCN'
+    get_correlation(model)

### 2025-01-29 paper/chapters/background.tex
Add thesis structure including title page, abstract, acknowledgments, conclusion, and related work sections

--- 2025-01-20 thesis/main.tex
@@
-\documentclass{article}
-\usepackage{geometry}
-\geometry{
-    a4paper,
-    left=30mm,
-    right=30mm,
-    top=30mm,
-    bottom=30mm
-}
+% \chapter{Theoretical Background}\label{chap:theoretical background}
 
-\usepackage{annotate-equations}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-% \usepackage{figure}
+% \section{Example citation \& symbol reference}\label{sec:citation}
+% For symbols look at \cite{latex_symbols_2017}.
 
-\graphicspath{ {./media/} }
-\usepackage[square,numbers]{natbib}
-\usepackage[nottoc]{tocbibind}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{enumitem}
-\usepackage{float}
+% \section{Example reference}
+% Example reference: Look at chapter~\ref{chap:introduction}, for sections, look at section~\ref{sec:citation}.
 
-\usepackage{amssymb}
-\usepackage{amsmath}
+% \section{Example image}
 
-\usepackage{tikz}
-\usepackage{listings}
-\usepackage{setspace}
-\definecolor{Code}{rgb}{0,0,0}
-\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
-\definecolor{Numbers}{rgb}{0.5,0,0}
-\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
-\definecolor{Keywords}{rgb}{0,0,1}
-\definecolor{self}{rgb}{0,0,0}
-\definecolor{Strings}{rgb}{0,0.63,0}
-\definecolor{Comments}{rgb}{0,0.63,1}
-\definecolor{Backquotes}{rgb}{0,0,0}
-\definecolor{Classname}{rgb}{0,0,0}
-\definecolor{FunctionName}{rgb}{0,0,0}
-\definecolor{Operators}{rgb}{0,0,0}
-\definecolor{Background}{rgb}{0.98,0.98,0.98}
-\lstdefinelanguage{Python}{
-	numbers=left,
-	numberstyle=\footnotesize,
-	numbersep=1em,
-	xleftmargin=1em,
-	framextopmargin=2em,
-	framexbottommargin=2em,
-	showspaces=false,
-	showtabs=false,
-	showstringspaces=false,
-	frame=l,
-	tabsize=4,
-	% Basic
-	basicstyle=\ttfamily\small\setstretch{1},
-	backgroundcolor=\color{Background},
-	% Comments
-	commentstyle=\color{Comments}\slshape,
-	% Strings
-	stringstyle=\color{Strings},
-	morecomment=[s][\color{Strings}]{"""}{"""},
-	morecomment=[s][\color{Strings}]{'''}{'''},
-	% keywords
-	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
-	keywordstyle={\color{Keywords}\bfseries},
-	% additional keywords
-	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
-	keywordstyle={[2]\color{Decorators}\slshape},
-	emph={self},
-	emphstyle={\color{self}\slshape},
-	%
-}
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{uni-logo}
+% 	\caption{Meaningful caption for this image}
+% 	\label{fig:uniLogo}
+% \end{figure}
 
-\title{\textbf{Bachelor thesis}\\
-Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}
+% Example figure reference: Look at Figure~\ref{fig:uniLogo} to see an image. It can be \texttt{jpg}, \texttt{png}, or best: \texttt{pdf} (if vector graphic).
 
-\author{Author: Wensheng Zhang}
+% \section{Example table}
 
-\date{\today}
+% \begin{table}
+% 	\centering
+% 	\begin{tabular}{lr}
+% 		First column & Number column \\
+% 		\hline
+% 		Accuracy & 0.532 \\
+% 		F1 score & 0.87
+% 	\end{tabular}
+% 	\caption{Meaningful caption for this table}
+% 	\label{tab:result}
+% \end{table}
 
-\begin{document}
+% Table~\ref{tab:result} shows a simple table\footnote{Check \url{https://en.wikibooks.org/wiki/LaTeX/Tables} on syntax}
 
-\maketitle
-
-\begin{abstract}
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
-\end{abstract}
-
-\section{Introduction}\label{sec:intro}
-Graph learning became a hot topic in the field of machine learning in recent years.
-Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
-The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
-This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.
-
-However, the behavior of GNNs is not well understood.
-Particularly, the relationship between graph parameters/characteristics and the empirical generalization error of GNNs is not clear.
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
-
-Speaking more specifically.
-First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree.
-In graph theory, \textit{graph parameter} is used to quantify them.
-And a dataset consists of multiple graphs, each with its graph parameter.
-In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset.
-In this thesis, 57 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
-Second, I train different GNN models on each dataset and find that their generalization abilities varied.
-I show that there is a certain relationship between generalization ability and different graph parameters.
-
-\subsection{Related work}
-The following section provides an overview of the related work.
-
-\subsubsection{Graph parameters}
-
-\subsubsection{Generalization error}
-
-\section{Background on learning on graphs}
+\chapter{Background on learning on graphs}\label{chap:background}
 The following sections provide an overview of the concepts and methods related to graph theory, machine learning, and graph neural networks.
 
-\subsection{Notion}
+\section{Notion}
 At first, we need to define some terms with regard to the graph.
@@
 
-\subsection{Machine learning}
+\section{Machine learning}
 In the following section, we provide an overview of the concepts and methods related to machine learning.
 
-\subsubsection{Supervised learning}
+\subsection{Supervised learning}
 Machine learning can be roughly divided into three categories: supervised learning, unsupervised learning, and reinforcement learning~\cite{bishop2006pattern}.
@@
 
-\subsubsection{Feed-forward neural networks}
+\subsection{Feed-forward neural networks}
 
@@
 
-where $x$ is the input vector, $W^{(i)}$ and $b^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function. The output $y$ is the predicted output of the network.
+where $x$ is the input vector, $W^{(i)}$ and $b^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function.
+The output $y$ is the predicted output of the network.
+$L$ is denoted as the depth of the network.
 
-\subsubsection{Loss function}
+\subsection{Loss function}
 The loss function is a function that measures the difference between the predicted output of a model and the true output.
@@
 
-\subsubsection{Activation function}
+\subsection{Activation function}
 An activation function is a non-linear function that is applied to the output of a neuron in a neural network.
@@
 $$
-    \text{ReLU}(\cdot)=\max(0,\cdot)
+    \textrm{ReLU}(\cdot)=\max(0,\cdot)
 $$
@@
 
-\subsubsection{Gradient Descent}
+\subsection{Gradient Descent}
 Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
@@
 
-\subsubsection{Stochastic Gradient Descent}
+\subsection{Stochastic Gradient Descent}
 Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
@@
 
-\subsubsection{Early Stopping}
+\subsection{Early Stopping}
 Early stopping is a technique used to prevent overfitting in machine learning models.
@@
 
-\subsubsection{Cross-validation}
+\subsection{Cross-validation}
 Cross-validation is a technique used to evaluate the performance of a machine learning model.
@@
 
-\subsubsection{Hyperparameter tuning}
+\subsection{Hyperparameter tuning}
 Hyperparameter tuning is the process of selecting the optimal hyperparameters for a machine learning model.
@@
 
-\subsubsection{Optimization algorithm}
+\subsection{Optimization algorithm}
 An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
@@
 
-\subsubsection{Generalization}
+\subsection{Generalization}
 A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
@@
 where $Acc_{train}$ is the accuracy of the model on the training dataset, and $Acc_{test}$ is the accuracy of the model on the test dataset.
-The accuracy $Acc$ on a dataset is defined as the proportion of correctly classified graphs, that is, $Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$.
+The accuracy $Acc$ on a dataset is defined as the proportion of correctly classified graphs, that is, $Acc = \frac{\textrm{Number of correctly classified graphs}}{\textrm{Total number of data points}}$.
 
@@
 
-\subsection{Graph Neural Networks}
+\section{Graph Neural Networks}
 Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
@@
 
-\subsubsection{Graph Convolutional Networks (GCN)}
+\subsection{Graph Convolutional Networks (GCN)}
 
@@
 where $H^{(l)}\in \mathbb{R}^{N\times D}$ is the node feature matrix at layer $l$; $H^{(0)} = X$.
-$\tilde{A} = A + I$ is the adjacency matrix of the graph with self-connections added, $\tilde{D}$ is the degree matrix of $\tilde{A}$, $W^{(l)}$ is the weight matrix of the layer, and $\sigma$ is the activation function, such as the $\text{ReLU}(\cdot)=\max(0,\cdot)$.
+$\tilde{A} = A + I$ is the adjacency matrix of the graph with self-connections added, $\tilde{D}$ is the degree matrix of $\tilde{A}$, $W^{(l)}$ is the weight matrix of the layer, and $\sigma$ is the activation function, such as the $\textrm{ReLU}(\cdot)=\max(0,\cdot)$.
 The GCN layer aggregates information from neighboring nodes and updates the node features by applying a linear transformation followed by a non-linear activation function.
@@
 
-\subsubsection{Simplified Graph Convolution (SGC)}
+\subsection{Simplified Graph Convolution (SGC)}
 
@@
 
-\subsubsection{Graph Attention Networks (GAT)}
-
-Graph Attention Networks (GAT)~\cite{velickovic2020pointer} are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes. The GAT model is defined as
+\subsection{Graph Attention Networks (GAT)}
+Graph Attention Networks (GAT) are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes.
+The GAT model updates the feature representation of a node by assigning different importance scores, known as attention coefficients, to its neighbors.
+The updated node feature $\mathbf{h}_i^{(l+1)}$ at layer $l+1$ is given by:
 
 $$
-    h_i^{(l+1)} = \sigma(\sum_{j\in N(i)}\alpha_{ij}^{(l)}W^{(l)}h_j^{(l)})
+\mathbf{h}_i^{(l+1)} = \sigma \left( \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l)} \mathbf{W}^{(l)} \mathbf{h}_j^{(l)} \right)
 $$
 
-where $h_i^{(l)}$ is the node feature vector of node $i$ at layer $l$, $W^{(l)}$ is the weight matrix of the layer, $\sigma$ is the activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between node $i$ and node $j$ at layer $l$.
-The attention coefficient is computed as
+where $\mathbf{h}_i^{(l)}$ is the feature vector of node $i$ at layer $l$, $\mathbf{W}^{(l)}$ is a learnable weight matrix, $\sigma$ is an activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between nodes $i$ and $j$.
+These coefficients are computed as:
 
-\subsubsection{Message Passing Neural Networks (MPNN)}
-Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} has been the leading model for graph learning. The MPNN model is defined as
+$$
+\alpha_{ij}^{(l)} = \frac{\exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l)^\top} [\mathbf{W}^{(l)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l)} \mathbf{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l)^\top} [\mathbf{W}^{(l)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l)} \mathbf{h}_k^{(l)}] \right) \right)}
+$$
+
+where $\|$ denotes the concatenation of node features, and $\mathbf{a}^{(l)}$ is a shared attention vector. The softmax function ensures the attention coefficients sum to one for a node's neighbors.
+
+GAT is particularly effective for tasks where different neighbors contribute unequally to a node's representation.
+By using attention mechanisms, GAT dynamically weighs neighbor contributions, enabling more expressive feature aggregation compared to earlier methods like GCNs.
+
+\subsection{Graph Attention Networks v2 (GATv2)}
+Graph Attention Networks v2 (GATv2)~\cite{brody2021attentive} is an improved version of the GAT model that introduces residual connections and multi-head attention. The GATv2 model is defined as
+
+$$
+    \mathbf{h}_i^{(l+1)} = \sigma \left( \sum_{h=1}^{H} \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l,h)} \mathbf{W}^{(l,h)} \mathbf{h}_j^{(l)} \right) + \mathbf{h}_i^{(l)}
+$$
+
+where $H$ is the number of attention heads, $\alpha_{ij}^{(l,h)}$ is the attention coefficient between nodes $i$ and $j$ for head $h$, and $\mathbf{W}^{(l,h)}$ is the weight matrix for head $h$.
+The attention coefficients are computed as
+
+$$
+    \alpha_{ij}^{(l,h)} = \frac{\exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l,h)^\top} [\mathbf{W}^{(l,h)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l,h)} \mathbf{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l,h)^\top} [\mathbf{W}^{(l,h)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l,h)} \mathbf{h}_k^{(l)}] \right) \right)}
+$$
+
+The GATv2 model uses multi-head attention to allow the model to attend to different parts of the input space.
+The model also introduces residual connections to improve the flow of information through the network.
+The GATv2 model has been shown to outperform the original GAT model on a wide range of tasks.
+
+\subsection{Message Passing Neural Networks (MPNN)}
+Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} have been the leading model for graph learning.
+The MPNN model operates by iteratively passing messages between nodes and updating their representations.
+At each iteration $t$, the message vector $m_i^{(t+1)}$ for node $i$ is computed as:
 
@@
 
-where $m_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is the message function, $h_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
+where $m_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is a learnable message function (typically implemented as a neural network, such as an MLP), $h_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $h_j^{(t)}$ is the node feature vector of node $j$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
 The message function $M^{(t)}$ is a neural network that takes as input the node feature vectors of node $i$ and node $j$, and the edge feature vector between them, and outputs the message vector $m_i^{(t)}$.
 
-\subsection{Graph parameters} \label{sec:graph_parameters}
+\section{Graph parameters} \label{sec:graph_parameters}
 Now we can introduce the concept of a graph parameter.
@@
 This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
-
-\section{Experimental study}
-
-\subsection{Experimental setup}
-The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.
-
-\subsubsection{Training Framework}
-The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
-PyTorch Geometric is a library for deep learning on graphs and other irregular structures.
-It consists of various methods and utilities to ease the implementation of GNNs.
-
-\subsubsection{Hyperparameters tuning}
-Before training the models, for each pair of dataset and model, the hyperparameters of the model are tuned.
-In the experiment, 5-fold cross-validation is used to tune the hyperparameters instead of 10-fold cross validation in the final experiment.
-The reason is that the 10-fold cross-validation is computationally expensive and time-consuming.
-
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler.
-Additionally, for the GATv2 model, the number of heads, the dropout rate, and residual are also tuned.
-
-The hyperparameters are tuned using the Bayesian optimization method\cite{frazier2018tutorial}.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-There are five models and 57 datasets, resulting in 285 pairs of dataset and model.
-For each pair, the hyperparameters are tuned using the Bayesian optimization method.
-The hyperparameters are tuned using the validation dataset.
-The validation dataset is a subset of the training dataset that is used to tune the hyperparameters of the model.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-\subsubsection{Datasets}
-The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
-TUDataset is often used for the GNN evaluation.
-It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
-The remaining folds are used for training.
-The training is repeated 10 times, each time with a different test fold.
-The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
-
-I list information about the 57 datasets used in the experiment in the appendix~\ref{sec:datasets}.
-
-\subsubsection{Models}
-In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
-The GCN model is shown in the appendix.
-The GCN model consists of four GCN layers, each followed by a ReLU activation function.
-The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.
-
-\subsubsection{Experimental details}
-The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
-To prevent overfitting and to optimize the use of time, the early stopping is employed.
-The loss function is defined as the cross-entropy loss function.
-The hyperparameters of the model are considered to be tuned.
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping.
-The generalization error is calculated as the difference between the training accuracy and the test accuracy.
-
-\subsubsection{Graph Parameters Under Investigation}
-As graph parameters defined abstractly in the section~\ref{sec:graph_parameters}, I give here the concrete definition of the graph parameters that are used in the experiment.
-The graph parameters are calculated for each dataset and used as input features for the model.
-The graph parameters are calculated using the NetworkX library~\cite{hagberg2008exploring}.
-
-\begin{description}
-    \item [Average degree] The average degree of the graph $d_{avg}$ is defined as the average of the degrees of all nodes in the graph, that is
-    $$ d_{avg} = \frac{1}{|V|} \sum_{v \in V} d(v)$$
-    \item [Average shortest path length] The average shortest path length of the graph $a$ is defined as the average of the shortest paths between all pairs of nodes in the graph.
-The shortest path $d(s, t)$ between two nodes $v$ and $w$ is the minimum number of edges that need to be traversed to go from $v$ to $w$.
-The formal definition is
-    $$
-a = \frac{1}{|V|(|V|-1)} \sum_{v \in V} \sum_{w \in V, w \neq v} d(v, w)
-    $$
-
-    \item [Graph diameter] The graph diameter $d$ is the maximum of the shortest paths between all pairs of nodes in the graph, that is,
-    $$
-d = \max_{v \in V} \max_{w \in V, w \neq v} d(v, w)
-    $$
-
-    \item [Graph density] The graph density $p$ is the ratio of the number of edges in the graph to the number of the maximum possible edges in the graph, that is,
-    $$
-p = \frac{2|E|}{|V|(|V|-1)}
-    $$
-
-    \item [Graph clustering coefficient] The graph clustering coefficient $C$ is a measure of the degree to which nodes in a graph tend to cluster together.
-The clustering coefficient of a node $v$ (as known as the local clustering coefficient) is defined as the fraction of the number of triangles that include node $v$ to the maximum possible number of triples centered on node $v$.
-The clustering coefficient of the graph (as known as the global clustering coefficient) is defined as the average of the clustering coefficients of all nodes in the graph.
-The formal definition is
-    $$
-C = \frac{1}{|V|} \sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}
-    $$
-    where the term $|\{(i,j)\in E \mid i, j \in N(v)\}|$ is the number of edges between the neighbors of node $v$, i.e.
-the number of triangles containing node $v$.
-Furthermore, the term $\sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}$ is the sum of the local clustering coefficients of all nodes in the graph, in which the degree of node $v$ is denoted as $d(v)$.
-
-    \item [Centrality measure of graphs] At first we have the definition of centrality measure in the \textbf{node level}.
-The centrality measure of a node is a measure of the importance of the node in the graph.
-There are many centrality measures, such as degree centrality, closeness centrality, betweenness centrality, and eigenvector centrality.
-
-    \textit{Degree centrality} is identical to the average degree of the graph defined above.
-
-    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of the shortest paths from the node $v$ to all other nodes in the graph, that is 
-    $$C_C(v) = \frac{1}{\sum_{w\in V}{d(v ,w)}}$$
-    where $d(v, w)$ is the shortest path between node $v$ and node $w$.
-
-    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of the shortest paths between all pairs of nodes that pass through node $v$, that is
-
-    $$
-        C_B(v) = \sum_{s,t \in V} \frac{\sigma_{st}(v)}{\sigma_{st}}
-    $$
-    where $\sigma_{st}$ is the number of the shortest paths between nodes $s$ and $t$, and $\sigma_{st}(v)$ is the number of the shortest paths between nodes $s$ and $t$ that pass through node $v$.
-
-    \textit{Eigenvector centrality} is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
-Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$-th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
-Mathematically, it can be expressed as:
-
-    \[ C_E(v) = \frac{1}{\lambda} \sum_{u \in N(v)} a_{vu} C_E(u) \]
-
-    where $ \lambda$ is the largest eigenvalue of the adjacency matrix $A$.
-$a_{vu}$ is the element of the adjacency matrix $A$ corresponding to the edge between nodes $v$  and $u$.
-$ C_E(u)$  is the eigenvector centrality of node $u$.
-
-    Finally, in the \textbf{graph level}, the centrality measure of the graph is defined as the average of the centrality measures over all nodes in the graph.
-
-    \item [Average number of coloring in the 1-WL algorithm] 
-    \sloppy
-    The 1-dimensional Weisfeiler-Leman algorithm (1-WL)~\cite{weisfeiler1968reduction} is an algorithm that assigns a unique label(color) to each node in the graph, also known as color refinement.
-The average number of coloring in the 1-WL algorithm is defined as the average number of colors used to color the nodes in the graph.
-The 1-WL algorithm is a powerful graph isomorphism algorithm that can be used to determine if two graphs are isomorphic.
-I give the procedure of the 1-WL algorithm here:
-    \begin{enumerate}
-        \item Assign the same color to all nodes in the graph.
-        \item Two nodes $v$, $u$ are assigned a different color if there is a color c such that the number of c-colored neighbors of $u$ is not equal to the number of c-colored neighbors of $v$.
-        \item Repeat step 2 until the colors of all nodes do not change.
-    \end{enumerate}
-
-\end{description}
-
-\subsection{Results}
-
-\subsubsection{Graph parameters of the datasets}
-
-\begin{table}[!ht]
-    \footnotesize
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-        \textbf{Name} & \textbf{Ave.
-degree} & \textbf{Ave.
-shortest path} & \textbf{Graph diameter} & \textbf{Graph density} & \textbf{Graph clustering coefficient} & \textbf{Ave.
-closeness centrality} & \textbf{Ave.
-betweenness centrality} & \textbf{Ave.
-eigenvector centrality} & \textbf{1-WL color count} \\ \hline
-        COIL-DEL & 4.673071633424515 & 2.128750184714701 & 4.06974358974359 & 0.3275202823564923 & 0.546258039207784 & 0.5122126871677409 & 0.0647750716657882 & 0.2431245565997526 & 21.102564102564106 \\ \hline
-        COIL-RAG & 1.8277218368573067 & 1.0604823111763986 & 1.242159383033419 & 0.924030303030303 & 0.5903545713545713 & 0.94372526076617 & 0.0462785547785547 & 0.5905014648511226 & 1.3115384615384615 \\ \hline
-        Cuneiform & 4.079588014981273 & 2.244427103288844 & 3.0 & 0.2222330604444725 & 0.8634154547075895 & 0.4613474974345972 & 0.0722909733763576 & 0.1963017855703223 & 2.0 \\ \hline
-        Fingerprint & 1.4868577990824814 & 2.115136284036567 & 4.344413012729844 & 0.4391785351497472 & 0.0017307791737759 & 0.5069423734352098 & 0.1840341453794884 & 0.4207756269406634 & 3.656584457887389 \\ \hline
-        FIRSTMM\_DB & 4.50236815941043 & 12.309044701937715 & 30.676056338028168 & 0.0074027477877271 & 0.2631922211539924 & 0.0551742654129266 & 0.0188189276256195 & 0.0092704028700914 & 1357.8292682926829 \\ \hline
-        Letter-high & 1.889683607525296 & 1.4794456563750826 & 2.444490301279405 & 0.5791851851851852 & 0.2976163139329805 & 0.6794971082752952 & 0.1657867724867724 & 0.4611670600331147 & 2.994222222222222 \\ \hline
-        Letter-low & 1.3213534599145254 & 1.33364428641149 & 1.955783308931186 & 0.4165470899470899 & 0.0 & 0.4955472438922087 & 0.1618904761904762 & 0.4407481624189365 & 2.471111111111111 \\ \hline
-        Letter-med & 1.352705840084288 & 1.3502031822344325 & 2.006610576923077 & 0.4245777777777778 & 0.0139393298059964 & 0.5071406868429822 & 0.1683222222222222 & 0.4416562761104123 & 2.517333333333333 \\ \hline
-        MSRC\_9 & 4.81534002269555 & 3.113629895894764 & 7.004524886877828 & 0.1235873024311543 & 0.5412981657910688 & 0.33102605797573 & 0.055215313789426 & 0.1368862401087341 & 40.36199095022624 \\ \hline
-        MSRC\_21 & 5.102391318360188 & 4.094474312024695 & 9.621669626998225 & 0.0680571076593652 & 0.5146660459581984 & 0.251511488615992 & 0.041532868642658 & 0.0936632954729105 & 77.22735346358792 \\ \hline
-        MSRC\_21C & 4.782574662751558 & 3.113761314016 & 6.971291866028708 & 0.1240107738760322 & 0.5427170070575877 & 0.3315153420789583 & 0.0557392711060186 & 0.1371850938080253 & 40.05263157894737 \\ \hline
-        DD & 4.979061666490266 & 7.919898418826995 & 19.70016611295681 & 0.0278322962071925 & 0.4793770769559906 & 0.1402074694227141 & 0.0324963430907113 & 0.0342447661028087 & 278.28013582342953 \\ \hline
-        ENZYMES & 3.862625308732192 & 4.2810541955964485 & 10.4265625 & 0.1598878125179543 & 0.4533912862690096 & 0.263573448964092 & 0.1158938852730127 & 0.1471447702872793 & 28.575 \\ \hline
-        KKI & 3.1856769969664422 & 3.500870554422239 & 8.144578313253012 & 0.1792960793494088 & 0.3526436673677589 & 0.3358793648012939 & 0.1297799757896069 & 0.1757034314039908 & 24.81927710843373 \\ \hline
-        OHSU & 4.327667933476122 & 4.921680537597515 & 12.69620253164557 & 0.0822944467200859 & 0.3808295357080805 & 0.2407028072344937 & 0.0655860979728088 & 0.0823969445758651 & 77.51898734177215 \\ \hline
-        Peking\_1 & 3.5514470044304343 & 3.968106920104182 & 9.623529411764704 & 0.1276151076564966 & 0.3673053988324483 & 0.2889094228756093 & 0.0998385744518594 & 0.1284748145692827 & 36.72941176470588 \\ \hline
-        PROTEINS & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        PROTEINS\_full & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        COLORS-3 & 2.928853359699249 & 2.5810313856214724 & 5.275766205587198 & 0.1695881211511339 & 0.1450387037596311 & 0.3502761440955542 & 0.0639043708084029 & 0.1737080119571242 & 56.95904761904762 \\ \hline
-        SYNTHETIC & 3.920000076293945 & 3.5064646464646465 & 7.0 & 0.0395959595959595 & 0.0203095238095238 & 0.2893391429701345 & 0.0255761698618841 & 0.0831547830080052 & 100.0 \\ \hline
-        SYNTHETICnew & 3.9250000715255737 & 3.4872567329242026 & 7.274834437086093 & 0.0396464646464646 & 0.0229497089947089 & 0.289441726009901 & 0.0255427746856318 & 0.0836273264155355 & 99.96333333333334 \\ \hline
-        Synthie & 3.6210444450378416 & 2.6348743925562266 & 5.494845360824742 & 0.038420429009193 & 0.0937036201778145 & 0.2766177855177352 & 0.0231922369186012 & 0.0786632559723412 & 90.6125 \\ \hline
-        TRIANGLES & 3.1404920884927114 & 2.263375484124684 & 4.557498816896771 & 0.2416135135324899 & 0.2286352011335792 & 0.4374025890339534 & 0.0821216496736849 & 0.226180376713217 & 19.88371111111111 \\ \hline
-        AIDS & 2.0128653862178325 & 3.490507728804514 & 7.762604013705335 & 0.1935408261794486 & 0.0071746166779525 & 0.3500774185559109 & 0.1911961844012523 & 0.262770387548969 & 11.8145 \\ \hline
-        BZR & 2.1466610419897387 & 5.154837461860052 & 11.65679012345679 & 0.0648920405178712 & 8.903397114779228e-05 & 0.2054846442932875 & 0.1245291263310628 & 0.1416530437212679 & 29.607407407407408 \\ \hline
-        BZR\_MD & 20.30392156862745 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2203726689661978 & 1.0 \\ \hline
-        COX2 & 2.107735009469108 & 5.936420803578038 & 13.790149892933618 & 0.0529052472359257 & 0.0007216110850642 & 0.1757209022905502 & 0.1262987138392391 & 0.1288265342157682 & 28.09421841541756 \\ \hline
-        COX2\_MD & 25.27722772277228 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.1957034193657646 & 1.0 \\ \hline
-        DHFR & 2.102359890622437 & 6.144674814243727 & 14.603174603174605 & 0.0536754666970741 & 0.0 & 0.1734264353163348 & 0.1288500765571343 & 0.1271607693927877 & 32.21560846560847 \\ \hline
-        DHFR\_MD & 22.8676844783715 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2076620678810238 & 1.0 \\ \hline
-        ER\_MD & 20.327354260089685 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2244695039966339 & 1.0 \\ \hline
-        FRANKENSTEIN & 2.0627741588132293 & 3.6742676066855062 & 8.423452029938762 & 0.1705038719060743 & 0.0106826329262756 & 0.3148146889108825 & 0.1923606317376928 & 0.2432099454364741 & 13.42448697256168 \\ \hline
-        MCF-7 & 2.1516180606917765 & 5.050070569624072 & 12.141178938535766 & 0.0980572307942984 & 0.0020345164969653 & 0.2175444791564102 & 0.1724077067751488 & 0.1725022149133201 & 21.418113071660063 \\ \hline
-        MCF-7H & 2.0888838372172147 & 5.858613378052236 & 13.306228605946709 & 0.0537227676449342 & 0.0005825022974507 & 0.1778419519669024 & 0.1198217621207925 & 0.1223362659022958 & 32.9756211739287 \\ \hline
-        MOLT-4 & 2.146077948348501 & 4.951738679286625 & 11.874633536790505 & 0.0987082247303717 & 0.0019246147011501 & 0.2183304220273518 & 0.1714407445609207 & 0.1734293274657891 & 21.028995347667543 \\ \hline
-        MOLT-4H & 2.0858484049375803 & 5.738056140581633 & 12.992424764134702 & 0.0539489355320176 & 0.0005343843281943 & 0.17815930623996 & 0.1192636780853368 & 0.1228930198480923 & 32.272249465610464 \\ \hline
-        Mutagenicity & 2.0379886209469995 & 4.418912992995495 & 9.63701923076923 & 0.0912875415379717 & 0.0031125822886973 & 0.2466634939984061 & 0.1371754284356414 & 0.1710356482094367 & 20.874567673507038 \\ \hline
-        MUTAG & 2.18877208359698 & 3.626150957182829 & 8.21808510638298 & 0.1384540671648269 & 0.0 & 0.293764054092514 & 0.1694459751944365 & 0.2197353385133972 & 14.8031914893617 \\ \hline
-        NCI1 & 2.15501380214726 & 5.234873158476093 & 12.659402381487306 & 0.088944910671084 & 0.0030999008340164 & 0.2026186665583615 & 0.1631676786426253 & 0.1607325923179734 & 24.721411192214116 \\ \hline
-        NCI109 & 2.156446177386937 & 5.183950502801717 & 12.49528936742934 & 0.0894286690245151 & 0.0030732389355228 & 0.20411132911515 & 0.1624231134845694 & 0.1617585552708976 & 24.52410952265568 \\ \hline
-        NCI-H23 & 2.1451602406810686 & 4.950946501654924 & 11.869525050337558 & 0.0987776628128759 & 0.0018996992922189 & 0.2183535143438838 & 0.1715792456717554 & 0.1735208031755432 & 20.99303645329963 \\ \hline
-        NCI-H23H & 2.085327596320919 & 5.734343001278942 & 12.983736711151325 & 0.0539842770435475 & 0.0005268942359655 & 0.1782099752168056 & 0.1192891041739607 & 0.1229635264798962 & 32.22578246970485 \\ \hline
-        OVCAR-8 & 2.145637268375766 & 4.945169149304127 & 11.85222800857742 & 0.0987730040211328 & 0.0018986224960467 & 0.2183941696064956 & 0.171403631603811 & 0.1735393405097124 & 20.98556125974924 \\ \hline
-        OVCAR-8H & 2.0856259705836995 & 5.728655397369023 & 12.966769410758882 & 0.0539777071171825 & 0.0005298176630677 & 0.1782129665549435 & 0.1192148511162624 & 0.1229665170804826 & 32.22561457202093 \\ \hline
-        P388 & 2.109217112454913 & 4.355752638151867 & 10.21824835544779 & 0.1190787859581164 & 0.0037544697177687 & 0.2459957278657192 & 0.1789538865626834 & 0.1958220277248745 & 17.133174189814813 \\ \hline
-        P388H & 2.0638945394922854 & 5.289795718220624 & 11.765664188214403 & 0.0639638393366292 & 0.0009642194122106 & 0.1971310478874152 & 0.1240122910178544 & 0.1373237905541068 & 26.71100983796296 \\ \hline
-        PC-3 & 2.1520653447146643 & 5.05018085139685 & 12.140862989009436 & 0.098055200309084 & 0.0019733135754618 & 0.2175815805232795 & 0.1725492873407526 & 0.172560720893664 & 21.37340506743248 \\ \hline
-        PC-3H & 2.08922384690422 & 5.857822430952191 & 13.30650249313117 & 0.0537656750613318 & 0.0005561305149752 & 0.1779189564869681 & 0.1200247359820712 & 0.1224665687629844 & 32.881929550328984 \\ \hline
-        PTC\_FM & 1.9758043374578045 & 3.311647990381311 & 7.36676217765043 & 0.2154944740700171 & 0.0091220986824968 & 0.3693003427913903 & 0.2055882581121011 & 0.2786143302706905 & 9.91404011461318 \\ \hline
-        PTC\_FR & 1.9863111707899304 & 3.387662268892836 & 7.589743589743589 & 0.2085568638656639 & 0.0088214579442649 & 0.3612672957602951 & 0.2045358868174996 & 0.2734008790739162 & 10.22222222222222 \\ \hline
-        PTC\_MM & 1.9701179610121815 & 3.301432053360394 & 7.339285714285714 & 0.2223452925857377 & 0.0130582137161084 & 0.374488207420213 & 0.2059637189235834 & 0.2823441282735879 & 9.803571428571429 \\ \hline
-        PTC\_MR & 1.9805375618297 & 3.3577641223936463 & 7.523255813953488 & 0.2137888896192228 & 0.009509685286154 & 0.3666473296924281 & 0.2062170509277356 & 0.2777684525909222 & 10.040697674418604 \\ \hline
-        SF-295 & 2.145489384462884 & 4.9445677038396125 & 11.852116182572614 & 0.09881526807439 & 0.0019131887956769 & 0.2184346701016761 & 0.1714761059761314 & 0.1735919743359789 & 20.97159246107621 \\ \hline
-        SF-295H & 2.0855234748235936 & 5.727434951743517 & 12.9664274556856 & 0.0539895579758234 & 0.0005299113307649 & 0.1782697110808576 & 0.1192036786794211 & 0.1229816733300816 & 32.196146110104046 \\ \hline
-        SN12C & 2.145026913904858 & 4.94825141099449 & 11.86401279205747 & 0.0987936439503507 & 0.001927945706436 & 0.2183468315283276 & 0.1714975830848956 & 0.1735570013676089 & 20.99167583241676 \\ \hline
-        SN12CH & 2.0853053252079072 & 5.730086714838555 & 12.973598487437071 & 0.0540104189866913 & 0.0005390487212868 & 0.1781938757210136 & 0.1192686561921279 & 0.1230077396296653 & 32.236301369863014 \\ \hline
-        SW-620 & 2.1452310279340394 & 4.94393636762053 & 11.851577038136291 & 0.0988746005232462 & 0.0018522578567537 & 0.2185003794708548 & 0.1714920826604129 & 0.1736489333480562 & 20.97197276226192 \\ \hline
-        SW-620H & 2.0854275176564645 & 5.725806234940699 & 12.962851360467733 & 0.054054544610838 & 0.0005110193017508 & 0.1783225632271403 & 0.1192839052512742 & 0.1230820111720522 & 32.19651139840126 \\ \hline
-        UACC257 & 2.145698715720169 & 4.955834964420495 & 11.885704040162564 & 0.0987250195703296 & 0.0018738116805416 & 0.218300263582104 & 0.1716221375949755 & 0.1734631006815176 & 20.994198259477844 \\ \hline
-        UACC257H & 2.0856917230912635 & 5.740515645090362 & 13.003174313183676 & 0.0539749990285044 & 0.0005209407683445 & 0.1781806662974605 & 0.1193640515072574 & 0.122956068725157 & 32.22436731019306 \\ \hline
-        Yeast & 2.099442849357738 & 4.364322361013096 & 10.26343257027636 & 0.1210553127513687 & 0.0022671334945899 & 0.2476806589296417 & 0.183060827627568 & 0.1985665767951158 & 16.67475282973832 \\ \hline
-        YeastH & 2.0589509621359707 & 5.245391698622407 & 11.6875493153864 & 0.0642704732457107 & 0.0005773570062507 & 0.1983872537891083 & 0.1254655281986756 & 0.1384817929367545 & 26.05320284921044 \\ \hline
-        Sum & 242.8347529362711 & 258.6723790469145 & 587.9183294923151 & 12.731666924394474 & 11.845921907393928 & 20.687237238791475 & 7.3848149134808 & 11.636469235194477 & 3245.599253687252 \\ \hline
-    \end{tabular}
-    \caption{Graph parameters of the datasets}
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of GCN model}
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\ \hline
-        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\ \hline
-        MOLT-4 & 0.0 & 0.014102176763117313 \\ \hline
-        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\ \hline
-        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\ \hline
-        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\ \hline
-        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\ \hline
-        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\ \hline
-        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\ \hline
-        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\ \hline
-        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\ \hline
-        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\ \hline
-        P388 & 0.008062511682510376 & 0.01043933816254139 \\ \hline
-        P388H & 0.006343752145767212 & 0.007148966193199158 \\ \hline
-        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\ \hline
-        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\ \hline
-        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\ \hline
-        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\ \hline
-        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\ \hline
-        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\ \hline
-        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\ \hline
-        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\ \hline
-        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\ \hline
-        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\ \hline
-        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\ \hline
-        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\ \hline
-        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\ \hline
-        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\ \hline
-        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\ \hline
-        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\ \hline
-        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\ \hline
-        DD & -0.1750326007604599 & 0.3490835428237915 \\ \hline
-        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\ \hline
-        KKI & 0.04776120185852051 & 0.2546080946922302 \\ \hline
-        OHSU & 0.39824172854423523 & 0.138640895485878 \\ \hline
-        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\ \hline
-        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\ \hline
-        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\ \hline
-        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\ \hline
-        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ \hline
-    \end{tabular}
-    \caption{Generalization error of the GCN model on 57 datasets}
-    \label{tab:ge_gcn} % ge -> generalization error
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of SGC model}
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        PROTEINS\_full & 0.04741409420967102 & 0.5624663829803467 \\ \hline
-        DD & -0.21720178425312042 & 0.40132829546928406 \\ \hline
-        ENZYMES & 0.3279166519641876 & 0.060605552047491074 \\ \hline
-        KKI & 0.10951493680477142 & 0.24877962470054626 \\ \hline
-        OHSU & 0.07604396343231201 & 0.1943538784980774 \\ \hline
-        Peking\_1 & 0.1769927442073822 & 0.22724425792694092 \\ \hline
-        COLORS-3 & 0.11781251430511475 & 0.04669201001524925 \\ \hline
-        SYNTHETIC & -0.37541666626930237 & 0.4494529068470001 \\ \hline
-        SYNTHETICnew & -0.36666664481163025 & 0.46157106757164 \\ \hline
-        Synthie & 0.13749998807907104 & 0.042466290295124054 \\ \hline
-        AIDS & 0.006437480449676514 & 0.011520843021571636 \\ \hline
-        BZR & 0.10815385729074478 & 0.21917256712913513 \\ \hline
-        BZR\_MD & 0.1678861677646637 & 0.09830881655216217 \\ \hline
-        COX2 & 0.07495072484016418 & 0.13212721049785614 \\ \hline
-        COX2\_MD & 0.14868313074111938 & 0.16540752351284027 \\ \hline
-        DHFR & 0.1332409381866455 & 0.1551705300807953 \\ \hline
-        DHFR\_MD & 0.0777045264840126 & 0.2503173351287842 \\ \hline
-        ER\_MD & -0.008367183618247509 & 0.15631815791130066 \\ \hline
-        FRANKENSTEIN & 0.10787498950958252 & 0.05383045971393585 \\ \hline
-        MCF-7 & 0.35490626096725464 & 0.17573890089988708 \\ \hline
-        MCF-7H & 0.3593124747276306 & 0.1884346306324005 \\ \hline
-        MOLT-4 & 0.18021871149539948 & 0.39803561568260193 \\ \hline
-        MOLT-4H & 0.18649999797344208 & 0.3838197886943817 \\ \hline
-        Mutagenicity & 0.04325000196695328 & 0.028246337547898293 \\ \hline
-        MUTAG & 0.07375730574131012 & 0.13988283276557922 \\ \hline
-        NCI1 & 0.09100000560283661 & 0.16161812841892242 \\ \hline
-        NCI109 & -0.06128125637769699 & 0.2943810522556305 \\ \hline
-        NCI-H23 & 0.31696873903274536 & 0.07884199917316437 \\ \hline
-        NCI-H23H & 0.3696562349796295 & 0.06490368396043777 \\ \hline
-        OVCAR-8 & 0.3291874825954437 & 0.0815950483083725 \\ \hline
-        OVCAR-8H & 0.2902187705039978 & 0.0771569237112999 \\ \hline
-        P388 & 0.3618437647819519 & 0.13428252935409546 \\ \hline
-        P388H & -0.052218757569789886 & 0.3646376132965088 \\ \hline
-        PC-3 & -0.08028124272823334 & 0.29225972294807434 \\ \hline
-        PC-3H & 0.2593437135219574 & 0.22314861416816711 \\ \hline
-        PTC\_FM & 0.10863511264324188 & 0.14730817079544067 \\ \hline
-        PTC\_FR & 0.08632432669401169 & 0.09645862877368927 \\ \hline
-        PTC\_MM & 0.09649830311536789 & 0.0817335695028305 \\ \hline
-        PTC\_MR & 0.060720354318618774 & 0.18291200697422028 \\ \hline
-        SF-295 & 0.3124375343322754 & 0.11770480871200562 \\ \hline
-        SF-295H & 0.28881245851516724 & 0.12331245839595795 \\ \hline
-        SN12C & 0.2917812764644623 & 0.05537300556898117 \\ \hline
-        SN12CH & 0.3397812247276306 & 0.09572991728782654 \\ \hline
-        SW-620 & 0.3427812457084656 & 0.2430398166179657 \\ \hline
-        SW-620H & 0.39274999499320984 & 0.1998475342988968 \\ \hline
-        UACC257 & -0.10218751430511475 & 0.2883416414260864 \\ \hline
-        UACC257H & 0.3322499692440033 & 0.22775331139564514 \\ \hline
-        Yeast & 0.0 & 0.0 \\ \hline
-        YeastH & 0.0 & 0.0 \\ \hline
-    \end{tabular}
-\end{table}
-
-\subsubsection{Generalization error of GATv2 model}
-
-\subsubsection{Generalization error of MPNN model}
-
-\subsubsection{Corrolation analysis between generalization error and graph parameters}
-
-\subsection{Discussion}
-
-\section{Conclusion}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{main} % refers to example.bib
-
-\clearpage
-
-\section{Appendix}
-
-\subsection{Basic information about TUDataset}\label{sec:datasets}
-This table~\ref{tab:datasets} shows the information about a list of datasets used in this thesis.
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|}
-    \hline
-        name & Graphs & Classes & Avg. Nodes & Avg. Edges & catagory \\ \hline
-        AIDS & 2000 & 2 & 15.69 & 16.20 & Small molecules \\ \hline
-        BZR & 405 & 2 & 35.75 & 38.36 & Small molecules \\ \hline
-        BZR\_MD & 306 & 2 & 21.30 & 225.06 & Small molecules \\ \hline
-        COX2 & 467 & 2 & 41.22 & 43.45 & Small molecules \\ \hline
-        COX2\_MD & 303 & 2 & 26.28 & 335.12 & Small molecules \\ \hline
-        DHFR & 756 & 2 & 42.43 & 44.54 & Small molecules \\ \hline
-        DHFR\_MD & 393 & 2 & 23.87 & 283.02 & Small molecules \\ \hline
-        ER\_MD & 446 & 2 & 21.33 & 234.85 & Small molecules \\ \hline
-        FRANKENSTEIN & 4337 & 2 & 16.90 & 17.88 & Small molecules \\ \hline
-        MCF-7 & 27770 & 2 & 26.40 & 28.53 & Small molecules \\ \hline
-        MCF-7H & 27770 & 2 & 47.31 & 49.44 & Small molecules \\ \hline
-        MOLT-4 & 39765 & 2 & 26.10 & 28.14 & Small molecules \\ \hline
-        MOLT-4H & 39765 & 2 & 46.70 & 48.74 & Small molecules \\ \hline
-        Mutagenicity & 4337 & 2 & 30.32 & 30.77 & Small molecules \\ \hline
-        MUTAG & 188 & 2 & 17.93 & 19.79 & Small molecules \\ \hline
-        NCI1 & 4110 & 2 & 29.87 & 32.30 & Small molecules \\ \hline
-        NCI109 & 4127 & 2 & 29.68 & 32.13 & Small molecules \\ \hline
-        NCI-H23 & 40353 & 2 & 26.07 & 28.10 & Small molecules \\ \hline
-        NCI-H23H & 40353 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        OVCAR-8 & 40516 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        OVCAR-8H & 40516 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        P388 & 41472 & 2 & 22.11 & 23.56 & Small molecules \\ \hline
-        P388H & 41472 & 2 & 40.45 & 41.89 & Small molecules \\ \hline
-        PC-3 & 27509 & 2 & 26.36 & 28.49 & Small molecules \\ \hline
-        PC-3H & 27509 & 2 & 47.20 & 49.33 & Small molecules \\ \hline
-        PTC\_FM & 349 & 2 & 14.11 & 14.48 & Small molecules \\ \hline
-        PTC\_FR & 351 & 2 & 14.56 & 15.00 & Small molecules \\ \hline
-        PTC\_MM & 336 & 2 & 13.97 & 14.32 & Small molecules \\ \hline
-        PTC\_MR & 344 & 2 & 14.29 & 14.69 & Small molecules \\ \hline
-        SF-295 & 40271 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SF-295H & 40271 & 2 & 46.65 & 48.68 & Small molecules \\ \hline
-        SN12C & 40004 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        SN12CH & 40004 & 2 & 46.69 & 48.72 & Small molecules \\ \hline
-        SW-620 & 40532 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SW-620H & 40532 & 2 & 46.63 & 48.66 & Small molecules \\ \hline
-        UACC257 & 39988 & 2 & 26.09 & 28.13 & Small molecules \\ \hline
-        UACC257H & 39988 & 2 & 46.68 & 48.71 & Small molecules \\ \hline
-        Yeast & 79601 & 2 & 21.54 & 22.84 & Small molecules \\ \hline
-        YeastH & 79601 & 2 & 39.45 & 40.75 & Small molecules \\ \hline
-        DD & 1178 & 2 & 284.32 & 715.66 & Bioinformatics \\ \hline
-        ENZYMES & 600 & 6 & 32.63 & 62.14 & Bioinformatics \\ \hline
-        KKI & 83 & 2 & 26.96 & 48.42 & Bioinformatics \\ \hline
-        OHSU & 79 & 2 & 82.01 & 199.66 & Bioinformatics \\ \hline
-        Peking\_1 & 85 & 2 & 39.31 & 77.35 & Bioinformatics \\ \hline
-        PROTEINS\_full & 1113 & 2 & 39.06 & 72.82 & Bioinformatics \\ \hline
-        COIL-DEL & 3900 & 100 & 21.54 & 54.24 & Computer vision \\ \hline
-        COIL-RAG & 3900 & 100 & 3.01 & 3.02 & Computer vision \\ \hline
-        Cuneiform & 267 & 30 & 21.27 & 44.80 & Computer vision \\ \hline
-        Fingerprint & 2149 & 15 & 7.06 & 5.76 & Computer vision \\ \hline
-        FIRSTMM\_DB & 41 & 11 & 1377.27 & 3074.10 & Computer vision \\ \hline
-        Letter-high & 2250 & 15 & 4.67 & 4.50 & Computer vision \\ \hline
-        Letter-low & 2250 & 15 & 4.68 & 3.13 & Computer vision \\ \hline
-        Letter-med & 2250 & 15 & 4.67 & 3.21 & Computer vision \\ \hline
-        MSRC\_9 & 221 & 8 & 40.58 & 97.94 & Computer vision \\ \hline
-        MSRC\_21 & 563 & 20 & 77.52 & 198.32 & Computer vision \\ \hline
-        MSRC\_21C & 209 & 20 & 40.28 & 96.60 & Computer vision \\ \hline
-        COLORS-3 & 10500 & 11 & 61.31 & 91.03 & Synthetic \\ \hline
-        SYNTHETIC & 300 & 2 & 100.00 & 196.00 & Synthetic \\ \hline
-        SYNTHETICnew & 300 & 2 & 100.00 & 196.25 & Synthetic \\ \hline
-        Synthie & 400 & 4 & 95.00 & 172.93 & Synthetic \\ \hline
-    \end{tabular}
-    \caption{Basic information about the datasets used in the experiment}
-    \label{tab:datasets}
-\end{table}
-
-\subsection{Example of GCN model}
-
-\begin{lstlisting}[language=Python]
-import torch
-
-\end{lstlisting}
-
-\end{document}

### 2025-01-29 paper/chapters/experimentalstudy.tex
Add thesis structure including title page, abstract, acknowledgments, conclusion, and related work sections

--- 2025-01-17 thesis/main.tex
@@
-\documentclass{article}
-\usepackage{geometry}
-\geometry{
-    a4paper,
-    left=30mm,
-    right=30mm,
-    top=30mm,
-    bottom=30mm
-}
-
-\usepackage{annotate-equations}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-% \usepackage{figure}
-
-\graphicspath{ {./media/} }
-\usepackage[square,numbers]{natbib}
-\usepackage[nottoc]{tocbibind}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{enumitem}
-\usepackage{float}
-
-\usepackage{amssymb}
-\usepackage{amsmath}
-
-\usepackage{tikz}
-\usepackage{listings}
-\usepackage{setspace}
-\definecolor{Code}{rgb}{0,0,0}
-\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
-\definecolor{Numbers}{rgb}{0.5,0,0}
-\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
-\definecolor{Keywords}{rgb}{0,0,1}
-\definecolor{self}{rgb}{0,0,0}
-\definecolor{Strings}{rgb}{0,0.63,0}
-\definecolor{Comments}{rgb}{0,0.63,1}
-\definecolor{Backquotes}{rgb}{0,0,0}
-\definecolor{Classname}{rgb}{0,0,0}
-\definecolor{FunctionName}{rgb}{0,0,0}
-\definecolor{Operators}{rgb}{0,0,0}
-\definecolor{Background}{rgb}{0.98,0.98,0.98}
-\lstdefinelanguage{Python}{
-	numbers=left,
-	numberstyle=\footnotesize,
-	numbersep=1em,
-	xleftmargin=1em,
-	framextopmargin=2em,
-	framexbottommargin=2em,
-	showspaces=false,
-	showtabs=false,
-	showstringspaces=false,
-	frame=l,
-	tabsize=4,
-	% Basic
-	basicstyle=\ttfamily\small\setstretch{1},
-	backgroundcolor=\color{Background},
-	% Comments
-	commentstyle=\color{Comments}\slshape,
-	% Strings
-	stringstyle=\color{Strings},
-	morecomment=[s][\color{Strings}]{"""}{"""},
-	morecomment=[s][\color{Strings}]{'''}{'''},
-	% keywords
-	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
-	keywordstyle={\color{Keywords}\bfseries},
-	% additional keywords
-	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
-	keywordstyle={[2]\color{Decorators}\slshape},
-	emph={self},
-	emphstyle={\color{self}\slshape},
-	%
-}
-
-\title{\textbf{Bachelor thesis}\\
-Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}
-
-\author{Author: Wensheng Zhang}
-
-\date{\today}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
-\end{abstract}
-
-\section{Introduction}\label{sec:intro}
-Graph learning became a hot topic in the field of machine learning in recent years.
-Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
-The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
-This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.
-
-However, the behavior of GNNs is not well understood.
-Particularly, the relationship between graph parameters/characteristics and the empirical generalization error of GNNs is not clear.
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
-
-Speaking more specifically.
-First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree.
-In graph theory, \textit{graph parameter} is used to quantify them.
-And a dataset consists of multiple graphs, each with its graph parameter.
-In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset.
-In this thesis, 57 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
-Second, I train different GNN models on each dataset and find that their generalization abilities varied.
-I show that there is a certain relationship between generalization ability and different graph parameters.
-
-\subsection{Related work}
-The following section provides an overview of the related work.
-
-\subsubsection{Graph parameters}
-
-\subsubsection{Generalization error}
-
-\section{Background on learning on graphs}
-The following sections provide an overview of the concepts and methods related to graph learning, machine learning, and graph neural networks.
-
-\subsection{Notion}
-At first, we need to define some terms with regard to the graph.
-In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
-We use $\mathbb{G}$ to represent the set of all possible graphs.
-The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$.
-The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
-In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.
-A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included.
-These vectors can be used to characterize graphs or nodes in graphs.
-The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph.
-The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.
-
-\subsection{Machine learning}
-Machine learning is a subfield of artificial intelligence that focuses on the development of algorithms that can learn from and make predictions or decisions based on data.
-The goal of machine learning is to develop models that can generalize well to unseen data.
-The model is trained on a training dataset, which consists of input-output pairs.
-The model is then evaluated on a test dataset, which is separate from the training dataset.
-
-\subsubsection{Gradient Descent}
-Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
-The algorithm works by computing the gradient of the function at a given point and then updating the point in the direction of the negative gradient.
-The update rule is given by
-
-$$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t)
-$$
-where $\theta_t$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(\theta_t)$ is the gradient of the function $f$ at $\theta_t$.
-The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Stochastic Gradient Descent}
-Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
-The algorithm works by randomly selecting a mini-batch of data points from the training dataset, computing the gradient of the loss function with respect to the mini-batch, and then updating the parameters based on the gradient.
-The update rule is given by
-
-$$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t; x_{i:t}, y_{i:t})
-$$
-where $x_{i:t}$ and $y_{i:t}$ are the mini-batch of data points and labels, respectively. The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Backpropagation}
-Backpropagation is an algorithm used to compute the gradients of the loss function with respect to the parameters of a neural network.
-The algorithm works by computing the gradient of the loss function with respect to the output of the network and then propagating the gradient backward through the network to compute the gradients of the loss function with respect to the parameters.
-The gradients are then used to update the parameters of the network using an optimization algorithm such as gradient descent.
-
-\subsubsection{Regularization}
-Regularization is a technique used to prevent overfitting in machine learning models.
-Overfitting occurs when a model learns the noise in the training data rather than the underlying pattern.
-Regularization works by adding a penalty term to the loss function that discourages the model from learning complex patterns that are specific to the training data.
-There are two common types of regularization: $L1$ regularization and $L2$ regularization.
-$L1$ regularization adds a penalty term that is proportional to the $L1$ norm of the parameters, while $L2$ regularization adds a penalty term that is proportional to the $L2$ norm of the parameters.
-The regularization parameter $\lambda$ controls the strength of the regularization.
-
-\subsubsection{Early Stopping}
-Early stopping is a technique used to prevent overfitting in machine learning models.
-The idea is to monitor the performance of the model on a validation dataset during training and stop training when the performance starts to degrade.
-This is done by saving the model parameters at each iteration and selecting the model with the best performance on the validation dataset.
-Early stopping is a form of regularization that prevents the model from learning the noise in the training data.
-
-\subsubsection{Cross-validation}
-Cross-validation is a technique used to evaluate the performance of a machine learning model.
-The idea is to split the dataset into multiple subsets, or folds, and train the model on one subset while evaluating it on the remaining subsets.
-This process is repeated multiple times, with each subset used as the test set once.
-The performance of the model is then averaged over all the folds to obtain an estimate of the model's generalization performance.
-Cross-validation is used to prevent overfitting and to obtain a more accurate estimate of the model's performance.
-
-\subsubsection{Hyperparameter tuning}
-Hyperparameter tuning is the process of selecting the optimal hyperparameters for a machine learning model.
-Hyperparameters are parameters that are set before the training process begins and control the behavior of the model.
-Examples of hyperparameters include the learning rate, batch size, number of hidden layers, and number of epochs.
-Hyperparameter tuning is typically done using a grid search or random search over a predefined set of hyperparameters.
-The goal is to find the set of hyperparameters that results in the best performance on a validation dataset.
-
-\subsubsection{Loss function}
-The loss function is a function that measures the difference between the predicted output of a model and the true output.
-The goal of training a machine learning model is to minimize the loss function, which is done by adjusting the parameters of the model using an optimization algorithm such as gradient descent.
-The choice of loss function depends on the task at hand.
-For classification tasks, the cross-entropy loss function is commonly used, while for regression tasks, the mean squared error loss function is often used.
-
-\subsubsection{Optimization algorithm}
-An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
-The goal is to find the set of parameters that minimizes the loss function.
-Gradient descent is a common optimization algorithm used in machine learning, but there are many variants of gradient descent that are designed to improve convergence speed and stability.
-Some popular optimization algorithms include Adam~\cite{kingma2014adam}, RMSprop~\cite{graves2013generating}, and Adagrad~\cite{duchi2011adaptive}.
-These algorithms use different strategies to update the parameters of the model and can be more effective than standard gradient descent in certain situations.
-
-\subsubsection{Generalization}
-A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
-This is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
-It is defined as
-
-$$
-    E_{gen} = {Acc_{train}} - {Acc_{test}}
-$$
-where $Acc_{train}$ is the accuracy of the model on the training dataset, and $Acc_{test}$ is the accuracy of the model on the test dataset.
-The accuracy $Acc$ on a dataset is defined as the proportion of correctly classified graphs, that is, $Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$.
-
-The empirical generalization error is also known as the generalization gap~\cite{goodfellow2016deep}.
-Typically, the learning on the training dataset and test dataset behaves differently.
-The model may perform well on the training dataset but poorly on the test dataset.
-By observing the generalization error, we can decide on a stopping criterion for the training process.
-And the generalization error can be used to determine whether the model is overfitting or underfitting.
-Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g.
-Graph parameter).
-
-\subsection{Graph Neural Networks}
-Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
-The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
-This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification, edge prediction, and graph classification.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN), Graph Attention Networks (GAT), and Message Passing Neural Networks (MPNN).
-
-\subsection{Graph parameters}
-Now we can introduce the concept of a graph parameter.
-A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
-Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
-A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
-This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
-
-\section{Experimental study}
-
-\subsection{Experimental setup}
+\chapter{Experimental study}\label{chap:experiments}
+\section{Experimental setup}
 The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.
 
-\subsubsection{Training Framework}
+\section{Experimental procedures}\label{sec:Experimental procedures}
+The Experimental procedures are as follows:
+
+\begin{enumerate}
+    \item Obtain the dataset using the setup outlined in Section~\ref{sec:datasets}.
+    \item Tune the hyperparameters using Bayesian optimization, as detailed in Section~\ref{sec:hyperparameters tuning}.
+    \item Train the models using the optimized hyperparameters and compute their generalization errors.
+    \item In the meanwile, calculate the graph parameters for each dataset, as detailed in Section~\ref{sec:graph parameters}.
+    \item Finally, evaluate the impact of the graph parameters on the generalization error of the models by calculating the correlation between the graph parameters and the generalization error.
+\end{enumerate}
+
+\subsection{Training Framework}
 The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
@@
 
-\subsubsection{Hyperparameters tuning}
+\subsection{Datasets}\label{sec:datasets}
+The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
+TUDataset is often used for the GNN evaluation.
+It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
+Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
+A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
+The remaining folds are used for training.
+The training is repeated 10 times, each time with a different test fold.
+The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
+
+For the dataset with large size, the first 4000 data points are selected.
+The remaining data points are discarded.
+The reason is that some datasets are too large to be trained in a reasonable amount of time.
+
+I list information about the 50 datasets used in the experiment in the appendix~\ref{sec:}.
+
+\subsection{Hyperparameters tuning}\label{sec:hyperparameters tuning}
 Before training the models, for each pair of dataset and model, the hyperparameters of the model are tuned.
@@
 
-\subsubsection{Datasets}
-The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
-TUDataset is often used for the GNN evaluation.
-It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
-The remaining folds are used for training.
-The training is repeated 10 times, each time with a different test fold.
-The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
-
-I list information about the 57 datasets used in the experiment in the appendix~\ref{sec:datasets}.
-
-\subsubsection{Models}
+\subsection{Models}\label{sec:models}
 In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
@@
 
-\subsubsection{Experimental details}
+\subsection{Experimental details}
 The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
@@
 
-\subsubsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
-As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.
+\section{Graph Parameters Under Investigation}\label{sec:graph parameters}
+As graph parameters defined abstractly in the section~\ref{sec:graph_parameters}, I give here the concrete definition of the graph parameters that are used in the experiment.
+The graph parameters are calculated for each dataset and used as input features for the model.
+The graph parameters are calculated using the NetworkX library~\cite{hagberg2008exploring}.
 
@@
 \end{description}
-
-\subsection{Results}
-
-\subsubsection{Graph parameters of the datasets}
-
-\begin{table}[!ht]
-    \footnotesize
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-        \textbf{Name} & \textbf{Ave.
-degree} & \textbf{Ave.
-shortest path} & \textbf{Graph diameter} & \textbf{Graph density} & \textbf{Graph clustering coefficient} & \textbf{Ave.
-closeness centrality} & \textbf{Ave.
-betweenness centrality} & \textbf{Ave.
-eigenvector centrality} & \textbf{1-WL color count} \\ \hline
-        COIL-DEL & 4.673071633424515 & 2.128750184714701 & 4.06974358974359 & 0.3275202823564923 & 0.546258039207784 & 0.5122126871677409 & 0.0647750716657882 & 0.2431245565997526 & 21.102564102564106 \\ \hline
-        COIL-RAG & 1.8277218368573067 & 1.0604823111763986 & 1.242159383033419 & 0.924030303030303 & 0.5903545713545713 & 0.94372526076617 & 0.0462785547785547 & 0.5905014648511226 & 1.3115384615384615 \\ \hline
-        Cuneiform & 4.079588014981273 & 2.244427103288844 & 3.0 & 0.2222330604444725 & 0.8634154547075895 & 0.4613474974345972 & 0.0722909733763576 & 0.1963017855703223 & 2.0 \\ \hline
-        Fingerprint & 1.4868577990824814 & 2.115136284036567 & 4.344413012729844 & 0.4391785351497472 & 0.0017307791737759 & 0.5069423734352098 & 0.1840341453794884 & 0.4207756269406634 & 3.656584457887389 \\ \hline
-        FIRSTMM\_DB & 4.50236815941043 & 12.309044701937715 & 30.676056338028168 & 0.0074027477877271 & 0.2631922211539924 & 0.0551742654129266 & 0.0188189276256195 & 0.0092704028700914 & 1357.8292682926829 \\ \hline
-        Letter-high & 1.889683607525296 & 1.4794456563750826 & 2.444490301279405 & 0.5791851851851852 & 0.2976163139329805 & 0.6794971082752952 & 0.1657867724867724 & 0.4611670600331147 & 2.994222222222222 \\ \hline
-        Letter-low & 1.3213534599145254 & 1.33364428641149 & 1.955783308931186 & 0.4165470899470899 & 0.0 & 0.4955472438922087 & 0.1618904761904762 & 0.4407481624189365 & 2.471111111111111 \\ \hline
-        Letter-med & 1.352705840084288 & 1.3502031822344325 & 2.006610576923077 & 0.4245777777777778 & 0.0139393298059964 & 0.5071406868429822 & 0.1683222222222222 & 0.4416562761104123 & 2.517333333333333 \\ \hline
-        MSRC\_9 & 4.81534002269555 & 3.113629895894764 & 7.004524886877828 & 0.1235873024311543 & 0.5412981657910688 & 0.33102605797573 & 0.055215313789426 & 0.1368862401087341 & 40.36199095022624 \\ \hline
-        MSRC\_21 & 5.102391318360188 & 4.094474312024695 & 9.621669626998225 & 0.0680571076593652 & 0.5146660459581984 & 0.251511488615992 & 0.041532868642658 & 0.0936632954729105 & 77.22735346358792 \\ \hline
-        MSRC\_21C & 4.782574662751558 & 3.113761314016 & 6.971291866028708 & 0.1240107738760322 & 0.5427170070575877 & 0.3315153420789583 & 0.0557392711060186 & 0.1371850938080253 & 40.05263157894737 \\ \hline
-        DD & 4.979061666490266 & 7.919898418826995 & 19.70016611295681 & 0.0278322962071925 & 0.4793770769559906 & 0.1402074694227141 & 0.0324963430907113 & 0.0342447661028087 & 278.28013582342953 \\ \hline
-        ENZYMES & 3.862625308732192 & 4.2810541955964485 & 10.4265625 & 0.1598878125179543 & 0.4533912862690096 & 0.263573448964092 & 0.1158938852730127 & 0.1471447702872793 & 28.575 \\ \hline
-        KKI & 3.1856769969664422 & 3.500870554422239 & 8.144578313253012 & 0.1792960793494088 & 0.3526436673677589 & 0.3358793648012939 & 0.1297799757896069 & 0.1757034314039908 & 24.81927710843373 \\ \hline
-        OHSU & 4.327667933476122 & 4.921680537597515 & 12.69620253164557 & 0.0822944467200859 & 0.3808295357080805 & 0.2407028072344937 & 0.0655860979728088 & 0.0823969445758651 & 77.51898734177215 \\ \hline
-        Peking\_1 & 3.5514470044304343 & 3.968106920104182 & 9.623529411764704 & 0.1276151076564966 & 0.3673053988324483 & 0.2889094228756093 & 0.0998385744518594 & 0.1284748145692827 & 36.72941176470588 \\ \hline
-        PROTEINS & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        PROTEINS\_full & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        COLORS-3 & 2.928853359699249 & 2.5810313856214724 & 5.275766205587198 & 0.1695881211511339 & 0.1450387037596311 & 0.3502761440955542 & 0.0639043708084029 & 0.1737080119571242 & 56.95904761904762 \\ \hline
-        SYNTHETIC & 3.920000076293945 & 3.5064646464646465 & 7.0 & 0.0395959595959595 & 0.0203095238095238 & 0.2893391429701345 & 0.0255761698618841 & 0.0831547830080052 & 100.0 \\ \hline
-        SYNTHETICnew & 3.9250000715255737 & 3.4872567329242026 & 7.274834437086093 & 0.0396464646464646 & 0.0229497089947089 & 0.289441726009901 & 0.0255427746856318 & 0.0836273264155355 & 99.96333333333334 \\ \hline
-        Synthie & 3.6210444450378416 & 2.6348743925562266 & 5.494845360824742 & 0.038420429009193 & 0.0937036201778145 & 0.2766177855177352 & 0.0231922369186012 & 0.0786632559723412 & 90.6125 \\ \hline
-        TRIANGLES & 3.1404920884927114 & 2.263375484124684 & 4.557498816896771 & 0.2416135135324899 & 0.2286352011335792 & 0.4374025890339534 & 0.0821216496736849 & 0.226180376713217 & 19.88371111111111 \\ \hline
-        AIDS & 2.0128653862178325 & 3.490507728804514 & 7.762604013705335 & 0.1935408261794486 & 0.0071746166779525 & 0.3500774185559109 & 0.1911961844012523 & 0.262770387548969 & 11.8145 \\ \hline
-        BZR & 2.1466610419897387 & 5.154837461860052 & 11.65679012345679 & 0.0648920405178712 & 8.903397114779228e-05 & 0.2054846442932875 & 0.1245291263310628 & 0.1416530437212679 & 29.607407407407408 \\ \hline
-        BZR\_MD & 20.30392156862745 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2203726689661978 & 1.0 \\ \hline
-        COX2 & 2.107735009469108 & 5.936420803578038 & 13.790149892933618 & 0.0529052472359257 & 0.0007216110850642 & 0.1757209022905502 & 0.1262987138392391 & 0.1288265342157682 & 28.09421841541756 \\ \hline
-        COX2\_MD & 25.27722772277228 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.1957034193657646 & 1.0 \\ \hline
-        DHFR & 2.102359890622437 & 6.144674814243727 & 14.603174603174605 & 0.0536754666970741 & 0.0 & 0.1734264353163348 & 0.1288500765571343 & 0.1271607693927877 & 32.21560846560847 \\ \hline
-        DHFR\_MD & 22.8676844783715 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2076620678810238 & 1.0 \\ \hline
-        ER\_MD & 20.327354260089685 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2244695039966339 & 1.0 \\ \hline
-        FRANKENSTEIN & 2.0627741588132293 & 3.6742676066855062 & 8.423452029938762 & 0.1705038719060743 & 0.0106826329262756 & 0.3148146889108825 & 0.1923606317376928 & 0.2432099454364741 & 13.42448697256168 \\ \hline
-        MCF-7 & 2.1516180606917765 & 5.050070569624072 & 12.141178938535766 & 0.0980572307942984 & 0.0020345164969653 & 0.2175444791564102 & 0.1724077067751488 & 0.1725022149133201 & 21.418113071660063 \\ \hline
-        MCF-7H & 2.0888838372172147 & 5.858613378052236 & 13.306228605946709 & 0.0537227676449342 & 0.0005825022974507 & 0.1778419519669024 & 0.1198217621207925 & 0.1223362659022958 & 32.9756211739287 \\ \hline
-        MOLT-4 & 2.146077948348501 & 4.951738679286625 & 11.874633536790505 & 0.0987082247303717 & 0.0019246147011501 & 0.2183304220273518 & 0.1714407445609207 & 0.1734293274657891 & 21.028995347667543 \\ \hline
-        MOLT-4H & 2.0858484049375803 & 5.738056140581633 & 12.992424764134702 & 0.0539489355320176 & 0.0005343843281943 & 0.17815930623996 & 0.1192636780853368 & 0.1228930198480923 & 32.272249465610464 \\ \hline
-        Mutagenicity & 2.0379886209469995 & 4.418912992995495 & 9.63701923076923 & 0.0912875415379717 & 0.0031125822886973 & 0.2466634939984061 & 0.1371754284356414 & 0.1710356482094367 & 20.874567673507038 \\ \hline
-        MUTAG & 2.18877208359698 & 3.626150957182829 & 8.21808510638298 & 0.1384540671648269 & 0.0 & 0.293764054092514 & 0.1694459751944365 & 0.2197353385133972 & 14.8031914893617 \\ \hline
-        NCI1 & 2.15501380214726 & 5.234873158476093 & 12.659402381487306 & 0.088944910671084 & 0.0030999008340164 & 0.2026186665583615 & 0.1631676786426253 & 0.1607325923179734 & 24.721411192214116 \\ \hline
-        NCI109 & 2.156446177386937 & 5.183950502801717 & 12.49528936742934 & 0.0894286690245151 & 0.0030732389355228 & 0.20411132911515 & 0.1624231134845694 & 0.1617585552708976 & 24.52410952265568 \\ \hline
-        NCI-H23 & 2.1451602406810686 & 4.950946501654924 & 11.869525050337558 & 0.0987776628128759 & 0.0018996992922189 & 0.2183535143438838 & 0.1715792456717554 & 0.1735208031755432 & 20.99303645329963 \\ \hline
-        NCI-H23H & 2.085327596320919 & 5.734343001278942 & 12.983736711151325 & 0.0539842770435475 & 0.0005268942359655 & 0.1782099752168056 & 0.1192891041739607 & 0.1229635264798962 & 32.22578246970485 \\ \hline
-        OVCAR-8 & 2.145637268375766 & 4.945169149304127 & 11.85222800857742 & 0.0987730040211328 & 0.0018986224960467 & 0.2183941696064956 & 0.171403631603811 & 0.1735393405097124 & 20.98556125974924 \\ \hline
-        OVCAR-8H & 2.0856259705836995 & 5.728655397369023 & 12.966769410758882 & 0.0539777071171825 & 0.0005298176630677 & 0.1782129665549435 & 0.1192148511162624 & 0.1229665170804826 & 32.22561457202093 \\ \hline
-        P388 & 2.109217112454913 & 4.355752638151867 & 10.21824835544779 & 0.1190787859581164 & 0.0037544697177687 & 0.2459957278657192 & 0.1789538865626834 & 0.1958220277248745 & 17.133174189814813 \\ \hline
-        P388H & 2.0638945394922854 & 5.289795718220624 & 11.765664188214403 & 0.0639638393366292 & 0.0009642194122106 & 0.1971310478874152 & 0.1240122910178544 & 0.1373237905541068 & 26.71100983796296 \\ \hline
-        PC-3 & 2.1520653447146643 & 5.05018085139685 & 12.140862989009436 & 0.098055200309084 & 0.0019733135754618 & 0.2175815805232795 & 0.1725492873407526 & 0.172560720893664 & 21.37340506743248 \\ \hline
-        PC-3H & 2.08922384690422 & 5.857822430952191 & 13.30650249313117 & 0.0537656750613318 & 0.0005561305149752 & 0.1779189564869681 & 0.1200247359820712 & 0.1224665687629844 & 32.881929550328984 \\ \hline
-        PTC\_FM & 1.9758043374578045 & 3.311647990381311 & 7.36676217765043 & 0.2154944740700171 & 0.0091220986824968 & 0.3693003427913903 & 0.2055882581121011 & 0.2786143302706905 & 9.91404011461318 \\ \hline
-        PTC\_FR & 1.9863111707899304 & 3.387662268892836 & 7.589743589743589 & 0.2085568638656639 & 0.0088214579442649 & 0.3612672957602951 & 0.2045358868174996 & 0.2734008790739162 & 10.22222222222222 \\ \hline
-        PTC\_MM & 1.9701179610121815 & 3.301432053360394 & 7.339285714285714 & 0.2223452925857377 & 0.0130582137161084 & 0.374488207420213 & 0.2059637189235834 & 0.2823441282735879 & 9.803571428571429 \\ \hline
-        PTC\_MR & 1.9805375618297 & 3.3577641223936463 & 7.523255813953488 & 0.2137888896192228 & 0.009509685286154 & 0.3666473296924281 & 0.2062170509277356 & 0.2777684525909222 & 10.040697674418604 \\ \hline
-        SF-295 & 2.145489384462884 & 4.9445677038396125 & 11.852116182572614 & 0.09881526807439 & 0.0019131887956769 & 0.2184346701016761 & 0.1714761059761314 & 0.1735919743359789 & 20.97159246107621 \\ \hline
-        SF-295H & 2.0855234748235936 & 5.727434951743517 & 12.9664274556856 & 0.0539895579758234 & 0.0005299113307649 & 0.1782697110808576 & 0.1192036786794211 & 0.1229816733300816 & 32.196146110104046 \\ \hline
-        SN12C & 2.145026913904858 & 4.94825141099449 & 11.86401279205747 & 0.0987936439503507 & 0.001927945706436 & 0.2183468315283276 & 0.1714975830848956 & 0.1735570013676089 & 20.99167583241676 \\ \hline
-        SN12CH & 2.0853053252079072 & 5.730086714838555 & 12.973598487437071 & 0.0540104189866913 & 0.0005390487212868 & 0.1781938757210136 & 0.1192686561921279 & 0.1230077396296653 & 32.236301369863014 \\ \hline
-        SW-620 & 2.1452310279340394 & 4.94393636762053 & 11.851577038136291 & 0.0988746005232462 & 0.0018522578567537 & 0.2185003794708548 & 0.1714920826604129 & 0.1736489333480562 & 20.97197276226192 \\ \hline
-        SW-620H & 2.0854275176564645 & 5.725806234940699 & 12.962851360467733 & 0.054054544610838 & 0.0005110193017508 & 0.1783225632271403 & 0.1192839052512742 & 0.1230820111720522 & 32.19651139840126 \\ \hline
-        UACC257 & 2.145698715720169 & 4.955834964420495 & 11.885704040162564 & 0.0987250195703296 & 0.0018738116805416 & 0.218300263582104 & 0.1716221375949755 & 0.1734631006815176 & 20.994198259477844 \\ \hline
-        UACC257H & 2.0856917230912635 & 5.740515645090362 & 13.003174313183676 & 0.0539749990285044 & 0.0005209407683445 & 0.1781806662974605 & 0.1193640515072574 & 0.122956068725157 & 32.22436731019306 \\ \hline
-        Yeast & 2.099442849357738 & 4.364322361013096 & 10.26343257027636 & 0.1210553127513687 & 0.0022671334945899 & 0.2476806589296417 & 0.183060827627568 & 0.1985665767951158 & 16.67475282973832 \\ \hline
-        YeastH & 2.0589509621359707 & 5.245391698622407 & 11.6875493153864 & 0.0642704732457107 & 0.0005773570062507 & 0.1983872537891083 & 0.1254655281986756 & 0.1384817929367545 & 26.05320284921044 \\ \hline
-        Sum & 242.8347529362711 & 258.6723790469145 & 587.9183294923151 & 12.731666924394474 & 11.845921907393928 & 20.687237238791475 & 7.3848149134808 & 11.636469235194477 & 3245.599253687252 \\ \hline
-    \end{tabular}
-    \caption{Graph parameters of the datasets}
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of GCN model}
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\ \hline
-        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\ \hline
-        MOLT-4 & 0.0 & 0.014102176763117313 \\ \hline
-        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\ \hline
-        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\ \hline
-        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\ \hline
-        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\ \hline
-        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\ \hline
-        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\ \hline
-        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\ \hline
-        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\ \hline
-        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\ \hline
-        P388 & 0.008062511682510376 & 0.01043933816254139 \\ \hline
-        P388H & 0.006343752145767212 & 0.007148966193199158 \\ \hline
-        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\ \hline
-        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\ \hline
-        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\ \hline
-        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\ \hline
-        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\ \hline
-        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\ \hline
-        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\ \hline
-        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\ \hline
-        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\ \hline
-        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\ \hline
-        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\ \hline
-        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\ \hline
-        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\ \hline
-        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\ \hline
-        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\ \hline
-        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\ \hline
-        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\ \hline
-        DD & -0.1750326007604599 & 0.3490835428237915 \\ \hline
-        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\ \hline
-        KKI & 0.04776120185852051 & 0.2546080946922302 \\ \hline
-        OHSU & 0.39824172854423523 & 0.138640895485878 \\ \hline
-        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\ \hline
-        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\ \hline
-        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\ \hline
-        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\ \hline
-        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ \hline
-    \end{tabular}
-    \caption{Generalization error of the GCN model on 57 datasets}
-    \label{tab:ge_gcn} % ge -> generalization error
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of SGC model}
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        PROTEINS\_full & 0.04741409420967102 & 0.5624663829803467 \\ \hline
-        DD & -0.21720178425312042 & 0.40132829546928406 \\ \hline
-        ENZYMES & 0.3279166519641876 & 0.060605552047491074 \\ \hline
-        KKI & 0.10951493680477142 & 0.24877962470054626 \\ \hline
-        OHSU & 0.07604396343231201 & 0.1943538784980774 \\ \hline
-        Peking\_1 & 0.1769927442073822 & 0.22724425792694092 \\ \hline
-        COLORS-3 & 0.11781251430511475 & 0.04669201001524925 \\ \hline
-        SYNTHETIC & -0.37541666626930237 & 0.4494529068470001 \\ \hline
-        SYNTHETICnew & -0.36666664481163025 & 0.46157106757164 \\ \hline
-        Synthie & 0.13749998807907104 & 0.042466290295124054 \\ \hline
-        AIDS & 0.006437480449676514 & 0.011520843021571636 \\ \hline
-        BZR & 0.10815385729074478 & 0.21917256712913513 \\ \hline
-        BZR\_MD & 0.1678861677646637 & 0.09830881655216217 \\ \hline
-        COX2 & 0.07495072484016418 & 0.13212721049785614 \\ \hline
-        COX2\_MD & 0.14868313074111938 & 0.16540752351284027 \\ \hline
-        DHFR & 0.1332409381866455 & 0.1551705300807953 \\ \hline
-        DHFR\_MD & 0.0777045264840126 & 0.2503173351287842 \\ \hline
-        ER\_MD & -0.008367183618247509 & 0.15631815791130066 \\ \hline
-        FRANKENSTEIN & 0.10787498950958252 & 0.05383045971393585 \\ \hline
-        MCF-7 & 0.35490626096725464 & 0.17573890089988708 \\ \hline
-        MCF-7H & 0.3593124747276306 & 0.1884346306324005 \\ \hline
-        MOLT-4 & 0.18021871149539948 & 0.39803561568260193 \\ \hline
-        MOLT-4H & 0.18649999797344208 & 0.3838197886943817 \\ \hline
-        Mutagenicity & 0.04325000196695328 & 0.028246337547898293 \\ \hline
-        MUTAG & 0.07375730574131012 & 0.13988283276557922 \\ \hline
-        NCI1 & 0.09100000560283661 & 0.16161812841892242 \\ \hline
-        NCI109 & -0.06128125637769699 & 0.2943810522556305 \\ \hline
-        NCI-H23 & 0.31696873903274536 & 0.07884199917316437 \\ \hline
-        NCI-H23H & 0.3696562349796295 & 0.06490368396043777 \\ \hline
-        OVCAR-8 & 0.3291874825954437 & 0.0815950483083725 \\ \hline
-        OVCAR-8H & 0.2902187705039978 & 0.0771569237112999 \\ \hline
-        P388 & 0.3618437647819519 & 0.13428252935409546 \\ \hline
-        P388H & -0.052218757569789886 & 0.3646376132965088 \\ \hline
-        PC-3 & -0.08028124272823334 & 0.29225972294807434 \\ \hline
-        PC-3H & 0.2593437135219574 & 0.22314861416816711 \\ \hline
-        PTC\_FM & 0.10863511264324188 & 0.14730817079544067 \\ \hline
-        PTC\_FR & 0.08632432669401169 & 0.09645862877368927 \\ \hline
-        PTC\_MM & 0.09649830311536789 & 0.0817335695028305 \\ \hline
-        PTC\_MR & 0.060720354318618774 & 0.18291200697422028 \\ \hline
-        SF-295 & 0.3124375343322754 & 0.11770480871200562 \\ \hline
-        SF-295H & 0.28881245851516724 & 0.12331245839595795 \\ \hline
-        SN12C & 0.2917812764644623 & 0.05537300556898117 \\ \hline
-        SN12CH & 0.3397812247276306 & 0.09572991728782654 \\ \hline
-        SW-620 & 0.3427812457084656 & 0.2430398166179657 \\ \hline
-        SW-620H & 0.39274999499320984 & 0.1998475342988968 \\ \hline
-        UACC257 & -0.10218751430511475 & 0.2883416414260864 \\ \hline
-        UACC257H & 0.3322499692440033 & 0.22775331139564514 \\ \hline
-        Yeast & 0.0 & 0.0 \\ \hline
-        YeastH & 0.0 & 0.0 \\ \hline
-    \end{tabular}
-\end{table}
-
-\subsubsection{Generalization error of GATv2 model}
-
-\subsubsection{Generalization error of MPNN model}
-
-\subsubsection{Corrolation analysis between generalization error and graph parameters}
-
-\subsection{Discussion}
-
-\section{Conclusion}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{main} % refers to example.bib
-
-\clearpage
-
-\section{Appendix}
-
-\subsection{Basic information about TUDataset}\label{sec:datasets}
-This table~\ref{tab:datasets} shows the information about a list of datasets used in this thesis.
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|}
-    \hline
-        name & Graphs & Classes & Avg. Nodes & Avg. Edges & catagory \\ \hline
-        AIDS & 2000 & 2 & 15.69 & 16.20 & Small molecules \\ \hline
-        BZR & 405 & 2 & 35.75 & 38.36 & Small molecules \\ \hline
-        BZR\_MD & 306 & 2 & 21.30 & 225.06 & Small molecules \\ \hline
-        COX2 & 467 & 2 & 41.22 & 43.45 & Small molecules \\ \hline
-        COX2\_MD & 303 & 2 & 26.28 & 335.12 & Small molecules \\ \hline
-        DHFR & 756 & 2 & 42.43 & 44.54 & Small molecules \\ \hline
-        DHFR\_MD & 393 & 2 & 23.87 & 283.02 & Small molecules \\ \hline
-        ER\_MD & 446 & 2 & 21.33 & 234.85 & Small molecules \\ \hline
-        FRANKENSTEIN & 4337 & 2 & 16.90 & 17.88 & Small molecules \\ \hline
-        MCF-7 & 27770 & 2 & 26.40 & 28.53 & Small molecules \\ \hline
-        MCF-7H & 27770 & 2 & 47.31 & 49.44 & Small molecules \\ \hline
-        MOLT-4 & 39765 & 2 & 26.10 & 28.14 & Small molecules \\ \hline
-        MOLT-4H & 39765 & 2 & 46.70 & 48.74 & Small molecules \\ \hline
-        Mutagenicity & 4337 & 2 & 30.32 & 30.77 & Small molecules \\ \hline
-        MUTAG & 188 & 2 & 17.93 & 19.79 & Small molecules \\ \hline
-        NCI1 & 4110 & 2 & 29.87 & 32.30 & Small molecules \\ \hline
-        NCI109 & 4127 & 2 & 29.68 & 32.13 & Small molecules \\ \hline
-        NCI-H23 & 40353 & 2 & 26.07 & 28.10 & Small molecules \\ \hline
-        NCI-H23H & 40353 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        OVCAR-8 & 40516 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        OVCAR-8H & 40516 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        P388 & 41472 & 2 & 22.11 & 23.56 & Small molecules \\ \hline
-        P388H & 41472 & 2 & 40.45 & 41.89 & Small molecules \\ \hline
-        PC-3 & 27509 & 2 & 26.36 & 28.49 & Small molecules \\ \hline
-        PC-3H & 27509 & 2 & 47.20 & 49.33 & Small molecules \\ \hline
-        PTC\_FM & 349 & 2 & 14.11 & 14.48 & Small molecules \\ \hline
-        PTC\_FR & 351 & 2 & 14.56 & 15.00 & Small molecules \\ \hline
-        PTC\_MM & 336 & 2 & 13.97 & 14.32 & Small molecules \\ \hline
-        PTC\_MR & 344 & 2 & 14.29 & 14.69 & Small molecules \\ \hline
-        SF-295 & 40271 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SF-295H & 40271 & 2 & 46.65 & 48.68 & Small molecules \\ \hline
-        SN12C & 40004 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        SN12CH & 40004 & 2 & 46.69 & 48.72 & Small molecules \\ \hline
-        SW-620 & 40532 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SW-620H & 40532 & 2 & 46.63 & 48.66 & Small molecules \\ \hline
-        UACC257 & 39988 & 2 & 26.09 & 28.13 & Small molecules \\ \hline
-        UACC257H & 39988 & 2 & 46.68 & 48.71 & Small molecules \\ \hline
-        Yeast & 79601 & 2 & 21.54 & 22.84 & Small molecules \\ \hline
-        YeastH & 79601 & 2 & 39.45 & 40.75 & Small molecules \\ \hline
-        DD & 1178 & 2 & 284.32 & 715.66 & Bioinformatics \\ \hline
-        ENZYMES & 600 & 6 & 32.63 & 62.14 & Bioinformatics \\ \hline
-        KKI & 83 & 2 & 26.96 & 48.42 & Bioinformatics \\ \hline
-        OHSU & 79 & 2 & 82.01 & 199.66 & Bioinformatics \\ \hline
-        Peking\_1 & 85 & 2 & 39.31 & 77.35 & Bioinformatics \\ \hline
-        PROTEINS\_full & 1113 & 2 & 39.06 & 72.82 & Bioinformatics \\ \hline
-        COIL-DEL & 3900 & 100 & 21.54 & 54.24 & Computer vision \\ \hline
-        COIL-RAG & 3900 & 100 & 3.01 & 3.02 & Computer vision \\ \hline
-        Cuneiform & 267 & 30 & 21.27 & 44.80 & Computer vision \\ \hline
-        Fingerprint & 2149 & 15 & 7.06 & 5.76 & Computer vision \\ \hline
-        FIRSTMM\_DB & 41 & 11 & 1377.27 & 3074.10 & Computer vision \\ \hline
-        Letter-high & 2250 & 15 & 4.67 & 4.50 & Computer vision \\ \hline
-        Letter-low & 2250 & 15 & 4.68 & 3.13 & Computer vision \\ \hline
-        Letter-med & 2250 & 15 & 4.67 & 3.21 & Computer vision \\ \hline
-        MSRC\_9 & 221 & 8 & 40.58 & 97.94 & Computer vision \\ \hline
-        MSRC\_21 & 563 & 20 & 77.52 & 198.32 & Computer vision \\ \hline
-        MSRC\_21C & 209 & 20 & 40.28 & 96.60 & Computer vision \\ \hline
-        COLORS-3 & 10500 & 11 & 61.31 & 91.03 & Synthetic \\ \hline
-        SYNTHETIC & 300 & 2 & 100.00 & 196.00 & Synthetic \\ \hline
-        SYNTHETICnew & 300 & 2 & 100.00 & 196.25 & Synthetic \\ \hline
-        Synthie & 400 & 4 & 95.00 & 172.93 & Synthetic \\ \hline
-    \end{tabular}
-    \caption{Basic information about the datasets used in the experiment}
-    \label{tab:datasets}
-\end{table}
-
-\subsection{Example of GCN model}
-
-\begin{lstlisting}[language=Python]
-import torch
-
-\end{lstlisting}
-
-\end{document}

### 2025-01-29 paper/chapters/introduction.tex
Add thesis structure including title page, abstract, acknowledgments, conclusion, and related work sections

--- 2025-01-17 thesis/main.tex
@@
-\documentclass{article}
-\usepackage{geometry}
-\geometry{
-    a4paper,
-    left=30mm,
-    right=30mm,
-    top=30mm,
-    bottom=30mm
-}
-
-\usepackage{annotate-equations}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-% \usepackage{figure}
-
-\graphicspath{ {./media/} }
-\usepackage[square,numbers]{natbib}
-\usepackage[nottoc]{tocbibind}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{enumitem}
-\usepackage{float}
-
-\usepackage{amssymb}
-\usepackage{amsmath}
-
-\usepackage{tikz}
-\usepackage{listings}
-\usepackage{setspace}
-\definecolor{Code}{rgb}{0,0,0}
-\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
-\definecolor{Numbers}{rgb}{0.5,0,0}
-\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
-\definecolor{Keywords}{rgb}{0,0,1}
-\definecolor{self}{rgb}{0,0,0}
-\definecolor{Strings}{rgb}{0,0.63,0}
-\definecolor{Comments}{rgb}{0,0.63,1}
-\definecolor{Backquotes}{rgb}{0,0,0}
-\definecolor{Classname}{rgb}{0,0,0}
-\definecolor{FunctionName}{rgb}{0,0,0}
-\definecolor{Operators}{rgb}{0,0,0}
-\definecolor{Background}{rgb}{0.98,0.98,0.98}
-\lstdefinelanguage{Python}{
-	numbers=left,
-	numberstyle=\footnotesize,
-	numbersep=1em,
-	xleftmargin=1em,
-	framextopmargin=2em,
-	framexbottommargin=2em,
-	showspaces=false,
-	showtabs=false,
-	showstringspaces=false,
-	frame=l,
-	tabsize=4,
-	% Basic
-	basicstyle=\ttfamily\small\setstretch{1},
-	backgroundcolor=\color{Background},
-	% Comments
-	commentstyle=\color{Comments}\slshape,
-	% Strings
-	stringstyle=\color{Strings},
-	morecomment=[s][\color{Strings}]{"""}{"""},
-	morecomment=[s][\color{Strings}]{'''}{'''},
-	% keywords
-	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
-	keywordstyle={\color{Keywords}\bfseries},
-	% additional keywords
-	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
-	keywordstyle={[2]\color{Decorators}\slshape},
-	emph={self},
-	emphstyle={\color{self}\slshape},
-	%
-}
-
-\title{\textbf{Bachelor thesis}\\
-Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}
-
-\author{Author: Wensheng Zhang}
-
-\date{\today}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
-\end{abstract}
-
-\section{Introduction}\label{sec:intro}
+\chapter{Introduction}\label{chap:introduction}
 Graph learning became a hot topic in the field of machine learning in recent years.
-Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
+Graph Neural Networks (GNNs)~\cite{gori2005new}, also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
 GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
@@
 
-Speaking more specifically.
+To reach this goal, I conduct two sets of experiments.
 First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree.
@@
 In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset.
-In this thesis, 57 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
+In this thesis, 50 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
 Second, I train different GNN models on each dataset and find that their generalization abilities varied.
@@
 
-\subsection{Related work}
-The following section provides an overview of the related work.
+The thesis is organized as follows.
+In Chapter~\ref{chap:background}, I provide background information on graph neural networks and generalization.
+In Chapter~\ref{chap:experiments}, I describe the methodology used to conduct the experiments.
+In Chapter~\ref{chap:results}, I present the experimental results and discuss the results and their implications.
+Finally, in Chapter~\ref{chap:conclusions}, I conclude the thesis and discuss future work.
 
-\subsubsection{Graph parameters}
-
-\subsubsection{Generalization error}
-
-\section{Background on learning on graphs}
-The following sections provide an overview of the concepts and methods related to graph learning, machine learning, and graph neural networks.
-
-\subsection{Notion}
-At first, we need to define some terms with regard to the graph.
-In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
-We use $\mathbb{G}$ to represent the set of all possible graphs.
-The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$.
-The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
-In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.
-A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included.
-These vectors can be used to characterize graphs or nodes in graphs.
-The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph.
-The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.
-
-\subsection{Machine learning}
-Machine learning is a subfield of artificial intelligence that focuses on the development of algorithms that can learn from and make predictions or decisions based on data.
-The goal of machine learning is to develop models that can generalize well to unseen data.
-The model is trained on a training dataset, which consists of input-output pairs.
-The model is then evaluated on a test dataset, which is separate from the training dataset.
-
-\subsubsection{Gradient Descent}
-Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
-The algorithm works by computing the gradient of the function at a given point and then updating the point in the direction of the negative gradient.
-The update rule is given by
-
-$$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t)
-$$
-where $\theta_t$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(\theta_t)$ is the gradient of the function $f$ at $\theta_t$.
-The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Stochastic Gradient Descent}
-Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
-The algorithm works by randomly selecting a mini-batch of data points from the training dataset, computing the gradient of the loss function with respect to the mini-batch, and then updating the parameters based on the gradient.
-The update rule is given by
-
-$$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t; x_{i:t}, y_{i:t})
-$$
-where $x_{i:t}$ and $y_{i:t}$ are the mini-batch of data points and labels, respectively. The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Backpropagation}
-Backpropagation is an algorithm used to compute the gradients of the loss function with respect to the parameters of a neural network.
-The algorithm works by computing the gradient of the loss function with respect to the output of the network and then propagating the gradient backward through the network to compute the gradients of the loss function with respect to the parameters.
-The gradients are then used to update the parameters of the network using an optimization algorithm such as gradient descent.
-
-\subsubsection{Regularization}
-Regularization is a technique used to prevent overfitting in machine learning models.
-Overfitting occurs when a model learns the noise in the training data rather than the underlying pattern.
-Regularization works by adding a penalty term to the loss function that discourages the model from learning complex patterns that are specific to the training data.
-There are two common types of regularization: $L1$ regularization and $L2$ regularization.
-$L1$ regularization adds a penalty term that is proportional to the $L1$ norm of the parameters, while $L2$ regularization adds a penalty term that is proportional to the $L2$ norm of the parameters.
-The regularization parameter $\lambda$ controls the strength of the regularization.
-
-\subsubsection{Early Stopping}
-Early stopping is a technique used to prevent overfitting in machine learning models.
-The idea is to monitor the performance of the model on a validation dataset during training and stop training when the performance starts to degrade.
-This is done by saving the model parameters at each iteration and selecting the model with the best performance on the validation dataset.
-Early stopping is a form of regularization that prevents the model from learning the noise in the training data.
-
-\subsubsection{Cross-validation}
-Cross-validation is a technique used to evaluate the performance of a machine learning model.
-The idea is to split the dataset into multiple subsets, or folds, and train the model on one subset while evaluating it on the remaining subsets.
-This process is repeated multiple times, with each subset used as the test set once.
-The performance of the model is then averaged over all the folds to obtain an estimate of the model's generalization performance.
-Cross-validation is used to prevent overfitting and to obtain a more accurate estimate of the model's performance.
-
-\subsubsection{Hyperparameter tuning}
-Hyperparameter tuning is the process of selecting the optimal hyperparameters for a machine learning model.
-Hyperparameters are parameters that are set before the training process begins and control the behavior of the model.
-Examples of hyperparameters include the learning rate, batch size, number of hidden layers, and number of epochs.
-Hyperparameter tuning is typically done using a grid search or random search over a predefined set of hyperparameters.
-The goal is to find the set of hyperparameters that results in the best performance on a validation dataset.
-
-\subsubsection{Loss function}
-The loss function is a function that measures the difference between the predicted output of a model and the true output.
-The goal of training a machine learning model is to minimize the loss function, which is done by adjusting the parameters of the model using an optimization algorithm such as gradient descent.
-The choice of loss function depends on the task at hand.
-For classification tasks, the cross-entropy loss function is commonly used, while for regression tasks, the mean squared error loss function is often used.
-
-\subsubsection{Optimization algorithm}
-An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
-The goal is to find the set of parameters that minimizes the loss function.
-Gradient descent is a common optimization algorithm used in machine learning, but there are many variants of gradient descent that are designed to improve convergence speed and stability.
-Some popular optimization algorithms include Adam~\cite{kingma2014adam}, RMSprop~\cite{graves2013generating}, and Adagrad~\cite{duchi2011adaptive}.
-These algorithms use different strategies to update the parameters of the model and can be more effective than standard gradient descent in certain situations.
-
-\subsubsection{Generalization}
-A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
-This is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
-It is defined as
-
-$$
-    E_{gen} = {Acc_{train}} - {Acc_{test}}
-$$
-where $Acc_{train}$ is the accuracy of the model on the training dataset, and $Acc_{test}$ is the accuracy of the model on the test dataset.
-The accuracy $Acc$ on a dataset is defined as the proportion of correctly classified graphs, that is, $Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$.
-
-The empirical generalization error is also known as the generalization gap~\cite{goodfellow2016deep}.
-Typically, the learning on the training dataset and test dataset behaves differently.
-The model may perform well on the training dataset but poorly on the test dataset.
-By observing the generalization error, we can decide on a stopping criterion for the training process.
-And the generalization error can be used to determine whether the model is overfitting or underfitting.
-Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g.
-Graph parameter).
+\section{Related work}
+In the following section, I will discuss the related work on graph neural networks and generalization.
 
 \subsection{Graph Neural Networks}
-Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
-The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
-This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification, edge prediction, and graph classification.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN), Graph Attention Networks (GAT), and Message Passing Neural Networks (MPNN).
+Graph neural networks were initially proposed by Gori et al.~\cite{gori2005new} and Scarselli et al.~\cite{scarselli2008graph} as a variant of recurrent neural networks and demonstrated its generalization capabilities.
+The work of Kipf and Welling~\cite{kipf2016semi} introduced the Graph Convolutional Networks (GCN) model, which received widespread attention from the research community.
+Velickovic et al.~\cite{velickovic2020pointer} proposed the Graph Attention Networks (GAT) model, which uses attention mechanisms to aggregate information from neighboring nodes.
+Brody et al.~\cite{brody2021attentive} proposed the GATv2 model, which improves the performance of the GAT model by introducing residual connections and multi-head attention.
+Gilmer et al.~\cite{gilmer2017neural} introduced the Message Passing Neural Networks (MPNN) model, which demonstrated the significant results on the molecular property prediction benchmark;
 
-\subsection{Graph parameters}
-Now we can introduce the concept of a graph parameter.
-A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
-Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
-A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
-This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
+\subsection{Generalization}
+While significant progress has been made in understanding the generalization properties of feed-forward neural networks (FNNs) and recurrent neural networks (RNNs), the generalization abilities of graph neural networks (GNNs) remain less explored due to their of irregular graph structures.
 
-\section{Experimental study}
+Golowich et al.~\cite{golowich2018size} showed the generalization abilities of Feed-forward neural networks (FNNs) with Rademacher complexity.
+The work of Zhang et al.~\cite{zhang2018stabilizing} used SVD-based parameterization to improve the generalization by effectively addressing gradient issues.
 
-\subsection{Experimental setup}
-The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.
+In terms of Recurrent neural networks(RNNs), Chen et al.~\cite{chen2019generalization} studied the generalization properties of vanilla RNNs as well as their variants.
+Z.
+Allen-Zhu et al.~\cite{allen2019can} demonstrates that vanilla SGD enables RNNs to efficiently learn concept classes and overcomes prior exponential generalization bounds.
 
-\subsubsection{Training Framework}
-The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
-PyTorch Geometric is a library for deep learning on graphs and other irregular structures.
-It consists of various methods and utilities to ease the implementation of GNNs.
+But unlike the FNNs and RNNs, GNNs deal with irregular data structures.
+The related work on the generalization of GNNs is limited.
+Scarselli et al.~\cite{scarselli2018vapnik} explored the generalization ability of GNNs by using the Vapnik-Chervonenkis (VC) dimension and further indicated that the generalization ability of such models improve as the number of connected nodes.
+After that, Garg et al.~\cite{garg2020generalization} studied the generalization ability of GNNs via Rademacher bounds.
+In comparison to the work of Scarselli et al., Garg et al.
+provided a tighter bound on the generalization error of GNNs.
 
-\subsubsection{Hyperparameters tuning}
-Before training the models, for each pair of dataset and model, the hyperparameters of the model are tuned.
-In the experiment, 5-fold cross-validation is used to tune the hyperparameters instead of 10-fold cross validation in the final experiment.
-The reason is that the 10-fold cross-validation is computationally expensive and time-consuming.
-
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler.
-Additionally, for the GATv2 model, the number of heads, the dropout rate, and residual are also tuned.
-
-The hyperparameters are tuned using the Bayesian optimization method\cite{frazier2018tutorial}.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-There are five models and 57 datasets, resulting in 285 pairs of dataset and model.
-For each pair, the hyperparameters are tuned using the Bayesian optimization method.
-The hyperparameters are tuned using the validation dataset.
-The validation dataset is a subset of the training dataset that is used to tune the hyperparameters of the model.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-\subsubsection{Datasets}
-The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
-TUDataset is often used for the GNN evaluation.
-It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
-The remaining folds are used for training.
-The training is repeated 10 times, each time with a different test fold.
-The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
-
-I list information about the 57 datasets used in the experiment in the appendix~\ref{sec:datasets}.
-
-\subsubsection{Models}
-In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
-The GCN model is shown in the appendix.
-The GCN model consists of four GCN layers, each followed by a ReLU activation function.
-The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.
-
-\subsubsection{Experimental details}
-The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
-To prevent overfitting and to optimize the use of time, the early stopping is employed.
-The loss function is defined as the cross-entropy loss function.
-The hyperparameters of the model are considered to be tuned.
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping.
-The generalization error is calculated as the difference between the training accuracy and the test accuracy.
-
-\subsubsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
-As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.
-
-\begin{description}
-    \item [Average degree] The average degree of the graph $d_{avg}$ is defined as the average of the degrees of all nodes in the graph, that is
-    $$ d_{avg} = \frac{1}{|V|} \sum_{v \in V} d(v)$$
-    \item [Average shortest path length] The average shortest path length of the graph $a$ is defined as the average of the shortest paths between all pairs of nodes in the graph.
-The shortest path $d(s, t)$ between two nodes $v$ and $w$ is the minimum number of edges that need to be traversed to go from $v$ to $w$.
-The formal definition is
-    $$
-a = \frac{1}{|V|(|V|-1)} \sum_{v \in V} \sum_{w \in V, w \neq v} d(v, w)
-    $$
-
-    \item [Graph diameter] The graph diameter $d$ is the maximum of the shortest paths between all pairs of nodes in the graph, that is,
-    $$
-d = \max_{v \in V} \max_{w \in V, w \neq v} d(v, w)
-    $$
-
-    \item [Graph density] The graph density $p$ is the ratio of the number of edges in the graph to the number of the maximum possible edges in the graph, that is,
-    $$
-p = \frac{2|E|}{|V|(|V|-1)}
-    $$
-
-    \item [Graph clustering coefficient] The graph clustering coefficient $C$ is a measure of the degree to which nodes in a graph tend to cluster together.
-The clustering coefficient of a node $v$ (as known as the local clustering coefficient) is defined as the fraction of the number of triangles that include node $v$ to the maximum possible number of triples centered on node $v$.
-The clustering coefficient of the graph (as known as the global clustering coefficient) is defined as the average of the clustering coefficients of all nodes in the graph.
-The formal definition is
-    $$
-C = \frac{1}{|V|} \sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}
-    $$
-    where the term $|\{(i,j)\in E \mid i, j \in N(v)\}|$ is the number of edges between the neighbors of node $v$, i.e.
-the number of triangles containing node $v$.
-Furthermore, the term $\sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}$ is the sum of the local clustering coefficients of all nodes in the graph, in which the degree of node $v$ is denoted as $d(v)$.
-
-    \item [Centrality measure of graphs] At first we have the definition of centrality measure in the \textbf{node level}.
-The centrality measure of a node is a measure of the importance of the node in the graph.
-There are many centrality measures, such as degree centrality, closeness centrality, betweenness centrality, and eigenvector centrality.
-
-    \textit{Degree centrality} is identical to the average degree of the graph defined above.
-
-    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of the shortest paths from the node $v$ to all other nodes in the graph, that is 
-    $$C_C(v) = \frac{1}{\sum_{w\in V}{d(v ,w)}}$$
-    where $d(v, w)$ is the shortest path between node $v$ and node $w$.
-
-    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of the shortest paths between all pairs of nodes that pass through node $v$, that is
-
-    $$
-        C_B(v) = \sum_{s,t \in V} \frac{\sigma_{st}(v)}{\sigma_{st}}
-    $$
-    where $\sigma_{st}$ is the number of the shortest paths between nodes $s$ and $t$, and $\sigma_{st}(v)$ is the number of the shortest paths between nodes $s$ and $t$ that pass through node $v$.
-
-    \textit{Eigenvector centrality} is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
-Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$-th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
-Mathematically, it can be expressed as:
-
-    \[ C_E(v) = \frac{1}{\lambda} \sum_{u \in N(v)} a_{vu} C_E(u) \]
-
-    where $ \lambda$ is the largest eigenvalue of the adjacency matrix $A$.
-$a_{vu}$ is the element of the adjacency matrix $A$ corresponding to the edge between nodes $v$  and $u$.
-$ C_E(u)$  is the eigenvector centrality of node $u$.
-
-    Finally, in the \textbf{graph level}, the centrality measure of the graph is defined as the average of the centrality measures over all nodes in the graph.
-
-    \item [Average number of coloring in the 1-WL algorithm] 
-    \sloppy
-    The 1-dimensional Weisfeiler-Leman algorithm (1-WL)~\cite{weisfeiler1968reduction} is an algorithm that assigns a unique label(color) to each node in the graph, also known as color refinement.
-The average number of coloring in the 1-WL algorithm is defined as the average number of colors used to color the nodes in the graph.
-The 1-WL algorithm is a powerful graph isomorphism algorithm that can be used to determine if two graphs are isomorphic.
-I give the procedure of the 1-WL algorithm here:
-    \begin{enumerate}
-        \item Assign the same color to all nodes in the graph.
-        \item Two nodes $v$, $u$ are assigned a different color if there is a color c such that the number of c-colored neighbors of $u$ is not equal to the number of c-colored neighbors of $v$.
-        \item Repeat step 2 until the colors of all nodes do not change.
-    \end{enumerate}
-
-\end{description}
-
-\subsection{Results}
-
-\subsubsection{Graph parameters of the datasets}
-
-\begin{table}[!ht]
-    \footnotesize
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-        \textbf{Name} & \textbf{Ave.
-degree} & \textbf{Ave.
-shortest path} & \textbf{Graph diameter} & \textbf{Graph density} & \textbf{Graph clustering coefficient} & \textbf{Ave.
-closeness centrality} & \textbf{Ave.
-betweenness centrality} & \textbf{Ave.
-eigenvector centrality} & \textbf{1-WL color count} \\ \hline
-        COIL-DEL & 4.673071633424515 & 2.128750184714701 & 4.06974358974359 & 0.3275202823564923 & 0.546258039207784 & 0.5122126871677409 & 0.0647750716657882 & 0.2431245565997526 & 21.102564102564106 \\ \hline
-        COIL-RAG & 1.8277218368573067 & 1.0604823111763986 & 1.242159383033419 & 0.924030303030303 & 0.5903545713545713 & 0.94372526076617 & 0.0462785547785547 & 0.5905014648511226 & 1.3115384615384615 \\ \hline
-        Cuneiform & 4.079588014981273 & 2.244427103288844 & 3.0 & 0.2222330604444725 & 0.8634154547075895 & 0.4613474974345972 & 0.0722909733763576 & 0.1963017855703223 & 2.0 \\ \hline
-        Fingerprint & 1.4868577990824814 & 2.115136284036567 & 4.344413012729844 & 0.4391785351497472 & 0.0017307791737759 & 0.5069423734352098 & 0.1840341453794884 & 0.4207756269406634 & 3.656584457887389 \\ \hline
-        FIRSTMM\_DB & 4.50236815941043 & 12.309044701937715 & 30.676056338028168 & 0.0074027477877271 & 0.2631922211539924 & 0.0551742654129266 & 0.0188189276256195 & 0.0092704028700914 & 1357.8292682926829 \\ \hline
-        Letter-high & 1.889683607525296 & 1.4794456563750826 & 2.444490301279405 & 0.5791851851851852 & 0.2976163139329805 & 0.6794971082752952 & 0.1657867724867724 & 0.4611670600331147 & 2.994222222222222 \\ \hline
-        Letter-low & 1.3213534599145254 & 1.33364428641149 & 1.955783308931186 & 0.4165470899470899 & 0.0 & 0.4955472438922087 & 0.1618904761904762 & 0.4407481624189365 & 2.471111111111111 \\ \hline
-        Letter-med & 1.352705840084288 & 1.3502031822344325 & 2.006610576923077 & 0.4245777777777778 & 0.0139393298059964 & 0.5071406868429822 & 0.1683222222222222 & 0.4416562761104123 & 2.517333333333333 \\ \hline
-        MSRC\_9 & 4.81534002269555 & 3.113629895894764 & 7.004524886877828 & 0.1235873024311543 & 0.5412981657910688 & 0.33102605797573 & 0.055215313789426 & 0.1368862401087341 & 40.36199095022624 \\ \hline
-        MSRC\_21 & 5.102391318360188 & 4.094474312024695 & 9.621669626998225 & 0.0680571076593652 & 0.5146660459581984 & 0.251511488615992 & 0.041532868642658 & 0.0936632954729105 & 77.22735346358792 \\ \hline
-        MSRC\_21C & 4.782574662751558 & 3.113761314016 & 6.971291866028708 & 0.1240107738760322 & 0.5427170070575877 & 0.3315153420789583 & 0.0557392711060186 & 0.1371850938080253 & 40.05263157894737 \\ \hline
-        DD & 4.979061666490266 & 7.919898418826995 & 19.70016611295681 & 0.0278322962071925 & 0.4793770769559906 & 0.1402074694227141 & 0.0324963430907113 & 0.0342447661028087 & 278.28013582342953 \\ \hline
-        ENZYMES & 3.862625308732192 & 4.2810541955964485 & 10.4265625 & 0.1598878125179543 & 0.4533912862690096 & 0.263573448964092 & 0.1158938852730127 & 0.1471447702872793 & 28.575 \\ \hline
-        KKI & 3.1856769969664422 & 3.500870554422239 & 8.144578313253012 & 0.1792960793494088 & 0.3526436673677589 & 0.3358793648012939 & 0.1297799757896069 & 0.1757034314039908 & 24.81927710843373 \\ \hline
-        OHSU & 4.327667933476122 & 4.921680537597515 & 12.69620253164557 & 0.0822944467200859 & 0.3808295357080805 & 0.2407028072344937 & 0.0655860979728088 & 0.0823969445758651 & 77.51898734177215 \\ \hline
-        Peking\_1 & 3.5514470044304343 & 3.968106920104182 & 9.623529411764704 & 0.1276151076564966 & 0.3673053988324483 & 0.2889094228756093 & 0.0998385744518594 & 0.1284748145692827 & 36.72941176470588 \\ \hline
-        PROTEINS & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        PROTEINS\_full & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        COLORS-3 & 2.928853359699249 & 2.5810313856214724 & 5.275766205587198 & 0.1695881211511339 & 0.1450387037596311 & 0.3502761440955542 & 0.0639043708084029 & 0.1737080119571242 & 56.95904761904762 \\ \hline
-        SYNTHETIC & 3.920000076293945 & 3.5064646464646465 & 7.0 & 0.0395959595959595 & 0.0203095238095238 & 0.2893391429701345 & 0.0255761698618841 & 0.0831547830080052 & 100.0 \\ \hline
-        SYNTHETICnew & 3.9250000715255737 & 3.4872567329242026 & 7.274834437086093 & 0.0396464646464646 & 0.0229497089947089 & 0.289441726009901 & 0.0255427746856318 & 0.0836273264155355 & 99.96333333333334 \\ \hline
-        Synthie & 3.6210444450378416 & 2.6348743925562266 & 5.494845360824742 & 0.038420429009193 & 0.0937036201778145 & 0.2766177855177352 & 0.0231922369186012 & 0.0786632559723412 & 90.6125 \\ \hline
-        TRIANGLES & 3.1404920884927114 & 2.263375484124684 & 4.557498816896771 & 0.2416135135324899 & 0.2286352011335792 & 0.4374025890339534 & 0.0821216496736849 & 0.226180376713217 & 19.88371111111111 \\ \hline
-        AIDS & 2.0128653862178325 & 3.490507728804514 & 7.762604013705335 & 0.1935408261794486 & 0.0071746166779525 & 0.3500774185559109 & 0.1911961844012523 & 0.262770387548969 & 11.8145 \\ \hline
-        BZR & 2.1466610419897387 & 5.154837461860052 & 11.65679012345679 & 0.0648920405178712 & 8.903397114779228e-05 & 0.2054846442932875 & 0.1245291263310628 & 0.1416530437212679 & 29.607407407407408 \\ \hline
-        BZR\_MD & 20.30392156862745 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2203726689661978 & 1.0 \\ \hline
-        COX2 & 2.107735009469108 & 5.936420803578038 & 13.790149892933618 & 0.0529052472359257 & 0.0007216110850642 & 0.1757209022905502 & 0.1262987138392391 & 0.1288265342157682 & 28.09421841541756 \\ \hline
-        COX2\_MD & 25.27722772277228 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.1957034193657646 & 1.0 \\ \hline
-        DHFR & 2.102359890622437 & 6.144674814243727 & 14.603174603174605 & 0.0536754666970741 & 0.0 & 0.1734264353163348 & 0.1288500765571343 & 0.1271607693927877 & 32.21560846560847 \\ \hline
-        DHFR\_MD & 22.8676844783715 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2076620678810238 & 1.0 \\ \hline
-        ER\_MD & 20.327354260089685 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2244695039966339 & 1.0 \\ \hline
-        FRANKENSTEIN & 2.0627741588132293 & 3.6742676066855062 & 8.423452029938762 & 0.1705038719060743 & 0.0106826329262756 & 0.3148146889108825 & 0.1923606317376928 & 0.2432099454364741 & 13.42448697256168 \\ \hline
-        MCF-7 & 2.1516180606917765 & 5.050070569624072 & 12.141178938535766 & 0.0980572307942984 & 0.0020345164969653 & 0.2175444791564102 & 0.1724077067751488 & 0.1725022149133201 & 21.418113071660063 \\ \hline
-        MCF-7H & 2.0888838372172147 & 5.858613378052236 & 13.306228605946709 & 0.0537227676449342 & 0.0005825022974507 & 0.1778419519669024 & 0.1198217621207925 & 0.1223362659022958 & 32.9756211739287 \\ \hline
-        MOLT-4 & 2.146077948348501 & 4.951738679286625 & 11.874633536790505 & 0.0987082247303717 & 0.0019246147011501 & 0.2183304220273518 & 0.1714407445609207 & 0.1734293274657891 & 21.028995347667543 \\ \hline
-        MOLT-4H & 2.0858484049375803 & 5.738056140581633 & 12.992424764134702 & 0.0539489355320176 & 0.0005343843281943 & 0.17815930623996 & 0.1192636780853368 & 0.1228930198480923 & 32.272249465610464 \\ \hline
-        Mutagenicity & 2.0379886209469995 & 4.418912992995495 & 9.63701923076923 & 0.0912875415379717 & 0.0031125822886973 & 0.2466634939984061 & 0.1371754284356414 & 0.1710356482094367 & 20.874567673507038 \\ \hline
-        MUTAG & 2.18877208359698 & 3.626150957182829 & 8.21808510638298 & 0.1384540671648269 & 0.0 & 0.293764054092514 & 0.1694459751944365 & 0.2197353385133972 & 14.8031914893617 \\ \hline
-        NCI1 & 2.15501380214726 & 5.234873158476093 & 12.659402381487306 & 0.088944910671084 & 0.0030999008340164 & 0.2026186665583615 & 0.1631676786426253 & 0.1607325923179734 & 24.721411192214116 \\ \hline
-        NCI109 & 2.156446177386937 & 5.183950502801717 & 12.49528936742934 & 0.0894286690245151 & 0.0030732389355228 & 0.20411132911515 & 0.1624231134845694 & 0.1617585552708976 & 24.52410952265568 \\ \hline
-        NCI-H23 & 2.1451602406810686 & 4.950946501654924 & 11.869525050337558 & 0.0987776628128759 & 0.0018996992922189 & 0.2183535143438838 & 0.1715792456717554 & 0.1735208031755432 & 20.99303645329963 \\ \hline
-        NCI-H23H & 2.085327596320919 & 5.734343001278942 & 12.983736711151325 & 0.0539842770435475 & 0.0005268942359655 & 0.1782099752168056 & 0.1192891041739607 & 0.1229635264798962 & 32.22578246970485 \\ \hline
-        OVCAR-8 & 2.145637268375766 & 4.945169149304127 & 11.85222800857742 & 0.0987730040211328 & 0.0018986224960467 & 0.2183941696064956 & 0.171403631603811 & 0.1735393405097124 & 20.98556125974924 \\ \hline
-        OVCAR-8H & 2.0856259705836995 & 5.728655397369023 & 12.966769410758882 & 0.0539777071171825 & 0.0005298176630677 & 0.1782129665549435 & 0.1192148511162624 & 0.1229665170804826 & 32.22561457202093 \\ \hline
-        P388 & 2.109217112454913 & 4.355752638151867 & 10.21824835544779 & 0.1190787859581164 & 0.0037544697177687 & 0.2459957278657192 & 0.1789538865626834 & 0.1958220277248745 & 17.133174189814813 \\ \hline
-        P388H & 2.0638945394922854 & 5.289795718220624 & 11.765664188214403 & 0.0639638393366292 & 0.0009642194122106 & 0.1971310478874152 & 0.1240122910178544 & 0.1373237905541068 & 26.71100983796296 \\ \hline
-        PC-3 & 2.1520653447146643 & 5.05018085139685 & 12.140862989009436 & 0.098055200309084 & 0.0019733135754618 & 0.2175815805232795 & 0.1725492873407526 & 0.172560720893664 & 21.37340506743248 \\ \hline
-        PC-3H & 2.08922384690422 & 5.857822430952191 & 13.30650249313117 & 0.0537656750613318 & 0.0005561305149752 & 0.1779189564869681 & 0.1200247359820712 & 0.1224665687629844 & 32.881929550328984 \\ \hline
-        PTC\_FM & 1.9758043374578045 & 3.311647990381311 & 7.36676217765043 & 0.2154944740700171 & 0.0091220986824968 & 0.3693003427913903 & 0.2055882581121011 & 0.2786143302706905 & 9.91404011461318 \\ \hline
-        PTC\_FR & 1.9863111707899304 & 3.387662268892836 & 7.589743589743589 & 0.2085568638656639 & 0.0088214579442649 & 0.3612672957602951 & 0.2045358868174996 & 0.2734008790739162 & 10.22222222222222 \\ \hline
-        PTC\_MM & 1.9701179610121815 & 3.301432053360394 & 7.339285714285714 & 0.2223452925857377 & 0.0130582137161084 & 0.374488207420213 & 0.2059637189235834 & 0.2823441282735879 & 9.803571428571429 \\ \hline
-        PTC\_MR & 1.9805375618297 & 3.3577641223936463 & 7.523255813953488 & 0.2137888896192228 & 0.009509685286154 & 0.3666473296924281 & 0.2062170509277356 & 0.2777684525909222 & 10.040697674418604 \\ \hline
-        SF-295 & 2.145489384462884 & 4.9445677038396125 & 11.852116182572614 & 0.09881526807439 & 0.0019131887956769 & 0.2184346701016761 & 0.1714761059761314 & 0.1735919743359789 & 20.97159246107621 \\ \hline
-        SF-295H & 2.0855234748235936 & 5.727434951743517 & 12.9664274556856 & 0.0539895579758234 & 0.0005299113307649 & 0.1782697110808576 & 0.1192036786794211 & 0.1229816733300816 & 32.196146110104046 \\ \hline
-        SN12C & 2.145026913904858 & 4.94825141099449 & 11.86401279205747 & 0.0987936439503507 & 0.001927945706436 & 0.2183468315283276 & 0.1714975830848956 & 0.1735570013676089 & 20.99167583241676 \\ \hline
-        SN12CH & 2.0853053252079072 & 5.730086714838555 & 12.973598487437071 & 0.0540104189866913 & 0.0005390487212868 & 0.1781938757210136 & 0.1192686561921279 & 0.1230077396296653 & 32.236301369863014 \\ \hline
-        SW-620 & 2.1452310279340394 & 4.94393636762053 & 11.851577038136291 & 0.0988746005232462 & 0.0018522578567537 & 0.2185003794708548 & 0.1714920826604129 & 0.1736489333480562 & 20.97197276226192 \\ \hline
-        SW-620H & 2.0854275176564645 & 5.725806234940699 & 12.962851360467733 & 0.054054544610838 & 0.0005110193017508 & 0.1783225632271403 & 0.1192839052512742 & 0.1230820111720522 & 32.19651139840126 \\ \hline
-        UACC257 & 2.145698715720169 & 4.955834964420495 & 11.885704040162564 & 0.0987250195703296 & 0.0018738116805416 & 0.218300263582104 & 0.1716221375949755 & 0.1734631006815176 & 20.994198259477844 \\ \hline
-        UACC257H & 2.0856917230912635 & 5.740515645090362 & 13.003174313183676 & 0.0539749990285044 & 0.0005209407683445 & 0.1781806662974605 & 0.1193640515072574 & 0.122956068725157 & 32.22436731019306 \\ \hline
-        Yeast & 2.099442849357738 & 4.364322361013096 & 10.26343257027636 & 0.1210553127513687 & 0.0022671334945899 & 0.2476806589296417 & 0.183060827627568 & 0.1985665767951158 & 16.67475282973832 \\ \hline
-        YeastH & 2.0589509621359707 & 5.245391698622407 & 11.6875493153864 & 0.0642704732457107 & 0.0005773570062507 & 0.1983872537891083 & 0.1254655281986756 & 0.1384817929367545 & 26.05320284921044 \\ \hline
-        Sum & 242.8347529362711 & 258.6723790469145 & 587.9183294923151 & 12.731666924394474 & 11.845921907393928 & 20.687237238791475 & 7.3848149134808 & 11.636469235194477 & 3245.599253687252 \\ \hline
-    \end{tabular}
-    \caption{Graph parameters of the datasets}
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of GCN model}
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\ \hline
-        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\ \hline
-        MOLT-4 & 0.0 & 0.014102176763117313 \\ \hline
-        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\ \hline
-        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\ \hline
-        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\ \hline
-        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\ \hline
-        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\ \hline
-        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\ \hline
-        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\ \hline
-        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\ \hline
-        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\ \hline
-        P388 & 0.008062511682510376 & 0.01043933816254139 \\ \hline
-        P388H & 0.006343752145767212 & 0.007148966193199158 \\ \hline
-        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\ \hline
-        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\ \hline
-        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\ \hline
-        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\ \hline
-        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\ \hline
-        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\ \hline
-        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\ \hline
-        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\ \hline
-        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\ \hline
-        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\ \hline
-        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\ \hline
-        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\ \hline
-        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\ \hline
-        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\ \hline
-        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\ \hline
-        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\ \hline
-        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\ \hline
-        DD & -0.1750326007604599 & 0.3490835428237915 \\ \hline
-        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\ \hline
-        KKI & 0.04776120185852051 & 0.2546080946922302 \\ \hline
-        OHSU & 0.39824172854423523 & 0.138640895485878 \\ \hline
-        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\ \hline
-        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\ \hline
-        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\ \hline
-        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\ \hline
-        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ \hline
-    \end{tabular}
-    \caption{Generalization error of the GCN model on 57 datasets}
-    \label{tab:ge_gcn} % ge -> generalization error
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of SGC model}
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        PROTEINS\_full & 0.04741409420967102 & 0.5624663829803467 \\ \hline
-        DD & -0.21720178425312042 & 0.40132829546928406 \\ \hline
-        ENZYMES & 0.3279166519641876 & 0.060605552047491074 \\ \hline
-        KKI & 0.10951493680477142 & 0.24877962470054626 \\ \hline
-        OHSU & 0.07604396343231201 & 0.1943538784980774 \\ \hline
-        Peking\_1 & 0.1769927442073822 & 0.22724425792694092 \\ \hline
-        COLORS-3 & 0.11781251430511475 & 0.04669201001524925 \\ \hline
-        SYNTHETIC & -0.37541666626930237 & 0.4494529068470001 \\ \hline
-        SYNTHETICnew & -0.36666664481163025 & 0.46157106757164 \\ \hline
-        Synthie & 0.13749998807907104 & 0.042466290295124054 \\ \hline
-        AIDS & 0.006437480449676514 & 0.011520843021571636 \\ \hline
-        BZR & 0.10815385729074478 & 0.21917256712913513 \\ \hline
-        BZR\_MD & 0.1678861677646637 & 0.09830881655216217 \\ \hline
-        COX2 & 0.07495072484016418 & 0.13212721049785614 \\ \hline
-        COX2\_MD & 0.14868313074111938 & 0.16540752351284027 \\ \hline
-        DHFR & 0.1332409381866455 & 0.1551705300807953 \\ \hline
-        DHFR\_MD & 0.0777045264840126 & 0.2503173351287842 \\ \hline
-        ER\_MD & -0.008367183618247509 & 0.15631815791130066 \\ \hline
-        FRANKENSTEIN & 0.10787498950958252 & 0.05383045971393585 \\ \hline
-        MCF-7 & 0.35490626096725464 & 0.17573890089988708 \\ \hline
-        MCF-7H & 0.3593124747276306 & 0.1884346306324005 \\ \hline
-        MOLT-4 & 0.18021871149539948 & 0.39803561568260193 \\ \hline
-        MOLT-4H & 0.18649999797344208 & 0.3838197886943817 \\ \hline
-        Mutagenicity & 0.04325000196695328 & 0.028246337547898293 \\ \hline
-        MUTAG & 0.07375730574131012 & 0.13988283276557922 \\ \hline
-        NCI1 & 0.09100000560283661 & 0.16161812841892242 \\ \hline
-        NCI109 & -0.06128125637769699 & 0.2943810522556305 \\ \hline
-        NCI-H23 & 0.31696873903274536 & 0.07884199917316437 \\ \hline
-        NCI-H23H & 0.3696562349796295 & 0.06490368396043777 \\ \hline
-        OVCAR-8 & 0.3291874825954437 & 0.0815950483083725 \\ \hline
-        OVCAR-8H & 0.2902187705039978 & 0.0771569237112999 \\ \hline
-        P388 & 0.3618437647819519 & 0.13428252935409546 \\ \hline
-        P388H & -0.052218757569789886 & 0.3646376132965088 \\ \hline
-        PC-3 & -0.08028124272823334 & 0.29225972294807434 \\ \hline
-        PC-3H & 0.2593437135219574 & 0.22314861416816711 \\ \hline
-        PTC\_FM & 0.10863511264324188 & 0.14730817079544067 \\ \hline
-        PTC\_FR & 0.08632432669401169 & 0.09645862877368927 \\ \hline
-        PTC\_MM & 0.09649830311536789 & 0.0817335695028305 \\ \hline
-        PTC\_MR & 0.060720354318618774 & 0.18291200697422028 \\ \hline
-        SF-295 & 0.3124375343322754 & 0.11770480871200562 \\ \hline
-        SF-295H & 0.28881245851516724 & 0.12331245839595795 \\ \hline
-        SN12C & 0.2917812764644623 & 0.05537300556898117 \\ \hline
-        SN12CH & 0.3397812247276306 & 0.09572991728782654 \\ \hline
-        SW-620 & 0.3427812457084656 & 0.2430398166179657 \\ \hline
-        SW-620H & 0.39274999499320984 & 0.1998475342988968 \\ \hline
-        UACC257 & -0.10218751430511475 & 0.2883416414260864 \\ \hline
-        UACC257H & 0.3322499692440033 & 0.22775331139564514 \\ \hline
-        Yeast & 0.0 & 0.0 \\ \hline
-        YeastH & 0.0 & 0.0 \\ \hline
-    \end{tabular}
-\end{table}
-
-\subsubsection{Generalization error of GATv2 model}
-
-\subsubsection{Generalization error of MPNN model}
-
-\subsubsection{Corrolation analysis between generalization error and graph parameters}
-
-\subsection{Discussion}
-
-\section{Conclusion}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{main} % refers to example.bib
-
-\clearpage
-
-\section{Appendix}
-
-\subsection{Basic information about TUDataset}\label{sec:datasets}
-This table~\ref{tab:datasets} shows the information about a list of datasets used in this thesis.
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|}
-    \hline
-        name & Graphs & Classes & Avg. Nodes & Avg. Edges & catagory \\ \hline
-        AIDS & 2000 & 2 & 15.69 & 16.20 & Small molecules \\ \hline
-        BZR & 405 & 2 & 35.75 & 38.36 & Small molecules \\ \hline
-        BZR\_MD & 306 & 2 & 21.30 & 225.06 & Small molecules \\ \hline
-        COX2 & 467 & 2 & 41.22 & 43.45 & Small molecules \\ \hline
-        COX2\_MD & 303 & 2 & 26.28 & 335.12 & Small molecules \\ \hline
-        DHFR & 756 & 2 & 42.43 & 44.54 & Small molecules \\ \hline
-        DHFR\_MD & 393 & 2 & 23.87 & 283.02 & Small molecules \\ \hline
-        ER\_MD & 446 & 2 & 21.33 & 234.85 & Small molecules \\ \hline
-        FRANKENSTEIN & 4337 & 2 & 16.90 & 17.88 & Small molecules \\ \hline
-        MCF-7 & 27770 & 2 & 26.40 & 28.53 & Small molecules \\ \hline
-        MCF-7H & 27770 & 2 & 47.31 & 49.44 & Small molecules \\ \hline
-        MOLT-4 & 39765 & 2 & 26.10 & 28.14 & Small molecules \\ \hline
-        MOLT-4H & 39765 & 2 & 46.70 & 48.74 & Small molecules \\ \hline
-        Mutagenicity & 4337 & 2 & 30.32 & 30.77 & Small molecules \\ \hline
-        MUTAG & 188 & 2 & 17.93 & 19.79 & Small molecules \\ \hline
-        NCI1 & 4110 & 2 & 29.87 & 32.30 & Small molecules \\ \hline
-        NCI109 & 4127 & 2 & 29.68 & 32.13 & Small molecules \\ \hline
-        NCI-H23 & 40353 & 2 & 26.07 & 28.10 & Small molecules \\ \hline
-        NCI-H23H & 40353 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        OVCAR-8 & 40516 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        OVCAR-8H & 40516 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        P388 & 41472 & 2 & 22.11 & 23.56 & Small molecules \\ \hline
-        P388H & 41472 & 2 & 40.45 & 41.89 & Small molecules \\ \hline
-        PC-3 & 27509 & 2 & 26.36 & 28.49 & Small molecules \\ \hline
-        PC-3H & 27509 & 2 & 47.20 & 49.33 & Small molecules \\ \hline
-        PTC\_FM & 349 & 2 & 14.11 & 14.48 & Small molecules \\ \hline
-        PTC\_FR & 351 & 2 & 14.56 & 15.00 & Small molecules \\ \hline
-        PTC\_MM & 336 & 2 & 13.97 & 14.32 & Small molecules \\ \hline
-        PTC\_MR & 344 & 2 & 14.29 & 14.69 & Small molecules \\ \hline
-        SF-295 & 40271 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SF-295H & 40271 & 2 & 46.65 & 48.68 & Small molecules \\ \hline
-        SN12C & 40004 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        SN12CH & 40004 & 2 & 46.69 & 48.72 & Small molecules \\ \hline
-        SW-620 & 40532 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SW-620H & 40532 & 2 & 46.63 & 48.66 & Small molecules \\ \hline
-        UACC257 & 39988 & 2 & 26.09 & 28.13 & Small molecules \\ \hline
-        UACC257H & 39988 & 2 & 46.68 & 48.71 & Small molecules \\ \hline
-        Yeast & 79601 & 2 & 21.54 & 22.84 & Small molecules \\ \hline
-        YeastH & 79601 & 2 & 39.45 & 40.75 & Small molecules \\ \hline
-        DD & 1178 & 2 & 284.32 & 715.66 & Bioinformatics \\ \hline
-        ENZYMES & 600 & 6 & 32.63 & 62.14 & Bioinformatics \\ \hline
-        KKI & 83 & 2 & 26.96 & 48.42 & Bioinformatics \\ \hline
-        OHSU & 79 & 2 & 82.01 & 199.66 & Bioinformatics \\ \hline
-        Peking\_1 & 85 & 2 & 39.31 & 77.35 & Bioinformatics \\ \hline
-        PROTEINS\_full & 1113 & 2 & 39.06 & 72.82 & Bioinformatics \\ \hline
-        COIL-DEL & 3900 & 100 & 21.54 & 54.24 & Computer vision \\ \hline
-        COIL-RAG & 3900 & 100 & 3.01 & 3.02 & Computer vision \\ \hline
-        Cuneiform & 267 & 30 & 21.27 & 44.80 & Computer vision \\ \hline
-        Fingerprint & 2149 & 15 & 7.06 & 5.76 & Computer vision \\ \hline
-        FIRSTMM\_DB & 41 & 11 & 1377.27 & 3074.10 & Computer vision \\ \hline
-        Letter-high & 2250 & 15 & 4.67 & 4.50 & Computer vision \\ \hline
-        Letter-low & 2250 & 15 & 4.68 & 3.13 & Computer vision \\ \hline
-        Letter-med & 2250 & 15 & 4.67 & 3.21 & Computer vision \\ \hline
-        MSRC\_9 & 221 & 8 & 40.58 & 97.94 & Computer vision \\ \hline
-        MSRC\_21 & 563 & 20 & 77.52 & 198.32 & Computer vision \\ \hline
-        MSRC\_21C & 209 & 20 & 40.28 & 96.60 & Computer vision \\ \hline
-        COLORS-3 & 10500 & 11 & 61.31 & 91.03 & Synthetic \\ \hline
-        SYNTHETIC & 300 & 2 & 100.00 & 196.00 & Synthetic \\ \hline
-        SYNTHETICnew & 300 & 2 & 100.00 & 196.25 & Synthetic \\ \hline
-        Synthie & 400 & 4 & 95.00 & 172.93 & Synthetic \\ \hline
-    \end{tabular}
-    \caption{Basic information about the datasets used in the experiment}
-    \label{tab:datasets}
-\end{table}
-
-\subsection{Example of GCN model}
-
-\begin{lstlisting}[language=Python]
-import torch
-
-\end{lstlisting}
-
-\end{document}
+Nevertheless, Morris et al.~\cite{morris2024futuredirectionstheorygraph} pointed out that the generalization ability of GNNs is still not well understood.
+The bounds established in these studies typically rely solely on general graph parameters, such as the maximum degree or total number of nodes, often overlooking more expressive graph parameters.

### 2025-01-29 paper/chapters/relatedwork.tex
Add thesis structure including title page, abstract, acknowledgments, conclusion, and related work sections

--- 2025-01-17 thesis/main.tex
@@
-\documentclass{article}
-\usepackage{geometry}
-\geometry{
-    a4paper,
-    left=30mm,
-    right=30mm,
-    top=30mm,
-    bottom=30mm
-}
+\subsection{Related work}
+In the following section, I provide an overview of the related work on the generalization of neural networks, including feed-forward neural networks, recurrent neural networks, and graph neural networks.
 
-\usepackage{annotate-equations}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-% \usepackage{figure}
-
-\graphicspath{ {./media/} }
-\usepackage[square,numbers]{natbib}
-\usepackage[nottoc]{tocbibind}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{enumitem}
-\usepackage{float}
-
-\usepackage{amssymb}
-\usepackage{amsmath}
-
-\usepackage{tikz}
-\usepackage{listings}
-\usepackage{setspace}
-\definecolor{Code}{rgb}{0,0,0}
-\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
-\definecolor{Numbers}{rgb}{0.5,0,0}
-\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
-\definecolor{Keywords}{rgb}{0,0,1}
-\definecolor{self}{rgb}{0,0,0}
-\definecolor{Strings}{rgb}{0,0.63,0}
-\definecolor{Comments}{rgb}{0,0.63,1}
-\definecolor{Backquotes}{rgb}{0,0,0}
-\definecolor{Classname}{rgb}{0,0,0}
-\definecolor{FunctionName}{rgb}{0,0,0}
-\definecolor{Operators}{rgb}{0,0,0}
-\definecolor{Background}{rgb}{0.98,0.98,0.98}
-\lstdefinelanguage{Python}{
-	numbers=left,
-	numberstyle=\footnotesize,
-	numbersep=1em,
-	xleftmargin=1em,
-	framextopmargin=2em,
-	framexbottommargin=2em,
-	showspaces=false,
-	showtabs=false,
-	showstringspaces=false,
-	frame=l,
-	tabsize=4,
-	% Basic
-	basicstyle=\ttfamily\small\setstretch{1},
-	backgroundcolor=\color{Background},
-	% Comments
-	commentstyle=\color{Comments}\slshape,
-	% Strings
-	stringstyle=\color{Strings},
-	morecomment=[s][\color{Strings}]{"""}{"""},
-	morecomment=[s][\color{Strings}]{'''}{'''},
-	% keywords
-	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
-	keywordstyle={\color{Keywords}\bfseries},
-	% additional keywords
-	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
-	keywordstyle={[2]\color{Decorators}\slshape},
-	emph={self},
-	emphstyle={\color{self}\slshape},
-	%
-}
-
-\title{\textbf{Bachelor thesis}\\
-Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks}
-
-\author{Author: Wensheng Zhang}
-
-\date{\today}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
-\end{abstract}
-
-\section{Introduction}\label{sec:intro}
-Graph learning became a hot topic in the field of machine learning in recent years.
-Graph Neural Networks (GNNs), also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
-The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
-This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.
-
-However, the behavior of GNNs is not well understood.
-Particularly, the relationship between graph parameters/characteristics and the empirical generalization error of GNNs is not clear.
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
-
-Speaking more specifically.
-First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree.
-In graph theory, \textit{graph parameter} is used to quantify them.
-And a dataset consists of multiple graphs, each with its graph parameter.
-In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset.
-In this thesis, 57 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
-Second, I train different GNN models on each dataset and find that their generalization abilities varied.
-I show that there is a certain relationship between generalization ability and different graph parameters.
-
-\subsection{Related work}
-The following section provides an overview of the related work.
-
-\subsubsection{Graph parameters}
-
-\subsubsection{Generalization error}
-
-\section{Background on learning on graphs}
-The following sections provide an overview of the concepts and methods related to graph learning, machine learning, and graph neural networks.
-
-\subsection{Notion}
-At first, we need to define some terms with regard to the graph.
-In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
-We use $\mathbb{G}$ to represent the set of all possible graphs.
-The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$.
-The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
-In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.
-A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included.
-These vectors can be used to characterize graphs or nodes in graphs.
-The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph.
-The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.
-
-\subsection{Machine learning}
-Machine learning is a subfield of artificial intelligence that focuses on the development of algorithms that can learn from and make predictions or decisions based on data.
-The goal of machine learning is to develop models that can generalize well to unseen data.
-The model is trained on a training dataset, which consists of input-output pairs.
-The model is then evaluated on a test dataset, which is separate from the training dataset.
-
-\subsubsection{Gradient Descent}
-Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
-The algorithm works by computing the gradient of the function at a given point and then updating the point in the direction of the negative gradient.
-The update rule is given by
-
-$$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t)
-$$
-where $\theta_t$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(\theta_t)$ is the gradient of the function $f$ at $\theta_t$.
-The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Stochastic Gradient Descent}
-Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
-The algorithm works by randomly selecting a mini-batch of data points from the training dataset, computing the gradient of the loss function with respect to the mini-batch, and then updating the parameters based on the gradient.
-The update rule is given by
-
-$$
-    \theta_{t+1} = \theta_t - \alpha \nabla f(\theta_t; x_{i:t}, y_{i:t})
-$$
-where $x_{i:t}$ and $y_{i:t}$ are the mini-batch of data points and labels, respectively. The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
-
-\subsubsection{Backpropagation}
-Backpropagation is an algorithm used to compute the gradients of the loss function with respect to the parameters of a neural network.
-The algorithm works by computing the gradient of the loss function with respect to the output of the network and then propagating the gradient backward through the network to compute the gradients of the loss function with respect to the parameters.
-The gradients are then used to update the parameters of the network using an optimization algorithm such as gradient descent.
-
-\subsubsection{Regularization}
-Regularization is a technique used to prevent overfitting in machine learning models.
-Overfitting occurs when a model learns the noise in the training data rather than the underlying pattern.
-Regularization works by adding a penalty term to the loss function that discourages the model from learning complex patterns that are specific to the training data.
-There are two common types of regularization: $L1$ regularization and $L2$ regularization.
-$L1$ regularization adds a penalty term that is proportional to the $L1$ norm of the parameters, while $L2$ regularization adds a penalty term that is proportional to the $L2$ norm of the parameters.
-The regularization parameter $\lambda$ controls the strength of the regularization.
-
-\subsubsection{Early Stopping}
-Early stopping is a technique used to prevent overfitting in machine learning models.
-The idea is to monitor the performance of the model on a validation dataset during training and stop training when the performance starts to degrade.
-This is done by saving the model parameters at each iteration and selecting the model with the best performance on the validation dataset.
-Early stopping is a form of regularization that prevents the model from learning the noise in the training data.
-
-\subsubsection{Cross-validation}
-Cross-validation is a technique used to evaluate the performance of a machine learning model.
-The idea is to split the dataset into multiple subsets, or folds, and train the model on one subset while evaluating it on the remaining subsets.
-This process is repeated multiple times, with each subset used as the test set once.
-The performance of the model is then averaged over all the folds to obtain an estimate of the model's generalization performance.
-Cross-validation is used to prevent overfitting and to obtain a more accurate estimate of the model's performance.
-
-\subsubsection{Hyperparameter tuning}
-Hyperparameter tuning is the process of selecting the optimal hyperparameters for a machine learning model.
-Hyperparameters are parameters that are set before the training process begins and control the behavior of the model.
-Examples of hyperparameters include the learning rate, batch size, number of hidden layers, and number of epochs.
-Hyperparameter tuning is typically done using a grid search or random search over a predefined set of hyperparameters.
-The goal is to find the set of hyperparameters that results in the best performance on a validation dataset.
-
-\subsubsection{Loss function}
-The loss function is a function that measures the difference between the predicted output of a model and the true output.
-The goal of training a machine learning model is to minimize the loss function, which is done by adjusting the parameters of the model using an optimization algorithm such as gradient descent.
-The choice of loss function depends on the task at hand.
-For classification tasks, the cross-entropy loss function is commonly used, while for regression tasks, the mean squared error loss function is often used.
-
-\subsubsection{Optimization algorithm}
-An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
-The goal is to find the set of parameters that minimizes the loss function.
-Gradient descent is a common optimization algorithm used in machine learning, but there are many variants of gradient descent that are designed to improve convergence speed and stability.
-Some popular optimization algorithms include Adam~\cite{kingma2014adam}, RMSprop~\cite{graves2013generating}, and Adagrad~\cite{duchi2011adaptive}.
-These algorithms use different strategies to update the parameters of the model and can be more effective than standard gradient descent in certain situations.
+\subsubsection{Graph Neural Networks}
+Graph neural networks were initially proposed by Gori et al.~\cite{gori2005new} and Scarselli et al.~\cite{scarselli2008graph} as a variant of recurrent neural networks and demonstrated its generalization capabilities.
+The work of Kipf and Welling~\cite{kipf2016semi} introduced the Graph Convolutional Networks (GCN) model, which received widespread attention from the research community.
+Velickovic et al.~\cite{velickovic2020pointer} proposed the Graph Attention Networks (GAT) model, which uses attention mechanisms to aggregate information from neighboring nodes.
+Brody et al.~\cite{brody2021attentive} proposed the GATv2 model, which improves the performance of the GAT model by introducing residual connections and multi-head attention.
+Gilmer et al.~\cite{gilmer2017neural} introduced the Message Passing Neural Networks (MPNN) model, which demonstrated the significant results on the molecular property prediction benchmark;
 
 \subsubsection{Generalization}
-A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
-This is a measure of how well the model generalizes to unseen data, which can be calculated as the difference between the training accuracy and the test accuracy.
-It is defined as
+While significant progress has been made in understanding the generalization properties of feed-forward neural networks (FNNs) and recurrent neural networks (RNNs), the generalization abilities of graph neural networks (GNNs) remain less explored due to their of irregular graph structures.
 
-$$
-    E_{gen} = {Acc_{train}} - {Acc_{test}}
-$$
-where $Acc_{train}$ is the accuracy of the model on the training dataset, and $Acc_{test}$ is the accuracy of the model on the test dataset.
-The accuracy $Acc$ on a dataset is defined as the proportion of correctly classified graphs, that is, $Acc = \frac{\text{Number of correctly classified graphs}}{\text{Total number of data points}}$.
+Golowich et al.~\cite{golowich2018size} showed the generalization abilities of Feed-forward neural networks (FNNs) with Rademacher complexity.
+The work of Zhang et al.~\cite{zhang2018stabilizing} used SVD-based parameterization to improve the generalization by effectively addressing gradient issues.
 
-The empirical generalization error is also known as the generalization gap~\cite{goodfellow2016deep}.
-Typically, the learning on the training dataset and test dataset behaves differently.
-The model may perform well on the training dataset but poorly on the test dataset.
-By observing the generalization error, we can decide on a stopping criterion for the training process.
-And the generalization error can be used to determine whether the model is overfitting or underfitting.
-Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g.
-Graph parameter).
+In terms of Recurrent neural networks(RNNs), Chen et al.~\cite{chen2019generalization} studied the generalization properties of vanilla RNNs as well as their variants.
+Z.
+Allen-Zhu et al.~\cite{allen2019can} demonstrates that vanilla SGD enables RNNs to efficiently learn concept classes and overcomes prior exponential generalization bounds.
 
-\subsection{Graph Neural Networks}
-Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
-The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
-This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification, edge prediction, and graph classification.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN), Graph Attention Networks (GAT), and Message Passing Neural Networks (MPNN).
+But unlike the FNNs and RNNs, GNNs deal with irregular data structures.
+The related work on the generalization of GNNs is limited.
+Scarselli et al.~\cite{scarselli2018vapnik} explored the generalization ability of GNNs by using the Vapnik-Chervonenkis (VC) dimension and further indicated that the generalization ability of such models improve as the number of connected nodes.
+After that, Garg et al.~\cite{garg2020generalization} studied the generalization ability of GNNs via Rademacher bounds.
+In comparison to the work of Scarselli et al., Garg et al.
+provided a tighter bound on the generalization error of GNNs.
 
-\subsection{Graph parameters}
-Now we can introduce the concept of a graph parameter.
-A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
-Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
-A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
-This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
-
-\section{Experimental study}
-
-\subsection{Experimental setup}
-The following section outlines the planned methods and materials to be employed in the experiment, including the training framework, the datasets, the models, and the graph parameters.
-
-\subsubsection{Training Framework}
-The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
-PyTorch Geometric is a library for deep learning on graphs and other irregular structures.
-It consists of various methods and utilities to ease the implementation of GNNs.
-
-\subsubsection{Hyperparameters tuning}
-Before training the models, for each pair of dataset and model, the hyperparameters of the model are tuned.
-In the experiment, 5-fold cross-validation is used to tune the hyperparameters instead of 10-fold cross validation in the final experiment.
-The reason is that the 10-fold cross-validation is computationally expensive and time-consuming.
-
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler.
-Additionally, for the GATv2 model, the number of heads, the dropout rate, and residual are also tuned.
-
-The hyperparameters are tuned using the Bayesian optimization method\cite{frazier2018tutorial}.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-There are five models and 57 datasets, resulting in 285 pairs of dataset and model.
-For each pair, the hyperparameters are tuned using the Bayesian optimization method.
-The hyperparameters are tuned using the validation dataset.
-The validation dataset is a subset of the training dataset that is used to tune the hyperparameters of the model.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-\subsubsection{Datasets}
-The dataset used for the classification is TUDataset~\cite{morris2020tudataset}.
-TUDataset is often used for the GNN evaluation.
-It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
-The remaining folds are used for training.
-The training is repeated 10 times, each time with a different test fold.
-The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
-
-I list information about the 57 datasets used in the experiment in the appendix~\ref{sec:datasets}.
-
-\subsubsection{Models}
-In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
-The GCN model is shown in the appendix.
-The GCN model consists of four GCN layers, each followed by a ReLU activation function.
-The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.
-
-\subsubsection{Experimental details}
-The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
-To prevent overfitting and to optimize the use of time, the early stopping is employed.
-The loss function is defined as the cross-entropy loss function.
-The hyperparameters of the model are considered to be tuned.
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping.
-The generalization error is calculated as the difference between the training accuracy and the test accuracy.
-
-\subsubsection{Graph Parameters Under Investigation} \label{sec:graph_parameters}
-As graph parameters defined abstractly in the section~\ref{sec:intro}, I give here the concrete definition of the graph parameters.
-
-\begin{description}
-    \item [Average degree] The average degree of the graph $d_{avg}$ is defined as the average of the degrees of all nodes in the graph, that is
-    $$ d_{avg} = \frac{1}{|V|} \sum_{v \in V} d(v)$$
-    \item [Average shortest path length] The average shortest path length of the graph $a$ is defined as the average of the shortest paths between all pairs of nodes in the graph.
-The shortest path $d(s, t)$ between two nodes $v$ and $w$ is the minimum number of edges that need to be traversed to go from $v$ to $w$.
-The formal definition is
-    $$
-a = \frac{1}{|V|(|V|-1)} \sum_{v \in V} \sum_{w \in V, w \neq v} d(v, w)
-    $$
-
-    \item [Graph diameter] The graph diameter $d$ is the maximum of the shortest paths between all pairs of nodes in the graph, that is,
-    $$
-d = \max_{v \in V} \max_{w \in V, w \neq v} d(v, w)
-    $$
-
-    \item [Graph density] The graph density $p$ is the ratio of the number of edges in the graph to the number of the maximum possible edges in the graph, that is,
-    $$
-p = \frac{2|E|}{|V|(|V|-1)}
-    $$
-
-    \item [Graph clustering coefficient] The graph clustering coefficient $C$ is a measure of the degree to which nodes in a graph tend to cluster together.
-The clustering coefficient of a node $v$ (as known as the local clustering coefficient) is defined as the fraction of the number of triangles that include node $v$ to the maximum possible number of triples centered on node $v$.
-The clustering coefficient of the graph (as known as the global clustering coefficient) is defined as the average of the clustering coefficients of all nodes in the graph.
-The formal definition is
-    $$
-C = \frac{1}{|V|} \sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}
-    $$
-    where the term $|\{(i,j)\in E \mid i, j \in N(v)\}|$ is the number of edges between the neighbors of node $v$, i.e.
-the number of triangles containing node $v$.
-Furthermore, the term $\sum_{v \in V} \frac{2\cdot |\{(i,j)\in E \mid i, j \in N(v)\}|}{d(v)(d(v)-1)}$ is the sum of the local clustering coefficients of all nodes in the graph, in which the degree of node $v$ is denoted as $d(v)$.
-
-    \item [Centrality measure of graphs] At first we have the definition of centrality measure in the \textbf{node level}.
-The centrality measure of a node is a measure of the importance of the node in the graph.
-There are many centrality measures, such as degree centrality, closeness centrality, betweenness centrality, and eigenvector centrality.
-
-    \textit{Degree centrality} is identical to the average degree of the graph defined above.
-
-    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of the shortest paths from the node $v$ to all other nodes in the graph, that is 
-    $$C_C(v) = \frac{1}{\sum_{w\in V}{d(v ,w)}}$$
-    where $d(v, w)$ is the shortest path between node $v$ and node $w$.
-
-    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of the shortest paths between all pairs of nodes that pass through node $v$, that is
-
-    $$
-        C_B(v) = \sum_{s,t \in V} \frac{\sigma_{st}(v)}{\sigma_{st}}
-    $$
-    where $\sigma_{st}$ is the number of the shortest paths between nodes $s$ and $t$, and $\sigma_{st}(v)$ is the number of the shortest paths between nodes $s$ and $t$ that pass through node $v$.
-
-    \textit{Eigenvector centrality} is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
-Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$-th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
-Mathematically, it can be expressed as:
-
-    \[ C_E(v) = \frac{1}{\lambda} \sum_{u \in N(v)} a_{vu} C_E(u) \]
-
-    where $ \lambda$ is the largest eigenvalue of the adjacency matrix $A$.
-$a_{vu}$ is the element of the adjacency matrix $A$ corresponding to the edge between nodes $v$  and $u$.
-$ C_E(u)$  is the eigenvector centrality of node $u$.
-
-    Finally, in the \textbf{graph level}, the centrality measure of the graph is defined as the average of the centrality measures over all nodes in the graph.
-
-    \item [Average number of coloring in the 1-WL algorithm] 
-    \sloppy
-    The 1-dimensional Weisfeiler-Leman algorithm (1-WL)~\cite{weisfeiler1968reduction} is an algorithm that assigns a unique label(color) to each node in the graph, also known as color refinement.
-The average number of coloring in the 1-WL algorithm is defined as the average number of colors used to color the nodes in the graph.
-The 1-WL algorithm is a powerful graph isomorphism algorithm that can be used to determine if two graphs are isomorphic.
-I give the procedure of the 1-WL algorithm here:
-    \begin{enumerate}
-        \item Assign the same color to all nodes in the graph.
-        \item Two nodes $v$, $u$ are assigned a different color if there is a color c such that the number of c-colored neighbors of $u$ is not equal to the number of c-colored neighbors of $v$.
-        \item Repeat step 2 until the colors of all nodes do not change.
-    \end{enumerate}
-
-\end{description}
-
-\subsection{Results}
-
-\subsubsection{Graph parameters of the datasets}
-
-\begin{table}[!ht]
-    \footnotesize
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-        \textbf{Name} & \textbf{Ave.
-degree} & \textbf{Ave.
-shortest path} & \textbf{Graph diameter} & \textbf{Graph density} & \textbf{Graph clustering coefficient} & \textbf{Ave.
-closeness centrality} & \textbf{Ave.
-betweenness centrality} & \textbf{Ave.
-eigenvector centrality} & \textbf{1-WL color count} \\ \hline
-        COIL-DEL & 4.673071633424515 & 2.128750184714701 & 4.06974358974359 & 0.3275202823564923 & 0.546258039207784 & 0.5122126871677409 & 0.0647750716657882 & 0.2431245565997526 & 21.102564102564106 \\ \hline
-        COIL-RAG & 1.8277218368573067 & 1.0604823111763986 & 1.242159383033419 & 0.924030303030303 & 0.5903545713545713 & 0.94372526076617 & 0.0462785547785547 & 0.5905014648511226 & 1.3115384615384615 \\ \hline
-        Cuneiform & 4.079588014981273 & 2.244427103288844 & 3.0 & 0.2222330604444725 & 0.8634154547075895 & 0.4613474974345972 & 0.0722909733763576 & 0.1963017855703223 & 2.0 \\ \hline
-        Fingerprint & 1.4868577990824814 & 2.115136284036567 & 4.344413012729844 & 0.4391785351497472 & 0.0017307791737759 & 0.5069423734352098 & 0.1840341453794884 & 0.4207756269406634 & 3.656584457887389 \\ \hline
-        FIRSTMM\_DB & 4.50236815941043 & 12.309044701937715 & 30.676056338028168 & 0.0074027477877271 & 0.2631922211539924 & 0.0551742654129266 & 0.0188189276256195 & 0.0092704028700914 & 1357.8292682926829 \\ \hline
-        Letter-high & 1.889683607525296 & 1.4794456563750826 & 2.444490301279405 & 0.5791851851851852 & 0.2976163139329805 & 0.6794971082752952 & 0.1657867724867724 & 0.4611670600331147 & 2.994222222222222 \\ \hline
-        Letter-low & 1.3213534599145254 & 1.33364428641149 & 1.955783308931186 & 0.4165470899470899 & 0.0 & 0.4955472438922087 & 0.1618904761904762 & 0.4407481624189365 & 2.471111111111111 \\ \hline
-        Letter-med & 1.352705840084288 & 1.3502031822344325 & 2.006610576923077 & 0.4245777777777778 & 0.0139393298059964 & 0.5071406868429822 & 0.1683222222222222 & 0.4416562761104123 & 2.517333333333333 \\ \hline
-        MSRC\_9 & 4.81534002269555 & 3.113629895894764 & 7.004524886877828 & 0.1235873024311543 & 0.5412981657910688 & 0.33102605797573 & 0.055215313789426 & 0.1368862401087341 & 40.36199095022624 \\ \hline
-        MSRC\_21 & 5.102391318360188 & 4.094474312024695 & 9.621669626998225 & 0.0680571076593652 & 0.5146660459581984 & 0.251511488615992 & 0.041532868642658 & 0.0936632954729105 & 77.22735346358792 \\ \hline
-        MSRC\_21C & 4.782574662751558 & 3.113761314016 & 6.971291866028708 & 0.1240107738760322 & 0.5427170070575877 & 0.3315153420789583 & 0.0557392711060186 & 0.1371850938080253 & 40.05263157894737 \\ \hline
-        DD & 4.979061666490266 & 7.919898418826995 & 19.70016611295681 & 0.0278322962071925 & 0.4793770769559906 & 0.1402074694227141 & 0.0324963430907113 & 0.0342447661028087 & 278.28013582342953 \\ \hline
-        ENZYMES & 3.862625308732192 & 4.2810541955964485 & 10.4265625 & 0.1598878125179543 & 0.4533912862690096 & 0.263573448964092 & 0.1158938852730127 & 0.1471447702872793 & 28.575 \\ \hline
-        KKI & 3.1856769969664422 & 3.500870554422239 & 8.144578313253012 & 0.1792960793494088 & 0.3526436673677589 & 0.3358793648012939 & 0.1297799757896069 & 0.1757034314039908 & 24.81927710843373 \\ \hline
-        OHSU & 4.327667933476122 & 4.921680537597515 & 12.69620253164557 & 0.0822944467200859 & 0.3808295357080805 & 0.2407028072344937 & 0.0655860979728088 & 0.0823969445758651 & 77.51898734177215 \\ \hline
-        Peking\_1 & 3.5514470044304343 & 3.968106920104182 & 9.623529411764704 & 0.1276151076564966 & 0.3673053988324483 & 0.2889094228756093 & 0.0998385744518594 & 0.1284748145692827 & 36.72941176470588 \\ \hline
-        PROTEINS & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        PROTEINS\_full & 3.734642166440163 & 4.602185787956082 & 11.297071129707112 & 0.2121756091042708 & 0.5141966922501331 & 0.3022857727840693 & 0.118375456251276 & 0.1695057643632408 & 34.46900269541779 \\ \hline
-        COLORS-3 & 2.928853359699249 & 2.5810313856214724 & 5.275766205587198 & 0.1695881211511339 & 0.1450387037596311 & 0.3502761440955542 & 0.0639043708084029 & 0.1737080119571242 & 56.95904761904762 \\ \hline
-        SYNTHETIC & 3.920000076293945 & 3.5064646464646465 & 7.0 & 0.0395959595959595 & 0.0203095238095238 & 0.2893391429701345 & 0.0255761698618841 & 0.0831547830080052 & 100.0 \\ \hline
-        SYNTHETICnew & 3.9250000715255737 & 3.4872567329242026 & 7.274834437086093 & 0.0396464646464646 & 0.0229497089947089 & 0.289441726009901 & 0.0255427746856318 & 0.0836273264155355 & 99.96333333333334 \\ \hline
-        Synthie & 3.6210444450378416 & 2.6348743925562266 & 5.494845360824742 & 0.038420429009193 & 0.0937036201778145 & 0.2766177855177352 & 0.0231922369186012 & 0.0786632559723412 & 90.6125 \\ \hline
-        TRIANGLES & 3.1404920884927114 & 2.263375484124684 & 4.557498816896771 & 0.2416135135324899 & 0.2286352011335792 & 0.4374025890339534 & 0.0821216496736849 & 0.226180376713217 & 19.88371111111111 \\ \hline
-        AIDS & 2.0128653862178325 & 3.490507728804514 & 7.762604013705335 & 0.1935408261794486 & 0.0071746166779525 & 0.3500774185559109 & 0.1911961844012523 & 0.262770387548969 & 11.8145 \\ \hline
-        BZR & 2.1466610419897387 & 5.154837461860052 & 11.65679012345679 & 0.0648920405178712 & 8.903397114779228e-05 & 0.2054846442932875 & 0.1245291263310628 & 0.1416530437212679 & 29.607407407407408 \\ \hline
-        BZR\_MD & 20.30392156862745 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2203726689661978 & 1.0 \\ \hline
-        COX2 & 2.107735009469108 & 5.936420803578038 & 13.790149892933618 & 0.0529052472359257 & 0.0007216110850642 & 0.1757209022905502 & 0.1262987138392391 & 0.1288265342157682 & 28.09421841541756 \\ \hline
-        COX2\_MD & 25.27722772277228 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.1957034193657646 & 1.0 \\ \hline
-        DHFR & 2.102359890622437 & 6.144674814243727 & 14.603174603174605 & 0.0536754666970741 & 0.0 & 0.1734264353163348 & 0.1288500765571343 & 0.1271607693927877 & 32.21560846560847 \\ \hline
-        DHFR\_MD & 22.8676844783715 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2076620678810238 & 1.0 \\ \hline
-        ER\_MD & 20.327354260089685 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.0 & 0.2244695039966339 & 1.0 \\ \hline
-        FRANKENSTEIN & 2.0627741588132293 & 3.6742676066855062 & 8.423452029938762 & 0.1705038719060743 & 0.0106826329262756 & 0.3148146889108825 & 0.1923606317376928 & 0.2432099454364741 & 13.42448697256168 \\ \hline
-        MCF-7 & 2.1516180606917765 & 5.050070569624072 & 12.141178938535766 & 0.0980572307942984 & 0.0020345164969653 & 0.2175444791564102 & 0.1724077067751488 & 0.1725022149133201 & 21.418113071660063 \\ \hline
-        MCF-7H & 2.0888838372172147 & 5.858613378052236 & 13.306228605946709 & 0.0537227676449342 & 0.0005825022974507 & 0.1778419519669024 & 0.1198217621207925 & 0.1223362659022958 & 32.9756211739287 \\ \hline
-        MOLT-4 & 2.146077948348501 & 4.951738679286625 & 11.874633536790505 & 0.0987082247303717 & 0.0019246147011501 & 0.2183304220273518 & 0.1714407445609207 & 0.1734293274657891 & 21.028995347667543 \\ \hline
-        MOLT-4H & 2.0858484049375803 & 5.738056140581633 & 12.992424764134702 & 0.0539489355320176 & 0.0005343843281943 & 0.17815930623996 & 0.1192636780853368 & 0.1228930198480923 & 32.272249465610464 \\ \hline
-        Mutagenicity & 2.0379886209469995 & 4.418912992995495 & 9.63701923076923 & 0.0912875415379717 & 0.0031125822886973 & 0.2466634939984061 & 0.1371754284356414 & 0.1710356482094367 & 20.874567673507038 \\ \hline
-        MUTAG & 2.18877208359698 & 3.626150957182829 & 8.21808510638298 & 0.1384540671648269 & 0.0 & 0.293764054092514 & 0.1694459751944365 & 0.2197353385133972 & 14.8031914893617 \\ \hline
-        NCI1 & 2.15501380214726 & 5.234873158476093 & 12.659402381487306 & 0.088944910671084 & 0.0030999008340164 & 0.2026186665583615 & 0.1631676786426253 & 0.1607325923179734 & 24.721411192214116 \\ \hline
-        NCI109 & 2.156446177386937 & 5.183950502801717 & 12.49528936742934 & 0.0894286690245151 & 0.0030732389355228 & 0.20411132911515 & 0.1624231134845694 & 0.1617585552708976 & 24.52410952265568 \\ \hline
-        NCI-H23 & 2.1451602406810686 & 4.950946501654924 & 11.869525050337558 & 0.0987776628128759 & 0.0018996992922189 & 0.2183535143438838 & 0.1715792456717554 & 0.1735208031755432 & 20.99303645329963 \\ \hline
-        NCI-H23H & 2.085327596320919 & 5.734343001278942 & 12.983736711151325 & 0.0539842770435475 & 0.0005268942359655 & 0.1782099752168056 & 0.1192891041739607 & 0.1229635264798962 & 32.22578246970485 \\ \hline
-        OVCAR-8 & 2.145637268375766 & 4.945169149304127 & 11.85222800857742 & 0.0987730040211328 & 0.0018986224960467 & 0.2183941696064956 & 0.171403631603811 & 0.1735393405097124 & 20.98556125974924 \\ \hline
-        OVCAR-8H & 2.0856259705836995 & 5.728655397369023 & 12.966769410758882 & 0.0539777071171825 & 0.0005298176630677 & 0.1782129665549435 & 0.1192148511162624 & 0.1229665170804826 & 32.22561457202093 \\ \hline
-        P388 & 2.109217112454913 & 4.355752638151867 & 10.21824835544779 & 0.1190787859581164 & 0.0037544697177687 & 0.2459957278657192 & 0.1789538865626834 & 0.1958220277248745 & 17.133174189814813 \\ \hline
-        P388H & 2.0638945394922854 & 5.289795718220624 & 11.765664188214403 & 0.0639638393366292 & 0.0009642194122106 & 0.1971310478874152 & 0.1240122910178544 & 0.1373237905541068 & 26.71100983796296 \\ \hline
-        PC-3 & 2.1520653447146643 & 5.05018085139685 & 12.140862989009436 & 0.098055200309084 & 0.0019733135754618 & 0.2175815805232795 & 0.1725492873407526 & 0.172560720893664 & 21.37340506743248 \\ \hline
-        PC-3H & 2.08922384690422 & 5.857822430952191 & 13.30650249313117 & 0.0537656750613318 & 0.0005561305149752 & 0.1779189564869681 & 0.1200247359820712 & 0.1224665687629844 & 32.881929550328984 \\ \hline
-        PTC\_FM & 1.9758043374578045 & 3.311647990381311 & 7.36676217765043 & 0.2154944740700171 & 0.0091220986824968 & 0.3693003427913903 & 0.2055882581121011 & 0.2786143302706905 & 9.91404011461318 \\ \hline
-        PTC\_FR & 1.9863111707899304 & 3.387662268892836 & 7.589743589743589 & 0.2085568638656639 & 0.0088214579442649 & 0.3612672957602951 & 0.2045358868174996 & 0.2734008790739162 & 10.22222222222222 \\ \hline
-        PTC\_MM & 1.9701179610121815 & 3.301432053360394 & 7.339285714285714 & 0.2223452925857377 & 0.0130582137161084 & 0.374488207420213 & 0.2059637189235834 & 0.2823441282735879 & 9.803571428571429 \\ \hline
-        PTC\_MR & 1.9805375618297 & 3.3577641223936463 & 7.523255813953488 & 0.2137888896192228 & 0.009509685286154 & 0.3666473296924281 & 0.2062170509277356 & 0.2777684525909222 & 10.040697674418604 \\ \hline
-        SF-295 & 2.145489384462884 & 4.9445677038396125 & 11.852116182572614 & 0.09881526807439 & 0.0019131887956769 & 0.2184346701016761 & 0.1714761059761314 & 0.1735919743359789 & 20.97159246107621 \\ \hline
-        SF-295H & 2.0855234748235936 & 5.727434951743517 & 12.9664274556856 & 0.0539895579758234 & 0.0005299113307649 & 0.1782697110808576 & 0.1192036786794211 & 0.1229816733300816 & 32.196146110104046 \\ \hline
-        SN12C & 2.145026913904858 & 4.94825141099449 & 11.86401279205747 & 0.0987936439503507 & 0.001927945706436 & 0.2183468315283276 & 0.1714975830848956 & 0.1735570013676089 & 20.99167583241676 \\ \hline
-        SN12CH & 2.0853053252079072 & 5.730086714838555 & 12.973598487437071 & 0.0540104189866913 & 0.0005390487212868 & 0.1781938757210136 & 0.1192686561921279 & 0.1230077396296653 & 32.236301369863014 \\ \hline
-        SW-620 & 2.1452310279340394 & 4.94393636762053 & 11.851577038136291 & 0.0988746005232462 & 0.0018522578567537 & 0.2185003794708548 & 0.1714920826604129 & 0.1736489333480562 & 20.97197276226192 \\ \hline
-        SW-620H & 2.0854275176564645 & 5.725806234940699 & 12.962851360467733 & 0.054054544610838 & 0.0005110193017508 & 0.1783225632271403 & 0.1192839052512742 & 0.1230820111720522 & 32.19651139840126 \\ \hline
-        UACC257 & 2.145698715720169 & 4.955834964420495 & 11.885704040162564 & 0.0987250195703296 & 0.0018738116805416 & 0.218300263582104 & 0.1716221375949755 & 0.1734631006815176 & 20.994198259477844 \\ \hline
-        UACC257H & 2.0856917230912635 & 5.740515645090362 & 13.003174313183676 & 0.0539749990285044 & 0.0005209407683445 & 0.1781806662974605 & 0.1193640515072574 & 0.122956068725157 & 32.22436731019306 \\ \hline
-        Yeast & 2.099442849357738 & 4.364322361013096 & 10.26343257027636 & 0.1210553127513687 & 0.0022671334945899 & 0.2476806589296417 & 0.183060827627568 & 0.1985665767951158 & 16.67475282973832 \\ \hline
-        YeastH & 2.0589509621359707 & 5.245391698622407 & 11.6875493153864 & 0.0642704732457107 & 0.0005773570062507 & 0.1983872537891083 & 0.1254655281986756 & 0.1384817929367545 & 26.05320284921044 \\ \hline
-        Sum & 242.8347529362711 & 258.6723790469145 & 587.9183294923151 & 12.731666924394474 & 11.845921907393928 & 20.687237238791475 & 7.3848149134808 & 11.636469235194477 & 3245.599253687252 \\ \hline
-    \end{tabular}
-    \caption{Graph parameters of the datasets}
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of GCN model}
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\ \hline
-        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\ \hline
-        MOLT-4 & 0.0 & 0.014102176763117313 \\ \hline
-        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\ \hline
-        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\ \hline
-        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\ \hline
-        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\ \hline
-        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\ \hline
-        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\ \hline
-        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\ \hline
-        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\ \hline
-        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\ \hline
-        P388 & 0.008062511682510376 & 0.01043933816254139 \\ \hline
-        P388H & 0.006343752145767212 & 0.007148966193199158 \\ \hline
-        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\ \hline
-        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\ \hline
-        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\ \hline
-        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\ \hline
-        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\ \hline
-        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\ \hline
-        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\ \hline
-        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\ \hline
-        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\ \hline
-        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\ \hline
-        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\ \hline
-        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\ \hline
-        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\ \hline
-        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\ \hline
-        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\ \hline
-        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\ \hline
-        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\ \hline
-        DD & -0.1750326007604599 & 0.3490835428237915 \\ \hline
-        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\ \hline
-        KKI & 0.04776120185852051 & 0.2546080946922302 \\ \hline
-        OHSU & 0.39824172854423523 & 0.138640895485878 \\ \hline
-        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\ \hline
-        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\ \hline
-        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\ \hline
-        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\ \hline
-        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ \hline
-    \end{tabular}
-    \caption{Generalization error of the GCN model on 57 datasets}
-    \label{tab:ge_gcn} % ge -> generalization error
-\end{table}
-
-\newpage
-
-\subsubsection{Generalization error of SGC model}
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-        Name & Ave. generalization error & Standard deviation \\ \hline
-        PROTEINS\_full & 0.04741409420967102 & 0.5624663829803467 \\ \hline
-        DD & -0.21720178425312042 & 0.40132829546928406 \\ \hline
-        ENZYMES & 0.3279166519641876 & 0.060605552047491074 \\ \hline
-        KKI & 0.10951493680477142 & 0.24877962470054626 \\ \hline
-        OHSU & 0.07604396343231201 & 0.1943538784980774 \\ \hline
-        Peking\_1 & 0.1769927442073822 & 0.22724425792694092 \\ \hline
-        COLORS-3 & 0.11781251430511475 & 0.04669201001524925 \\ \hline
-        SYNTHETIC & -0.37541666626930237 & 0.4494529068470001 \\ \hline
-        SYNTHETICnew & -0.36666664481163025 & 0.46157106757164 \\ \hline
-        Synthie & 0.13749998807907104 & 0.042466290295124054 \\ \hline
-        AIDS & 0.006437480449676514 & 0.011520843021571636 \\ \hline
-        BZR & 0.10815385729074478 & 0.21917256712913513 \\ \hline
-        BZR\_MD & 0.1678861677646637 & 0.09830881655216217 \\ \hline
-        COX2 & 0.07495072484016418 & 0.13212721049785614 \\ \hline
-        COX2\_MD & 0.14868313074111938 & 0.16540752351284027 \\ \hline
-        DHFR & 0.1332409381866455 & 0.1551705300807953 \\ \hline
-        DHFR\_MD & 0.0777045264840126 & 0.2503173351287842 \\ \hline
-        ER\_MD & -0.008367183618247509 & 0.15631815791130066 \\ \hline
-        FRANKENSTEIN & 0.10787498950958252 & 0.05383045971393585 \\ \hline
-        MCF-7 & 0.35490626096725464 & 0.17573890089988708 \\ \hline
-        MCF-7H & 0.3593124747276306 & 0.1884346306324005 \\ \hline
-        MOLT-4 & 0.18021871149539948 & 0.39803561568260193 \\ \hline
-        MOLT-4H & 0.18649999797344208 & 0.3838197886943817 \\ \hline
-        Mutagenicity & 0.04325000196695328 & 0.028246337547898293 \\ \hline
-        MUTAG & 0.07375730574131012 & 0.13988283276557922 \\ \hline
-        NCI1 & 0.09100000560283661 & 0.16161812841892242 \\ \hline
-        NCI109 & -0.06128125637769699 & 0.2943810522556305 \\ \hline
-        NCI-H23 & 0.31696873903274536 & 0.07884199917316437 \\ \hline
-        NCI-H23H & 0.3696562349796295 & 0.06490368396043777 \\ \hline
-        OVCAR-8 & 0.3291874825954437 & 0.0815950483083725 \\ \hline
-        OVCAR-8H & 0.2902187705039978 & 0.0771569237112999 \\ \hline
-        P388 & 0.3618437647819519 & 0.13428252935409546 \\ \hline
-        P388H & -0.052218757569789886 & 0.3646376132965088 \\ \hline
-        PC-3 & -0.08028124272823334 & 0.29225972294807434 \\ \hline
-        PC-3H & 0.2593437135219574 & 0.22314861416816711 \\ \hline
-        PTC\_FM & 0.10863511264324188 & 0.14730817079544067 \\ \hline
-        PTC\_FR & 0.08632432669401169 & 0.09645862877368927 \\ \hline
-        PTC\_MM & 0.09649830311536789 & 0.0817335695028305 \\ \hline
-        PTC\_MR & 0.060720354318618774 & 0.18291200697422028 \\ \hline
-        SF-295 & 0.3124375343322754 & 0.11770480871200562 \\ \hline
-        SF-295H & 0.28881245851516724 & 0.12331245839595795 \\ \hline
-        SN12C & 0.2917812764644623 & 0.05537300556898117 \\ \hline
-        SN12CH & 0.3397812247276306 & 0.09572991728782654 \\ \hline
-        SW-620 & 0.3427812457084656 & 0.2430398166179657 \\ \hline
-        SW-620H & 0.39274999499320984 & 0.1998475342988968 \\ \hline
-        UACC257 & -0.10218751430511475 & 0.2883416414260864 \\ \hline
-        UACC257H & 0.3322499692440033 & 0.22775331139564514 \\ \hline
-        Yeast & 0.0 & 0.0 \\ \hline
-        YeastH & 0.0 & 0.0 \\ \hline
-    \end{tabular}
-\end{table}
-
-\subsubsection{Generalization error of GATv2 model}
-
-\subsubsection{Generalization error of MPNN model}
-
-\subsubsection{Corrolation analysis between generalization error and graph parameters}
-
-\subsection{Discussion}
-
-\section{Conclusion}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{main} % refers to example.bib
-
-\clearpage
-
-\section{Appendix}
-
-\subsection{Basic information about TUDataset}\label{sec:datasets}
-This table~\ref{tab:datasets} shows the information about a list of datasets used in this thesis.
-
-\begin{table}[!ht]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|}
-    \hline
-        name & Graphs & Classes & Avg. Nodes & Avg. Edges & catagory \\ \hline
-        AIDS & 2000 & 2 & 15.69 & 16.20 & Small molecules \\ \hline
-        BZR & 405 & 2 & 35.75 & 38.36 & Small molecules \\ \hline
-        BZR\_MD & 306 & 2 & 21.30 & 225.06 & Small molecules \\ \hline
-        COX2 & 467 & 2 & 41.22 & 43.45 & Small molecules \\ \hline
-        COX2\_MD & 303 & 2 & 26.28 & 335.12 & Small molecules \\ \hline
-        DHFR & 756 & 2 & 42.43 & 44.54 & Small molecules \\ \hline
-        DHFR\_MD & 393 & 2 & 23.87 & 283.02 & Small molecules \\ \hline
-        ER\_MD & 446 & 2 & 21.33 & 234.85 & Small molecules \\ \hline
-        FRANKENSTEIN & 4337 & 2 & 16.90 & 17.88 & Small molecules \\ \hline
-        MCF-7 & 27770 & 2 & 26.40 & 28.53 & Small molecules \\ \hline
-        MCF-7H & 27770 & 2 & 47.31 & 49.44 & Small molecules \\ \hline
-        MOLT-4 & 39765 & 2 & 26.10 & 28.14 & Small molecules \\ \hline
-        MOLT-4H & 39765 & 2 & 46.70 & 48.74 & Small molecules \\ \hline
-        Mutagenicity & 4337 & 2 & 30.32 & 30.77 & Small molecules \\ \hline
-        MUTAG & 188 & 2 & 17.93 & 19.79 & Small molecules \\ \hline
-        NCI1 & 4110 & 2 & 29.87 & 32.30 & Small molecules \\ \hline
-        NCI109 & 4127 & 2 & 29.68 & 32.13 & Small molecules \\ \hline
-        NCI-H23 & 40353 & 2 & 26.07 & 28.10 & Small molecules \\ \hline
-        NCI-H23H & 40353 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        OVCAR-8 & 40516 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        OVCAR-8H & 40516 & 2 & 46.67 & 48.70 & Small molecules \\ \hline
-        P388 & 41472 & 2 & 22.11 & 23.56 & Small molecules \\ \hline
-        P388H & 41472 & 2 & 40.45 & 41.89 & Small molecules \\ \hline
-        PC-3 & 27509 & 2 & 26.36 & 28.49 & Small molecules \\ \hline
-        PC-3H & 27509 & 2 & 47.20 & 49.33 & Small molecules \\ \hline
-        PTC\_FM & 349 & 2 & 14.11 & 14.48 & Small molecules \\ \hline
-        PTC\_FR & 351 & 2 & 14.56 & 15.00 & Small molecules \\ \hline
-        PTC\_MM & 336 & 2 & 13.97 & 14.32 & Small molecules \\ \hline
-        PTC\_MR & 344 & 2 & 14.29 & 14.69 & Small molecules \\ \hline
-        SF-295 & 40271 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SF-295H & 40271 & 2 & 46.65 & 48.68 & Small molecules \\ \hline
-        SN12C & 40004 & 2 & 26.08 & 28.11 & Small molecules \\ \hline
-        SN12CH & 40004 & 2 & 46.69 & 48.72 & Small molecules \\ \hline
-        SW-620 & 40532 & 2 & 26.06 & 28.09 & Small molecules \\ \hline
-        SW-620H & 40532 & 2 & 46.63 & 48.66 & Small molecules \\ \hline
-        UACC257 & 39988 & 2 & 26.09 & 28.13 & Small molecules \\ \hline
-        UACC257H & 39988 & 2 & 46.68 & 48.71 & Small molecules \\ \hline
-        Yeast & 79601 & 2 & 21.54 & 22.84 & Small molecules \\ \hline
-        YeastH & 79601 & 2 & 39.45 & 40.75 & Small molecules \\ \hline
-        DD & 1178 & 2 & 284.32 & 715.66 & Bioinformatics \\ \hline
-        ENZYMES & 600 & 6 & 32.63 & 62.14 & Bioinformatics \\ \hline
-        KKI & 83 & 2 & 26.96 & 48.42 & Bioinformatics \\ \hline
-        OHSU & 79 & 2 & 82.01 & 199.66 & Bioinformatics \\ \hline
-        Peking\_1 & 85 & 2 & 39.31 & 77.35 & Bioinformatics \\ \hline
-        PROTEINS\_full & 1113 & 2 & 39.06 & 72.82 & Bioinformatics \\ \hline
-        COIL-DEL & 3900 & 100 & 21.54 & 54.24 & Computer vision \\ \hline
-        COIL-RAG & 3900 & 100 & 3.01 & 3.02 & Computer vision \\ \hline
-        Cuneiform & 267 & 30 & 21.27 & 44.80 & Computer vision \\ \hline
-        Fingerprint & 2149 & 15 & 7.06 & 5.76 & Computer vision \\ \hline
-        FIRSTMM\_DB & 41 & 11 & 1377.27 & 3074.10 & Computer vision \\ \hline
-        Letter-high & 2250 & 15 & 4.67 & 4.50 & Computer vision \\ \hline
-        Letter-low & 2250 & 15 & 4.68 & 3.13 & Computer vision \\ \hline
-        Letter-med & 2250 & 15 & 4.67 & 3.21 & Computer vision \\ \hline
-        MSRC\_9 & 221 & 8 & 40.58 & 97.94 & Computer vision \\ \hline
-        MSRC\_21 & 563 & 20 & 77.52 & 198.32 & Computer vision \\ \hline
-        MSRC\_21C & 209 & 20 & 40.28 & 96.60 & Computer vision \\ \hline
-        COLORS-3 & 10500 & 11 & 61.31 & 91.03 & Synthetic \\ \hline
-        SYNTHETIC & 300 & 2 & 100.00 & 196.00 & Synthetic \\ \hline
-        SYNTHETICnew & 300 & 2 & 100.00 & 196.25 & Synthetic \\ \hline
-        Synthie & 400 & 4 & 95.00 & 172.93 & Synthetic \\ \hline
-    \end{tabular}
-    \caption{Basic information about the datasets used in the experiment}
-    \label{tab:datasets}
-\end{table}
-
-\subsection{Example of GCN model}
-
-\begin{lstlisting}[language=Python]
-import torch
-
-\end{lstlisting}
-
-\end{document}
+Nevertheless, Morris et al.~\cite{morris2024futuredirectionstheorygraph} pointed out that the generalization ability of GNNs is still not well understood.
+The bounds established in these studies typically rely solely on general graph parameters, such as the maximum degree or total number of nodes, often overlooking more expressive graph parameters.

### 2025-01-29 paper/chapters/results.tex
Add thesis structure including title page, abstract, acknowledgments, conclusion, and related work sections

\chapter{Results \& Discussion}\label{chap:results}

In this chapter, the results of the experiments are presented and discussed. The experiments were conducted to evaluate the impact of different neural network structures and parameters on image reconstruction. The experiments were conducted using the four neural network architectures described in Chapter \ref{chap:experiments}. The neural networks were trained and tested using the datasets described in Section \ref{sec:datasets}. The experiments were conducted using the training and testing procedures described in Section \ref{sec:Experimental procedures}.

\section{Graph parameters}

The graph parameters calculated in the experiments are shown in Table \ref{tab:gp1}~\ref{tab:gp2}.

\section{Graph Convolutional Networks}
The results of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gcn}.

\begin{table}[!ht]
    \centering
    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
    \hline
    \toprule
        Name & Ave. generalization error & Standard deviation \\ 
    \midrule
        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\
        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\
        MOLT-4 & 0.0 & 0.014102176763117313 \\
        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\
        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\
        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\
        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\
        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\
        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\
        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\
        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\
        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\
        P388 & 0.008062511682510376 & 0.01043933816254139 \\
        P388H & 0.006343752145767212 & 0.007148966193199158 \\
        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\
        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\
        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\
        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\
        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\
        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\
        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\
        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\
        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\
        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\
        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\
        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\
        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\
        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\
        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\
        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\
        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\
        DD & -0.1750326007604599 & 0.3490835428237915 \\
        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\
        KKI & 0.04776120185852051 & 0.2546080946922302 \\
        OHSU & 0.39824172854423523 & 0.138640895485878 \\
        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\
        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\
        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\
        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\
        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ 
        \bottomrule
    \end{tabular}
    \caption{Generalization error of the GCN model on 57 datasets}
    \label{tab:ge_gcn} % ge -> generalization error
\end{table}

### 2025-01-29 paper/includes/abstract.tex
Add thesis structure including title page, abstract, acknowledgments, conclusion, and related work sections

% !TeX spellcheck = en_US
% !TeX encoding = UTF-8
\chapter*{Abstract}
The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).

### 2025-01-30 src/train.py
Update dataset loading to include shuffle seed option

@@ -256,7 +256,7 @@ def get_generalization_error_from_a_dataset(dataset_name: str, model_name: str, 
     # Load dataset
     # dataset = TUDataset(root='data/TUDataset', name=dataset_name, use_node_attr=True)
     # dataset = dataset.shuffle()
-    dataset = load_dataset(dataset_name)
+    dataset = load_dataset(dataset_name, use_shuffle_seed=True)
 
     centered_line = f'Dataset: {dataset}'.center(93)
     print('=' * 93 + f'\n{centered_line}\n' + '=' * 93 + '\n')

### 2025-01-31 src/main.py
Update get_best_hyperparameters function to support additional parameters for bt_GATv2 model

@@ -252,18 +252,35 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
     df = pd.read_csv(dataset_csv_path)
     sweep_ids = df[df['project'] == project_name]['sweep_id'].values
 
-    df_hyperparameters = pd.DataFrame({
-        'sweep_id': [],
-        'model_name': [],  # use project name
-        'batch_size': [],
-        'hidden_size': [],
-        'dataset_name': [],
-        'normlization': [],
-        'learning_rate': [],
-        'default_patience': [],
-        'patience_plateau': [],
-        'num_hidden_layers': []
-    })
+    if project_name == 'bt_GATv2':
+        df_hyperparameters = pd.DataFrame({
+            'sweep_id': [],
+            'model_name': [],  # use project name
+            'batch_size': [],
+            'hidden_size': [],
+            'dataset_name': [],
+            'normlization': [],
+            'learning_rate': [],
+            'default_patience': [],
+            'patience_plateau': [],
+            'num_hidden_layers': [],
+            'heads': [],
+            'dropout': [],
+            'residual': [],
+        })
+    else:
+        df_hyperparameters = pd.DataFrame({
+            'sweep_id': [],
+            'model_name': [],  # use project name
+            'batch_size': [],
+            'hidden_size': [],
+            'dataset_name': [],
+            'normlization': [],
+            'learning_rate': [],
+            'default_patience': [],
+            'patience_plateau': [],
+            'num_hidden_layers': []
+        })
 
     for sweep_id in sweep_ids:
         sweep = api.sweep(
@@ -277,22 +294,40 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
         # get the best hyperparameters
         best_hyperparameters = runs[0].config
         # save the best hyperparameters to dataframe
-        df_hyperparameters.loc[len(df_hyperparameters)] = [
-            sweep_id,
-            project_name,
-            best_hyperparameters['batch_size'],
-            best_hyperparameters['hidden_size'],
-            best_hyperparameters['dataset_name'],
-            best_hyperparameters['normlization'],
-            best_hyperparameters['learning_rate'],
-            best_hyperparameters['default_patience'],
-            best_hyperparameters['patience_plateau'],
-            best_hyperparameters['num_hidden_layers']
-        ]
+
+        if project_name == 'bt_GATv2':
+            df_hyperparameters.loc[len(df_hyperparameters)] = [
+                sweep_id,
+                project_name,
[…]

### 2025-01-31 src/main.py
Update get_correlation function to change default model to SGC and improve plot layout

@@ -147,11 +147,11 @@ def compare_generalization_error_and_parameters():
     plt.xlabel('Ave. Shortest Path')
     plt.ylabel('Ave. Generalization Error')
 
-    plt.tight_layout()
+    plt.tight_layout(rect=[0, 0, 1.5, 1])
     plt.show()
 
 
-def get_correlation(model: str = 'GCN'):
+def get_correlation(model: str = 'SGC'):
     '''
     Get the correlation between the generalization error and the parameters
     1. Ave. degree
@@ -169,9 +169,11 @@ def get_correlation(model: str = 'GCN'):
     Use scatter plot to show the correlation between the generalization error and the parameters
     '''
 
+    # generalization_error_file = f'results/generalization_error_{model}.csv'
+    generalization_error_file = f'results/output_{model}.csv'
 
 
-    df1 = pd.read_csv(f'results/generalization_error_bt_{model}.csv')
+    df1 = pd.read_csv(generalization_error_file)
     df2 = pd.read_csv('results/parameters.csv')
 
     df_combined = pd.merge(df1, df2, on='Name').drop(columns=['Unnamed: 0'])
@@ -181,11 +183,13 @@ def get_correlation(model: str = 'GCN'):
     # if the number of graphs is less than 1000, show the point in the scatter plot with color blue
     # if the number of graphs is more than 1000 but less than 4000, show the point in the scatter plot with color green
     # if the number of graphs is more than 4000, show the point in the scatter plot with color red
-    num_columns = len(df_combined.drop(columns= ['Name', 'Standard deviation']).columns)
+    num_columns = len(df_combined.drop(columns=['Name', 'Standard deviation']).columns)
     num_rows = (num_columns + 2) // 3
-    plt.figure(figsize=(20, 20))
-    for i, column in enumerate(df_combined.drop(columns= ['Name', 'Standard deviation']).columns):
-        plt.subplot(num_rows, 3, i+1)
+    plt.figure(figsize=(10, 12))
+    for i, column in enumerate(df_combined.drop(columns=['Name', 'Standard deviation']).columns):
+        if i == 0:
+            continue
+        plt.subplot(num_rows, 3, i)
         colors = []
         for name in df_combined['Name']:
             num_graphs = number_of_graphs(name)
@@ -195,11 +199,18 @@ def get_correlation(model: str = 'GCN'):
                 colors.append('green')
             else:
[…]

### 2025-01-31 src/main.py
Update get_best_hyperparameters function to handle bt_GATv2 model with additional parameters

@@ -265,18 +265,35 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
     df = pd.read_csv(dataset_csv_path)
     sweep_ids = df[df['project'] == project_name]['sweep_id'].values
 
-    df_hyperparameters = pd.DataFrame({
-        'sweep_id': [],
-        'model_name': [],  # use project name
-        'batch_size': [],
-        'hidden_size': [],
-        'dataset_name': [],
-        'normlization': [],
-        'learning_rate': [],
-        'default_patience': [],
-        'patience_plateau': [],
-        'num_hidden_layers': []
-    })
+    if project_name == 'bt_GATv2':
+        df_hyperparameters = pd.DataFrame({
+            'sweep_id': [],
+            'model_name': [],  # use project name
+            'batch_size': [],
+            'hidden_size': [],
+            'dataset_name': [],
+            'normlization': [],
+            'learning_rate': [],
+            'default_patience': [],
+            'patience_plateau': [],
+            'num_hidden_layers': [],
+            'heads': [],
+            'dropout': [],
+            'residual': [],
+        })
+    else:
+        df_hyperparameters = pd.DataFrame({
+            'sweep_id': [],
+            'model_name': [],  # use project name
+            'batch_size': [],
+            'hidden_size': [],
+            'dataset_name': [],
+            'normlization': [],
+            'learning_rate': [],
+            'default_patience': [],
+            'patience_plateau': [],
+            'num_hidden_layers': []
+        })
 
     for sweep_id in sweep_ids:
         sweep = api.sweep(
@@ -290,22 +307,40 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
         # get the best hyperparameters
         best_hyperparameters = runs[0].config
         # save the best hyperparameters to dataframe
-        df_hyperparameters.loc[len(df_hyperparameters)] = [
-            sweep_id,
-            project_name,
-            best_hyperparameters['batch_size'],
-            best_hyperparameters['hidden_size'],
-            best_hyperparameters['dataset_name'],
-            best_hyperparameters['normlization'],
-            best_hyperparameters['learning_rate'],
-            best_hyperparameters['default_patience'],
-            best_hyperparameters['patience_plateau'],
-            best_hyperparameters['num_hidden_layers']
-        ]
+
+        if project_name == 'bt_GATv2':
+            df_hyperparameters.loc[len(df_hyperparameters)] = [
+                sweep_id,
+                project_name,
[…]

### 2025-02-02 paper/chapters/results.tex
Update results.tex to include generalization error data for additional datasets and enhance correlation analysis visuals

@@
 \section{Graph Convolutional Networks}
-The results of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gcn}.
+The calculated generalization error of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gcn}.
 
@@
     \centering
+    \footnotesize
     \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
@@
     \midrule
-        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\
-        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\
-        MOLT-4 & 0.0 & 0.014102176763117313 \\
-        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\
-        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\
-        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\
-        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\
-        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\
-        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\
-        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\
-        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\
-        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\
-        P388 & 0.008062511682510376 & 0.01043933816254139 \\
-        P388H & 0.006343752145767212 & 0.007148966193199158 \\
-        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\
-        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\
-        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\
-        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\
-        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\
-        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\
-        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\
-        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\
-        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\
-        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\
-        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\
-        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\
-        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\
-        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\
-        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\
-        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\
-        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\
-        DD & -0.1750326007604599 & 0.3490835428237915 \\
-        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\
-        KKI & 0.04776120185852051 & 0.2546080946922302 \\
-        OHSU & 0.39824172854423523 & 0.138640895485878 \\
-        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\
-        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\
-        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\
-        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\
-        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ 
-        \bottomrule
+        AIDS & 0.0081874905154109 & 0.0117165874689817 \\ 
+        BZR & 0.0708846226334571 & 0.0609733723104 \\ 
+        BZR\_MD & 0.0961788743734359 & 0.1091229766607284 \\ 
+        COLORS-3 & 0.06828124076128 & 0.0298492461442947 \\ 
+        COX2 & 0.0840000063180923 & 0.1163316890597343 \\ 
+        COX2\_MD & 0.0750205665826797 & 0.1105385944247245 \\ 
+        DD & 0.0138164404779672 & 0.0569455623626709 \\ 
+        DHFR & 0.1413267403841018 & 0.0572429783642292 \\ 
+        DHFR\_MD & 0.0547252781689167 & 0.1071747243404388 \\ 
+        ENZYMES & 0.1968750059604644 & 0.1035036742687225 \\ 
+        ER\_MD & 0.0477907545864582 & 0.0669434815645217 \\ 
+        FRANKENSTEIN & 0.0549374930560588 & 0.0326129123568534 \\ 
+        KKI & 0.1822761297225952 & 0.3100946843624115 \\ 
+        MCF-7 & 0.0019999979995191 & 0.0135001158341765 \\ 
+        MCF-7H & 0.003406238509342 & 0.0127300517633557 \\ 
+        MOLT-4 & 0.0015624940861016 & 0.0123682264238595 \\ 
+        MOLT-4H & 0.0034062266349792 & 0.0167727246880531 \\ 
+        MUTAG & 0.1002193242311477 & 0.0946124866604805 \\ 
+        Mutagenicity & 0.040156252682209 & 0.0229900479316711 \\ 
+        NCI-H23 & 0.0028750181663781 & 0.0120867453515529 \\ 
+        NCI-H23H & 0.0005312621360644 & 0.0108473878353834 \\ 
+        NCI1 & 0.0832187384366989 & 0.0319501645863056 \\ 
+        NCI109 & 0.0711562559008598 & 0.0383276790380477 \\ 
+        OHSU & 0.3857143521308899 & 0.2356772273778915 \\ 
+        OVCAR-8 & 0.0038125098217278 & 0.0155245345085859 \\ 
+        OVCAR-8H & 0.0028437494765967 & 0.0162141937762498 \\ 
+        P388 & 0.0043125031515955 & 0.013600654900074 \\ 
+        P388H & 0.0070000053383409 & 0.0142645183950662 \\ 
+        PC-3 & 0.0024375021457672 & 0.0098565947264432 \\ 
+        PC-3H & 0.0060312449932098 & 0.0117860734462738 \\ 
+        PROTEINS\_full & 0.0026662945747375 & 0.0525967963039875 \\ 
+        PTC\_FM & 0.0923068895936012 & 0.1087017878890037 \\ 
+        PTC\_FR & 0.1018810272216796 & 0.1225867569446563 \\ 
+        PTC\_MM & 0.088215485215187 & 0.0875236690044403 \\ 
+        PTC\_MR & 0.0782608613371849 & 0.0882423818111419 \\ 
+        Peking\_1 & 0.2760869860649109 & 0.2045421004295349 \\ 
+        SF-295 & 0.0032500028610229 & 0.0157351642847061 \\ 
+        SF-295H & 0.0017812550067901 & 0.0091287596151232 \\ 
+        SN12C & 0.0003750085888896 & 0.0128499586135149 \\ 
+        SN12CH & 0.0031250000465661 & 0.0179813411086797 \\ 
+        SW-620 & 0.0014062583213672 & 0.0130064394325017 \\ 
+        SW-620H & 0.0014687419170513 & 0.0133227882906794 \\ 
+        SYNTHETIC & 0.0120833460241556 & 0.0160114392638206 \\ 
+        SYNTHETICnew & 0.1366666555404663 & 0.1849549412727356 \\ 
+        Synthie & 0.1234375014901161 & 0.0413857623934745 \\ 
+        UACC257 & 0.0011249959934502 & 0.0108615579083561 \\ 
+        UACC257H & 0.000843757414259 & 0.0126192783936858 \\ 
+        Yeast & 0.0053749978542327 & 0.027795847505331 \\ 
+        YeastH & 0.0001875102461781 & 0.0135009009391069 \\ 
     \end{tabular}
-    \caption{Generalization error of the GCN model on 57 datasets}
+    \caption{Generalization error of the GCN model on 49 datasets}
     \label{tab:ge_gcn} % ge -> generalization error
 \end{table}
+
+The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_GCN} and Figure~\ref{fig:correlation_ignore_less_than_1000_GCN}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{images/correlation_GCN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Graph Convolutional Network (GCN).
+Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
+    \label{fig:correlation_GCN}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{images/correlation_ignore_less_than_1000_GCN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Graph Convolutional Network (GCN).
+Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
+Only datasets with more than 1000 graphs are considered.}
+    \label{fig:correlation_ignore_less_than_1000_GCN}
+\end{figure}
+
+\subsection{Discussion}
+
+\section{Simplified Graph Convolution}
+The calculated generalization error of the experiments using Simplified Graph Convolution are shown in Table~\ref{tab:ge_sgc}.
+
+\begin{table}[!ht]
+    \centering
+    \footnotesize
+    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
+    \hline
+    \toprule
+        Name & Ave. generalization error & Standard deviation \\ 
+    \midrule
+        AIDS & 0.0094999792054295 & 0.0067623262293636 \\
+        BZR & 0.0398076958954334 & 0.0535244457423687 \\
+        BZR\_MD & 0.1050406470894813 & 0.095137633383274 \\
+        COLORS-3 & 0.0739687532186508 & 0.0297187566757202 \\
+        COX2 & 0.0861333459615707 & 0.0670665428042411 \\
+        COX2\_MD & 0.0440740659832954 & 0.1867186874151229 \\
+        DD & 0.1082454919815063 & 0.0635362416505813 \\
+        DHFR & 0.1035643592476844 & 0.0682980865240097 \\
+        DHFR\_MD & 0.0555799715220928 & 0.1178753077983856 \\
+        ENZYMES & 0.1837499886751175 & 0.0857001841068267 \\
+        ER\_MD & 0.0475622005760669 & 0.0829107165336608 \\
+        FRANKENSTEIN & 0.061875008046627 & 0.0329361073672771 \\
+        KKI & 0.0291044823825359 & 0.2818436622619629 \\
+        MCF-7 & 0.000656247138977 & 0.0137401102110743 \\
+        MCF-7H & 0.001156234764494 & 0.0151891019195318 \\
+        MOLT-4 & 0.0018124937778338 & 0.0116189513355493 \\
+        MOLT-4H & 0.0018437386024743 & 0.0139454510062932 \\
+        MUTAG & 0.1163011640310287 & 0.0678915232419967 \\
+        Mutagenicity & 0.0481875017285347 & 0.0258940625935792 \\
+        NCI-H23 & 0.0031250119209289 & 0.0100476266816258 \\
+        NCI-H23H & 5.9604645663569045e-09 & 0.0108693270012736 \\
+        NCI1 & 0.0839374884963035 & 0.0166628845036029 \\
+        NCI109 & 0.0677187517285347 & 0.0309047140181064 \\
+        OHSU & 0.0270329676568508 & 0.2689114809036255 \\
+        OVCAR-8 & 0.0021875083912163 & 0.0154096204787492 \\
+        OVCAR-8H & 0.0021250010468065 & 0.0172242671251297 \\
+        P388 & 0.0042812586762011 & 0.0127577884122729 \\
+        P388H & 0.0118749979883432 & 0.0183747168630361 \\
+        PC-3 & -0.0001562476099934 & 0.0097229816019535 \\
+        PC-3H & 0.000968748354353 & 0.0120369335636496 \\
+        PROTEINS\_full & 0.0114296078681945 & 0.0617067217826843 \\
+        PTC\_FM & 0.101800300180912 & 0.1584279388189315 \\
+        PTC\_FR & 0.102684274315834 & 0.0604767650365829 \\
+        PTC\_MM & 0.1027272716164588 & 0.1311521083116531 \\
+        PTC\_MR & 0.1173060312867164 & 0.1128198280930519 \\
+        Peking\_1 & 0.232065200805664 & 0.290688544511795 \\
+        SF-295 & 0.0006874978425912 & 0.0154270688071846 \\
+        SF-295H & 0.0021562576293945 & 0.0088528767228126 \\
+        SN12C & 0.001562523888424 & 0.0126561466604471 \\
+        SN12CH & -6.249547004699707e-05 & 0.0126207722350955 \\
+        SW-620 & 0.0008437514188699 & 0.0120212435722351 \\
+        SW-620H & 0.0024687468539923 & 0.0140694072470068 \\
+        SYNTHETIC & 0.0154166761785745 & 0.0234100967645645 \\
+        SYNTHETICnew & 0.1204166635870933 & 0.0984339192509651 \\
+        Synthie & 0.1784375011920929 & 0.0635749474167823 \\
+        UACC257 & 3.124475551885553e-05 & 0.0105321435257792 \\
+        UACC257H & 5.9604645663569045e-09 & 0.0123304584994912 \\
+        Yeast & 0.0027187527157366 & 0.0283915027976036 \\
+        YeastH & 0.0021875023376196 & 0.0149637833237648 \\
+    \end{tabular}
+    \caption{Generalization error of the SGC model on 49 datasets}
+    \label{tab:ge_sgc} % ge -> generalization error
+\end{table}
+
+The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_SGC} and Figure~\ref{fig:correlation_ignore_less_than_1000_SGC}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{images/correlation_SGC.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
+Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
+    \label{fig:correlation_SGC}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{images/correlation_ignore_less_than_1000_SGC.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
+Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
+Only datasets with more than 1000 graphs are considered.}
+    \label{fig:correlation_ignore_less_than_1000_SGC}
+\end{figure}

### 2025-02-03 paper/chapters/background.tex
No code changes made.

@@
 
-\subsection{Supervised learning}
+\paragraph{Supervised learning}
 Machine learning can be roughly divided into three categories: supervised learning, unsupervised learning, and reinforcement learning~\cite{bishop2006pattern}.
@@
 
-\subsection{Feed-forward neural networks}
+\paragraph{Feed-forward neural networks}
 
@@
 $L$ is denoted as the depth of the network.
+See Figure~\ref{fig:neural_network} for an illustration of a single neuron in a feed-forward neural network.
 
-\subsection{Loss function}
+\usetikzlibrary{decorations.pathreplacing}
+\begin{figure}[h!]
+    \centering
+\begin{tikzpicture}[>=stealth, scale=1.5, every node/.style={scale=1.2}]
+
+    % Input signals
+    \node at (-1.5, 1.5) (x1) {$x_1$};
+    \node at (-1.5, 0.5) (x2) {$x_2$};
+    \node at (-1.5, -1) (xm) {$x_m$};
+    \node at (-1.5, -0.25) (dots) {$\vdots$};
+
+    % Input brackets
+    \draw[decorate, decoration={brace, amplitude=5pt}] (-1.8, -1.1) -- (-1.8, 1.6) node[midway, left, xshift=-0.2cm, scale=0.8] {Input signal};
+
+    % Weights
+    \node[draw, circle] at (0.3, 1.5) (w1) {$W_1$};
+    \node[draw, circle] at (0.3, 0.5) (w2) {$W_2$};
+    \node[draw, circle] at (0.3, -1) (wm) {$W_m$};
+
+    \draw[->] (x1) -- (w1);
+    \draw[->] (x2) -- (w2);
+    \draw[->] (xm) -- (wm);
+
+    % Sum node
+    \node[draw, circle] at (2, 0) (sum) {$\Sigma$};
+
+    % Weighted connections to sum
+    \draw[->] (w1) -- (sum);
+    \draw[->] (w2) -- (sum);
+    \draw[->] (wm) -- (sum);
+
+    % Bias
+    \node[scale=0.8] at (2, 1.6) (biasText) {Bias};
+    \node at (2, 1.2) (biasEq) {$b$};
+    \draw[->] (biasEq) -- (sum);
+
+    % Activation function
+    \node[draw, rectangle] at (3.5, 0) (activation) {$\phi(\cdot)$};
+    \node at (5, 0) (y) {$y$};
+    \draw[->] (sum) -- (activation);
+    \draw[->] (activation) -- (y);
+
+    % Activation function label
+    \node[scale=0.8] at (3.5, 0.6) {Activation function};
+
+    % Weight label
+    \node[scale=0.8] at (0.3, -1.7) {Weights};
+
+    % Sum label
+    \node[scale=0.8] at (2.05, -0.5) {Sum};
+\end{tikzpicture}
+\caption{An illustration of a single neuron in a feed-forward neural network.
+The neuron computes a weighted sum of the input signals, adds a bias term, and applies an activation function to produce the output.}
+\label{fig:neural_network}
+\end{figure}
+
+\paragraph{Loss function}
 The loss function is a function that measures the difference between the predicted output of a model and the true output.
@@
 The cross-entropy loss function is used to measure the difference between the true output and the predicted output of a classification model.
+See Figure~\ref{fig:loss_function} for an example of a cost function surface in machine learning.
 
-\subsection{Activation function}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{loss_function.pdf}
+    \caption{3D representation of a cost function surface in machine learning. Optimization algorithms aim to navigate this surface to reach the global minimum, improving model accuracy.}
+    \label{fig:loss_function}
+\end{figure}
+
+\paragraph{Activation function}
 An activation function is a non-linear function that is applied to the output of a neuron in a neural network.
@@
 
-\subsection{Gradient Descent}
+\paragraph{Gradient Descent}
 Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
@@
 
-\subsection{Stochastic Gradient Descent}
+\paragraph{Stochastic Gradient Descent}
 Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
@@
 
-\subsection{Early Stopping}
+\paragraph{Early Stopping}
 Early stopping is a technique used to prevent overfitting in machine learning models.
@@
 
-\subsection{Cross-validation}
+\paragraph{Cross-validation}
 Cross-validation is a technique used to evaluate the performance of a machine learning model.
@@
 Cross-validation is used to prevent overfitting and to obtain a more accurate estimate of the model's performance.
+See Figure~\ref{fig:cross-validation} for an example of 5-fold cross-validation.
 
-\subsection{Hyperparameter tuning}
+\begin{center}
+    \begin{tikzpicture}[scale=1.0]
+
+    % Run 1
+    \draw[thick] (0, 5) rectangle (5, 5.5);
+    \fill[red!70] (0, 5) rectangle (1, 5.5);
+    \draw[thick] (1, 5) -- (1, 5.5);
+    \draw[thick] (2, 5) -- (2, 5.5);
+    \draw[thick] (3, 5) -- (3, 5.5);
+    \draw[thick] (4, 5) -- (4, 5.5);
+
+    \node[right=6pt] at (5, 5.25) {run 1};
+
+    % Run 2
+    \draw[thick] (0, 4.5) rectangle (5, 5);
+    \fill[red!70] (1, 4.5) rectangle (2, 5);
+    \draw[thick] (1, 4.5) -- (1, 5);
+    \draw[thick] (2, 4.5) -- (2, 5);
+    \draw[thick] (3, 4.5) -- (3, 5);
+    \draw[thick] (4, 4.5) -- (4, 5);
+
+    \node[right=6pt] at (5, 4.75) {run 2};
+
+    % Run 3
+    \draw[thick] (0, 4) rectangle (5, 4.5);
+    \fill[red!70] (2, 4) rectangle (3, 4.5);
+    \draw[thick] (1, 4) -- (1, 4.5);
+    \draw[thick] (2, 4) -- (2, 4.5);
+    \draw[thick] (3, 4) -- (3, 4.5);
+    \draw[thick] (4, 4) -- (4, 4.5);
+    \node[right=6pt] at (5, 4.25) {run 3};
+
+    % Run 4
+    \draw[thick] (0, 3.5) rectangle (5, 4);
+    \fill[red!70] (3, 3.5) rectangle (4, 4);
+    \draw[thick] (1, 3.5) -- (1, 4);
+    \draw[thick] (2, 3.5) -- (2, 4);
+    \draw[thick] (3, 3.5) -- (3, 4);
+    \draw[thick] (4, 3.5) -- (4, 4);
+    \node[right=6pt] at (5, 3.75) {run 4};
+
+    % Run 5
+    \draw[thick] (0, 3) rectangle (5, 3.5);
+    \fill[red!70] (4, 3) rectangle (5, 3.5);
+    \draw[thick] (1, 3) -- (1, 3.5);
+    \draw[thick] (2, 3) -- (2, 3.5);
+    \draw[thick] (3, 3) -- (3, 3.5);
+    \draw[thick] (4, 3) -- (4, 3.5);
+    \node[right=6pt] at (5, 3.25) {run 5};
+
+    \end{tikzpicture}
+    \captionof{figure}{Example of 5-fold cross-validation, where the dataset is split into 5 folds and the model is trained and evaluated on each fold.
+The red portion of each fold represents the test set, while the white portion represents the training set.
+The performance of the model is averaged over all the folds to obtain an estimate of the model's generalization performance.}
+    \label{fig:cross-validation}
+\end{center}
+
+\paragraph{Hyperparameter tuning}
 Hyperparameter tuning is the process of selecting the optimal hyperparameters for a machine learning model.
@@
 
-\subsection{Optimization algorithm}
+\paragraph{Optimization algorithm}
 An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
@@
 
-\subsection{Generalization}
+\paragraph{Generalization}
 A key concept in evaluating model performance or generalization ability in such task is the empirical generalization error $E_{gen}$.
@@
 
-\subsection{Graph Convolutional Networks (GCN)}
+\paragraph{Graph Convolutional Networks (GCN)}
 
@@
 
-\subsection{Simplified Graph Convolution (SGC)}
+\paragraph{Simplified Graph Convolution (SGC)}
 
@@
 
-\subsection{Graph Attention Networks (GAT)}
+\paragraph{Graph Attention Networks (GAT)}
 Graph Attention Networks (GAT) are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes.
@@
 
-\subsection{Graph Attention Networks v2 (GATv2)}
+\paragraph{Graph Attention Networks v2 (GATv2)}
 Graph Attention Networks v2 (GATv2)~\cite{brody2021attentive} is an improved version of the GAT model that introduces residual connections and multi-head attention. The GATv2 model is defined as
@@
 
-\subsection{Message Passing Neural Networks (MPNN)}
+\paragraph{Message Passing Neural Networks (MPNN)}
 Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} have been the leading model for graph learning.

### 2025-02-03 paper/chapters/experimentalstudy.tex
Update experimentalstudy.tex to correct dataset count and clarify GATv2 terminology

@@
 
-I list information about the 50 datasets used in the experiment in the appendix~\ref{sec:}.
+I list information about the 49 datasets used in the experiment in the appendix~\ref{sec:TODO}.
 
@@
 \subsection{Models}\label{sec:models}
-In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
+In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks v2(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
 The GCN model is shown in the appendix.

### 2025-02-03 paper/chapters/results.tex
finish correlation analysis

@@
 In this chapter, the results of the experiments are presented and discussed.
-The experiments were conducted to evaluate the impact of different neural network structures and parameters on image reconstruction.
-The experiments were conducted using the four neural network architectures described in Chapter \ref{chap:experiments}.
-The neural networks were trained and tested using the datasets described in Section \ref{sec:datasets}.
+The experiments were conducted to evaluate the generalization performance of four GNN architectures on 49 graph classification datasets.
+The four neural network architectures described in Chapter \ref{chap:experiments}.
+The datasets using for training and testing are described in Section \ref{sec:datasets}.
 The experiments were conducted using the training and testing procedures described in Section \ref{sec:Experimental procedures}.
 
-\section{Graph parameters}
+The following sections present the results of the experiments.
+First, the graph parameters calculated for the datasets are shown in~\ref{sec:result_graph_parameters}.
+Then, the generalization error of the four GNN architectures is presented individually in~\ref{sec:result_gcn},~\ref{sec:result_sgc},~\ref{sec:result_gatv2}, and~\ref{sec:result_mpnn}.
+Finally, the correlation analysis between the generalization error and the graph parameters is discussed in each section.
+
+Note that, the correlation analysis for each architecture is presented with two scatter plots.
+One contains all datasets, and the other contains only datasets with more than 1000 graphs.
+The reason for this separation is that the datasets with fewer graphs tend to have higher variability in generalization error, which can lead to misleading correlations.
+
+\section{Graph parameters}~\label{sec:result_graph_parameters}
 
@@
 
-\section{Graph Convolutional Networks}
+TODO: some datasets have 0 as the result, need to mention that
+
+\section{Graph Convolutional Networks}~\label{sec:result_gcn}
 The calculated generalization error of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gcn}.
@@
     \centering
-    \includegraphics[scale=0.6]{images/correlation_GCN.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Graph Convolutional Network (GCN).
-Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
+    \includegraphics[width=\textwidth]{images/correlation_GCN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Convolutional Networks (GCNs).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
 Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
@@
     \centering
-    \includegraphics[scale=0.6]{images/correlation_ignore_less_than_1000_GCN.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Graph Convolutional Network (GCN).
-Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
-Only datasets with more than 1000 graphs are considered.}
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_GCN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Convolutional Networks (GCNs).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 40 datasets in this plot and another 19 datasets are not included.}
     \label{fig:correlation_ignore_less_than_1000_GCN}
@@
 
+% -------------------------------------------------------------------------------------------------
+
 \subsection{Discussion}
 
-\section{Simplified Graph Convolution}
+The experimental results presented with \ref{fig:correlation_GCN} and \ref{fig:correlation_ignore_less_than_1000_GCN}  above demonstrate the relationships between graph parameters and the average generalization error across datasets of varying sizes.
+It gives insights into how different graph parameters influence the generalization performance of Graph Convolutional Networks (GCNs) in graph classification tasks.
+The following observations are noted from the results:
+
+\subsubsection{Correlation Analysis}
+
+\paragraph{Negative Correlations with Graph Diameter and Shortest Path}
+The results indicate a moderate negative correlation between generalization error and both graph diameter (-0.21) and average shortest path (-0.27) in the full dataset analysis~\ref{fig:correlation_GCN}.
+When considering only larger datasets~\ref{fig:correlation_ignore_less_than_1000_GCN}, these correlations become stronger (-0.33 and -0.36, respectively), suggesting that GNNs generalize better on graphs with shorter path lengths and smaller diameters.
+
+\paragraph{Influence of Graph Density and Clustering Coefficient}
+The correlation with graph density is relatively weak (0.09 in the full dataset~\ref{fig:correlation_GCN}, 0.27 in the filtered dataset~\ref{fig:correlation_ignore_less_than_1000_GCN}), but the clustering coefficient shows a higher correlation of 0.29 in the full dataset, which drops to 0.04 in the filtered dataset.
+This suggests that clustering coefficient may influence generalization, but likely due to the higher noise levels in smaller samples, the effect diminishes when excluding small datasets.
+On the contrary, the graph density indicate a moderate positive correlation in the filtered dataset, which is not observed in the full dataset.
+
+\paragraph{Centrality Measures}
+Closeness centrality shows a consistent positive correlation with generalization error (0.15 in the full dataset, 0.35 in the filtered dataset).
+On the other hand, betweenness centrality has a moderate negative correlation (-0.23 in the full dataset, -0.03 in the filtered dataset).
+Eigenvector Centrality shows weak correlations in both cases (-0.06 and 0.21).
+Overall, if the dataset size is considered, closeness centrality and eigenvector centrality appear to have a moderate positive influence on generalization error, while betweenness centrality has a negative effect.
+
+\paragraph{1-WL Color Count}
+The correlation with 1-WL color count is relatively weak (0.09 and 0.03 in full and filtered datasets, respectively).
+This finding is interesting, as it indicates that while the Weisfeiler-Lehman test is commonly used as a measure of GNN expressiveness, it does not necessarily dictate generalization behavior, for the GCN model at least.
+
+\subsubsection{Summary}
+Overall, structural features like average shortest path, graph diameter, and  centrality measure have stronger relationships with generalization error compared to measures like 1-WL color count and potentially clustering coefficient.
+Nonetheless, none of the parameters shows a highly significant correlation.
+% -------------------------------------------------------------------------------------------------
+
+\section{Simplified Graph Convolution}~\label{sec:result_sgc}
 The calculated generalization error of the experiments using Simplified Graph Convolution are shown in Table~\ref{tab:ge_sgc}.
@@
     \centering
-    \includegraphics[scale=0.6]{images/correlation_SGC.png}
+    \includegraphics[width=\textwidth]{images/correlation_SGC.png}
     \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
-Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
 Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
@@
     \centering
-    \includegraphics[scale=0.6]{images/correlation_ignore_less_than_1000_SGC.png}
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_SGC.png}
     \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
-Each subplot presents the correlation coefficient between a specific graph property and the generalization error.
-Only datasets with more than 1000 graphs are considered.}
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 40 datasets in this plot and another 19 datasets are not included.}
     \label{fig:correlation_ignore_less_than_1000_SGC}
 \end{figure}
+
+\subsection{Discussion}
+
+The experimental results presented with \ref{fig:correlation_SGC} and \ref{fig:correlation_ignore_less_than_1000_SGC}  above demonstrate the relationships between graph parameters and the average generalization error across datasets of varying sizes.
+It gives insights into how different graph parameters influence the generalization performance of Simplified Graph Convolution (SGC) in graph classification tasks.
+The following observations are noted from the results:
+
+\subsubsection{Correlation Analysis}
+
+\paragraph{Graph Average Degree}
+The average degree shows a weak positive correlation with generalization error in the full dataset (0.13), which increases substantially to a strong correlation (0.56) when only datasets with more than 1000 graphs are considered.
+This implies that generalization error is more sensitive to average degree in larger graph datasets.
+The weak correlation in the full dataset may be due to noise introduced by smaller datasets.
+
+\paragraph{Graph Diameter and Shortest Path}
+Both graph diameter (-0.31) and average shortest path (-0.34) exhibit moderate negative correlations with generalization error in the full dataset, indicating that datasets with more compact graph structures (smaller diameters and shorter path lengths) tend to generalize better.
+Interestingly, these correlations diminish in the filtered dataset to 0.05 and -0.00, respectively.
+It suggests that the significance of these measures decreases due to larger size of datasets.
+
+\paragraph{Graph Density and Clustering Coefficient}
+The clustering coefficient shows a moderate positive correlation with generalization error in both datasets (0.26 in the full dataset and 0.44 in the filtered dataset).
+This indicates that generalization error increases in denser neighborhoods, particularly in larger datasets.
+Graph density, on the other hand, shows weak correlations in both cases (0.14 in the full dataset and 0.12 in the filtered dataset).
+It suggests a weaker effect on generalization behavior compared to clustering coefficient.
+
+\paragraph{Centrality Measures}
+Among the centrality measures, betweenness centrality exhibits negative correlations with generalization error (-0.22 in the full dataset and -0.36 in the filtered dataset).
+This indicates that higher betweenness centrality leads to lower generalization error, particularly in larger datasets.
+Closeness centrality and eigenvector centrality exhibit weak to moderate correlations (0.20 and 0.07 in the full dataset; 0.17 and -0.12 in the filtered dataset), comparing to the betweenness centrality.
+Overall, centrality measures have a weak to moderate influence on generalization error, with betweenness centrality showing the most significant effect.
+
+\paragraph{1-WL Color Count}
+The 1-WL color count demonstrates a weak positive correlation with generalization error in the full dataset (0.20), which becomes substantially stronger in the filtered dataset (0.58).
+It suggests that the expressiveness of the graph structure, as measured by 1-WL color count, plays a more significant role in generalization behavior in larger datasets.
+
+\subsubsection{Summary}
+The results indicate that structural features like average degree and clustering coefficient are more predictive of generalization behavior in larger datasets, as reflected by their stronger correlations in the filtered dataset.
+In contrast, graph parameters like average graph diameter and shortest path, which show moderate correlations in the full dataset, diminish as the dataset size increases.
+Centrality measures, particularly betweenness centrality, exhibit a more consistent relationship with generalization error, with stronger correlations in the filtered dataset.
+Lastly, 1-WL coloring number shows the most significant correlation with generalization error, indicating that the expressiveness of the graph structure plays an important role in generalization ability.
+
+\section{Graph Attention Networks v2}~\label{sec:result_gatv2}
+The calculated generalization error of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gatv2}.
+
+\begin{table}[!ht]
+    \centering
+    \footnotesize
+    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
+    \hline
+    \toprule
+        Name & Ave. generalization error & Standard deviation \\ 
+    \midrule
+    AIDS & 0.0043124915100634 & 0.0093050524592399 \\ 
+    BZR & 0.0609999969601631 & 0.0820248797535896 \\ 
+    BZR\_MD & 0.0472357682883739 & 0.1092826277017593 \\ 
+    COLORS-3 & 0.043281253427267 & 0.0240429937839508 \\ 
+    COX2 & 0.0630377084016799 & 0.0825407281517982 \\ 
+    COX2\_MD & 0.085967056453228 & 0.0940771996974945 \\ 
+    DD & 0.1108267903327941 & 0.0513695515692234 \\ 
+    DHFR & 0.1174587234854698 & 0.0517340935766696 \\ 
+    DHFR\_MD & 0.0339438319206237 & 0.1088754534721374 \\ 
+    ENZYMES & 0.2141666859388351 & 0.0753771364688873 \\ 
+    ER\_MD & 0.0706957802176475 & 0.0536176972091198 \\ 
+    FRANKENSTEIN & 0.0540624968707561 & 0.0219314694404602 \\ 
+    KKI & 0.2389925420284271 & 0.3365208804607391 \\ 
+    MCF-7H & 0.0001249790220754 & 0.0124741122126579 \\ 
+    MCF-7 & 0.0007500052452087 & 0.0141399931162595 \\ 
+    MOLT-4H & 0.0006562412017956 & 0.0142586100846529 \\ 
+    MOLT-4 & 0.0004374861600808 & 0.0111289750784635 \\ 
+    MUTAG & 0.0780701860785484 & 0.0887901559472084 \\ 
+    Mutagenicity & 0.0441875047981739 & 0.0323983952403068 \\ 
+    NCI-H23H & 5.9604645663569045e-09 & 0.0108693270012736 \\ 
+    NCI-H23 & 9.377002425026149e-05 & 0.0100130606442689 \\ 
+    NCI109 & 0.087562508881092 & 0.0293439049273729 \\ 
+    NCI1 & 0.079031229019165 & 0.0203865990042686 \\ 
+    OHSU & 0.2868131995201111 & 0.3649870157241821 \\ 
+    OVCAR-8H & 6.25073880655691e-05 & 0.0174949076026678 \\ 
+    OVCAR-8 & 0.0003125071525573 & 0.0130370762199163 \\ 
+    P388H & 0.0005312621360644 & 0.0131217204034328 \\ 
+    P388 & 0.0042187571525573 & 0.0145163964480161 \\ 
+    PC-3H & -5.9604645663569045e-09 & 0.0116321872919797 \\ 
+    PC-3 & 0.0003437519189901 & 0.0097120413556694 \\ 
+    PROTEINS\_full & 0.0294719096273183 & 0.0491058491170406 \\ 
+    PTC\_FM & 0.0593364052474498 & 0.0939571186900138 \\ 
+    PTC\_FR & 0.0619827024638652 & 0.0776680409908294 \\ 
+    PTC\_MM & 0.0872390493750572 & 0.1021735519170761 \\ 
+    PTC\_MR & 0.0601662322878837 & 0.0595390647649765 \\ 
+    Peking\_1 & 0.250543475151062 & 0.2304597347974777 \\ 
+    SF-295H & 5.9604645663569045e-09 & 0.0102338008582592 \\ 
+    SF-295 & 0.0002187669306294 & 0.0146516626700758 \\ 
+    SN12CH & 0.0 & 0.0145929940044879 \\ 
+    SN12C & 0.0006562650087289 & 0.0130099598318338 \\ 
+    SW-620H & 0.0002187490463256 & 0.0138334389775991 \\ 
+    SW-620 & 0.0002812623861245 & 0.0136981671676039 \\ 
+    SYNTHETIC & 0.0212500095367431 & 0.0290307682007551 \\ 
+    SYNTHETICnew & 0.1174999922513961 & 0.0795870795845985 \\ 
+    Synthie & 0.1574999988079071 & 0.1155846491456031 \\ 
+    UACC257H & 5.9604645663569045e-09 & 0.0123304584994912 \\ 
+    UACC257 & 0.0005000054952688 & 0.0106954481452703 \\ 
+    YeastH & 0.0011562525760382 & 0.0136780375614762 \\ 
+    Yeast & 0.0016562461387366 & 0.0281631872057914 \\ 
+    \end{tabular}
+    \caption{Generalization error of the GATv2 model on 49 datasets}
+    \label{tab:ge_gatv2} % ge -> generalization error
+\end{table}
+
+The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_GATv2} and Figure~\ref{fig:correlation_ignore_less_than_1000_GATv2}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_GATv2.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Attention Networks v2 (GATv2).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
+    \label{fig:correlation_GATv2}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_GATv2.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Attention Networks v2 (GATv2).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 40 datasets in this plot and another 19 datasets are not included.}
+    \label{fig:correlation_ignore_less_than_1000_GATv2}
+\end{figure}
+
+\subsection{Discussion}
+
+The experimental results presented with \ref{fig:correlation_GATv2} and \ref{fig:correlation_ignore_less_than_1000_GATv2} above demonstrate the relationships between graph parameters and the average generalization error across datasets of varying sizes.
+It gives insights into how different graph parameters influence the generalization performance of Graph Attention Networks v2 (GATv2) in graph classification tasks.
+The following observations are noted from the results:
+
+\subsubsection{Correlation Analysis}
+
+\paragraph{Average Degree}
+A weak positive correlation of 0.12 between average degree and generalization error is observed in the full dataset analysis (\ref{fig:correlation_GATv2}).
+This correlation becomes significantly stronger (0.60) in the larger datasets (\ref{fig:correlation_ignore_less_than_1000_GATv2}), indicating that higher average degree may negatively impact generalization.
+This trend suggests that increased connectivity might lead to reduce the model's ability to effectively generalize to unseen data.
+
+\paragraph{Shortest Path and Graph Diameter}
+In the full dataset, a negative correlation is noted between generalization error and both shortest path (-0.22) and graph diameter (-0.16), indicating that smaller and more compact graphs are associated with better generalization.
+However, in larger datasets, the negative correlation with the shortest path diminishes (0.11), while graph diameter shows a weak positive correlation (0.18).
+My interpretation is that the noise in smaller datasets may have influenced the initial negative correlations.
+
+\paragraph{Graph Density and Clustering Coefficient}
+Graph density shows a very weak correlation in the full dataset (0.07) and remains weak in larger datasets (0.09).
+On the other hand, the clustering coefficient demonstrates considerable variability, with a strong positive correlation of 0.35 in the full dataset, which increases further (0.51) in the filtered dataset.
+This suggests the clustering coefficient has more impact on generalization than graph density, particularly in larger datasets.
+
+\paragraph{Centrality Measures}
+Betweenness centrality exhibits a moderate negative correlation (-0.29) in the full dataset and has similar correlation in the filtered dataset (-0.31).
+The average eigenvector centrality has also a negative correlation (-0.16 both in the full dataset and the filtered dataset), but relatively weaker than betweenness centrality.
+Closeness centrality, however, has a weak positive correlation (0.12 in the full dataset, 0.09 in the filtered dataset), indicating little impact on generalization error.
+It is the weakest among the centrality measures.
+
+\paragraph{1-WL Color Count}
+The 1-WL color count demonstrates moderate positive correlation in the full dataset (0.26), but this correlation increases significantly in larger datasets (0.59).
+It is similar to the results observed in the SGC model, suggesting that the expressiveness of the graph structure plays a more significant role in generalization behavior in larger datasets.
+
+\subsubsection{Summary}
+The results indicate that structural features like average degree and clustering coefficient are more predictive of generalization behavior in larger datasets, as reflected by their stronger correlations in the filtered dataset.
+In contrast, graph parameters like average graph diameter and shortest path, which show moderate negative correlations in the full dataset, but it becomes weak positive correlations in the filtered dataset.
+One possible explanation is that the noise in smaller datasets may have influenced the initial negative correlations.
+Centrality measures, particularly betweenness centrality, exhibit a more consistent relationship with generalization error, with stronger correlations in the filtered dataset.
+Lastly, 1-WL coloring number shows the most significant correlation with generalization error, indicating that the expressiveness of the graph structure plays an important role in generalization ability.
+
+\section{Message Passing Neural Networks}~\label{sec:result_mpnn}

### 2025-02-04 src/main.py
Add support for 'bt_MPNN' project in hyperparameter retrieval function

@@ -281,6 +281,20 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
             'dropout': [],
             'residual': [],
         })
+    elif project_name == 'bt_MPNN':
+        df_hyperparameters = pd.DataFrame({
+            'sweep_id': [],
+            'model_name': [],  # use project name
+            'batch_size': [],
+            'hidden_size': [],
+            'dataset_name': [],
+            'normlization': [],
+            'learning_rate': [],
+            'default_patience': [],
+            'patience_plateau': [],
+            'num_hidden_layers': [],
+            'mlp_hidden_dim': []
+        })
     else:
         df_hyperparameters = pd.DataFrame({
             'sweep_id': [],
@@ -323,6 +337,20 @@ def get_best_hyperparameters(project_name: str = 'bt_GCN'):
                 best_hyperparameters['heads'],
                 best_hyperparameters['dropout'],
                 best_hyperparameters['residual'],
+            ]
+        elif project_name == 'bt_MPNN':
+            df_hyperparameters.loc[len(df_hyperparameters)] = [
+                sweep_id,
+                project_name,
+                best_hyperparameters['batch_size'],
+                best_hyperparameters['hidden_size'],
+                best_hyperparameters['dataset_name'],
+                best_hyperparameters['normlization'],
+                best_hyperparameters['learning_rate'],
+                best_hyperparameters['default_patience'],
+                best_hyperparameters['patience_plateau'],
+                best_hyperparameters['num_hidden_layers'],
+                best_hyperparameters['mlp_hidden_dim']
             ]
         else:
             df_hyperparameters.loc[len(df_hyperparameters)] = [
@@ -430,4 +458,5 @@ if __name__ == '__main__':
     # model = 'GCN'
     # get_correlation(model)
 
-    get_best_hyperparameters('bt_GATv2')
+    project_name = 'bt_MPNN'
+    get_best_hyperparameters(project_name)

### 2025-02-20 paper/chapters/background.tex
Update thesis tex files to latest version

@@
-% \chapter{Theoretical Background}\label{chap:theoretical background}
-
-% \section{Example citation \& symbol reference}\label{sec:citation}
-% For symbols look at \cite{latex_symbols_2017}.
-
-% \section{Example reference}
-% Example reference: Look at chapter~\ref{chap:introduction}, for sections, look at section~\ref{sec:citation}.
-
-% \section{Example image}
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.5\linewidth]{uni-logo}
-% 	\caption{Meaningful caption for this image}
-% 	\label{fig:uniLogo}
-% \end{figure}
-
-% Example figure reference: Look at Figure~\ref{fig:uniLogo} to see an image. It can be \texttt{jpg}, \texttt{png}, or best: \texttt{pdf} (if vector graphic).
-
-% \section{Example table}
-
-% \begin{table}
-% 	\centering
-% 	\begin{tabular}{lr}
-% 		First column & Number column \\
-% 		\hline
-% 		Accuracy & 0.532 \\
-% 		F1 score & 0.87
-% 	\end{tabular}
-% 	\caption{Meaningful caption for this table}
-% 	\label{tab:result}
-% \end{table}
-
-% Table~\ref{tab:result} shows a simple table\footnote{Check \url{https://en.wikibooks.org/wiki/LaTeX/Tables} on syntax}
-
-\chapter{Background on learning on graphs}\label{chap:background}
+\chapter{Background}\label{chap:background}
 The following sections provide an overview of the concepts and methods related to graph theory, machine learning, and graph neural networks.
 
-\section{Notion}
-At first, we need to define some terms with regard to the graph.
-In graph theory, we assume that $G=(V,E)$ is an undirected graph, where $V$ is the set of nodes and $E  \subseteq \{\{v,w\}\mid v,w \in V , v \neq w\}$ is the set of edges.
-We use $\mathbb{G}$ to represent the set of all possible graphs.
-The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in E\}$.
+\section{Notation}
+First, it is necessary to define key terms related to graphs.
+In graph theory, it is assumed that $\mathcal{G}=(\mathcal{V},\mathcal{E})$ is an undirected graph, where $\mathcal{V}$ is the set of nodes and $\mathcal{E}  \subseteq \{\{v,w\}\mid v,w \in \mathcal{V} , v \neq w\}$ is the set of edges.
+The term $\mathbb{G}$ is used to represent the set of all possible graphs.
+The neighborhood of a node $v$ is denoted as $N(v)$, defined as $N(v) = \{w \mid \{v,w\} \in \mathcal{E}\}$.
 The degree of a node $v$, denoted as $d(v)$, is the number of neighbors of $v$, that is, $d(v) = |N(v)|$.
-In addition to the nodes and edges that comprise the graph, we can attach a more complex set of data to each node.
-A feature vector $x_n\in \mathbb{R}^k$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included.
-These vectors can be used to characterize graphs or nodes in graphs.
-The adjacency matrix $A \in \mathbb{R}^{|V| \times |V|}$ is a matrix that represents the connections between nodes in the graph.
+
+The adjacency matrix $\vec{A} \in \{0,1\}^{|\mathcal{V}| \times |\mathcal{V}|}$ is a matrix that represents the connections between nodes in the graph.
 The element $a_{ij}$ of the adjacency matrix is 1 if there is an edge between node $v_i$ and node $v_j$, and 0 otherwise.
 
+In addition to the nodes and edges that comprise the graph, it is possible to attach a more complex set of data to each node.
+A feature vector $\vec{x}_n\in \mathbb{R}^D$ with $0 \leq n < |\mathcal{V}|$, is attached to a node $v_n$, and in some cases, edge feature vectors are also included, where $D$ is the number of dimension of feature vectors.
+Then a matrix $\vec{X} \in \mathbb{R}^{|\mathcal{V}|\times D}$ can be constituted by stacking thesis node features vectors:
+
+$$
+    \vec{X} = \begin{bmatrix}
+    \vec{x}_1 \\
+    \vec{x}_2 \\
+    \vdots \\
+    \vec{x}_{|V|}
+    \end{bmatrix}
+$$
+
+These vectors can be used to characterize graphs or nodes in graphs.
+
 \section{Machine learning}
-In the following section, we provide an overview of the concepts and methods related to machine learning.
+In the subsequent section, an overview of the concepts and methodologies associated with machine learning is presented.
 
@@
 
-\paragraph{Feed-forward neural networks}
+\paragraph{Feed-forward Neural Networks}
 
-Feed-forward neural networks, also known as multilayer perceptrons (MLPs), are a type of neural network that consists of multiple layers of neurons.
+Feed-forward Neural Networks (FNNs), also known as multilayer perceptrons (MLPs), are a type of neural network that consists of multiple layers of neurons.
 The neurons in each layer are connected to the neurons in the next layer, and the output of each neuron is computed as a weighted sum of the inputs followed by a non-linear activation function.
@@
 $$ 
-    y = f(W^{(L)} \cdot f(W^{(L-1)} \cdot \ldots \cdot f(W^{(1)} \cdot x + b^{(1)}) + b^{(2)}) + \ldots + b^{(L)})
+    \vec{y} = f(\vec{W}^{(L)} \cdot f(\vec{W}^{(L-1)} \cdot \ldots \cdot f(\vec{W}^{(1)} \cdot \vec{x} + \vec{b}^{(1)}) + \vec{b}^{(2)}) + \ldots + \vec{b}^{(L)})
 $$
 
-where $x$ is the input vector, $W^{(i)}$ and $b^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function.
-The output $y$ is the predicted output of the network.
+where $\vec{x}\in \mathbb{R}^D$ is the input vector, $\vec{W}^{(i)}$ and $\vec{b}^{(i)}$ are the weights and biases of the $i$-th layer, and $f$ is the activation function.
+The output $\vec{y}$ is the predicted output of the network.
 $L$ is denoted as the depth of the network.
@@
     % Input brackets
-    \draw[decorate, decoration={brace, amplitude=5pt}] (-1.8, -1.1) -- (-1.8, 1.6) node[midway, left, xshift=-0.2cm, scale=0.8] {Input signal};
+    \draw[decorate, decoration={brace, amplitude=5pt}] (-1.8, -1.1) -- (-1.8, 1.6) node[midway, left, xshift=-0.2cm, scale=0.8] {Input vector};
 
     % Weights
-    \node[draw, circle] at (0.3, 1.5) (w1) {$W_1$};
-    \node[draw, circle] at (0.3, 0.5) (w2) {$W_2$};
-    \node[draw, circle] at (0.3, -1) (wm) {$W_m$};
+    \node[draw, circle] at (0.3, 1.5) (w1) {$w_1$};
+    \node[draw, circle] at (0.3, 0.5) (w2) {$w_2$};
+    \node[draw, circle] at (0.3, -1) (wm) {$w_m$};
 
@@
 \end{tikzpicture}
-\caption{An illustration of a single neuron in a feed-forward neural network.
-The neuron computes a weighted sum of the input signals, adds a bias term, and applies an activation function to produce the output.}
+\caption{The diagram illustrates the basic structure of a neuron in an artificial neural network.
+Inputs $x_1, x_2, \ldots, x_m \in \mathbb{R}$ are multiplied by their respective weights $w_1, w_2, \ldots, w_m \in \mathbb{R}$ and summed together including a bias term $b$.
+The result is then passed through an activation function $\phi(\cdot)$ to produce the output $y$.}
 \label{fig:neural_network}
@@
 $$
-    L(y, \hat{y}) = -\sum_{i} y_i \log(\hat{y}_i)
+    L(\vec{y}, \hat{\vec{y}}) = -\sum_{i} \vec{y_i} \log(\hat{\vec{y}}_i)
 $$
 
-where $y$ is the true output, $\hat{y}$ is the predicted output, and $i$ is the index of the classes.
+where $\vec{y}$ is the true output, $\hat{\vec{y}}$ is the predicted output, and $i$ is the index of the classes.
 The cross-entropy loss function is used to measure the difference between the true output and the predicted output of a classification model.
-See Figure~\ref{fig:loss_function} for an example of a cost function surface in machine learning.
+See Figure~\ref{fig:loss_function} for a simple example of a cost function surface in machine learning.
 
@@
     \includegraphics[width=0.8\textwidth]{loss_function.pdf}
-    \caption{3D representation of a cost function surface in machine learning. Optimization algorithms aim to navigate this surface to reach the global minimum, improving model accuracy.}
+    \caption{A 3D representation of a cost function surface used in machine learning optimization.
+The x1 and x2 axes represent input parameters, while the y-axis represents the cost value.
+The surface highlights the nature of the optimization landscape.}
     \label{fig:loss_function}
@@
 The activation function introduces non-linearity into the network, allowing it to learn complex patterns in the data.
-There are many activation functions that can be used in neural networks, such as the sigmoid function, the tanh function, and the ReLU function.
+There are many activation functions that can be used in neural networks, such as the Sigmoid function, the Hyperbolic Tangent (Tanh) function, the Rectified Linear Unit (ReLU) function \cite{nair2010rectified} and its variant Leaky Rectified Linear Unit (LeakyReLU) \cite{xu2015empirical}.
 The ReLU function is one of the most commonly used activation functions in deep learning because it is simple and computationally efficient.
-The ReLU function is defined as
+The ReLU function is defined as:
 
-$$
-    \textrm{ReLU}(\cdot)=\max(0,\cdot)
-$$
+\begin{equation*}
+    \textrm{ReLU}(x)=\max(0,x)
+\end{equation*}
+
+And its variant, the LeakyReLU function, is defined as:
+
+\begin{equation*}
+    \mathrm{LeakyReLU}(x) = 
+    \begin{cases} 
+        x, & \text{if } x > 0 \\
+        \alpha x, & \text{otherwise}
+    \end{cases}
+\end{equation*}
+
+where $\alpha$ is a small positive constant that controls the slope of the function for negative values of $x$.
 
@@
 
-\paragraph{Gradient Descent}
+\paragraph{Gradient descent}
 Gradient descent is an optimization algorithm used to minimize a function by iteratively moving in the direction of the steepest decrease of the function.
@@
 
-$$
-    W^{(t+1)} = W^{(t)} - \alpha \nabla f(W^{(t)})
-$$
-where $W^{(t)}$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(W^{(t)})$ is the gradient of the function $f$ with respect to the parameters $W^{(t)}$.
+\begin{equation} \label{eq:gradient_descent}
+    \vec{W}^{(t+1)} = \vec{W}^{(t)} - \alpha \nabla f(\vec{W}^{(t)})
+\end{equation}
+
+where $\vec{W}^{(t)}$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, and $\nabla f(\vec{W}^{(t)})$ is the gradient of the function $f$ with respect to the parameters $\vec{W}^{(t)}$.
 The learning rate $\alpha$ is a hyperparameter that controls the step size of the update.
@@
 
-\paragraph{Stochastic Gradient Descent}
-Stochastic gradient descent (SGD) is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
+\paragraph{Stochastic gradient descent}
+Stochastic gradient descent~\cite{robbins1951stochastic} is a variant of gradient descent that uses a random sample of the training data to compute the gradient at each iteration.
 The algorithm works by randomly selecting a mini-batch of data points from the training dataset, computing the gradient of the loss function with respect to the mini-batch, and then updating the parameters based on the gradient.
@@
 
-$$
-    W^{(t+1)} = W^{(t)} - \alpha \nabla f(W^{(t)}, x^{(t)})
-$$
-where $x^{(t)}$ is a mini-batch of data points from the training dataset.
-Stochastic gradient descent is more computationally efficient than standard gradient descent and can be used to train large-scale machine learning models.
+\begin{equation} \label{eq:stochastic_gradient_descent}
+    \vec{W}^{(t+1)} = \vec{W}^{(t)} - \alpha \nabla f(\vec{W}^{(t)}, \vec{x}^{(t)})
+\end{equation}
 
-\paragraph{Early Stopping}
-Early stopping is a technique used to prevent overfitting in machine learning models.
+where $\vec{W}^{(t)}$ is the parameter vector at iteration $t$, $\alpha$ is the learning rate, $\nabla f(\vec{W}^{(t)}, \vec{x}^{(t)})$ is the gradient of the function $f$ with respect to the parameters $\vec{W}^{(t)}$ and the mini-batch $\vec{x}^{(t)}$.
+Stochastic gradient descent is more computationally efficient than standard gradient descent~\ref{eq:gradient_descent} and can be used to train large-scale machine learning models.
+
+\paragraph{Optimization algorithm}
+An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
+The goal is to find the set of parameters that minimizes the loss function.
+Gradient descent is a common optimization algorithm used in machine learning, but there are many variants of gradient descent that are designed to improve convergence speed and stability.
+Some popular optimization algorithms include Adam~\cite{kingma2014adam}, RMSprop~\cite{graves2013generating}, and Adagrad~\cite{duchi2011adaptive}.
+These algorithms use different strategies to update the parameters of the model and can be more effective than standard gradient descent in certain situations.
+
+\paragraph{Early stopping}
+Early stopping \cite{morgan1989generalization}\cite{prechelt2002early} is a technique used to prevent overfitting in machine learning models.
 The idea is to monitor the performance of the model on a validation dataset during training and stop training when the performance starts to degrade.
@@
 \begin{center}
-    \begin{tikzpicture}[scale=1.0]
+    \begin{tikzpicture}[scale=1.2]
 
@@
 
+    % Fold labels
+    \node[below=6pt] at (0.5, 3) {fold 1};
+    \node[below=6pt] at (1.5, 3) {fold 2};
+    \node[below=6pt] at (2.5, 3) {fold 3};
+    \node[below=6pt] at (3.5, 3) {fold 4};
+    \node[below=6pt] at (4.5, 3) {fold 5};
+
     \end{tikzpicture}
@@
 Hyperparameter tuning is an important step in the machine learning pipeline and can have a significant impact on the performance of the model.
-There are many techniques for hyperparameter tuning, such as grid search, random search, and Bayesian optimization.
-In this thesis, Bayesian optimization is used to tune the hyperparameters of the models.
+There are many techniques for hyperparameter tuning, such as grid search, random search~\cite{bergstra2012random}, and Bayesian optimization~\cite{snoek2012practical}.
+This thesis employs Bayesian optimization to optimize the hyperparameters of the models.
 
 Bayesian optimization is more efficient than grid search and random search because it uses a probabilistic model to guide the search for the optimal hyperparameters.
-The idea is to model the objective function (e.g.
-the validation accuracy of the model) as a Gaussian process and use the model to select the next set of hyperparameters to evaluate.
+The idea is to model the objective function (e.g., the validation accuracy of the model) as a Gaussian process and use the model to select the next set of hyperparameters to evaluate.
 This process is repeated until the optimal hyperparameters are found.
-
-\paragraph{Optimization algorithm}
-An optimization algorithm is an algorithm used to minimize a function by iteratively updating the parameters of the model.
-The goal is to find the set of parameters that minimizes the loss function.
-Gradient descent is a common optimization algorithm used in machine learning, but there are many variants of gradient descent that are designed to improve convergence speed and stability.
-Some popular optimization algorithms include Adam~\cite{kingma2014adam}, RMSprop~\cite{graves2013generating}, and Adagrad~\cite{duchi2011adaptive}.
-These algorithms use different strategies to update the parameters of the model and can be more effective than standard gradient descent in certain situations.
 
@@
 The model may perform well on the training dataset but poorly on the test dataset.
-By observing the generalization error, we can decide on a stopping criterion for the training process.
+By observing the generalization error, I can decide on a stopping criterion for the training process.
 And the generalization error can be used to determine whether the model is overfitting or underfitting.
-Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g.
-Graph parameter).
+Furthermore, the generalization error can be influenced by many factors, such as the model architecture, the hyperparameters, and the data properties in the dataset (e.g., graph parameter).
 
-\section{Graph Neural Networks}
-Graph Neural Networks (GNNs) are a class of neural networks that can operate on graph-structured data.
+\section{Graph Neural Network}
+GNN is a class of neural networks that can operate on graph-structured data.
 GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
@@
 
-In the following sections, we provide an overview of the methods related to this thesis.
+In the following sections, I provide an overview of the methods related to this thesis.
 
-\paragraph{Graph Convolutional Networks (GCN)}
+\paragraph{Graph Convolutional Network}
 
-Graph Convolutional Networks (GCNs) are a class of neural networks that can operate on graph-structured data.
-The GCN model $f(X, A)$, as proposed by Kipf and Welling~\cite{kipf2016semi}, is defined as
+Graph Convolutional Network (GCNs) is a class of neural networks that can operate on graph-structured data.
+The GCN model $f(\vec{X}, \vec{A})$, as proposed by Kipf and Welling~\cite{kipf2016semi}, is defined as
 
 $$ 
- H^{(l+1)} = \sigma(\tilde{D}^{-\frac{1}{2}}\tilde{A}\tilde{D}^{-\frac{1}{2}}H^{(l)}W^{(l)})
+ \vec{h}^{(l+1)} = \sigma(\tilde{\vec{D}}^{-\frac{1}{2}}\tilde{\vec{A}}\tilde{\vec{D}}^{-\frac{1}{2}}\vec{h}^{(l)}\vec{W}^{(l)})
 $$
 
-where $H^{(l)}\in \mathbb{R}^{N\times D}$ is the node feature matrix at layer $l$; $H^{(0)} = X$.
-$\tilde{A} = A + I$ is the adjacency matrix of the graph with self-connections added, $\tilde{D}$ is the degree matrix of $\tilde{A}$, $W^{(l)}$ is the weight matrix of the layer, and $\sigma$ is the activation function, such as the $\textrm{ReLU}(\cdot)=\max(0,\cdot)$.
+where $\vec{h}^{(l)}\in \mathbb{R}^{N\times D}$ is the node feature matrix at layer $l$; $\vec{h}^{(0)} = \vec{X} \in \mathbb{R}^{\mathcal{V}\times D}$.
+$\tilde{\vec{A}} = \vec{A} + \vec{I}$ is the adjacency matrix of the graph with self-connections added, $\tilde{\vec{D}}_{ii}=\sum_{j=0} \tilde{\vec{A}}_{ij}$ its diagonal degree matrix.
+$\vec{W}^{(l)}$ is the weight matrix of the layer, and $\sigma$ is the activation function, such as the $\textrm{ReLU}(\cdot)=\max(0,\cdot)$.
 The GCN layer aggregates information from neighboring nodes and updates the node features by applying a linear transformation followed by a non-linear activation function.
@@
 
-\paragraph{Simplified Graph Convolution (SGC)}
+\paragraph{Simplified Graph Convolution}
 
@@
 $$
- X' = (\tilde{D}^{-\frac{1}{2}}\tilde{A}\tilde{D}^{-\frac{1}{2}})^K XW
+ \vec{X}' = (\tilde{\vec{D}}^{-\frac{1}{2}}\tilde{\vec{A}}\tilde{\vec{D}}^{-\frac{1}{2}})^K \vec{X}\vec{W}
 $$
 
-where $X$ is the node feature matrix, $W$ is the weight matrix, $\tilde{A}$ is the adjacency matrix with self-connections added, $\tilde{D}$ is the degree matrix of $\tilde{A}$, and $K$ is the number of layers.
+where $\vec{X}$ is the node feature matrix, $W$ is the weight matrix, $\tilde{\vec{A}}$ is the adjacency matrix with self-connections added, $\tilde{\vec{D}}$ is the degree matrix of $\tilde{\vec{A}}$, and $K$ is the number of layers.
 
-\paragraph{Graph Attention Networks (GAT)}
-Graph Attention Networks (GAT) are a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes.
+\paragraph{Graph Attention Network}
+Graph Attention Network (GAT) \cite{velivckovic2017graph} is a class of neural networks that use attention mechanisms to aggregate information from neighboring nodes.
 The GAT model updates the feature representation of a node by assigning different importance scores, known as attention coefficients, to its neighbors.
-The updated node feature $\mathbf{h}_i^{(l+1)}$ at layer $l+1$ is given by:
+The updated node feature $\vec{h}_i^{(l+1)} \in \mathbb{R}^{D'}$ at layer $l+1$ is given by:
 
 $$
-\mathbf{h}_i^{(l+1)} = \sigma \left( \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l)} \mathbf{W}^{(l)} \mathbf{h}_j^{(l)} \right)
+\vec{h}_i^{(l+1)} = \sigma \left( \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l)} \vec{W}^{(l)} \vec{h}_j^{(l)} \right)
 $$
 
-where $\mathbf{h}_i^{(l)}$ is the feature vector of node $i$ at layer $l$, $\mathbf{W}^{(l)}$ is a learnable weight matrix, $\sigma$ is an activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between nodes $i$ and $j$.
+where $\vec{h}_i^{(l)} \in \mathbb{R}^D$ is the feature vector of node $i$ at layer $l$, $\vec{W}^{(l)} \in \mathbb{R}^{D' \times D}$ is a learnable weight matrix, $\sigma$ is an activation function, and $\alpha_{ij}^{(l)}$ is the attention coefficient between nodes $i$ and $j$.
 These coefficients are computed as:
@@
 $$
-\alpha_{ij}^{(l)} = \frac{\exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l)^\top} [\mathbf{W}^{(l)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l)} \mathbf{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l)^\top} [\mathbf{W}^{(l)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l)} \mathbf{h}_k^{(l)}] \right) \right)}
+\alpha_{ij}^{(l)} = \frac{\exp \left( \textrm{LeakyReLU} \left( \vec{a}^{(l)^\top} [\vec{W}^{(l)} \vec{h}_i^{(l)} \| \vec{W}^{(l)} \vec{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \textrm{LeakyReLU} \left( \vec{a}^{(l)^\top} [\vec{W}^{(l)} \vec{h}_i^{(l)} \| \vec{W}^{(l)} \vec{h}_k^{(l)}] \right) \right)}
 $$
 
-where $\|$ denotes the concatenation of node features, and $\mathbf{a}^{(l)}$ is a shared attention vector. The softmax function ensures the attention coefficients sum to one for a node's neighbors.
+where $\|$ denotes the concatenation of node features, and $\vec{a}^{(l)} \in \mathbb{R}^{2D'}$ is a shared attention vector.
+The softmax function ensures the attention coefficients sum to one for a node's neighbors.
 
-GAT is particularly effective for tasks where different neighbors contribute unequally to a node's representation.
-By using attention mechanisms, GAT dynamically weighs neighbor contributions, enabling more expressive feature aggregation compared to earlier methods like GCNs.
-
-\paragraph{Graph Attention Networks v2 (GATv2)}
-Graph Attention Networks v2 (GATv2)~\cite{brody2021attentive} is an improved version of the GAT model that introduces residual connections and multi-head attention. The GATv2 model is defined as
+\paragraph{Graph Attention Network v2 (GATv2)}
+Graph Attention Network v2 (GATv2) \cite{brody2021attentive} is an improved version of the GAT model that introduces residual connections and multi-head attention. The GATv2 model is defined as
 
 $$
-    \mathbf{h}_i^{(l+1)} = \sigma \left( \sum_{h=1}^{H} \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l,h)} \mathbf{W}^{(l,h)} \mathbf{h}_j^{(l)} \right) + \mathbf{h}_i^{(l)}
+    \vec{h}_i^{(l+1)} = \sigma \left( \sum_{h=1}^{H} \sum_{j \in \mathcal{N}(i)} \alpha_{ij}^{(l,h)} \vec{W}^{(l,h)} \vec{h}_j^{(l)} \right) + \vec{h}_i^{(l)}
 $$
 
-where $H$ is the number of attention heads, $\alpha_{ij}^{(l,h)}$ is the attention coefficient between nodes $i$ and $j$ for head $h$, and $\mathbf{W}^{(l,h)}$ is the weight matrix for head $h$.
+where $H$ is the number of attention heads, $\alpha_{ij}^{(l,h)}$ is the attention coefficient between nodes $i$ and $j$ for head $h$, and $\vec{W}^{(l,h)}$ is the weight matrix for head $h$.
 The attention coefficients are computed as
@@
 $$
-    \alpha_{ij}^{(l,h)} = \frac{\exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l,h)^\top} [\mathbf{W}^{(l,h)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l,h)} \mathbf{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \textrm{LeakyReLU} \left( \mathbf{a}^{(l,h)^\top} [\mathbf{W}^{(l,h)} \mathbf{h}_i^{(l)} \| \mathbf{W}^{(l,h)} \mathbf{h}_k^{(l)}] \right) \right)}
+    \alpha_{ij}^{(l,h)} = \frac{\exp \left( \vec{a}^{(l,h)^\top} \textrm{LeakyReLU} \left( \vec{W}^{(l,h)} [ \vec{h}_i^{(l)} \| \vec{h}_j^{(l)}] \right) \right)}{\sum_{k \in \mathcal{N}(i)} \exp \left( \vec{a}^{(l,h)^\top} \textrm{LeakyReLU} \left( \vec{W}^{(l,h)} [ \vec{h}_i^{(l)} \| \vec{h}_j^{(l)}] \right) \right)}
 $$
 
-The GATv2 model uses multi-head attention to allow the model to attend to different parts of the input space.
-The model also introduces residual connections to improve the flow of information through the network.
-The GATv2 model has been shown to outperform the original GAT model on a wide range of tasks.
+In comparison to the original GAT model, GATv2 get the ability to compute dynamic attention by modifying the order of internal operations, which allows the model outperforms GAT with respect to accuracy.
 
-\paragraph{Message Passing Neural Networks (MPNN)}
-Message Passing Neural Networks (MPNNs)~\cite{gilmer2017neural} have been the leading model for graph learning.
+\paragraph{Message Passing Neural Networks}
+Message Passing Neural Network (MPNN) \newline \cite{gilmer2017neural} has been the leading model for graph learning.
 The MPNN model operates by iteratively passing messages between nodes and updating their representations.
@@
 $$
-    m_i^{(t+1)} = \sum_{j\in N(i)}M^{(t)}(h_i^{(t)}, h_j^{(t)}, e_{ij})
+    \vec{m}_i^{(t+1)} = \sum_{j\in N(i)}M^{(t)}(\vec{h}_i^{(t)}, \vec{h}_j^{(t)}, e_{ij})
 $$
 
-where $m_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is a learnable message function (typically implemented as a neural network, such as an MLP), $h_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $h_j^{(t)}$ is the node feature vector of node $j$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
-The message function $M^{(t)}$ is a neural network that takes as input the node feature vectors of node $i$ and node $j$, and the edge feature vector between them, and outputs the message vector $m_i^{(t)}$.
+where $\vec{m}_i^{(t)}$ is the message vector of node $i$ at iteration $t$, $M^{(t)}$ is a learnable message function (typically implemented as a neural network, such as an MLP), $\vec{h}_i^{(t)}$ is the node feature vector of node $i$ at iteration $t$, $\vec{h}_j^{(t)}$ is the node feature vector of node $j$ at iteration $t$, $e_{ij}$ is the edge feature vector between node $i$ and node $j$, and $N(i)$ is the neighborhood of node $i$.
+The message function $M^{(t)}$ is a neural network that takes as input the node feature vectors of node $i$ and node $j$, and the edge feature vector between them, and outputs the message vector $\vec{m}_i^{(t)}$.
 
-\section{Graph parameters} \label{sec:graph_parameters}
-Now we can introduce the concept of a graph parameter.
-A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a d-dimensional vector over the reals.
-Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
-A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-WL algorithm, etc.).
-This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:graph_parameters}.
+\section{Graph parameters} \label{sec:theoretical_graph_parameters}
+Now I can introduce the concept of a graph parameter.
+A graph parameter is a function $f: \mathbb{G} \rightarrow \mathbb{R}^d$ for $d\in \mathbb{N} >0$, which maps a graph to a $d$-dimensional vector over the reals.
+Furthermore, such functions need to be permutation invariant, i.e., $f(G) = f(\pi(G))$ for any permutation $\pi$ of the nodes of $G$, where a permutation is a bijective function $\pi: V \rightarrow V$ and $\pi(G)$ denotes the graph obtained by permuting the nodes of $G$ according to $\pi$.
+A graph parameter allows us to quantify certain properties of a graph, from the basic structural numbers (number of nodes, number of edges, average degree, etc.) to distance properties (average shortest path length, diameter, etc.) to more complex properties (graph clustering coefficient, average number of coloring in the 1-dimensional Weisfeiler-Leman graph isomorphism heuristic (1-WL)~\cite{weisfeiler1968reduction}, etc.).
+This thesis will focus on seven graph parameters, with definitions provided in section~\ref{sec:practical_graph_parameters}.

### 2025-02-20 paper/chapters/conclusion.tex
Update thesis tex files to latest version

\chapter{Conclusion and future work}\label{chap:conclusions}

This thesis examines the impact of various graph parameters on the generalization error of different Graph Neural Network (GNN) architectures. I conducted extensive experiments on 49 graph classification datasets in TUDataset using four GNN models: Graph Convolutional Networks (GCN), Simplified Graph Convolution (SGC), Graph Attention Networks v2 (GATv2), and Message Passing Neural Networks (MPNN).

This work investigated the graph parameters including the average degree, the average clustering coefficient, the average shortest path length, the graph diameter, the graph density, the graph clustering coefficient, centrality measures and 1-WL color count.

Overall, this study provides valuable insights into the relationship between graph parameters and the generalization performance of GNNs. These findings can inform the selection of appropriate GNN architectures for training and evaluation, when working with graphs of varying properties.

Future work can focus on expanding the range of GNN architectures and datasets to validate the findings across a broader spectrum. Given the considerable variation in the average number of nodes and edges and other quantitative properties of the datasets used in this thesis, it is considered to generate synthetic datasets with controlled properties to further investigate the impact of graph parameters on the generalization error of GNNs.

### 2025-02-20 paper/chapters/experimentalstudy.tex
Update thesis tex files to latest version

--- 2025-01-29 paper/chapters/experimentalstudy.tex
@@
 \begin{enumerate}
-    \item Obtain the dataset using the setup outlined in Section~\ref{sec:datasets}.
-    \item Tune the hyperparameters using Bayesian optimization, as detailed in Section~\ref{sec:hyperparameters tuning}.
-    \item Train the models using the optimized hyperparameters and compute their generalization errors.
-    \item In the meanwile, calculate the graph parameters for each dataset, as detailed in Section~\ref{sec:graph parameters}.
+    \item Obtain the dataset following the setup described in Section~\ref{sec:datasets}.
+    \item Perform hyperparameter optimization using Bayesian methods, as detailed in Section~\ref{sec:hyperparameters tuning}.
+    \item Train the models with the optimized hyperparameters and evaluate their generalization errors.
+    \item Concurrently, calculate the graph parameters for each dataset, as detailed in Section~\ref{sec:practical_graph_parameters}.
     \item Finally, evaluate the impact of the graph parameters on the generalization error of the models by calculating the correlation between the graph parameters and the generalization error.
@@
 
-\subsection{Training Framework}
+\subsection{Training framework}
 The training framework is based on PyTorch Geometric~\cite{fey2019fast}.
@@
 It consists of data from different domains, including small molecules, bioinformatics, social networks and synthetic.
-Since the size of some datasets is quite small (less than 500 data points/graphs), I use 10-fold cross validation in the training process, in order to fully utilize the data.
-A dataset is split into 1:1:8, where one of the folds is treated as the test dataset and another is treated as the validation dataset.
+Since the size of some datasets is quite small (less than 500 data points/graphs), 10-fold cross-validation is implemented to maximize data utilization.
+The dataset is divided into three parts in a 1:1:8 ratio, with one portion designated as the test set, another as the validation set, and the remaining larger portion used for training.
 The remaining folds are used for training.
-The training is repeated 10 times, each time with a different test fold.
+The training is repeated 10 times, each time with a different test/val fold.
 The average of the generalization error over the 10 runs is calculated as the final generalization error of the model.
 
-For the dataset with large size, the first 4000 data points are selected.
+For the dataset with large size, the random 4000 data points are selected.
 The remaining data points are discarded.
@@
 
-I list information about the 50 datasets used in the experiment in the appendix~\ref{sec:}.
+General information of the 49 datasets utilized in the experiment are provided in Appendix~\ref{chap:basic-info}.
 
@@
 
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler.
+The hyperparameters were optimized using the Bayesian optimization method~\cite{frazier2018tutorial}, facilitated by the Weights and Biases (WandB) framework~\cite{wandb}, which enabled precise tracking of validation accuracy and corresponding hyperparameters throughout the tuning process.
+A total of 196 dataset-model pairs were evaluated, derived from the combination of four models and 49 datasets.
+For each pair, the optimization process systematically adjusted hyperparameters to maximize validation accuracy.
+
+The hyperparameters that have been tuned include the learning rate, batch size, hidden dimension, number of epochs, patience in early stopping, number of hidden layers, type of normalization, and patience of plateau scheduler.
 Additionally, for the GATv2 model, the number of heads, the dropout rate, and residual are also tuned.
-
-The hyperparameters are tuned using the Bayesian optimization method\cite{frazier2018tutorial}.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
-
-There are five models and 57 datasets, resulting in 285 pairs of dataset and model.
-For each pair, the hyperparameters are tuned using the Bayesian optimization method.
-The hyperparameters are tuned using the validation dataset.
-The validation dataset is a subset of the training dataset that is used to tune the hyperparameters of the model.
-The hyperparameters that result in the highest validation accuracy are selected as the optimal hyperparameters for the model.
+Furthermore, for the MPNN model, the number of MLP layers is tuned.
 
 \subsection{Models}\label{sec:models}
-In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
-The GCN model is shown in the appendix.
-The GCN model consists of four GCN layers, each followed by a ReLU activation function.
-The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.
+In the experiment, I used four different GNN layers in each model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks v2(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}.
 
-\subsection{Experimental details}
-The Adam optimizer~\cite{kingma2014adam} is considered to be employed in the model.
-To prevent overfitting and to optimize the use of time, the early stopping is employed.
-The loss function is defined as the cross-entropy loss function.
-The hyperparameters of the model are considered to be tuned.
-The hyperparameters include the learning rate, batch size, hidden dimension, number of epochs, and patience in early stopping.
-The generalization error is calculated as the difference between the training accuracy and the test accuracy.
-
-\section{Graph Parameters Under Investigation}\label{sec:graph parameters}
-As graph parameters defined abstractly in the section~\ref{sec:graph_parameters}, I give here the concrete definition of the graph parameters that are used in the experiment.
+\section{Graph parameters under investigation}\label{sec:practical_graph_parameters}
+As graph parameters defined abstractly in the section~\ref{sec:theoretical_graph_parameters}, I give here the concrete definition of the graph parameters that are used in the experiment.
 The graph parameters are calculated for each dataset and used as input features for the model.
@@
 
-    \item [Graph diameter] The graph diameter $d$ is the maximum of the shortest paths between all pairs of nodes in the graph, that is,
+     \item [Graph diameter] The graph diameter $\delta$ is the maximum of the shortest paths between all pairs of nodes in the graph, that is,
     $$
-d = \max_{v \in V} \max_{w \in V, w \neq v} d(v, w)
+        \delta = \max_{v \in V} \max_{w \in V, w \neq v} d(v, w)
     $$
@@
 
-    \item [Graph clustering coefficient] The graph clustering coefficient $C$ is a measure of the degree to which nodes in a graph tend to cluster together.
+    \item [Graph clustering coefficient]~\cite{luce1949method} The graph clustering coefficient $C$ is a measure of the degree to which nodes in a graph tend to cluster together.
 The clustering coefficient of a node $v$ (as known as the local clustering coefficient) is defined as the fraction of the number of triangles that include node $v$ to the maximum possible number of triples centered on node $v$.
@@
 
-    \textit{Closeness centrality} $C_C(v)$ is defined as the reciprocal of the sum of the length of the shortest paths from the node $v$ to all other nodes in the graph, that is 
+    \textit{Closeness centrality}~\cite{bavelas1950communication} $C_C(v)$ is defined as the reciprocal of the sum of the length of the shortest paths from the node $v$ to all other nodes in the graph, that is
     $$C_C(v) = \frac{1}{\sum_{w\in V}{d(v ,w)}}$$
@@
 
-    \textit{Betweenness centrality} $C_B(v)$ is the sum of the fraction of the shortest paths between all pairs of nodes that pass through node $v$, that is
+    \textit{Betweenness centrality}~\cite{freeman1977set} $C_B(v)$ is the sum of the fraction of the shortest paths between all pairs of nodes that pass through node $v$, that is
 
@@
 
-    \textit{Eigenvector centrality} is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
+    \textit{Eigenvector centrality}~\cite{bonacich1972factoring}\cite{bonacich2007some} is a measure of the influence of a node in a graph based on the concept that connections to high-scoring nodes contribute more to the score of the node in question.
 Formally, the eigenvector centrality $C_E(v)$ of a node $v$  is defined as the $v$-th component of the eigenvector corresponding to the largest eigenvalue of the adjacency matrix $A$ of the graph.
@@
     \sloppy
-    The 1-dimensional Weisfeiler-Leman algorithm (1-WL)~\cite{weisfeiler1968reduction} is an algorithm that assigns a unique label(color) to each node in the graph, also known as color refinement.
+    The 1-dimensional Weisfeiler-Leman algorithm (1-WL)~\cite{weisfeiler1968reduction} is an algorithm that assigns a unique label (color) to each node in the graph, also known as color refinement.
 The average number of coloring in the 1-WL algorithm is defined as the average number of colors used to color the nodes in the graph.
-The 1-WL algorithm is a powerful graph isomorphism algorithm that can be used to determine if two graphs are isomorphic.
-I give the procedure of the 1-WL algorithm here:
-    \begin{enumerate}
-        \item Assign the same color to all nodes in the graph.
-        \item Two nodes $v$, $u$ are assigned a different color if there is a color c such that the number of c-colored neighbors of $u$ is not equal to the number of c-colored neighbors of $v$.
-        \item Repeat step 2 until the colors of all nodes do not change.
-    \end{enumerate}
-
+The 1-WL algorithm is a powerful graph isomorphism algorithm that can be used to determine if two graphs are isomorphic for a broad class of graphs~\cite{babai1979canonical}.
 \end{description}

### 2025-02-20 paper/chapters/introduction.tex
Update thesis tex files to latest version

@@
 \chapter{Introduction}\label{chap:introduction}
-Graph learning became a hot topic in the field of machine learning in recent years.
+Graph representation learning has emerged as a prominent area within machine learning, driven by its capacity to model relationships in graph-structured data effectively.
 Graph Neural Networks (GNNs)~\cite{gori2005new}, also known as deep learning on graphs, are a class of neural networks that can operate on graph-structured data, such as social networks~\cite{easley2010networks}, biological networks~\cite{barabasi2004network}, and images~\cite{simonovsky2017dynamic}.
-GNNs use the structure of a graph to perform "message passing", allowing information to propagate across nodes and edges.
+GNNs use the structure of a graph to perform ``message passing'', allowing information to propagate across nodes and edges.
 The key idea is to iteratively aggregate and update node features by exchanging information with local neighboring nodes, which allows GNNs to capture the structural information of the graph.
 This information is then used to make predictions.
-GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{morselli2021network}, and graph classification~\cite{gilmer2017neural}.
-Popular GNNs in recent years include Graph Convolutional Networks (GCN)~\cite{kipf2016semi}, Graph Attention Networks (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Networks (MPNN)~\cite{gilmer2017neural}.
+GNNs have been demonstrated to be effective in a wide range of tasks, such as node classification~\cite{hamilton2017inductive}, edge prediction~\cite{kipf2016variational}, and graph classification~\cite{gilmer2017neural}.
+Popular GNNs in recent years include Graph Convolutional Network (GCN)~\cite{kipf2016semi}, Graph Attention Network (GAT)~\cite{velickovic2020pointer}, and Message Passing Neural Network (MPNN)~\cite{gilmer2017neural}.
 
-However, the behavior of GNNs is not well understood.
-Particularly, the relationship between graph parameters/characteristics and the empirical generalization error of GNNs is not clear.
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics impact the generalization error of GNNs.
+From the perspective of \cite{morris2024futuredirectionstheorygraph}, the behavior of GNNs remains insufficiently understood, particularly with respect to how graph parameters/characteristics influence their empirical generalization error.
+This thesis aims to address this gap by conducting an empirical investigation into the impact of graph parameters on the generalization performance of GNNs.
 
-To reach this goal, I conduct two sets of experiments.
-First, I calculate the graph parameters for a set of datasets: Each graph has its own unique properties, such as the average degree.
-In graph theory, \textit{graph parameter} is used to quantify them.
-And a dataset consists of multiple graphs, each with its graph parameter.
-In the case, I calculate the average value of our desired graph parameters over all graphs in the dataset.
-In this thesis, 50 datasets from the TUDataset~\cite{morris2020tudataset} is used for the calculation.
-Second, I train different GNN models on each dataset and find that their generalization abilities varied.
-I show that there is a certain relationship between generalization ability and different graph parameters.
+To achieve this objective, two sets of experiments were conducted:
 
-The thesis is organized as follows.
-In Chapter~\ref{chap:background}, I provide background information on graph neural networks and generalization.
-In Chapter~\ref{chap:experiments}, I describe the methodology used to conduct the experiments.
-In Chapter~\ref{chap:results}, I present the experimental results and discuss the results and their implications.
-Finally, in Chapter~\ref{chap:conclusions}, I conclude the thesis and discuss future work.
+First, graph parameters were computed for a set of 49 datasets selected from the TUDataset~\cite{morris2020tudataset} In graph theory, each graph have its own unique properties, such as the average degree.
+In graph theory, graph parameters are used to quantify them.
+A dataset consist of multiple graphs, each with its graph parameter.
+For each dataset, the average values of the specified graph parameters were calculated across all graphs.
+In this thesis, 49 datasets from the TUDataset~\cite{morris2020tudataset} were used for the calculation.
+
+Secondly, various GNN architectures were trained across multiple datasets, and it is revealed that their generalization abilities varied.
+The analysis identified a notable correlation between generalization capabilities and specific graph-theoretic parameters.
+
+The thesis is organized as follows:
+Chapter~\ref{chap:background} provides background information on graph neural networks and generalization.
+Chapter~\ref{chap:experiments} describes the methodology used to conduct the experiments.
+Chapter~\ref{chap:results} presents the experimental results and discusses the results and their implications.
+Finally, Chapter~\ref{chap:conclusions} concludes the thesis and discusses future work.
 
 \section{Related work}
-In the following section, I will discuss the related work on graph neural networks and generalization.
+The subsequent section examines related work on GNNs and a focus on their generalization capabilities.
 
 \subsection{Graph Neural Networks}
-Graph neural networks were initially proposed by Gori et al.~\cite{gori2005new} and Scarselli et al.~\cite{scarselli2008graph} as a variant of recurrent neural networks and demonstrated its generalization capabilities.
+GNNs were initially proposed by Gori et al.~\cite{gori2005new} and Scarselli et al.~\cite{scarselli2008graph} as a variant of recurrent neural networks.
+These models demonstrated its significant generalization capabilities, marking a foundational step in the development of graph-based learning frameworks.
 The work of Kipf and Welling~\cite{kipf2016semi} introduced the Graph Convolutional Networks (GCN) model, which received widespread attention from the research community.
-Velickovic et al.~\cite{velickovic2020pointer} proposed the Graph Attention Networks (GAT) model, which uses attention mechanisms to aggregate information from neighboring nodes.
-Brody et al.~\cite{brody2021attentive} proposed the GATv2 model, which improves the performance of the GAT model by introducing residual connections and multi-head attention.
-Gilmer et al.~\cite{gilmer2017neural} introduced the Message Passing Neural Networks (MPNN) model, which demonstrated the significant results on the molecular property prediction benchmark;
+Gilmer et al.~\cite{gilmer2017neural} introduced the Message Passing Neural Networks (MPNN) model, which demonstrated the significant results on the molecular property prediction benchmark.
+Velickovic et al.~\cite{velivckovic2017graph} proposed the Graph Attention Networks (GAT) model, which uses attention mechanisms to aggregate information from neighboring nodes.
+Brody et al.~\cite{brody2021attentive} proposed the GATv2 model, which outperforms the GAT model by introducing a dynamic graph attention variant.
 
 \subsection{Generalization}
-While significant progress has been made in understanding the generalization properties of feed-forward neural networks (FNNs) and recurrent neural networks (RNNs), the generalization abilities of graph neural networks (GNNs) remain less explored due to their of irregular graph structures.
+While significant progress has been made in understanding the generalization properties of Feed-forward Neural Networks (FNNs) and Recurrent Neural Networks (RNNs).
+The generalization capabilities of GNNs remain underexplored, primarily due to the challenges posed by the irregular and non-Euclidean nature of graph structures.
 
-Golowich et al.~\cite{golowich2018size} showed the generalization abilities of Feed-forward neural networks (FNNs) with Rademacher complexity.
+Golowich et al.~\cite{golowich2018size} showed the generalization abilities of FNNs with Rademacher complexity.
 The work of Zhang et al.~\cite{zhang2018stabilizing} used SVD-based parameterization to improve the generalization by effectively addressing gradient issues.
 
-In terms of Recurrent neural networks(RNNs), Chen et al.~\cite{chen2019generalization} studied the generalization properties of vanilla RNNs as well as their variants.
+In terms of RNNs, Chen et al.~\cite{chen2019generalization} studied the generalization properties of vanilla RNNs as well as their variants.
 Z.
@@
 
-But unlike the FNNs and RNNs, GNNs deal with irregular data structures.
+In contrast to the FNNs and RNNs, GNNs deal with irregular data structures.
 The related work on the generalization of GNNs is limited.
@@
 Nevertheless, Morris et al.~\cite{morris2024futuredirectionstheorygraph} pointed out that the generalization ability of GNNs is still not well understood.
-The bounds established in these studies typically rely solely on general graph parameters, such as the maximum degree or total number of nodes, often overlooking more expressive graph parameters.
+The bounds established in these studies typically rely solely on general graph parameters, such as the maximum degree or total number of nodes, while often overlooking more expressive graph parameters.

### 2025-02-20 paper/chapters/results.tex
Update thesis tex files to latest version

@@
-\chapter{Results \& Discussion}\label{chap:results}
+\chapter{Results \& discussion}\label{chap:results}
 
@@
 The experiments were conducted to evaluate the generalization performance of four GNN architectures on 49 graph classification datasets.
-The four neural network architectures described in Chapter \ref{chap:experiments}.
+The four neural network architectures are described in Chapter \ref{chap:experiments}.
 The datasets using for training and testing are described in Section \ref{sec:datasets}.
@@
 
-Note that, the correlation analysis for each architecture is presented with two scatter plots.
-One contains all datasets, and the other contains only datasets with more than 1000 graphs.
-The reason for this separation is that the datasets with fewer graphs tend to have higher variability in generalization error, which can lead to misleading correlations.
+It should be noted that the correlation analysis for each architecture is presented with two scatter plots.
+The first contains all datasets, while the second contains only datasets with more than 1000 graphs.
+The reason for filtering the datasets in this way is that the datasets with fewer graphs tend to have higher variance in generalization error, which may lead to misleading correlations.
 
@@
 
-The graph parameters calculated in the experiments are shown in Table \ref{tab:gp1}~\ref{tab:gp2}.
-
-TODO: some datasets have 0 as the result, need to mention that
+The graph parameters calculated in the experiments are shown in the Chapter~\ref{chap:graph-parameters}.
 
@@
         YeastH & 0.0001875102461781 & 0.0135009009391069 \\ 
+    \bottomrule
     \end{tabular}
@@
 The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_GCN} and Figure~\ref{fig:correlation_ignore_less_than_1000_GCN}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{images/correlation_GCN.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Convolutional Networks (GCNs).
-Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
-Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
-    \label{fig:correlation_GCN}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_GCN.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Convolutional Networks (GCNs).
-Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
-Only datasets with more than 1000 graphs are considered.
-There are 40 datasets in this plot and another 19 datasets are not included.}
-    \label{fig:correlation_ignore_less_than_1000_GCN}
-\end{figure}
 
@@
 
-\subsubsection{Correlation Analysis}
+\subsubsection{Correlation analysis}
 
-\paragraph{Negative Correlations with Graph Diameter and Shortest Path}
+\paragraph{Negative correlations with graph diameter and shortest path}
 The results indicate a moderate negative correlation between generalization error and both graph diameter (-0.21) and average shortest path (-0.27) in the full dataset analysis~\ref{fig:correlation_GCN}.
@@
 
-\paragraph{Influence of Graph Density and Clustering Coefficient}
+\paragraph{Influence of graph density and clustering coefficient}
 The correlation with graph density is relatively weak (0.09 in the full dataset~\ref{fig:correlation_GCN}, 0.27 in the filtered dataset~\ref{fig:correlation_ignore_less_than_1000_GCN}), but the clustering coefficient shows a higher correlation of 0.29 in the full dataset, which drops to 0.04 in the filtered dataset.
@@
 
-\paragraph{Centrality Measures}
+\paragraph{Centrality measures}
 Closeness centrality shows a consistent positive correlation with generalization error (0.15 in the full dataset, 0.35 in the filtered dataset).
@@
 
-\paragraph{1-WL Color Count}
+\paragraph{1-WL color count}
 The correlation with 1-WL color count is relatively weak (0.09 and 0.03 in full and filtered datasets, respectively).
@@
 % -------------------------------------------------------------------------------------------------
+
+\newpage
 
@@
         YeastH & 0.0021875023376196 & 0.0149637833237648 \\
+    \bottomrule
     \end{tabular}
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{images/correlation_SGC.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
-Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
-Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
-    \label{fig:correlation_SGC}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_SGC.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
-Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
-Only datasets with more than 1000 graphs are considered.
-There are 40 datasets in this plot and another 19 datasets are not included.}
-    \label{fig:correlation_ignore_less_than_1000_SGC}
-\end{figure}
-
 \subsection{Discussion}
@@
 
-\subsubsection{Correlation Analysis}
+\subsubsection{Correlation analysis}
 
-\paragraph{Graph Average Degree}
+\paragraph{Graph average degree}
 The average degree shows a weak positive correlation with generalization error in the full dataset (0.13), which increases substantially to a strong correlation (0.56) when only datasets with more than 1000 graphs are considered.
@@
 
-\paragraph{Graph Diameter and Shortest Path}
+\paragraph{Graph diameter and shortest path}
 Both graph diameter (-0.31) and average shortest path (-0.34) exhibit moderate negative correlations with generalization error in the full dataset, indicating that datasets with more compact graph structures (smaller diameters and shorter path lengths) tend to generalize better.
@@
 
-\paragraph{Graph Density and Clustering Coefficient}
+\paragraph{Graph density and clustering coefficient}
 The clustering coefficient shows a moderate positive correlation with generalization error in both datasets (0.26 in the full dataset and 0.44 in the filtered dataset).
@@
 
-\paragraph{Centrality Measures}
+\paragraph{Centrality measures}
 Among the centrality measures, betweenness centrality exhibits negative correlations with generalization error (-0.22 in the full dataset and -0.36 in the filtered dataset).
@@
 
-\paragraph{1-WL Color Count}
+\paragraph{1-WL color count}
 The 1-WL color count demonstrates a weak positive correlation with generalization error in the full dataset (0.20), which becomes substantially stronger in the filtered dataset (0.58).
@@
     Yeast & 0.0016562461387366 & 0.0281631872057914 \\ 
+    \bottomrule
     \end{tabular}
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{images/correlation_GATv2.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Attention Networks v2 (GATv2).
-Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
-Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
-    \label{fig:correlation_GATv2}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_GATv2.png}
-    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Attention Networks v2 (GATv2).
-Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
-Only datasets with more than 1000 graphs are considered.
-There are 40 datasets in this plot and another 19 datasets are not included.}
-    \label{fig:correlation_ignore_less_than_1000_GATv2}
-\end{figure}
-
 \subsection{Discussion}
@@
 
-\subsubsection{Correlation Analysis}
+\subsubsection{Correlation analysis}
 
-\paragraph{Average Degree}
+\paragraph{Average degree}
 A weak positive correlation of 0.12 between average degree and generalization error is observed in the full dataset analysis (\ref{fig:correlation_GATv2}).
@@
 
-\paragraph{Shortest Path and Graph Diameter}
+\paragraph{Shortest path and graph diameter}
 In the full dataset, a negative correlation is noted between generalization error and both shortest path (-0.22) and graph diameter (-0.16), indicating that smaller and more compact graphs are associated with better generalization.
@@
 
-\paragraph{Graph Density and Clustering Coefficient}
+\paragraph{Graph density and clustering coefficient}
 Graph density shows a very weak correlation in the full dataset (0.07) and remains weak in larger datasets (0.09).
@@
 
-\paragraph{Centrality Measures}
+\paragraph{Centrality measures}
 Betweenness centrality exhibits a moderate negative correlation (-0.29) in the full dataset and has similar correlation in the filtered dataset (-0.31).
@@
 
-\paragraph{1-WL Color Count}
+\paragraph{1-WL color count}
 The 1-WL color count demonstrates moderate positive correlation in the full dataset (0.26), but this correlation increases significantly in larger datasets (0.59).
@@
 \section{Message Passing Neural Networks}~\label{sec:result_mpnn}
+The calculated generalization error of the experiments using Message Passing Neural Networks are shown in Table~\ref{tab:ge_mpnn}.
+
+\begin{table}[!ht]
+    \centering
+    \footnotesize
+    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
+    \hline
+    \toprule
+        Name & Ave. generalization error & Standard deviation \\ 
+    \midrule
+    AIDS & 0.0091874841600656 & 0.0070713576860725 \\ 
+    BZR\_MD & 0.1059349551796913 & 0.141946479678154 \\ 
+    BZR & 0.063807688653469 & 0.0739696696400642 \\ 
+    COLORS-3 & 0.076031245291233 & 0.0253504272550344 \\ 
+    COX2\_MD & 0.1141152158379554 & 0.0899139121174812 \\ 
+    COX2 & 0.0715246349573135 & 0.0796237140893936 \\ 
+    DD & 0.0929188206791877 & 0.0893803909420967 \\ 
+    DHFR\_MD & 0.0675946250557899 & 0.1037261709570884 \\ 
+    DHFR & 0.1216765642166137 & 0.063124693930149 \\ 
+    ENZYMES & 0.1668750047683715 & 0.1106084510684013 \\ 
+    ER\_MD & 0.0358938574790954 & 0.0568079650402069 \\ 
+    FRANKENSTEIN & 0.0718437507748603 & 0.0375203862786293 \\ 
+    KKI & 0.1231343299150466 & 0.2515161037445068 \\ 
+    MCF-7H & 0.0091874776408076 & 0.0150008797645568 \\ 
+    MCF-7 & 0.0080625060945749 & 0.0152003578841686 \\ 
+    MOLT-4H & -0.0004062592925038 & 0.0148166185244917 \\ 
+    MOLT-4 & 0.0010624944698065 & 0.0125815030187368 \\ 
+    MUTAG & 0.0487573221325874 & 0.0706913545727729 \\ 
+    Mutagenicity & 0.0664687603712081 & 0.0282005369663238 \\ 
+    NCI-H23H & 0.0011562525760382 & 0.0115329325199127 \\ 
+    NCI-H23 & 0.0021250187419354 & 0.0086612496525049 \\ 
+    NCI109 & 0.0788125097751617 & 0.0241683777421712 \\ 
+    NCI1 & 0.0700937509536743 & 0.0207409560680389 \\ 
+    OHSU & 0.1410989016294479 & 0.2492884248495102 \\ 
+    OVCAR-8H & 0.0036250054836273 & 0.0197824537754058 \\ 
+    OVCAR-8 & 0.0032187581527978 & 0.0174466092139482 \\ 
+    P388H & 0.0135312620550394 & 0.0137673774734139 \\ 
+    P388 & 0.0091250063851475 & 0.0158420968800783 \\ 
+    PC-3H & 0.0118124904111027 & 0.0230077672749757 \\ 
+    PC-3 & 0.0024374960921704 & 0.0094347447156906 \\ 
+    PROTEINS\_full & 0.0246215872466564 & 0.0341414250433445 \\ 
+    PTC\_FM & 0.0814946442842483 & 0.1237905248999595 \\ 
+    PTC\_FR & 0.0976715683937072 & 0.104591965675354 \\ 
+    PTC\_MM & 0.1219191774725914 & 0.0936376005411148 \\ 
+    PTC\_MR & 0.085997425019741 & 0.1167371049523353 \\ 
+    Peking\_1 & 0.1918478459119796 & 0.1804585009813308 \\ 
+    SF-295H & 0.0026875077746808 & 0.0119734490290284 \\ 
+    SF-295 & 0.0074062468484044 & 0.0222921669483184 \\ 
+    SN12CH & 0.0016874969005584 & 0.0161193944513797 \\ 
+    SN12C & -0.0001249790220754 & 0.0123165436089038 \\ 
+    SW-620H & 0.0044999956153333 & 0.0196564402431249 \\ 
+    SW-620 & 0.0040312530472874 & 0.0153152821585536 \\ 
+    SYNTHETIC & 0.0133333448320627 & 0.0172132737934589 \\ 
+    SYNTHETICnew & 0.1375000178813934 & 0.0440958477556705 \\ 
+    Synthie & 0.0699999928474426 & 0.0399163626134395 \\ 
+    UACC257H & 0.0002187550126109 & 0.0126776117831468 \\ 
+    UACC257 & -5.9604645663569045e-09 & 0.0111375767737627 \\ 
+    YeastH & 0.0019687532912939 & 0.0153990918770432 \\ 
+    Yeast & 0.0017500042449682 & 0.0269955322146415 \\ 
+    \bottomrule
+    \end{tabular}
+    \caption{Generalization error of the MPNN model on 49 datasets}
+    \label{tab:ge_mpnn} % ge -> generalization error
+\end{table}
+
+The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_MPNN} and Figure~\ref{fig:correlation_ignore_less_than_1000_MPNN}.
+
+\subsection{Discussion}
+
+The experimental results illustrated in Figures \ref{fig:correlation_MPNN} and \ref{fig:correlation_ignore_less_than_1000_MPNN} explore the relationship between various graph structural parameters and the average generalization error across datasets of varied sizes.
+The analysis distinguishes between the full dataset (including datasets with fewer than 1000 graphs) and the filtered dataset (only datasets with more than 1000 graphs) to minimize the impact of high variability in smaller datasets.
+The key findings are detailed below.
+
+\subsubsection{Correlation analysis}
+
+\paragraph{Average degree}
+In the full dataset, the average degree exhibits a moderate positive correlation (0.25) with generalization error, indicating a trend where higher average connectivity lowers generalization.
+However, this relationship strengthens significantly in larger datasets (correlation of 0.51), suggesting that average degree plays a more pronounced role in influencing generalization in datasets with robust sample sizes.
+
+\paragraph{Shortest path and graph diameter}
+The shortest path and graph diameter both exhibit moderate negative correlations (-0.36 and -0.32, respectively) with generalization error in the full dataset.
+This result suggests that more compact graph structures are generally favorable for generalization.
+However, these relationships weaken substantially in the filtered dataset, with correlations of -0.09 and -0.04, respectively.
+This divergence highlights the potential influence of noise in smaller datasets, reducing the reliability of these correlations when analyzing subsets of smaller sample sizes.
+
+\paragraph{Graph density and clustering coefficient}
+Graph density demonstrates a mild positive correlation (0.24) in the full dataset but substantially weakens (0.19) in the filtered dataset.
+Conversely, the clustering coefficient stands out with a more substantial positive correlation (0.41) in the full dataset, which remains consistent (0.43) in the filtered dataset.
+These findings underscore the significant impact of the clustering coefficient on generalization.
+It suggests the local grouping properties of a graph play a larger role in influencing model behavior across datasets of various sizes.
+
+\paragraph{Centrality measures}
+Betweenness centrality shows a consistent negative correlation (-0.29 in the full dataset and -0.32 in the filtered dataset).
+Conversely, closeness centrality exhibits a weak but positive correlation (0.29 in the full dataset and 0.25 in the filtered dataset), suggesting mild relevance to generalization.
+Finally, eigenvector centrality has minimal impact, with very weak correlations (0.06 in the full dataset and -0.05 in the filtered dataset), implying it is a less influential factor for generalization performance.
+
+\paragraph{1-WL color count}
+The 1-WL color count displays a moderate positive correlation (0.17) with generalization error in the full dataset, which grows stronger (0.49) in the filtered dataset.
+This clear trend across larger datasets emphasizes the influence of graph structure expressiveness as captured by the 1-WL test, suggesting that more diverse graph features challenge generalization potential.
+
+\subsubsection{Summary}
+The results highlight notable variations in the influence of graph parameters across full and filtered datasets.
+Average degree and the clustering coefficient emerge as consistently impactful structural features, with relatively stronger correlations observed in larger datasets.
+In contrast, parameters such as shortest path and graph diameter exhibit diminishing correlations in filtered datasets, likely due to noise in smaller samples.
+Notably, 1-WL color count reinforces the significance of graph expressiveness in generalization.
+
+\newpage
+
+\section{Limitations}~\label{sec:limitations}
+
+\paragraph{Time-consuming hyperparameter tuning}
+To conduct the experiments, I used a high-performance computing cluster with a NVIDIA A10 for the GCN, SGC, and GATv2 models, and a NVIDIA L40S for the MPNN model (due to its high memory requirements).
+While the computational resources were sufficient, the primary bottleneck arose from the lengthy hyperparameter tuning process.
+For each model, optimizing hyperparameters across all 49 datasets required approximately 2-3 weeks.
+This time-consuming process limited the scalability of the study to a larger number of models and datasets.
+
+\paragraph{Noise in smaller datasets}
+Some datesets have a small number of graphs, which introduce noise and reduce the reliability of the correlation analysis.
+To address this issue, I have filtered out datasets with fewer than 1000 graphs in the correlation analysis.
+However, this approach may have overlooked datasets with potentially valuable insights.
+
+\paragraph{High concentration of generalization error values}
+The generalization error values for all models are highly concentrated, with approximately half falling within a 2\% range.
+Specifically, 26 out of 49 values for the GCN model, 25 out of 49 for the SGC model, 25 out of 49 for the GATv2 model, and 24 out of 49 for the MPNN model exhibit this level of concentration.
+This may be the result that there is no significantly strong correlation between the graph parameters and the generalization error for the models and datasets used in this study.
+
+\paragraph{Limited model selection}
+The study focuses on four popular graph neural network models (GCN, SGC, GATv2, and MPNN) and may not capture the full spectrum of graph neural network architectures.
+The results may not be generalizable to other models, and further research is needed to explore the relationship between graph parameters and generalization error across a broader range of models.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_GCN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Convolutional Networks (GCNs).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), green (1000-4000 graphs), and red (>4000 graphs).}
+    \label{fig:correlation_GCN}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_GCN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Convolutional Networks (GCNs).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 30 datasets in this plot and another 19 datasets are not included.}
+    \label{fig:correlation_ignore_less_than_1000_GCN}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_SGC.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), green (1000-4000 graphs), and red (>4000 graphs).}
+    \label{fig:correlation_SGC}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_SGC.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model.
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 30 datasets in this plot and another 19 datasets are not included.}
+    \label{fig:correlation_ignore_less_than_1000_SGC}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_GATv2.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Attention Networks v2 (GATv2).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), green (1000-4000 graphs), and red (>4000 graphs).}
+    \label{fig:correlation_GATv2}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_GATv2.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Graph Attention Networks v2 (GATv2).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 30 datasets in this plot and another 19 datasets are not included.}
+    \label{fig:correlation_ignore_less_than_1000_GATv2}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_MPNN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Message Passing Neural Networks (MPNN).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Colors indicate dataset sizes: blue (<1000 graphs), green (1000-4000 graphs), and red (>4000 graphs).}
+    \label{fig:correlation_MPNN}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{images/correlation_ignore_less_than_1000_MPNN.png}
+    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of Message Passing Neural Networks (MPNN).
+Each subplot presents the correlation coefficient between a specific graph parameter and the generalization error.
+Only datasets with more than 1000 graphs are considered.
+There are 30 datasets in this plot and another 19 datasets are not included.}
+    \label{fig:correlation_ignore_less_than_1000_MPNN}
+\end{figure}

### 2025-02-20 paper/includes/abstract.tex
Update thesis tex files to latest version

@@
 \chapter*{Abstract}
-The goal of this bachelor thesis is to understand empirically how graph parameters/characteristics influence the generalization error of Graph Neural Networks (GNNs).
+
+This thesis investigates the impact of various graph parameters on the generalization error of different Graph Neural Network (GNN) architectures.
+Extensive experiments were conducted on 49 graph classification datasets from TUDataset using four GNN models: Graph Convolutional Networks (GCN), Simplified Graph Convolution (SGC), Graph Attention Networks v2 (GATv2), and Message Passing Neural Networks (MPNN).
+The study examines graph parameters such as average degree, average clustering coefficient, average shortest path length, graph diameter, graph density, centrality measures, and 1-WL color count.
+The findings provide valuable insights into the relationship between graph parameters and the generalization performance of GNNs, informing the selection of appropriate GNN architectures for various graph parameters.
+Future work will focus on expanding the range of GNN architectures and datasets, as well as generating synthetic datasets with controlled properties to further investigate the impact of graph parameters on GNN generalization.
